% AUTOGENERATED
\xdtbeforeclasses
\begin{longtabu} to \textwidth { l | X }
\hiderowcolors \multicolumn{2}{l}{\xdtClasses} \tabularnewline \midrule \showrowcolors
Actor & Base class used by drones for sight, movement etc. \\
Inventory & Basic Inventory system for actors and structures. Just contains a dictionary of resource type and amount at present. \\
World\-Info & This class is used to store the locaiton of all the player marines, drones and resources
 inn the game world. \\
Factor & A Factor is some quantifiable element that affects the average utility of an Action. \\
Timeout\-Authenticator & An authenticator that disconnects connections if they don't
     authenticate within a specified time limit. \\
Network\-Animator & A component to synchronize Mecanim animation states for networked objects. \\
Network\-Lobby\-Manager & This is a specialized Network\-Manager that includes a networked lobby. \\
Network\-Lobby\-Player & This component works in conjunction with the Network\-Lobby\-Manager to make up the multiplayer lobby system.
     The Lobby\-Prefab object of the Network\-Lobby\-Manager must have this component on it. This component holds basic lobby player data required for the lobby to function. Game specific data for lobby players can be put in other components on the Lobby\-Prefab or in scripts derived from Network\-Lobby\-Player. \\
Network\-Proximity\-Checker & Component that controls visibility of networked objects for players.
     Any object with this component on it will not be visible to players more than a (configurable) distance away. \\
Network\-Proximity\-Checker & Enumeration of methods to use to check proximity. \\
Network\-Room\-Manager & This is a specialized Network\-Manager that includes a networked room. \\
Network\-Room\-Player & This component works in conjunction with the Network\-Room\-Manager to make up the multiplayer room system.
     The Room\-Prefab object of the Network\-Room\-Manager must have this component on it. This component holds basic room player data required for the room to function. Game specific data for room players can be put in other components on the Room\-Prefab or in scripts derived from Network\-Room\-Player. \\
Network\-Scene\-Checker & Component that controls visibility of networked objects between scenes.
     Any object with this component on it will only be visible to other objects in the same scene
     This would be used when the server has multiple additive subscenes loaded to isolate players to their respective subscenes \\
Network\-Transform\-Child & A component to synchronize the position of child transforms of networked objects.
     There must be a Network\-Transform on the root object of the hierarchy. There can be multiple Network\-Transform\-Child components on an object. This does not use physics for synchronization, it simply synchronizes the local\-Position and local\-Rotation of the child transform and lerps towards the recieved values. \\
Client\-Scene & A client manager which contains static client information and functions.
     This manager contains references to tracked static local objects such as spawner registrations. It also has the default message handlers used by clients when they registered none themselves. The manager handles adding/removing player objects to the game after a client connection has been set as ready.
     The Client\-Scene is a singleton, and it has static convenience methods such as Client\-Scene.Ready().
     The Client\-Scene is used by the Network\-Manager, but it can be used by itself.
     As the Client\-Scene manages player objects on the client, it is where clients request to add players. The Network\-Manager does this via the Client\-Scene automatically when auto-add-players is set, but it can be done through code using the function Client\-Scene.Add\-Player(). This sends an Add\-Player message to the server and will cause a player object to be created for this client.
     Like Network\-Server, the Client\-Scene understands the concept of the local client. The function Client\-Scene.Connect\-Local\-Server() is used to become a host by starting a local client (when a server is already running). \\
Sync\-Var\-Attribute & Sync\-Vars are used to synchronize a variable from the server to all clients automatically.
     Value must be changed on server, not directly by clients.  Hook parameter allows you to define a client-side method to be invoked when the client gets an update from the server. \\
Command\-Attribute & Call this from a client to run this function on the server.
     Make sure to validate input etc. It's not possible to call this from a server. \\
Client\-Rpc\-Attribute & The server uses a Remote Procedure Call (RPC) to run this function on clients. \\
Target\-Rpc\-Attribute & The server uses a Remote Procedure Call (RPC) to run this function on a specific client. \\
Sync\-Event\-Attribute & Sync\-Events are networked events like Client\-Rpc's, but instead of calling a function on the game object, they trigger Events instead. \\
Server\-Attribute & Prevents clients from running this method.
     Prints a warning if a client tries to execute this method. \\
Server\-Callback\-Attribute & Prevents clients from running this method.
     No warning is thrown. \\
Client\-Attribute & Prevents the server from running this method.
     Prints a warning if the server tries to execute this method. \\
Client\-Callback\-Attribute & Prevents the server from running this method.
     No warning is printed. \\
Scene\-Attribute & Converts a string property into a Scene property in the inspector \\
Unity\-Event\-Network\-Connection & Unity Event for the Network\-Connection \\
Network\-Authenticator & Base class for implementing component-based authentication during the Connect phase \\
Network\-Behaviour & Base class which should be inherited by scripts which contain networking functionality. \\
Network\-Behaviour & Delegate for Command functions. \\
Network\-Client & This is a network client class used by the networking system. It contains a Network\-Connection that is used to connect to a network server.
     The Network\-Client handle connection state, messages handlers, and connection configuration. There can be many Network\-Client instances in a process at a time, but only one that is connected to a game server (Network\-Server) that uses spawned objects.
     Network\-Client has an internal update function where it handles events from the transport layer. This includes asynchronous connect events, disconnect events and incoming data from a server.
     The Network\-Manager has a Network\-Client instance that it uses for games that it starts, but the Network\-Client may be used by itself. \\
Network\-Connection & A High level network connection. This is used for connections from client-to-server and for connection from server-to-client. \\
Network\-Diagnostics & Provides profiling information from mirror
     A profiler can subscribe to these events and
     present the data in a friendly way to the user \\
Message\-Info & Describes an outgoing message \\
Network\-Diagnostics & Event that gets raised when Mirror sends a message
         Subscribe to this if you want to diagnose the network \\
Network\-Diagnostics & Event that gets raised when Mirror receives a message
         Subscribe to this if you want to profile the network \\
Network\-Identity & The Network\-Identity identifies objects across the network, between server and clients. Its primary data is a Network\-Instance\-Id which is allocated by the server and then set on clients. This is used in network communications to be able to lookup game objects on different machines. \\
Network\-Identity & The delegate type for the client\-Authority\-Callback. \\
Network\-Manager\-HUD & An extension for the Network\-Manager that displays a default HUD for controlling the network state of the game.
     This component also shows useful internal state for the networking system in the inspector window of the editor. It allows users to view connections, networked objects, message handlers, and packet statistics. This information can be helpful when debugging networked games. \\
Network\-Server & The Network\-Server. \\
Network\-Start\-Position & This component is used to make a game\-Object a starting position for spawning player objects in multiplayer games.
     This object's transform will be automatically registered and unregistered with the Network\-Manager as a starting position. \\
Network\-Time & Synchronize time between the server and the clients \\
Argument &  \\
Constant &  \\
Expression &  \\
Function &  \\
Function\-Parameter &  \\
Iterative\-Operator\-Parameters &  \\
Argument\-Parameter &  \\
Token\-Stack\-Element &  \\
Kw\-Str\-Comparator &  \\
Desc\-Kw\-Len\-Comparator &  \\
Kw\-Type\-Comparator &  \\
Token\-Modification &  \\
m\-Xparser &  \\
Primitive\-Element &  \\
Recursive\-Argument &  \\
Tutorial &  \\
Inheritance & Handles inheritance between Tyd\-Nodes via handle and source attributes.
    
     To use Inheritance:
     1. Call Initialize().
     2. Register all the nodes you want to interact with each other.
     3. Call Resolve\-All(). This will modify the registered nodes in-place with any inheritance data, and then resets.
    
     Only use Reset() to recover from errors. \\
Tyd\-File & Represents a file of Tyd data.
     To read a file: Use From\-File to create a Tyd\-File from a file on disk, and then read the data you want from the Tyd\-File.
     To write to a file: Build your Tyd\-Document, create a Tyd\-File from it, then write the Tyd\-File to disk. \\
Tyd\-Xml & Utility methods for converting from XML to Ty\-D.
 To load XML this way, it must be formatted a specific way. \\
Enterable\-Building & A building that actors can enter. \\
Command & A container for a method that can be done or undone at will. \\
Command\-Manager & Manages the undo/redo stack for undoing and redoing commands. \\
Debug\-Console\-Entry & And entry in the in-game Debug\-Console. \\
Drone & Drones are used by the enemy AI/CI to interact in the world \\
Resource & Abstract class for all gatherable resources to derive from. \\
Resource\-Healthbar & Manages health bar component of Resources \\
RTSLua\-Manager & Handles Lua stuff. \\
Setup & Sets up the game so it works. \\
Event\-Manager & The actual channel being listened to \\
Room\-Player &  \\
RTSNetwork\-Room\-Manager & This is a specialized Network\-Manager that includes a networked room.
     The room has slots that track the joined players, and a maximum player count that is enforced.
     It requires that the Network\-Room\-Player component be on the room player objects.
     Network\-Room\-Manager is derived from Network\-Manager, and so it implements many of the virtual functions provided by the Network\-Manager class. \\
Walking & By attaching the Walkingscript to a Game\-Object it can move in the gameworld
 towards a target position or waypoints.  Remember to add a Nav\-Mesh\-Agent to the gameobject this script is 
 attached to. \\
Laser\-Weapon & Range weapon that can be attached to actors, giving them the ability to shoot. \\
Factory & Factory component that lets the object it's attached to build drones \\
Draggable\-UIElement & Makes it possible to drag a UI element around. \\
Resizable\-UIElement & Lets a UI element be resized by dragging its edges. \\
Assigned\-Drone\-Percentage & Factor for amount of drones assigned to a certain task, set at factor creaton \\
Drone\-Number & Factor for amount of drones. Currently just takes the totalt amount of drones, TODO expand to work with other drone types. \\
Need\-Defense\-Group & A factor for checking if the CI needs another defensive group \\
Need\-Fighter\-Group & A factor for checking if the CI needs another group of fighters \\
Need\-Mixed\-Group & A factor for checking if the CI needs another mixed group \\
Need\-Scout\-Group & A factor for checking if the CI needs another scout group \\
Need\-Worker\-Group & A factor for checking if the CI needs another group of workers \\
Resource\-Amount & Factor for the amount of a resource currently held. \\
Bbbt\-Behaviour\-Tree & A Bbbt\-Behaviour\-Tree scriptable object that can be loaded into and edited in the bb\-BT editor window. \\
Bbbt\-Behaviour\-Tree\-Component & Mono\-Behaviour component for using bb\-BT behaviour trees with Game\-Objects. \\
Bbbt\-Behaviour\-Tree\-Editor\-Save\-Data & Contains data needed to save and load a bb\-BT behaviour tree. \\
Bbbt\-Behaviour\-Tree\-Save\-Data & Data needed to serialise and deserialise a behaviour tree. \\
Bbbt\-Connection\-Save\-Data & Contains data needed to save and load a bb\-BT behaviour tree connection. \\
Bbbt\-Node\-Save\-Data & Contains data needed to save and load a bb\-BT behaviour tree node. \\
Bbbt\-Constants & Contains bb\-BT constants. \\
DOTween\-Module\-Unity\-Version & Shortcuts/functions that are not strictly related to specific Modules
     but are available only on some Unity versions \\
DOTween\-Module\-Utils & Utility functions that deal with available Modules.
     Modules defines:
     - DOTAUDIO
     - DOTPHYSICS
     - DOTPHYSICS2D
     - DOTSPRITE
     - DOTUI
     Extra defines set and used for implementation of external assets:
     - DOTWEEN\_TMP  Text\-Mesh Pro
     - DOTWEEN\_TK2D  2D Toolkit \\
Network\-Discovery\-Base & Base implementation for Network Discovery.  Extend this component
     to provide custom discovery with game specific data
      for a sample implementation \\
Moon\-Sharp\-Vs\-Code\-Debug\-Server & Class implementing a debugger allowing attaching from a Visual Studio Code debugging session. \\
Linq\-Helpers & LINQ helper methods \\
Namespace\-Doc & Namespace containing all the most commonly used classes for Moon\-Sharp operation.
	 When in doubt, refer to  and  classes as starting points. \\
Namespace\-Doc & Namespace containing the implementation of the Lua standard library, as Moon\-Sharp modules.
	 There's seldom the need to access these classes directly. \\
Namespace\-Doc & Namespace containing userdata classes for the 'io' module \\
Namespace\-Doc & Namespace containing classes used to support debuggers \\
Namespace\-Doc & Namespace containing classes used to support self diagnostics (e.g. performance counters) \\
Namespace\-Doc & Namespace containing classes used to customize and support advanced interoperations between
	 scripts and CLR code. \\
Namespace\-Doc & Namespace containing classes used to provide a minimal support for porting code based on the classic
	 "Lua\-State" model (e.g. code based on Kopi\-Lua, Uni\-Lua or Lua itself). \\
Namespace\-Doc & Namespace containing classes used to customized how scripts are loaded from external files. \\
Namespace\-Doc & Namespace containing classes used to customize how the interfacing with the operative system happens
	 for the 'os' and 'io' modules, and for future modules/classes which may require OS access.
	 See  and  . \\
Namespace\-Doc & Contains classes useful to implement REPL interpreters.
	 See : \\
Script & This class implements a Moon\-Sharp scripting session. Multiple Script objects can coexist in the same program but cannot share
	 data among themselves unless some mechanism is put in place. \\
Script\-Global\-Options & Class containing script global options, that is options which cannot be customized per-script. \\
Script\-Options & This class contains options to customize behaviour of Script objects. \\
Astronomical\-Constants &  \\
Binary\-Relations &  \\
Boolean\-Algebra &  \\
Calculus &  \\
Coefficients &  \\
Evaluate &  \\
Math\-Constants &  \\
Math\-Functions &  \\
Number\-Theory &  \\
Physical\-Constants &  \\
Primes\-Cache &  \\
Probability\-Distributions &  \\
Special\-Functions &  \\
Special\-Value &  \\
Special\-Value\-Trigonometric &  \\
Statistics &  \\
Units &  \\
Binary\-Relation &  \\
Bitwise\-Operator &  \\
Boolean\-Operator &  \\
Calculus\-Operator &  \\
Constant\-Value &  \\
Function1Arg &  \\
Function2Arg &  \\
Function3Arg &  \\
Function\-Variadic &  \\
Key\-Word &  \\
Operator &  \\
Parser\-Symbol &  \\
Random\-Variable &  \\
Token &  \\
Unit &  \\
Performance\-Tests &  \\
Performance\-Test\-Result &  \\
Test\-Thread &  \\
Test\-Simple\-Calc\-Thread &  \\
Test011Thread &  \\
Test012Thread &  \\
Test013Thread &  \\
Test014Thread &  \\
Test015Thread &  \\
Test016Thread &  \\
Test017Thread &  \\
Test018Thread &  \\
Test019Thread &  \\
Test020Thread &  \\
Reg\-Test\-Expression &  \\
Reg\-Test\-Expression\-API &  \\
Reg\-Test\-Syntax &  \\
Fun\-Ext &  \\
Fun\-Ext\-Var &  \\
Pi\-Mult\-Arg\-Ext &  \\
Run\-Test &  \\
Parse\-Exception &  \\
Simple\-Char\-Stream &  \\
Token &  \\
Tyd\-Collection & A Tyd\-Node that contains a collection of sub-nodes. \\
Tyd\-Document & Represents an entire Tyd document. \\
Tyd\-List & Contains an ordered collection of anonymous Tyd\-Nodes. \\
Tyd\-Node & Root class of all Tyd nodes. \\
Tyd\-String & Represents a record of a single string. Also used to represent records with null values. \\
Tyd\-Table & Contains an ordered collection of named Tyd\-Nodes. \\
BBInput & A very basic input wrapper that allows for event-driven input
 with the ability to prioritise listeners and which gives listeners the ability to eat input.
 Usage: Call Load\-Profiles(), then Initialize(). \\
BBInput\-Axis & Represents an axis that can be bound in the BBInput system.
 Analogous to Unity' Input axes. \\
BBInput\-Axis\-Display & Displays BBInput\-Axis debug info. \\
BBInput\-Binding\-Display & Displays one of a BBInput\-Axis's bindings' debug info. \\
BBInput\-Debugger & Displays BBInput debug info. \\
BBInput\-Key\-Display & Displays a BBInput binding key's name and state in the debug window. \\
BBInput\-Profile & Contains a set of input axes which work together.
 Used to exclude certain actions from being performed depending on context. \\
BBInput\-Profile\-Display & Displays BBInput\-Profile debug info. \\
BBInput\-Updater & Updates BBInput profiles and axes and triggers events. \\
pb\_Missing\-Script\-Editor &  \\
pb\_Scene\-Post\-Processor &  \\
Pro\-Grids\-No\-Snap\-Attribute &  \\
Pro\-Grids\-Conditional\-Snap\-Attribute &  \\
pg\_Toggle\-Content &  \\
Player\-Pointer\-Event\-Data & Each touch event creates one of these containing all the relevant information. \\
CIBuild\-Drone & Central intelligence behavior node for gathering crystal \\
CIGather\-Crystal & Central intelligence behavior node for gathering crystal \\
CIGather\-Metal & Central intelligence behavior node for gathering metal \\
CIGather\-Resource & Behavior for gathering various resourcers. NOTE: Init MUST be run to select resource type, or this will not work properly. \\
CIWants\-Worker\-Group & Central intelligence behavior node for the desire to have a worker group \\
Camera\-Follow & Camera mode for following a target. \\
Camera\-Normal & Camera mode used for moving the camera according to input. \\
Camera\-Transit & The camera mode for moving to a Game\-Object. \\
WFX\_Bullet\-Hole\-Decal &  \\
WFX\_Light\-Flicker &  \\
Bbbt\-Behaviour\-Tree\-Caller\-Behaviour\-Editor & Custom editor for Bbbt\-Behaviour\-Tree\-Caller\-Behaviours \\
Bbbt\-Behaviour\-Tree\-Component\-Editor & Custom editor for Bbbt\-Behaviour\-Tree\-Components \\
Bbbt\-Connection & Represents the connection between two Bbbt\-Nodes. \\
Bbbt\-Connection\-Point & A point on a Bbbt\-Node which can be used to connect it to another node. \\
Bbbt\-Connection\-Preview & Used for previewing a connection that is currently being created. \\
Bbbt\-Node & A node for use in the bb\-BT behaviour tree editor. \\
Bbbt\-Node\-Editor & Custom editor for editing individual behaviour tree nodes. \\
Bbbt\-Prompt & A pop-up window with some text where you have to push a button to get rid of it.
     Usa \\
Bbbt\-Prompt\-Option & A Bbbt\-Prompt\-Option is one of the buttons that the user can click when faced with a prompt in the bb\-BT editor. \\
Bbbt\-Window & The container window for the Benjamin Bergseth Behaviour Tree editor.
     (I might want to work on that name.) \\
Bbbt\-Window\-Tab & A single tab to be displayed in the Bbbt\-Window. \\
Bbbt\-Behaviour & A behaviour to be attached to a Bbbt\-Node. \\
Bbbt\-Composite\-Behaviour & A behaviour which can have multiple children. \\
Bbbt\-Decorator\-Behaviour & A decorator is a behaviour which has a single child. \\
Bbbt\-Leaf\-Behaviour & A leaf behaviour has no children and is responsible for the behaviour tree actually doing something.
     Examples of a lead node could be capable of are shooting enemies, gathering resources, or even calling
     another behaviour tree. \\
Bbbt\-Flank\-Target\-Behind &  \\
Bbbt\-Flank\-Target\-Behind & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Flank\-Target\-Frontal &  \\
Bbbt\-Flank\-Target\-Frontal & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Flank\-Target\-Left &  \\
Bbbt\-Flank\-Target\-Left & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Flank\-Target\-Right &  \\
Bbbt\-Flank\-Target\-Right & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Got\-Flanking\-Behind\-Message &  \\
Bbbt\-Got\-Flanking\-Behind\-Message & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Got\-Flanking\-Frontal\-Message &  \\
Bbbt\-Got\-Flanking\-Frontal\-Message & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Got\-Flanking\-Left\-Message &  \\
Bbbt\-Got\-Flanking\-Left\-Message & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Got\-Flanking\-Right\-Message &  \\
Bbbt\-Got\-Flanking\-Right\-Message & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Got\-Frontal\-Assault\-Message &  \\
Bbbt\-Got\-Frontal\-Assault\-Message & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Group\-All\-Drones\-Attack &  \\
Bbbt\-Group\-All\-Drones\-Attack & Leaf node for commanding all drones in a group to attack their targets. \\
Bbbt\-Group\-All\-Drones\-Flank\-Enemy & Decorator node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Group\-Got\-Attack\-Message\-From\-CI &  \\
Bbbt\-Group\-Got\-Attack\-Message\-From\-CI & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Group\-Got\-Flanking\-Message\-From\-CI &  \\
Bbbt\-Group\-Got\-Flanking\-Message\-From\-CI & Leaf node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Group\-Have\-Adequate\-Forces & Attacks the actors current target using the actors attack method. \\
Bbbt\-Have\-Two\-Or\-More\-Groups & Decorator node for checking if there's enough forces to risk attacking an enemy \\
Bbbt\-Root & Marks the entry point of a behaviour tree. Inherits from Bbbt\-Behaviour for convenience but isn't actually
     included in a behaviour tree, and is used in the editor to point to the real root node. \\
Bbbt\-Wait\-Behaviour & Behaviour which just makes an actor do nothing for x seconds. \\
Bbbt\-Inverter & Inverters the result of the child node \\
Bbbt\-Repeater & Repeats a child node for a set amount of times \\
Bbbt\-Repeat\-Until\-Fail & Repeats the child nodes untills it returns Bbbt\-Behaviour\-Status.Failure \\
Bbbt\-Behaviour\-Save\-Data & Abstract class for storing Bbbt\-Behaviour save data. \\
Bbbt\-Behaviour\-Tree\-Caller\-Behaviour\-Save\-Data & Contains serializable save data for Bbbt\-Behaviour\-Tree\-Caller\-Behaviour. \\
Bbbt\-Debug\-Log\-Behaviour\-Save\-Data & Contains serializable save data for Bbbt\-Debug\-Log\-Behaviour. \\
Bbbt\-Root\-Save\-Data & Contains serializable save data for Bbbt\-Root. \\
Bbbt\-Selector\-Save\-Data & Contains serializable save data for Bbbt\-Selector \\
Bbbt\-Sequencer\-Save\-Data & Contains serializable save data for Bbbt\-Sequencer \\
Basic\-Module & Class implementing basic Lua functions (print, type, tostring, etc) as a Moon\-Sharp module. \\
Bit32Module & Class implementing bit32 Lua functions \\
Coroutine\-Module & Class implementing coroutine Lua functions \\
Debug\-Module & Class implementing debug Lua functions. Support for the debug module is partial. \\
Dynamic\-Module & Class implementing dynamic expression evaluations at runtime (a Moon\-Sharp addition). \\
Error\-Handling\-Module & Class implementing error handling Lua functions (pcall and xpcall) \\
Io\-Module & Class implementing io Lua functions. Proper support requires a compatible IPlatform\-Accessor \\
Load\-Module & Class implementing loading Lua functions like 'require', 'load', etc. \\
Math\-Module & Class implementing math Lua functions \\
Meta\-Table\-Module & Class implementing metatable related Lua functions (xxxmetatable and rawxxx). \\
Os\-System\-Module & Class implementing system related Lua functions from the 'os' module.
	 Proper support requires a compatible IPlatform\-Accessor \\
Os\-Time\-Module & Class implementing time related Lua functions from the 'os' module. \\
String\-Module & Class implementing string Lua functions \\
Table\-Iterators\-Module & Class implementing table Lua iterators (pairs, ipairs, next) \\
Table\-Module & Class implementing table Lua functions \\
Table\-Module\_Globals & Class exposing table.unpack and table.pack in the global namespace (to work around the most common Lua 5.1 compatibility issue). \\
Extension\_Methods & Extension methods used in the whole project. \\
Fast\-Stack & A preallocated, non-resizable, stack \\
Fast\-Stack\-Dynamic & A non preallocated, non\_fixed size stack \\
Linked\-List\-Index & An index to accelerate operations on a Linked\-List using a single key of type 
	 More than one Linked\-List\-Index can index the same linked list, but every node in the linked list must be indexed by one and only one
	 Linked\-List\-Index object. \\
Multi\-Dictionary & A Dictionary where multiple values can be associated to the same key \\
Reference\-Equality\-Comparer & Implementation of IEquality\-Comparer enforcing reference equality \\
Slice & Provides facility to create a "sliced" view over an existing IList \\
Slice & Gets or sets the element at the specified index. \\
Callback\-Arguments & This class is a container for arguments received by a Callback\-Function \\
Callback\-Arguments & Gets the  at the specified index, or Void if not found \\
Callback\-Function & This class wraps a CLR function \\
Closure & A class representing a script function \\
Closure & Type of closure based on upvalues \\
Closure & The closure has no upvalues (thus, technically, it's a function and not a closure!) \\
Closure & The closure has \_ENV as its only upvalue \\
Closure & The closure is a "real" closure, with multiple upvalues \\
Coroutine & A class representing a script coroutine \\
Coroutine & Possible types of coroutine \\
Coroutine & A valid coroutine \\
Coroutine & A CLR callback assigned to a coroutine. \\
Coroutine & A CLR callback assigned to a coroutine and already executed. \\
Lua\-Type\-Extensions & Extension methods to Data\-Type \\
Dyn\-Value & A class representing a value in a Lua/Moon\-Sharp script. \\
Ref\-Id\-Object & A base class for many Moon\-Sharp objects. 
	 Helds a Reference\-ID property which gets a different value for every object instance, for debugging
	 purposes. Note that the ID is not assigned in a thread safe manner for speed reason, so the IDs
	 are guaranteed to be unique only if everything is running on one thread at a time. \\
Symbol\-Ref & This class stores a possible l-value (that is a potential target of an assignment) \\
Table & A class representing a Lua table. \\
Table & Gets or sets the 
		  with the specified key(s).
		 This will marshall CLR and Moon\-Sharp objects in the best possible way.
		 Multiple keys can be used to access subtables. \\
Table & Gets or sets the  with the specified key(s).
		 This will marshall CLR and Moon\-Sharp objects in the best possible way. \\
Table\-Pair & A class representing a key/value pair for Table use \\
Tail\-Call\-Data & Class used to support "tail" continuations - a way for C\# / Lua interaction which supports 
	 coroutine yielding (at the expense of a LOT of added complexity in calling code). \\
User\-Data & Class exposing C\# objects as Lua userdata.
	 For efficiency, a global registry of types is maintained, instead of a per-script one. \\
Well\-Known\-Symbols & Constants of well known "symbols" in the Moon\-Sharp grammar \\
Yield\-Request & Class wrapping a request to yield a coroutine \\
Debugger\-Action & Wrapper for a debugger initiated action \\
Debugger\-Action & Type of the action \\
Debugger\-Action & Step-in at the bytecode level \\
Debugger\-Action & Step-over at the bytecode level \\
Debugger\-Action & Step-out at the bytecode level \\
Debugger\-Action & Step-in at the source level \\
Debugger\-Action & Step-over at the source level \\
Debugger\-Action & Step-out at the source level \\
Debugger\-Action & Continue execution "freely" \\
Debugger\-Action & Toggles breakpoint \\
Debugger\-Action & Sets a breakpoint \\
Debugger\-Action & Clears a breakpoint \\
Debugger\-Action & Reset all breakpoints \\
Debugger\-Action & Refresh the data \\
Debugger\-Action & Hard refresh of data \\
Debugger\-Action & No action \\
Debug\-Service & Class providing services specific to debugger implementations. \\
Source\-Code & Class representing the source code of a given script \\
Source\-Ref & Class representing a reference to source code interval \\
Watch\-Item & A watch item for the debugger to consume.
	 Most properties make or not sense depending on the Watch\-Type. \\
Performance\-Result & The result of a performance counter \\
Performance\-Statistics & A single object of this type exists for every script and gives access to performance statistics. \\
Dynamic\-Expression\-Exception & Exception thrown when a dynamic expression is invalid \\
Internal\-Error\-Exception & Exception thrown when an inconsistent state is reached in the interpreter \\
Interpreter\-Exception & Base type of all exceptions thrown in Moon\-Sharp \\
Script\-Runtime\-Exception & Exception for all runtime errors. In addition to constructors, it offers a lot of static methods
	 generating more "standard" Lua errors. \\
Syntax\-Error\-Exception & Exception for all parsing/lexing errors. \\
Dynamic\-Expression & Represents a dynamic expression in the script \\
Script\-Execution\-Context & Class giving access to details of the environment where the script is executing \\
Custom\-Converters\-Collection & A collection of custom converters between Moon\-Sharp types and CLR types.
	 If a converter function is not specified or returns null, the standard conversion path applies. \\
Descriptor\-Helpers & Helper extension methods used to simplify some parts of userdata descriptor implementations \\
Interop\-Registration\-Policy & Collection of the standard policies to handle User\-Data type registrations.
	 Provided mostly for compile-time backward compatibility with old code.
	 See also :  . \\
Property\-Table\-Assigner & Utility class which may be used to set properties on an object of type T, from values contained in a Lua table.
	 Properties must be decorated with the .
	 This is a generic version of . \\
Property\-Table\-Assigner & Utility class which may be used to set properties on an object from values contained in a Lua table.
	 Properties must be decorated with the .
	 See  for a generic compile time type-safe version. \\
Reflection\-Special\-Name & Class helping identifying special names found with reflection \\
Bin\-Dump\-Binary\-Reader & "Optimized" Binary\-Reader which shares strings and use a dumb compression for integers \\
Bin\-Dump\-Binary\-Writer & "Optimized" Binary\-Writer which shares strings and use a dumb compression for integers \\
Undisposable\-Stream & An adapter over Stream which bypasses the Dispose and Close methods.
	 Used to work around the pesky wrappers .NET has over Stream (Binary\-Reader, Stream\-Writer, etc.) which think they
	 own the Stream and close them when they shouldn't. Damn. \\
Embedded\-Resources\-Script\-Loader & A script loader loading scripts from an assembly resources \\
File\-System\-Script\-Loader & A script loader loading scripts directly from the file system (does not go through platform object) \\
Invalid\-Script\-Loader & A script loader used for platforms we cannot initialize in any better way.. \\
Script\-Loader\-Base & A base implementation of IScript\-Loader, offering resolution of module names. \\
Streaming\-Assets\-Script\-Loader & A script loader loading scripts from /Streaming\-Assets/Lua/. When loading files the subpath of the aforementioned
	 folder should be used. \\
Unity\-Assets\-Script\-Loader & A script loader which can load scripts from assets in Unity3D.
	 Scripts should be saved as .txt files in a subdirectory of Assets/Resources.
	 
	 When Moon\-Sharp is activated on Unity3D and the default script loader is used,
	 scripts should be saved as .txt files in Assets/Resources/Moon\-Sharp/Scripts. \\
Module\-Register & Class managing modules (mostly as extension methods) \\
Moon\-Sharp\-Module\-Attribute & Marks a CLR type to be a Moon\-Sharp module.
	 Modules are the fastest way to bring interop between scripts and CLR code, albeit at the cost of a very increased
	 complexity in writing them. Modules is what's used for the standard library, for maximum efficiency.
	 
	 Modules are basically classes containing only static methods, with the callback function signature.
	 
	 See  and  for (extension) methods used to register modules to a 
	 table.
	 
	 See  for information regarding the standard callback signature along with easier ways
	 to marshal methods.
	 
	 See  for easier object marshalling. \\
Moon\-Sharp\-Module\-Constant\-Attribute & In a module type, mark fields with this attribute to have them exposed as a module constant.
	 
	 See  for more information about modules. \\
Moon\-Sharp\-Module\-Method\-Attribute & In a module type, mark methods or fields with this attribute to have them exposed as module functions.
	 Methods must have the signature "public static Dyn\-Value ...(Script\-Execution\-Context\-Callback\-Arguments)".
	 Fields must be static or const strings, with an anonymous Lua function inside.
	 
	 See  for more information about modules. \\
Limited\-Platform\-Accessor & A class implementing all the bits needed to have a minimal support of a platform.
	 This does not support the 'io'/'file' modules and has partial support of the 'os' module. \\
Platform\-Accessor\-Base & An abstract class which offers basic services on top of IPlatform\-Accessor to provide easier implementation of platforms. \\
Platform\-Auto\-Detector & A static class offering properties for autodetection of system/platform details \\
Standard\-Platform\-Accessor & Class providing the IPlatform\-Accessor interface for standard full-feaured implementations. \\
Repl\-History\-Interpreter & An implementation of  which supports a very basic history of recent input lines. \\
Repl\-Interpreter & This class provides a simple REPL intepreter ready to be reused in a simple way. \\
Repl\-Interpreter\-Script\-Loader & A script loader loading scripts directly from the file system (does not go through platform object)
	 AND starts with module paths taken from environment variables (again, not going through the platform object).
	 
	 The paths are preconstructed using :
			* The MOONSHARP\_PATH environment variable if it exists
			* The LUA\_PATH\_5\_2 environment variable if MOONSHARP\_PATH does not exists
			* The LUA\_PATH environment variable if LUA\_PATH\_5\_2 and MOONSHARP\_PATH do not exists
			* The "?;?.lua" path if all the above fail
			
	 Also, everytime a module is require(d), the "LUA\_PATH" global variable is checked. If it exists, those paths
	 will be used to load the module instead of the global ones. \\
Serialization\-Extensions &  \\
Module & Contains module data. \\
Debug\-Console & Displays messages from Debug\-Logger. \\
Debug\-Console\-Entry & And entry in the in-game Debug\-Console. \\
Debug\-Console\-Suggestions\-Panel & Panel which shows suggestions when something is typed into the console input field. \\
Json\-Menu\-Item & Adds a "Create\-{\tt >}Json" option the the Assets menu. \\
Lua\-Menu\-Item & Adds a "Create\-{\tt >}Lua Script" option the the Assets menu. \\
Txt\-Menu\-Item & Adds a "Create\-{\tt >}txt" option the the Assets menu. \\
Tyd\-Menu\-Item & Adds a "Create\-{\tt >}Ty\-D" option the the Assets menu. \\
Xml\-Menu\-Item & Adds a "Create\-{\tt >}Xml" option the the Assets menu. \\
Lua\-Manager & Handles Lua stuff. \\
Lua\-Object\-Component & A component which runs Unity methods from Lua. \\
Moon\-Sharp\-Alias\-Attribute & Marks a class with a Moon\-Sharp.Interpreter.Moon\-Sharp\-User\-Data\-Attribute as going by another name. \\
Yeeter\-Script\-Loader & Script Loader for Dungeon\-Yeeter. \\
Draggable\-UIElement & Makes it possible to drag a UI element around. \\
Resizable\-UIElement & Lets a UI element be resized by dragging its edges. \\
pb\_About\-Window\-Setup &  \\
pb\_About\-Window\-Setup &  \\
pb\_About\-Window &  \\
pb\_Update\-Check &  \\
pb\_About\-Entry &  \\
pb\_Version\-Util &  \\
Highlight\-Nearest\-Face &  \\
pg\_About\-Window\-Setup &  \\
pg\_About\-Window\-Setup &  \\
Advertisement\-Thumb &  \\
Player\-Pointer\-Event\-Handler\-Example & Example handler of Player Pointer Events. \\
UIPointer & A simple pointer for Unity UI. \\
Canvas\-Scaler\-Ext & This class exists only for the purpose of being able to force a refresh on the canvas scaler to prevent drawing artifacts when changing the scale on Awake/Enable \\
Canvas\-Scaler\-Fitter & Adjusts the scale based on the current screen aspect ratio to try to fit the content sensibly.
     Uses break points to determine current scale settings. \\
Control\-Mapper & Event sent when the UI is closed.
         This is a .NET event. If you are using Unity Events,
         use the on\-Screen\-Closed event. \\
Control\-Mapper & Event sent when the UI is opened.
         This is a .NET event. If you are using Unity Events,
         use the on\-Screen\-Opened event. \\
Control\-Mapper & Event sent when a popup window is closed.
         This is a .NET event. If you are using Unity Events,
         use the on\-Popup\-Window\-Closed event. \\
Control\-Mapper & Event sent when a popup window is opened.
         This is a .NET event. If you are using Unity Events,
         use the on\-Popup\-Window\-Opened event. \\
Control\-Mapper & Event sent when polling for input has started.
         This is a .NET event. If you are using Unity Events,
         use the on\-Input\-Polling\-Started event. \\
Control\-Mapper & Event sent when polling for input has ended.
         This is a .NET event. If you are using Unity Events,
         use the on\-Input\-Polling\-Stopped event. \\
Control\-Mapper & Unity event sent when the UI is closed.
         This is a Unity event. For the .NET event,
         use Screen\-Closed\-Event. \\
Control\-Mapper & Unity event sent when the UI is opened.
         This is a Unity event. For the .NET event,
         use Screen\-Opened\-Event. \\
Control\-Mapper & Unity event sent when a popup window is closed.
         This is a Unity event. For the .NET event,
         use Popup\-Window\-Closed\-Event. \\
Control\-Mapper & Unity event sent when a popup window is opened.
         This is a Unity event. For the .NET event,
         use Popup\-Window\-Opened\-Event. \\
Control\-Mapper & Unity event sent when polling for input has started.
         This is a Unity event. For the .NET event,
         use Input\-Polling\-Started\-Event. \\
Control\-Mapper & Unity event sent when polling for input has ended.
         This is a Unity event. For the .NET event,
         use Input\-Polling\-Ended\-Event. \\
Custom\-Button & Overrides auto-navigation in Selectable because it's inadequate for selectables inside a scroll rect
     Also enables selection of disabled controls for better navigation experience. \\
Custom\-Slider & Overrides auto-navigation in Selectable because it's inadequate for selectables inside a scroll rect
     Also enables selection of disabled controls for better navigation experience. \\
Custom\-Toggle & Overrides auto-navigation in Selectable because it's inadequate for selectables inside a scroll rect
     Also enables selection of disabled controls for better navigation experience. \\
Scrollbar\-Visibility\-Helper & Hides Scroll\-Rect scrollbars based on the dimensions of the content.
     This must be placed on the Scroll\-Rect.content Game\-Object.
     This component is no longer necessary in Unity 5.2+ because Scroll\-Rect now handles Scroll\-Bar visibility. \\
Gamepad\-Template & Class representing a Gamepad Template.
     This class contains constants. Do not use this class to interact with the Rewired API. 
     Use the interface  instead. \\
Racing\-Wheel\-Template & Class representing a Racing Wheel Template.
     This class contains constants. Do not use this class to interact with the Rewired API. 
     Use the interface  instead. \\
HOTASTemplate & Class representing a HOTAS Template.
     This class contains constants. Do not use this class to interact with the Rewired API. 
     Use the interface  instead. \\
Flight\-Yoke\-Template & Class representing a Flight Yoke Template.
     This class contains constants. Do not use this class to interact with the Rewired API. 
     Use the interface  instead. \\
Flight\-Pedals\-Template & Class representing a Flight Pedals Template.
     This class contains constants. Do not use this class to interact with the Rewired API. 
     Use the interface  instead. \\
Six\-Dof\-Controller\-Template & Class representing a 6 Do\-F Controller Template.
     This class contains constants. Do not use this class to interact with the Rewired API. 
     Use the interface  instead. \\
Controller\-Template\-Factory & Factory class for creating Controller Templates.
     This is for internal use only. \\
User\-Data\-Store\_Player\-Prefs & Class for saving data to Player\-Prefs. Add this as a component to your Rewired Input Manager to save and load data automatically to Player\-Prefs.
     Copy this class and customize it to your needs to create a new custom data storage system. \\
External\-Tools &  \\
FPSCounter & Add this class to a game\-Object with a Text component and it'll feed it the number of FPS in real time. \\
WFX\_Demo &  \\
WFX\_Demo\_Wall &  \\
Remove\-Connection\-Command & Command which removes a connection in the bb\-BT editor. \\
Create\-Node\-Command & Command which creates a node in the bb\-BT editor. \\
Last\-Reset\-Command & An empty command used to mark the last reset in the command history browser. \\
Move\-Node\-Command & Command which moves a node in the bb\-BT editor. \\
Create\-Connection\-Command & Command which creates a connection in the bb\-BT editor. \\
Remove\-Node\-Command & Command which removes a node in the bb\-BT editor. \\
Bbbt\-Command\-History\-Browser & Displays the currently open tab's command history. \\
Bbbt\-Help\-Menu & Help menu/manual displayed in the Bbbt\-Side\-Panel. \\
Bbbt\-Help\-Section & A section of the Bbbt\-Help\-Menu. \\
Bbbt\-Side\-Panel & The side panel shown on the left side of the bb\-BT editor window. \\
Bbbt\-Side\-Panel\-Content & Content that goes into the Bbbt\-Side\-Panel. \\
Bbbt\-Tab\-Command\-History & Lets the user browse the commands they have performed in the editor. \\
Bbbt\-Tree\-Validation\-Panel & Side panel content used for validating the structure of the behaviour tree. \\
Bbbt\-Selector & Behaviour which selects the leftmost valid child for execution. \\
Bbbt\-Sequencer & Runs through its child behaviours sequentially. \\
Bbbt\-All\-Enemies\-In\-Sight & This behavior fills up the Actor class visible\-Enmies List variable with enemies the actor can see. \\
Bbbt\-Attack\-Target & Attacks the actors current target using the actors attack method. \\
Bbbt\-Behaviour\-Tree\-Caller\-Behaviour & Leaf node which calls another behaviour tree. \\
Bbbt\-Debug\-Log\-Behaviour & Leaf node which prints a message to the Unity console. \\
Bbbt\-Enter\-Building\-Behaviour & Leaf node which causes an actor to enter the nearest building. \\
Bbbt\-Leave\-Building\-Behaviour & Leaf node which causes an actor to enter the nearest building. \\
Bbbt\-Lua\-Behaviour & Loads a behaviour from Lua. \\
Bbbt\-Move\-In\-Range\-Of\-Resource\-Behaviour & Checks if the target is within attack distance of the actor \\
Bbbt\-Move\-In\-Range\-Of\-Target\-Behaviour & Checks if the target is within attack distance of the actor \\
Bbbt\-Move\-To\-CIBehaviour & Move near the CI \\
Bbbt\-Target\-Nearest & This class targets the closest enemy of the actor \\
Bbbt\-Attack\-Distance\-Check & Checks if the target is within attack distance of the actor \\
Bbbt\-Can\-See\-Enemy\-Check & Leaf node determines if the actor can see an enemy. \\
Bbbt\-Inventory\-Empty\-Check & Leaf node that checks if Inventory component is empty \\
Bbbt\-Inventory\-Full\-Check & Leaf node that checks if Inventory component is full \\
Bbbt\-Is\-In\-Building\-Check & Leaf node which checks if an actor is in a building or not. \\
Buffer\-Pool & This buffer pool is instance thread safe
     Use Get\-Buffer to get a Memory\-Stream (with a publically accessible buffer)
     Calling Close on this Memory\-Stream will clear its internal buffer and return the buffer to the pool for reuse
     Memory\-Streams can grow larger than the DEFAULT\_BUFFER\_SIZE (or whatever you passed in)
     and the underlying buffers will be returned to the pool at their larger sizes \\
Public\-Buffer\-Memory\-Stream & This memory stream is not instance thread safe (not to be confused with the Buffer\-Pool which is instance thread safe) \\
Ping\-Pong\-Manager & Ping Pong Manager used to facilitate ping pong Web\-Socket messages \\
Ping\-Pong\-Manager & Raised when a Pong frame is received \\
Pong\-Event\-Args & Pong Event\-Args \\
Web\-Socket\-Client\-Factory & Web socket client factory used to open web socket client connections \\
Web\-Socket\-Client\-Options & Client Web\-Socket init options \\
Web\-Socket\-Http\-Context & The Web\-Socket HTTP Context used to initiate a Web\-Socket handshake \\
Web\-Socket\-Server\-Factory & Web socket server factory used to open web socket server connections \\
Web\-Socket\-Server\-Options & Server Web\-Socket init options \\
File\-User\-Data & Abstract class implementing a file Lua userdata. Methods are meant to be called by Lua code. \\
File\-User\-Data\-Base & Abstract class implementing a file Lua userdata. Methods are meant to be called by Lua code. \\
Standard\-IOFile\-User\-Data\-Base & Abstract class implementing an unclosable file Lua userdata. Methods are meant to be called by Lua code. \\
Stream\-File\-User\-Data\-Base & Abstract class implementing a file Lua userdata. Methods are meant to be called by Lua code. \\
Global\-Performance\-Stopwatch & This class is not *really* IDisposable.. it's just use to have a RAII like pattern.
	 You are free to reuse this instance after calling Dispose. \\
Performance\-Stopwatch & This class is not *really* IDisposable.. it's just use to have a RAII like pattern.
	 You are free to reuse this instance after calling Dispose. \\
Closure\-Context & The scope of a closure (container of upvalues) \\
Moon\-Sharp\-Hidden\-Attribute & Forces a class member visibility to scripts. Can be used to hide public members. Equivalent to Moon\-Sharp\-Visible(false). \\
Moon\-Sharp\-Hide\-Member\-Attribute & Lists a userdata member not to be exposed to scripts referencing it by name. \\
Moon\-Sharp\-Property\-Attribute & Marks a property as a configruation property \\
Moon\-Sharp\-User\-Data\-Attribute & Marks a type of automatic registration as userdata (which happens only if User\-Data.Register\-Assembly is called). \\
Moon\-Sharp\-User\-Data\-Metamethod\-Attribute & Marks a method as the handler of metamethods of a userdata type \\
Moon\-Sharp\-Visible\-Attribute & Forces a class member visibility to scripts. Can be used to hide public members or to expose non-public ones. \\
Dispatching\-User\-Data\-Descriptor & An abstract user data descriptor which accepts members described by  objects and
	 correctly dispatches to them.
	 Metamethods are also by default dispatched to operator overloads and other similar methods - see
	  . \\
Member\-Descriptor & Extension methods for  and  . \\
Parameter\-Descriptor & Descriptor of parameters used in  implementations. \\
Numeric\-Conversions & Static functions to handle conversions of numeric types \\
Lua\-Base & Classes using the classic interface should inherit from this class.
	 This class defines only static methods and is really meant to be used only
	 from C\# and not other .NET languages. 
	 
	 For easier operation they should also define:
			using ptrdiff\_t = System.Int32;
			using lua\_Integer = System.Int32;
			using LUA\_INTFRM\_T = System.Int64;
			using UNSIGNED\_LUA\_INTFRM\_T = System.UInt64; \\
Lua\-State &  \\
Anon\-Wrapper & Internal type used by  for registration \\
Anon\-Wrapper & Wrapper which allows for easier management of userdata without registering a new userdata type - useful 
	 if a type which is not exposed to scripts but can be managed as a "black box" by scripts is desired. \\
Enumerable\-Wrapper & Wrappers for enumerables as return types \\
Delegate\-Proxy\-Factory & Implementation of IProxy\-Factory taking two delegates for simple instancing of proxies. \\
Automatic\-Registration\-Policy & Similar to , but with automatic type registration is disabled. \\
Default\-Registration\-Policy & The default registration policy used by Moon\-Sharp unless explicitely replaced.
	 Deregistrations are allowed, but registration of a new descriptor are not allowed
	 if a descriptor is already registered for that type.
	 
	 Automatic type registration is disabled. \\
Permanent\-Registration\-Policy & A registration policy which makes registration permanent and not deletable.
	 Deregistrations are not allowed and registrations of a new descriptor are not allowed
	 if a descriptor is already registered for that type. \\
Auto\-Describing\-User\-Data\-Descriptor & Descriptor which acts as a non-containing adapter from IUser\-Data\-Type to IUser\-Data\-Descriptor \\
Composite\-User\-Data\-Descriptor & A user data descriptor which aggregates multiple descriptors and tries dispatching members
	 on them, in order.
	 
	 Used, for example, for objects implementing multiple interfaces but for which no descriptor is 
	 specifically registered. \\
Proxy\-User\-Data\-Descriptor & Data descriptor used for proxy objects \\
Standard\-Enum\-User\-Data\-Descriptor & Standard descriptor for Enum values \\
Standard\-Generics\-User\-Data\-Descriptor & Standard user data descriptor used to instantiate generics. \\
Standard\-User\-Data\-Descriptor & Standard descriptor for userdata types. \\
Extension\-Methods\-Registry & Registry of all extension methods. Use User\-Data statics to access these. \\
Type\-Descriptor\-Registry & Registry of all type descriptors. Use User\-Data statics to access these. \\
Json\-Null & User\-Data representing a null value in a table converted from Json \\
Json\-Table\-Converter & Class performing conversions between Tables and Json.
	 NOTE : the conversions are done respecting json syntax but using Lua constructs. This means mostly that:
	 1) Lua string escapes can be accepted while they are not technically valid JSON, and viceversa
	 2) Null values are represented using a static userdata of type Json\-Null
	 3) Do not use it when input cannot be entirely trusted \\
Binary\-Operator\-Expression &  \\
Focus\-Grabber & Focus\-Grabber contains one checkbox - Is\-Active and maintains it so there is only one Focus\-Grabber that is active at any given time.
     If you check this box - it will be unchecked on any other Focus\-Grabbers.
     You can use this component to control groups of Fire\-Controls and Move\-Controls.
     One game unit could require many components that react on user input so with Focus\-Grabber you can control them all at once. \\
Move\-Control1 & These classes encapsulate logic to control Move\-En. You can define speed, height, jump parameters, camera, and other.
     
     This, Move\-Control1, is the first one and only supposed to be used in the editor only. \\
Move\-Control2 & These classes encapsulate logic to control Move\-En. You can define speed, height, jump parameters, camera, and other.
    
     This, Move\-Control2, places a camera in top-down view. \\
Move\-Control3 & These classes encapsulate logic to control Move\-En. You can define speed, height, jump parameters, camera, and other.
     
     This, Move\-Control3, not controls the camera. It is supposed to be used by Moveen\-Npc1 class only. \\
Move\-Control5 & These classes encapsulate logic to control Move\-En. You can define speed, height, jump parameters, camera, and other.
     
     This, Move\-Control5, places the camera in "from behind" position. \\
Moveen\-Bridle1 &  \\
Moveen\-Mix &  \\
Moveen\-Ragdoll1 & A simple switch to ragdoll. Turns on and turns off what is needed - stepper, copiers, etc, and switches Rigidbody's is\-Kinematic. Its editor contains buttons for ragdoll generation and manual (editor only) ragdoll switch. \\
Moveen\-Ragdoll2 & Switch one limb to the ragdoll state AND detach it from the skeleton. \\
Moveen\-Ragdoll3 & Switch one limb to the ragdoll state AND possibly turn it on back. \\
Moveen\-Surface\-Detector1 &  \\
Moveen\-Surface\-Detector2 & Implements surface detection for the Moveen\-Stepper5. Must be located on the same Game\-Object.
     You can implement your own version with more simple or more complex detection which can utilize specifics of your game.
     For example, it can be 2D or utilize some sort of grid search. \\
Step2Event & This component executes Startables when the leg steps on the ground. It can be used to generate different effects on this event (dust, sound, etc) \\
pb\_Export\-Obj &  \\
pb\_Make\-Mesh\-Asset &  \\
pb\_Pro\-Builderize &  \\
pb\_Bridge\-Edges &  \\
pb\_Conform\-Normals &  \\
pb\_Connect\-Edges &  \\
pb\_Detach\-Delete\-Face &  \\
pb\_Extrude\-Element &  \\
pb\_Flip\-Edge &  \\
pb\_Flip\-Normals &  \\
pb\_Freeze\-Transform &  \\
pb\_Merge\-Faces &  \\
pb\_Set\-Pivot &  \\
pb\_Triangulate &  \\
pb\_Vertex\-Merge\-Weld &  \\
pb\_Force\-Scene\-Refresh &  \\
pb\_Rebuild\-Meshes &  \\
pb\_Rebuild\-Shared\-Indices &  \\
pb\_Remove\-Degenerate\-Tris &  \\
pb\_Repair\-Colors &  \\
pb\_Repair\-Mesh\-References &  \\
pb\_Repair\-UV &  \\
pb\_Reset\-Entity\-Materials &  \\
pb\_Upgrade\-Basic\-To\-Advanced &  \\
pb\_Edge\-Selection &  \\
pb\_Expand\-Selection &  \\
pb\_Invert\-Selection &  \\
pb\_Material\-Selection &  \\
pb\_Material\-Selection\-Shortcut &  \\
pb\_Pro\-Builder\-Menu\-Items &  \\
Generic\-Priority\-Queue & A copy of Stable\-Priority\-Queue which also has generic priority-type \\
Simple\-Priority\-Queue & A simplified priority queue implementation.  Is stable, auto-resizes, and thread-safe, at the cost of being slightly slower than
     Fast\-Priority\-Queue
     Methods tagged as O(1) or O(log n) are assuming there are no duplicates.  Duplicates may increase the algorithmic complexity. \\
Simple\-Priority\-Queue & A simplified priority queue implementation.  Is stable, auto-resizes, and thread-safe, at the cost of being slightly slower than
     Fast\-Priority\-Queue
     This class is kept here for backwards compatibility.  It's recommended you use Simple\-Priority\-Queue\&lt;TItem, TPriority\&gt; \\
Events & Use the Guid to locate this Event\-Source in Perf\-View using the Additional Providers box (without wildcard characters) \\
Web\-Socket\-Frame\-Reader & Reads a Web\-Socket frame
     see http://tools.ietf.org/html/rfc6455 for specification \\
Web\-Socket\-Implementation & Main implementation of the Web\-Socket abstract class \\
Array\-Member\-Descriptor & Member descriptor for indexer of array types \\
Dyn\-Value\-Member\-Descriptor & Class providing a simple descriptor for constant Dyn\-Values in userdata \\
Function\-Member\-Descriptor\-Base & Class providing easier marshalling of CLR functions \\
Object\-Callback\-Member\-Descriptor & Member descriptor which allows to define new members which behave similarly to class instance members \\
Event\-Member\-Descriptor & Class providing easier marshalling of CLR events. Handling is limited to a narrow range of handler signatures, which,
	 however, covers in practice most of all available events. \\
Field\-Member\-Descriptor & Class providing easier marshalling of CLR fields \\
Method\-Member\-Descriptor & Class providing easier marshalling of CLR functions \\
Overloaded\-Method\-Member\-Descriptor & Class providing easier marshalling of overloaded CLR functions \\
Overloadable\-Member\-Descriptor\-Comparer & Comparer class for IOverloadable\-Member\-Descriptor \\
Property\-Member\-Descriptor & Class providing easier marshalling of CLR properties \\
Value\-Type\-Default\-Ctor\-Member\-Descriptor & Member descriptor for the default constructor of value types. \\
Dir\-Control &  \\
Everything\-Starter & Starts all Startable. Very handy to start different effects by event without scripting. For example - when step or fire is made. \\
Fire\-Control2 & Listens to the player's action (Fire1, Fire2, etc) and starts Startables.
     Startables can be all of the sorts: sound starters, Particle\-Systems (even though they are not Startable), recoils, hit scanners, etc. \\
Global\-Motor & This component applies acceleration to the Rigidbody in order to reach target pos/rot. It contains its own speed representation so can be used without Rigidbody too. \\
Hit\-Calculator1 & Example class that shows how to easily implement gunshot logic. \\
Hitscanner & Determines target on the sight. Gun barrel is considered looking at (1, 0, 0) (i.e. right) \\
Hitscanner\-Mouse & Determines target on the sight from camera, through mouse. \\
Local\-Motor & This component tries to reach target pos/rot in local space. It can be useful for local, physics-independent animation - barrel recoil, revolver, etc.
     TODO implement rotation \\
Recoil\-Global\-Motor\-Starter & Used to just increase current speed of the Global\-Motor. Example: recoil after a fire or hit. \\
Recoil\-Local\-Motor\-Starter & Used to just increase current speed of the Local\-Motor. Example: recoil after a fire. \\
Recoil\-Rigid\-Body\-Starter & Used to just increase current speed of the Rigidbody. Example: recoil after a fire or hit. \\
Sound\-Starter &  \\
\bottomrule
\end{longtabu}
\xdtbeforemembers

\xdtbeforemembersof{Actor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_lua\-Object & protected & Lua\-Object\-Component & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Contains the actor's lua script and table.} \\ \tabuphantomline
\_is\-Selected & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Whether the actor is selected.} \\ \tabuphantomline
Gun\-End & public & Transform & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The muzzle is the end of the gun, from where the projectile will be shot} \\ \tabuphantomline
Target & public & Game\-Object & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The current target of the actor, this is the enemy that the actor will attack} \\ \tabuphantomline
Projectile\-Prefab & public & Game\-Object & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The prefab of the bullet that will be spawned when the weapon is fired.} \\ \tabuphantomline
Shot\-Duration & public & Wait\-For\-Seconds & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{How long the laser will be visible after it has been shot} \\ \tabuphantomline
Next\-Fire & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Line\-Of\-Sight & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{How far the actor can look, i.e it's view radius.} \\ \tabuphantomline
Enemy\-In\-Sight & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{If we can see an enemy} \\ \tabuphantomline
Last\-Sighting & public & Vector3 & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{inference, AI difficulty} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Type & public & string & \{ get; protected set; \} & The actor's type. \\
Health & public & int & \{ get; protected set; \} & Current Health Points the actor has \\
Max\-Health & public & int & \{ get; protected set; \} & Max health points the actor has \\
Attack\-Range & public & float & \{ get; protected set; \} & How far the Actor can attack \\
Gun\-Damage & public & float & \{ get; protected set; \} & The amount of damage the projectile deals to the target \\
Fire\-Rate & public & float & \{ get; protected set; \} & How fast the weapon shoots projectiles \\
Enemy\-In\-Range & public & bool & \{ get; protected set; \} & This bool indicates if an enemy is within attacking distance of the actor. \\
Name & public & string & \{ get =\-{\tt >} name; \} [Header("Faction")] /// {\tt <}\-summary\-{\tt >} /// The faction the actor is alligned with /// {\tt <}\-/summary\-{\tt >} public Factions My\-Faction; \#endregion \#region Audio /// {\tt <}\-summary\-{\tt >} /// /// {\tt <}\-/summary\-{\tt >} private Audio\-Source \_gun\-Audio; \#endregion /// {\tt <}\-summary\-{\tt >} /// Speciacations of the actor class determines how to attack /// {\tt <}\-/summary\-{\tt >} public virtual  & A personal name that can be used for drones or marines. Note that this is 
         distinct from drone ID's. \\
Name & public & string & \{ get =\-{\tt >} name; \} [Header("Faction")] /// {\tt <}\-summary\-{\tt >} /// The faction the actor is alligned with /// {\tt <}\-/summary\-{\tt >} public Factions My\-Faction; \#endregion \#region Audio /// {\tt <}\-summary\-{\tt >} /// /// {\tt <}\-/summary\-{\tt >} private Audio\-Source \_gun\-Audio; \#endregion /// {\tt <}\-summary\-{\tt >} /// Speciacations of the actor class determines how to attack /// {\tt <}\-/summary\-{\tt >} public virtual  & The faction the actor is alligned with \\
Name & public & string & \{ get =\-{\tt >} name; \} [Header("Faction")] /// {\tt <}\-summary\-{\tt >} /// The faction the actor is alligned with /// {\tt <}\-/summary\-{\tt >} public Factions My\-Faction; \#endregion \#region Audio /// {\tt <}\-summary\-{\tt >} /// /// {\tt <}\-/summary\-{\tt >} private Audio\-Source \_gun\-Audio; \#endregion /// {\tt <}\-summary\-{\tt >} /// Speciacations of the actor class determines how to attack /// {\tt <}\-/summary\-{\tt >} public virtual  &  \\
Name & public & string & \{ get =\-{\tt >} name; \} [Header("Faction")] /// {\tt <}\-summary\-{\tt >} /// The faction the actor is alligned with /// {\tt <}\-/summary\-{\tt >} public Factions My\-Faction; \#endregion \#region Audio /// {\tt <}\-summary\-{\tt >} /// /// {\tt <}\-/summary\-{\tt >} private Audio\-Source \_gun\-Audio; \#endregion /// {\tt <}\-summary\-{\tt >} /// Speciacations of the actor class determines how to attack /// {\tt <}\-/summary\-{\tt >} public virtual  & Speciacations of the actor class determines how to attack \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Take\-Damage & public virtual & void & (int damage) & Causes the actor to take damage. \\
Shoot\-Laser & protected & IEnumerator & () & Draws the laser line \\
Get\-Value & public & Dyn\-Value & (string key) & Gets a value from the Actor's table. \\
Set\-Value & public & void & (string key, Dyn\-Value value) & Sets a value in the Actor's table. \\
Get\-Table\-Pairs & public & IEnumerable{\tt <}\-Table\-Pair\-{\tt >} & () & Returns every pair in the actor's table. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Inventory}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Capacity & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{How many resources the Inventory could hold} \\ \tabuphantomline
\_amount\-In\-Inventory & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{How} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Contents & public & Dictionary{\tt <}\-string, int\-{\tt >} & \{ get; private set; \} & The string will be resource type, the int will be amount. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Deposit & public & int & (string resource\-Type, int amount) & Put Amount of Resource Resource\-Type in the inventory. Returns the amount that could be deposited. \\
Withdraw & public & int & (string resource\-Type, int amount) & Try to withdraw the given amount of a resource. Returns the amount actually withdrawn, which could be smaller if one attempts to withdraw more than the inventory has. \\
Get\-Available\-Space & public & int & () & Returns amount of space available for resources in the inventory \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WorldInfo}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Drone\-Types & public static & List{\tt <}\-string\-{\tt >} & \{ get; private set; \} & List of all the drone types in the game. \\
Resource\-Types & public static & List{\tt <}\-string\-{\tt >} & \{ get; private set; \} & List of all the resource types in the game. \\
Chunks & public static & List{\tt <}\-Vector2Int\-{\tt >} & \{ get; private set; \} & List of all enterable buildings in the game. \\
Enterable\-Buildings & public static & List{\tt <}\-Enterable\-Building\-{\tt >} & \{ get; private set; \} & List of all enterable buildings in the game. \\
Actors & public static & List{\tt <}\-Actor\-{\tt >} & \{ get; private set; \} & List of all actors in the game. \\
Marines & public static & List{\tt <}\-Game\-Object\-{\tt >} & \{ get; private set; \} & List of marines \\
Resources & public static & List{\tt <}\-Game\-Object\-{\tt >} & \{ get; private set; \} & List of all resources in the game. \\
Depots & public static & List{\tt <}\-Game\-Object\-{\tt >} & \{ get; private set; \} & List of all buildings that can hold resources in the game. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{UtilityAction}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Utility\-Action & public & (List{\tt <}\-Factor\-{\tt >} factors, Action behaviour) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes the Utility action with the factors that affect its utility and the behavior it executes} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Factor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Math\-Function & public & Function & \{ get; protected set; \} & mxparser function for the utility function. MUST be set, MANUALLY in all inherited classes. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Utility & public & float & () & Returns the utility value of the Factor \\
Update\-Utility & public abstract & void & () & Update the Factor's utility by whatever metric the derived class uses \\
Validate & protected & void & () & Debug function - verify that the factor's utility is between 0.00 and 1.00. Should always be called before returning in Get\-Utility() \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ScriptableObjectBase}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Load\-Remote & public & IEnumerator & () & Should be called at startup to retrieve the external settings \\
Save\-Remote & public & IEnumerator & () & Should be called to send the information to the server
     TODO: not sure if coroutine is a good idea, since this wont work in editor mode \\
Load\-Data & public abstract & void & (string data) & Load data into your object after receiving the file from the server \\
Get\-Save\-Data & public abstract & string & () & Serialises the Scriptable Objects data and sends it to the server \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{LargeTerrain}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
dont\-Update\-Size & public & void & () & Prevent one time from updating size, after terrain size has changed manually \\
Sample\-Height & public & float & (Vector3 position) & Gets the height at position in world units. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TerrainGenerator}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
terrain\-Resolution & public & Large\-Terrain\-Resolution & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Warning: Large resolutions can freeze your application for minutes while building} \\ \tabuphantomline
terrain\-Roughness & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The terrain roughness. Must be a value between 1 and 100!} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
clear & public & void & () & Clear this terrain.
	 Warning: Deletes als child objects of this transform \\
build & public & bool & () & Build a new terrain. Rund clear() before building. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PreprocessorDefine}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add\-Define\-Symbols & public static & void & () & Add define symbols as soon as Unity gets done compiling. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkAnimator}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
animator & public & Animator & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The animator component to synchronize.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Serialize & public override & bool & (Network\-Writer writer, bool initial\-State) & Custom Serialization \\
On\-Deserialize & public override & void & (Network\-Reader reader, bool initial\-State) & Custom Deserialization \\
Set\-Trigger & public & void & (string trigger\-Name) & Causes an animation trigger to be invoked for a networked object.
         If local authority is set, and this is called from the client, then the trigger will be invoked on the server and all clients. If not, then this is called on the server, and the trigger will be called on all clients. \\
Reset\-Trigger & public & void & (string trigger\-Name) & Causes an animation trigger to be reset for a networked object.
         If local authority is set, and this is called from the client, then the trigger will be reset on the server and all clients. If not, then this is called on the server, and the trigger will be reset on all clients. \\
Set\-Trigger & public & void & (int hash) & Causes an animation trigger to be invoked for a networked object. \\
Reset\-Trigger & public & void & (int hash) & Causes an animation trigger to be reset for a networked object. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkProximityChecker}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
vis\-Range & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The maximim range that objects will be visible at.} \\ \tabuphantomline
vis\-Update\-Interval & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{How often (in seconds) that this object should update the list of observers that can see it.} \\ \tabuphantomline
check\-Method & public & Check\-Method & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Which method to use for checking proximity of players.
         Physics3D uses 3D physics to determine proximity.
         Physics2D uses 2D physics to determine proximity.} \\ \tabuphantomline
force\-Hidden & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Flag to force this object to be hidden for players.
         If this object is a player object, it will not be hidden for that player.} \\ \tabuphantomline
cast\-Layers & public & Layer\-Mask & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Select only the Player's layer to avoid unnecessary Sphere\-Casts against the Terrain, etc.
         \textasciitilde\{\}0 means 'Everything'.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Check\-Observer & public override & bool & (Network\-Connection new\-Observer) & Called when a new player enters \\
On\-Rebuild\-Observers & public override & bool & (Hash\-Set{\tt <}\-Network\-Connection\-{\tt >} observers, bool initial) & Called when a new player enters, and when scene changes occur \\
On\-Set\-Host\-Visibility & public override & void & (bool visible) & Called when hiding and showing objects on the host.
         On regular clients, objects simply spawn/despawn.
         On host, objects need to remain in scene because the host is also the server.
            In that case, we simply hide/show meshes for the host player. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkRoomManager}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Room\-Scene & public & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The scene to use for the room. This is similar to the offline\-Scene of the Network\-Manager.} \\ \tabuphantomline
Gameplay\-Scene & public & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The scene to use for the playing the game from the room. This is similar to the online\-Scene of the Network\-Manager.} \\ \tabuphantomline
pending\-Players & public & List{\tt <}\-Pending\-Player\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{List of players that are in the Room} \\ \tabuphantomline
room\-Slots & public & List{\tt <}\-Network\-Room\-Player\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{These slots track players that enter the room.
         The slot\-Id on players is global to the game - across all players.} \\ \tabuphantomline
all\-Players\-Ready & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{True when all players have submitted a Ready message} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Server\-Ready & public override & void & (Network\-Connection conn) & Called on the server when a client is ready.
         The default implementation of this function calls Network\-Server.Set\-Client\-Ready() to continue the network setup process. \\
Check\-Ready\-To\-Begin & public & void & () & Check\-Ready\-To\-Begin checks all of the players in the room to see if their ready\-To\-Begin flag is set.
         If all of the players are ready, then the server switches from the Room\-Scene to the Play\-Scene - essentially starting the game. This is called automatically in response to Network\-Room\-Player.Send\-Ready\-To\-Begin\-Message(). \\
On\-Server\-Connect & public override & void & (Network\-Connection conn) & Called on the server when a new client connects.
         Unity calls this on the Server when a Client connects to the Server. Use an override to tell the Network\-Manager what to do when a client connects to the server. \\
On\-Server\-Disconnect & public override & void & (Network\-Connection conn) & Called on the server when a client disconnects.
         This is called on the Server when a Client disconnects from the Server. Use an override to decide what should happen when a disconnection is detected. \\
On\-Server\-Add\-Player & public override & void & (Network\-Connection conn) & Called on the server when a client adds a new player with Client\-Scene.Add\-Player.
         The default implementation for this function creates a new player object from the player\-Prefab. \\
Server\-Change\-Scene & public override & void & (string scene\-Name) & This causes the server to switch scenes and sets the network\-Scene\-Name.
         Clients that connect to this server will automatically switch to this scene. This is called autmatically if online\-Scene or offline\-Scene are set, but it can be called from user code to switch scenes again while the game is in progress. This automatically sets clients to be not-ready. The clients must call Network\-Client.Ready() again to participate in the new scene. \\
On\-Server\-Scene\-Changed & public override & void & (string scene\-Name) & Called on the server when a scene is completed loaded, when the scene load was initiated by the server with Server\-Change\-Scene(). \\
On\-Start\-Server & public override & void & () & This is invoked when a server is started - including when a host is started.
         Start\-Server has multiple signatures, but they all cause this hook to be called. \\
On\-Start\-Host & public override & void & () & This is invoked when a host is started.
         Start\-Host has multiple signatures, but they all cause this hook to be called. \\
On\-Stop\-Server & public override & void & () & This is called when a server is stopped - including when a host is stopped. \\
On\-Stop\-Host & public override & void & () & This is called when a host is stopped. \\
On\-Start\-Client & public override & void & () & This is invoked when the client is started. \\
On\-Client\-Connect & public override & void & (Network\-Connection conn) & Called on the client when connected to a server.
         The default implementation of this function sets the client as ready and adds a player. Override the function to dictate what happens when the client connects. \\
On\-Client\-Disconnect & public override & void & (Network\-Connection conn) & Called on clients when disconnected from a server.
         This is called on the client when it disconnects from the server. Override this function to decide what happens when the client disconnects. \\
On\-Stop\-Client & public override & void & () & This is called when a client is stopped. \\
On\-Client\-Scene\-Changed & public override & void & (Network\-Connection conn) & Called on clients when a scene has completed loaded, when the scene load was initiated by the server.
         Scene changes can cause player objects to be destroyed. The default implementation of On\-Client\-Scene\-Changed in the Network\-Manager is to add a player object for the connection if no player object exists. \\
On\-Room\-Start\-Host & public virtual & void & () & This is called on the host when a host is started. \\
On\-Room\-Stop\-Host & public virtual & void & () & This is called on the host when the host is stopped. \\
On\-Room\-Start\-Server & public virtual & void & () & This is called on the server when the server is started - including when a host is started. \\
On\-Room\-Server\-Connect & public virtual & void & (Network\-Connection conn) & This is called on the server when a new client connects to the server. \\
On\-Room\-Server\-Disconnect & public virtual & void & (Network\-Connection conn) & This is called on the server when a client disconnects. \\
On\-Room\-Server\-Scene\-Changed & public virtual & void & (string scene\-Name) & This is called on the server when a networked scene finishes loading. \\
On\-Room\-Server\-Create\-Room\-Player & public virtual & Game\-Object & (Network\-Connection conn) & This allows customization of the creation of the room-player object on the server.
         By default the room\-Player\-Prefab is used to create the room-player, but this function allows that behaviour to be customized. \\
On\-Room\-Server\-Create\-Game\-Player & public virtual & Game\-Object & (Network\-Connection conn) & Obsolete: Use  instead. \\
On\-Room\-Server\-Create\-Game\-Player & public virtual & Game\-Object & (Network\-Connection conn, Game\-Object room\-Player) & This allows customization of the creation of the Game\-Player object on the server.
         By default the game\-Player\-Prefab is used to create the game-player, but this function allows that behaviour to be customized. The object returned from the function will be used to replace the room-player on the connection. \\
On\-Room\-Server\-Add\-Player & public virtual & void & (Network\-Connection conn) & This allows customization of the creation of the Game\-Player object on the server.
         This is only called for subsequent Game\-Play scenes after the first one.
         See  to customize the player object for the initial Game\-Play scene. \\
On\-Room\-Server\-Scene\-Loaded\-For\-Player & public virtual & bool & (Game\-Object room\-Player, Game\-Object game\-Player) & Obsolete: Use  instead. \\
On\-Room\-Server\-Scene\-Loaded\-For\-Player & public virtual & bool & (Network\-Connection conn, Game\-Object room\-Player, Game\-Object game\-Player) & This is called on the server when it is told that a client has finished switching from the room scene to a game player scene.
         When switching from the room, the room-player is replaced with a game-player object. This callback function gives an opportunity to apply state from the room-player to the game-player object. \\
On\-Room\-Server\-Players\-Ready & public virtual & void & () & This is called on the server when all the players in the room are ready.
         The default implementation of this function uses Server\-Change\-Scene() to switch to the game player scene. By implementing this callback you can customize what happens when all the players in the room are ready, such as adding a countdown or a confirmation for a group leader. \\
On\-Room\-Client\-Enter & public virtual & void & () & This is a hook to allow custom behaviour when the game client enters the room. \\
On\-Room\-Client\-Exit & public virtual & void & () & This is a hook to allow custom behaviour when the game client exits the room. \\
On\-Room\-Client\-Connect & public virtual & void & (Network\-Connection conn) & This is called on the client when it connects to server. \\
On\-Room\-Client\-Disconnect & public virtual & void & (Network\-Connection conn) & This is called on the client when disconnected from a server. \\
On\-Room\-Start\-Client & public virtual & void & () & This is called on the client when a client is started. \\
On\-Room\-Stop\-Client & public virtual & void & () & This is called on the client when the client stops. \\
On\-Room\-Client\-Scene\-Changed & public virtual & void & (Network\-Connection conn) & This is called on the client when the client is finished loading a new networked scene. \\
On\-Room\-Client\-Add\-Player\-Failed & public virtual & void & () & Called on the client when adding a player to the room fails.
         This could be because the room is full, or the connection is not allowed to have more players. \\
On\-GUI & public virtual & void & () & virtual so inheriting classes can roll their own \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkRoomPlayer}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
show\-Room\-GUI & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{This flag controls whether the default UI is shown for the room player.
         As this UI is rendered using the old GUI system, it is only recommended for testing purposes.} \\ \tabuphantomline
ready\-To\-Begin & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{This is a flag that control whether this player is ready for the game to begin.
         When all players are ready to begin, the game will start. This should not be set directly, the Send\-Ready\-To\-Begin\-Message function should be called on the client to set it on the server.} \\ \tabuphantomline
index & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Current index of the player, e.g. Player1, Player2, etc.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Start & public & void & () & Do not use Start - Override On\-Startr\-Host / On\-Start\-Client instead! \\
On\-Client\-Enter\-Room & public virtual & void & () & This is a hook that is invoked on all player objects when entering the room.
         Note: is\-Local\-Player is not guaranteed to be set until On\-Start\-Local\-Player is called. \\
On\-Client\-Exit\-Room & public virtual & void & () & This is a hook that is invoked on all player objects when exiting the room. \\
On\-Client\-Ready & public virtual & void & (bool ready\-State) & This is a hook that is invoked on clients when a Room\-Player switches between ready or not ready.
         This function is called when the a client player calls Send\-Ready\-To\-Begin\-Message() or Send\-Not\-Ready\-To\-Begin\-Message(). \\
On\-GUI & public virtual & void & () & Render a UI for the room.   Override to provide your on UI \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkSceneChecker}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
force\-Hidden & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Flag to force this object to be hidden from all observers.
         If this object is a player object, it will not be hidden for that client.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Check\-Observer & public override & bool & (Network\-Connection conn) & Called when a new player enters the scene \\
On\-Set\-Host\-Visibility & public override & void & (bool visible) & Called when hiding and showing objects on the host.
         On regular clients, objects simply spawn/despawn.
         On host, objects need to remain in scene because the host is also the server.
         In that case, we simply hide/show meshes for the host player. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ClientScene}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
prefabs & public static & Dictionary{\tt <}\-Guid, Game\-Object\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{This is a dictionary of the prefabs that are registered on the client with Client\-Scene.Register\-Prefab().
         The key to the dictionary is the prefab asset Id.} \\ \tabuphantomline
spawnable\-Objects & public static & Dictionary{\tt <}\-ulong, Network\-Identity\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{This is dictionary of the disabled Network\-Identity objects in the scene that could be spawned by messages from the server.
         The key to the dictionary is the Network\-Identity scene\-Id.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
local\-Player & public static & Network\-Identity & \{ get; private set; \} & Network\-Identity of the local\-Player \\
ready & public static & bool & \{ get; internal set; \} & Returns true when a client's connection has been set to ready.
         A client that is ready recieves state updates from the server, while a client that is not ready does not. This useful when the state of the game is not normal, such as a scene change or end-of-game.
         This is read-only. To change the ready state of a client, use Client\-Scene.Ready(). The server is able to set the ready state of clients using Network\-Server.Set\-Client\-Ready(), Network\-Server.Set\-Client\-Not\-Ready() and Network\-Server.Set\-All\-Clients\-Not\-Ready().
         This is done when changing scenes so that clients don't receive state update messages during scene loading. \\
ready\-Connection & public static & Network\-Connection & \{ get; private set; \} & The Network\-Connection object that is currently "ready". This is the connection to the server where objects are spawned from.
         This connection can be used to send messages to the server. There can only be one ready connection at a time. There can be multiple Network\-Client instances in existence, each with their own Network\-Connections, but there is only one Client\-Scene instance and corresponding ready connection. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add\-Player & public static & bool & () & This adds a player Game\-Object for this client.
         This causes an Add\-Player message to be sent to the server, and Network\-Manager.On\-Server\-Add\-Player is called. \\
Add\-Player & public static & bool & (Network\-Connection ready\-Conn) & This adds a player Game\-Object for this client. This causes an Add\-Player message to be sent to the server, and Network\-Manager.On\-Server\-Add\-Player is called. If an extra message was passed to Add\-Player, then On\-Server\-Add\-Player will be called with a Network\-Reader that contains the contents of the message. \\
Add\-Player & public static & bool & (Network\-Connection ready\-Conn, byte[] extra\-Data) & This adds a player Game\-Object for this client. This causes an Add\-Player message to be sent to the server, and Network\-Manager.On\-Server\-Add\-Player is called. If an extra message was passed to Add\-Player, then On\-Server\-Add\-Player will be called with a Network\-Reader that contains the contents of the message.
         extra\-Message can contain character selection, etc. \\
Remove\-Player & public static & bool & () & Removes the player from the game. \\
Ready & public static & bool & (Network\-Connection conn) & Signal that the client connection is ready to enter the game.
         This could be for example when a client enters an ongoing game and has finished loading the current scene. The server should respond to the SYSTEM\_READY event with an appropriate handler which instantiates the players object for example. \\
Prepare\-To\-Spawn\-Scene\-Objects & public static & void & () & Call this after loading/unloading a scene in the client after connection to register the spawnable objects \\
Get\-Prefab & public static & bool & (Guid asset\-Id, out Game\-Object prefab) & Find the registered prefab for this asset id.
         Useful for debuggers \\
Register\-Prefab & public static & void & (Game\-Object prefab, Guid new\-Asset\-Id) & Registers a prefab with the spawning system.
         When a Network\-Identity object is spawned on a server with Network\-Server.Spawn\-Object(), and the prefab that the object was created from was registered with Register\-Prefab(), the client will use that prefab to instantiate a corresponding client object with the same net\-Id.
         The Network\-Manager has a list of spawnable prefabs, it uses this function to register those prefabs with the Client\-Scene.
         The set of current spawnable object is available in the Client\-Scene static member variable Client\-Scene.prefabs, which is a dictionary of Network\-Asset\-Ids and prefab references. \\
Register\-Prefab & public static & void & (Game\-Object prefab) & Registers a prefab with the spawning system.
         When a Network\-Identity object is spawned on a server with Network\-Server.Spawn\-Object(), and the prefab that the object was created from was registered with Register\-Prefab(), the client will use that prefab to instantiate a corresponding client object with the same net\-Id.
         The Network\-Manager has a list of spawnable prefabs, it uses this function to register those prefabs with the Client\-Scene.
         The set of current spawnable object is available in the Client\-Scene static member variable Client\-Scene.prefabs, which is a dictionary of Network\-Asset\-Ids and prefab references. \\
Register\-Prefab & public static & void & (Game\-Object prefab, Spawn\-Delegate spawn\-Handler, Un\-Spawn\-Delegate unspawn\-Handler) & Registers a prefab with the spawning system.
         When a Network\-Identity object is spawned on a server with Network\-Server.Spawn\-Object(), and the prefab that the object was created from was registered with Register\-Prefab(), the client will use that prefab to instantiate a corresponding client object with the same net\-Id.
         The Network\-Manager has a list of spawnable prefabs, it uses this function to register those prefabs with the Client\-Scene.
         The set of current spawnable object is available in the Client\-Scene static member variable Client\-Scene.prefabs, which is a dictionary of Network\-Asset\-Ids and prefab references. \\
Register\-Prefab & public static & void & (Game\-Object prefab, Spawn\-Handler\-Delegate spawn\-Handler, Un\-Spawn\-Delegate unspawn\-Handler) & Registers a prefab with the spawning system.
         When a Network\-Identity object is spawned on a server with Network\-Server.Spawn\-Object(), and the prefab that the object was created from was registered with Register\-Prefab(), the client will use that prefab to instantiate a corresponding client object with the same net\-Id.
         The Network\-Manager has a list of spawnable prefabs, it uses this function to register those prefabs with the Client\-Scene.
         The set of current spawnable object is available in the Client\-Scene static member variable Client\-Scene.prefabs, which is a dictionary of Network\-Asset\-Ids and prefab references. \\
Unregister\-Prefab & public static & void & (Game\-Object prefab) & Removes a registered spawn prefab that was setup with Client\-Scene.Register\-Prefab. \\
Register\-Spawn\-Handler & public static & void & (Guid asset\-Id, Spawn\-Delegate spawn\-Handler, Un\-Spawn\-Delegate unspawn\-Handler) & This is an advanced spawning function that registers a custom asset\-Id with the UNET spawning system.
         This can be used to register custom spawning methods for an asset\-Id - instead of the usual method of registering spawning methods for a prefab. This should be used when no prefab exists for the spawned objects - such as when they are constructed dynamically at runtime from configuration data. \\
Register\-Spawn\-Handler & public static & void & (Guid asset\-Id, Spawn\-Handler\-Delegate spawn\-Handler, Un\-Spawn\-Delegate unspawn\-Handler) & This is an advanced spawning function that registers a custom asset\-Id with the UNET spawning system.
         This can be used to register custom spawning methods for an asset\-Id - instead of the usual method of registering spawning methods for a prefab. This should be used when no prefab exists for the spawned objects - such as when they are constructed dynamically at runtime from configuration data. \\
Unregister\-Spawn\-Handler & public static & void & (Guid asset\-Id) & Removes a registered spawn handler function that was registered with Client\-Scene.Register\-Handler(). \\
Clear\-Spawners & public static & void & () & This clears the registered spawn prefabs and spawn handler functions for this client. \\
Destroy\-All\-Client\-Objects & public static & void & () & Destroys all networked objects on the client.
         This can be used to clean up when a network connection is closed. \\
Find\-Local\-Object & public static & Game\-Object & (uint net\-Id) & Obsolete: Use  instead. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ULocalConnectionToClient}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Disconnect & public override & void & () & Disconnects this connection. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ULocalConnectionToServer}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Disconnect\-Internal & internal & void & () & Disconnects this connection. \\
Disconnect & public override & void & () & Disconnects this connection. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{AddPlayerMessage}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
value & public & byte[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Obsolete: Create your own message instead. See Custom Players} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Deserialize & public & void & (Network\-Reader reader) & Obsolete: Create your own message instead. See Custom Players \\
Serialize & public & void & (Network\-Writer writer) & Obsolete: Create your own message instead. See Custom Players \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkAuthenticator}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
On\-Server\-Authenticated & public & Unity\-Event\-Network\-Connection & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Notify subscribers on the server when a client is authenticated} \\ \tabuphantomline
On\-Client\-Authenticated & public & Unity\-Event\-Network\-Connection & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Notify subscribers on the client when the client is authenticated} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Start\-Server & public virtual & void & () & Called on server from Start\-Server to initialize the Authenticator
         Server message handlers should be registered in this method. \\
On\-Server\-Authenticate & public abstract & void & (Network\-Connection conn) & Called on server from On\-Server\-Authenticate\-Internal when a client needs to authenticate \\
On\-Start\-Client & public virtual & void & () & Called on client from Start\-Client to initialize the Authenticator
         Client message handlers should be registered in this method. \\
On\-Client\-Authenticate & public abstract & void & (Network\-Connection conn) & Called on client from On\-Client\-Authenticate\-Internal when a client needs to authenticate \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkBehaviour}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
sync\-Mode & public & Sync\-Mode & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{sync mode for On\-Serialize} \\ \tabuphantomline
sync\-Interval & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{sync interval for On\-Serialize (in seconds)} \\ \tabuphantomline
sync\-Objects & protected readonly & List{\tt <}\-Sync\-Object\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{objects that can synchronize themselves, such as synclists} \\ \tabuphantomline
net\-Identity\-Cache &  & Network\-Identity & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Network\-Identity component caching for easier access} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
is\-Server & public & bool & \{ get; \} & Returns true if this object is active on an active server.
         This is only true if the object has been spawned. This is different from Network\-Server.active, which is true if the server itself is active rather than this object being active. \\
is\-Client & public & bool & \{ get; \} & Returns true if running as a client and this object was spawned by a server. \\
is\-Local\-Player & public & bool & \{ get; \} & This returns true if this object is the one that represents the player on the local machine.
         In multiplayer games, there are multiple instances of the Player object. The client needs to know which one is for "themselves" so that only that player processes input and potentially has a camera attached. The Is\-Local\-Player function will return true only for the player instance that belongs to the player on the local machine, so it can be used to filter out input for non-local players. \\
is\-Server\-Only & public & bool & \{ get; \} & True if this object only exists on the server \\
is\-Client\-Only & public & bool & \{ get; \} & True if this object exists on a client that is not also acting as a server \\
has\-Authority & public & bool & \{ get; \} & This returns true if this object is the authoritative version of the object in the distributed network application.
         The Network\-Identity.has\-Authority value on the Network\-Identity determines how authority is determined. For most objects, authority is held by the server. For objects with Network\-Identity.has\-Authority set, authority is held by the client of that player. \\
net\-Id & public & uint & \{ get; \} & The unique network Id of this object.
         This is assigned at runtime by the network server and will be unique for all objects for that network session. \\
connection\-To\-Server & public & Network\-Connection & \{ get; \} & The Network\-Connection associated with this Network\-Identity. This is only valid for player objects on the server. \\
connection\-To\-Client & public & Network\-Connection & \{ get; \} & The Network\-Connection associated with this Network\-Identity. This is only valid for player objects on the server. \\
m\_Sync\-Objects & protected & List{\tt <}\-Sync\-Object\-{\tt >} & \{ get; \} & Obsolete: Use  instead. \\
net\-Identity & public & Network\-Identity & \{ get if (net\-Identity\-Cache == null) \{ Debug.Log\-Error("There is no Network\-Identity on " + name + ". Please add one."); \} return net\-Identity\-Cache; \} \} & Returns the Network\-Identity of this object \\
Component\-Index & public & int & \{ get // this should never happen Debug.Log\-Error("Could not find component in Game\-Object. You should not add/remove components in networked objects dynamically", this); return -1; \} \} & Returns the index of the component on this object \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Invoke\-Command & public virtual & bool & (int cmd\-Hash, Network\-Reader reader) & Manually invoke a Command. \\
Invoke\-RPC & public virtual & bool & (int rpc\-Hash, Network\-Reader reader) & Manually invoke an RPC function. \\
Invoke\-Sync\-Event & public virtual & bool & (int event\-Hash, Network\-Reader reader) & Manually invoke a Sync\-Event. \\
Get\-Rpc\-Handler & public static & Cmd\-Delegate & (int cmd\-Hash) & Gets the handler function for a given hash
         Can be used by profilers and debuggers \\
Set\-Dirty\-Bit & public & void & (ulong dirty\-Bit) & Used to set the behaviour as dirty, so that a network update will be sent for the object.
         these are masks, not bit numbers, ie. 0x004 not 2 \\
Clear\-All\-Dirty\-Bits & public & void & () & This clears all the dirty bits that were set on this script by Set\-Dirty\-Bits();
         This is automatically invoked when an update is sent for this object, but can be called manually as well. \\
On\-Serialize & public virtual & bool & (Network\-Writer writer, bool initial\-State) & Virtual function to override to send custom serialization data. The corresponding function to send serialization data is On\-Deserialize(). \\
On\-Deserialize & public virtual & void & (Network\-Reader reader, bool initial\-State) & Virtual function to override to receive custom serialization data. The corresponding function to send serialization data is On\-Serialize(). \\
On\-Network\-Destroy & public virtual & void & () & This is invoked on clients when the server has caused this object to be destroyed.
         This can be used as a hook to invoke effects or do client specific cleanup. \\
On\-Start\-Server & public virtual & void & () & This is invoked for Network\-Behaviour objects when they become active on the server.
         This could be triggered by Network\-Server.Listen() for objects in the scene, or by Network\-Server.Spawn() for objects that are dynamically created.
         This will be called for objects on a "host" as well as for object on a dedicated server. \\
On\-Start\-Client & public virtual & void & () & Called on every Network\-Behaviour when it is activated on a client.
         Objects on the host have this function called, as there is a local client on the host. The values of Sync\-Vars on object are guaranteed to be initialized correctly with the latest state from the server when this function is called on the client. \\
On\-Start\-Local\-Player & public virtual & void & () & Called when the local player object has been set up.
         This happens after On\-Start\-Client(), as it is triggered by an ownership message from the server. This is an appropriate place to activate components or functionality that should only be active for the local player, such as cameras and input. \\
On\-Start\-Authority & public virtual & void & () & This is invoked on behaviours that have authority, based on context and Network\-Identity.has\-Authority.
         This is called after On\-Start\-Server and before On\-Start\-Client.
         When  is called on the server, this will be called on the client that owns the object. When an object is spawned with Network\-Server.Spawn with a Network\-Connection parameter included, this will be called on the client that owns the object. \\
On\-Stop\-Authority & public virtual & void & () & This is invoked on behaviours when authority is removed.
         When Network\-Identity.Remove\-Client\-Authority is called on the server, this will be called on the client that owns the object. \\
On\-Rebuild\-Observers & public virtual & bool & (Hash\-Set{\tt <}\-Network\-Connection\-{\tt >} observers, bool initialize) & Callback used by the visibility system to (re)construct the set of observers that can see this object.
         Implementations of this callback should add network connections of players that can see this object to the observers set. \\
On\-Set\-Host\-Visibility & public virtual & void & (bool visible) & Callback used by the visibility system for objects on a host.
         Objects on a host (with a local client) cannot be disabled or destroyed when they are not visibile to the local client. So this function is called to allow custom code to hide these objects. A typical implementation will disable renderer components on the object. This is only called on local clients on a host. \\
On\-Check\-Observer & public virtual & bool & (Network\-Connection conn) & Callback used by the visibility system to determine if an observer (player) can see this object.
         If this function returns true, the network connection will be added as an observer. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkClient}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
singleton & public static & Network\-Client & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Obsolete: Use  directly.
         Singleton isn't needed anymore, all functions are static now. For example: Network\-Client.Send(message) instead of Network\-Client.singleton.Send(message).} \\ \tabuphantomline
handlers & static readonly & Dictionary{\tt <}\-int, Network\-Message\-Delegate\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The registered network message handlers.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
all\-Clients & public static & List{\tt <}\-Network\-Client\-{\tt >} & \{ get; \} & A list of all the active network clients in the current process.
         This is NOT a list of all clients that are connected to the remote server, it is client instances on the local game. \\
connection & public static & Network\-Connection & \{ get; internal set; \} & The Network\-Connection object this client is using. \\
server\-Ip & public static & string & \{ get; \} & The IP address of the server that this client is connected to.
         This will be empty if the client has not connected yet. \\
active & public static & bool & \{ get; \} & active is true while a client is connecting/connected
         (= while the network is active) \\
is\-Connected & public static & bool & \{ get; \} & This gives the current connection status of the client. \\
is\-Local\-Client & public static & bool & \{ get; \} & Network\-Client can connect to local server in host mode too \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Connect & public static & void & (string address) & Connect client to a Network\-Server instance. \\
Connect & public static & void & (Uri uri) & Connect client to a Network\-Server instance. \\
Connect\-Local\-Server & internal static & void & () & connect host mode \\
Disconnect & public static & void & () & Disconnect from server.
         The disconnect message will be invoked. \\
Send & public static & bool & (short msg\-Type, Message\-Base msg) & Obsolete: Use  instead with no message id instead \\
Send & public static & bool & (T message, int channel\-Id = Channels.Default\-Reliable) & This sends a network message with a message Id to the server. This message is sent on channel zero, which by default is the reliable channel.
         The message must be an instance of a class derived from Message\-Base.
         The message id passed to Send() is used to identify the handler function to invoke on the server when the message is received. \\
Get\-RTT & public static & float & () & Obsolete: Use  instead \\
Register\-Handler & public static & void & (int msg\-Type, Network\-Message\-Delegate handler) & Obsolete: Use  instead \\
Register\-Handler & public static & void & (Msg\-Type msg\-Type, Network\-Message\-Delegate handler) & Obsolete: Use  instead \\
Register\-Handler & public static & void & (Action{\tt <}\-Network\-Connection, T\-{\tt >} handler, bool require\-Authentication = true) & Register a handler for a particular message type.
         There are several system message types which you can add handlers for. You can also add your own message types. \\
Register\-Handler & public static & void & (Action{\tt <}\-T\-{\tt >} handler, bool require\-Authentication = true) & Register a handler for a particular message type.
         There are several system message types which you can add handlers for. You can also add your own message types. \\
Unregister\-Handler & public static & void & (int msg\-Type) & Obsolete: Use  instead \\
Unregister\-Handler & public static & void & (Msg\-Type msg\-Type) & Obsolete: Use  instead \\
Unregister\-Handler & public static & void & () & Unregisters a network message handler. \\
Shutdown & public static & void & () & Shut down a client.
         This should be done when a client is no longer going to be used. \\
Shutdown\-All & public static & void & () & Obsolete: Call  instead. There is only one client. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkConnection}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
connection\-Id & public readonly & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Unique identifier for this connection that is assigned by the transport layer.} \\ \tabuphantomline
is\-Authenticated & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Flag that indicates the client has been authenticated.} \\ \tabuphantomline
authentication\-Data & public & object & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{General purpose object to hold authentication data, character selection, tokens, etc.
         associated with the connection for reference after Authentication completes.} \\ \tabuphantomline
is\-Ready & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Flag that tells if the connection has been marked as "ready" by a client calling Client\-Scene.Ready().
         This property is read-only. It is set by the system on the client when Client\-Scene.Ready() is called, and set by the system on the server when a ready message is received from a client.
         A client that is ready is sent spawned objects by the server and updates to the state of spawned objects. A client that is not ready is not sent spawned objects.} \\ \tabuphantomline
last\-Message\-Time & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The last time that a message was received on this connection.
         This includes internal system messages (such as Commands and Client\-Rpc calls) and user messages.} \\ \tabuphantomline
client\-Owned\-Objects & public readonly & Hash\-Set{\tt <}\-Network\-Identity\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{A list of the Network\-Identity objects owned by this connection. This list is read-only.
         This includes the player object for the connection - if it has local\-Player\-Autority set, and any objects spawned with local authority or set with Assign\-Local\-Authority.
         This list can be used to validate messages from clients, to ensure that clients are only trying to control objects that they own.} \\ \tabuphantomline
log\-Network\-Messages & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Setting this to true will log the contents of network message to the console.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
address & public abstract & string & \{ get; \} & The IP address / URL / FQDN associated with the connection.
         Can be useful for a game master to do IP Bans etc. \\
player\-Controller & public & Network\-Identity & \{ get internal set \} & Obsolete: use  instead \\
identity & public & Network\-Identity & \{ get; internal set; \} & The Network\-Identity for this connection. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Network\-Connection & internal & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new Network\-Connection with the specified address} \\ \tabuphantomline
Network\-Connection & internal & (int network\-Connection\-Id) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new Network\-Connection with the specified address and connection\-Id} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Dispose & public & void & () & Disposes of this connection, releasing channel buffers that it holds. \\
Disconnect & public abstract & void & () & Disconnects this connection. \\
Register\-Handler & public & void & (short msg\-Type, Network\-Message\-Delegate handler) & Obsolete: Use  or  instead \\
Unregister\-Handler & public & void & (short msg\-Type) & Obsolete: Use  and  instead \\
Send & public & bool & (int msg\-Type, Message\-Base msg, int channel\-Id = Channels.Default\-Reliable) & Obsolete: use  instead \\
Send & public & bool & (T msg, int channel\-Id = Channels.Default\-Reliable) & This sends a network message with a message ID on the connection. This message is sent on channel zero, which by default is the reliable channel. \\
Invoke\-Handler\-No\-Data & public & bool & (int msg\-Type) & Obsolete: Use  instead \\
Invoke\-Handler & public & bool & (T msg, int channel\-Id) & This function invokes the registered handler function for a message.
         Network connections used by the Network\-Client and Network\-Server use this function for handling network messages. \\
Transport\-Receive & internal & void & (Array\-Segment{\tt <}\-byte\-{\tt >} buffer, int channel\-Id) & This function allows custom network connection classes to process data from the network before it is passed to the application. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkConnectionToClient}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Disconnect & public override & void & () & Disconnects this connection. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkConnectionToServer}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Disconnect & public override & void & () & Disconnects this connection. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkDiagnostics}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
message & public readonly & IMessage\-Base & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The message being sent} \\ \tabuphantomline
channel & public readonly & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{channel through which the message was sent} \\ \tabuphantomline
bytes & public readonly & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{how big was the message (does not include transport headers)} \\ \tabuphantomline
count & public readonly & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{How many connections was the message sent to
             If an object has a lot of observers this count could be high} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkIdentity}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
observers & public & Dictionary{\tt <}\-int, Network\-Connection\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The set of network connections (players) that can see this object.
         null until On\-Start\-Server was called. this is necessary for Send\-To* to work properly in server-only mode.} \\ \tabuphantomline
scene\-Id & public & ulong & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{A unique identifier for Network\-Identity objects within a scene.
         This is used for spawning scene objects on clients.} \\ \tabuphantomline
server\-Only & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Flag to make this object only exist when the game is running as a server (or host).} \\ \tabuphantomline
spawned & public static readonly & Dictionary{\tt <}\-uint, Network\-Identity\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{All spawned Network\-Identities by net\-Id. Available on server and client.} \\ \tabuphantomline
client\-Authority\-Callback & public static & Client\-Authority\-Callback & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{A callback that can be populated to be notified when the client-authority state of objects changes.
         Whenever an object is spawned using Spawn\-With\-Client\-Authority, or the client authority status of an object is changed with Assign\-Client\-Authority or Remove\-Client\-Authority, then this callback will be invoked.
         This callback is only invoked on the server.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
is\-Client & public & bool & \{ get; internal set; \} & Returns true if running as a client and this object was spawned by a server. \\
is\-Server & public & bool & \{ get; \} & Returns true if Network\-Server.active and server is not stopped. \\
is\-Local\-Player & public & bool & \{ get; \} & This returns true if this object is the one that represents the player on the local machine.
         This is set when the server has spawned an object for this particular client. \\
has\-Authority & public & bool & \{ get; internal set; \} & This returns true if this object is the authoritative player object on the client.
         This value is determined at runtime. For most objects, authority is held by the server.
         For objects that had their authority set by Assign\-Client\-Authority on the server, this will be true on the client that owns the object. NOT on other clients. \\
net\-Id & public & uint & \{ get; internal set; \} & Unique identifier for this particular object instance, used for tracking objects between networked clients and the server.
         This is a unique identifier for this particular Game\-Object instance. Use it to track Game\-Objects between networked clients and the server. \\
client\-Authority\-Owner & public & Network\-Connection\-To\-Client & \{ get; \} & Obsolete: Use  instead \\
connection\-To\-Server & public & Network\-Connection & \{ get; internal set; \} & The Network\-Connection associated with this Network\-Identity. This is only valid for player objects on a local client. \\
connection\-To\-Client & public & Network\-Connection\-To\-Client & \{ get =\-{\tt >} \_connection\-To\-Client; internal set \} & The Network\-Connection associated with this Network\-Identity. This is valid for player and other owned objects in the server.
         Use it to return details such as the connection\&apos;s identity, IP address and ready status. \\
asset\-Id & public & Guid & \{ get internal set else Debug.Log\-Warning(\$"Set\-Dynamic\-Asset\-Id object \{this.name\} already has an asset\-Id \{m\_Asset\-Id\}, new asset id \{new\-Asset\-Id\-String\}"); \} \} & Unique identifier used to find the source assets when server spawns the on clients. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Scene\-Idenity & public static & Network\-Identity & (ulong id) & Obsolete: Use  instead \\
Get\-Scene\-Identity & public static & Network\-Identity & (ulong id) & Gets the Network\-Identity from the scene\-Ids dictionary with the corresponding id \\
Reset\-Next\-Network\-Id & public static & void & () & Resets next\-Network\-Id = 1 \\
Rebuild\-Observers & public & void & (bool initialize) & This causes the set of players that can see this object to be rebuild. The On\-Rebuild\-Observers callback function will be invoked on each Network\-Behaviour. \\
Assign\-Client\-Authority & public & bool & (Network\-Connection conn) & Assign control of an object to a client via the client's Network\-Connection.
         This causes has\-Authority to be set on the client that owns the object, and Network\-Behaviour.On\-Start\-Authority will be called on that client. This object then will be in the Network\-Connection.client\-Owned\-Objects list for the connection.
         Authority can be removed with Remove\-Client\-Authority. Only one client can own an object at any time. This does not need to be called for player objects, as their authority is setup automatically. \\
Remove\-Client\-Authority & public & bool & (Network\-Connection conn) & Obsolete: Use  instead \\
Remove\-Client\-Authority & public & void & () & Removes ownership for an object.
         This applies to objects that had authority set by Assign\-Client\-Authority, or Network\-Server.Spawn with a Network\-Connection parameter included.
         Authority cannot be removed for player objects. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkManager}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
dont\-Destroy\-On\-Load & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{A flag to control whether the Network\-Manager object is destroyed when the scene changes.
         This should be set if your game has a single Network\-Manager that exists for the lifetime of the process. If there is a Network\-Manager in each scene, then this should not be set.} \\ \tabuphantomline
run\-In\-Background & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Controls whether the program runs when it is in the background.
         This is required when multiple instances of a program using networking are running on the same machine, such as when testing using localhost. But this is not recommended when deploying to mobile platforms.} \\ \tabuphantomline
start\-On\-Headless & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Automatically invoke Start\-Server()
         If the application is a Server Build or run with the -batch\-Mode command line arguement, Start\-Server is automatically invoked.} \\ \tabuphantomline
show\-Debug\-Messages & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Enables verbose debug messages in the console} \\ \tabuphantomline
server\-Tick\-Rate & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Server Update frequency, per second. Use around 60Hz for fast paced games like Counter-Strike to minimize latency. Use around 30Hz for games like Wo\-W to minimize computations. Use around 1-10Hz for slow paced games like EVE.} \\ \tabuphantomline
offline\-Scene & public & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The scene to switch to when offline.
         Setting this makes the Network\-Manager do scene management. This scene will be switched to when a network session is completed - such as a client disconnect, or a server shutdown.} \\ \tabuphantomline
online\-Scene & public & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The scene to switch to when online.
         Setting this makes the Network\-Manager do scene management. This scene will be switched to when a network session is started - such as a client connect, or a server listen.} \\ \tabuphantomline
network\-Address & public & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The network address currently in use.
         For clients, this is the address of the server that is connected to. For servers, this is the local address.} \\ \tabuphantomline
max\-Connections & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The maximum number of concurrent network connections to support.
         This effects the memory usage of the network layer.} \\ \tabuphantomline
player\-Prefab & public & Game\-Object & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The default prefab to be used to create player objects on the server.
         Player objects are created in the default handler for Add\-Player() on the server. Implementing On\-Server\-Add\-Player overrides this behaviour.} \\ \tabuphantomline
auto\-Create\-Player & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{A flag to control whether or not player objects are automatically created on connect, and on scene change.} \\ \tabuphantomline
player\-Spawn\-Method & public & Player\-Spawn\-Method & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The current method of spawning players used by the Network\-Manager.} \\ \tabuphantomline
spawn\-Prefabs & public & List{\tt <}\-Game\-Object\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{List of prefabs that will be registered with the spawning system.
         For each of these prefabs, Client\-Manager.Register\-Prefab() will be automatically invoke.} \\ \tabuphantomline
singleton & public static & Network\-Manager & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Network\-Manager singleton} \\ \tabuphantomline
is\-Network\-Active & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{True if the server or client is started and running
         This is set True in Start\-Server / Start\-Client, and set False in Stop\-Server / Stop\-Client} \\ \tabuphantomline
client\-Loaded\-Scene & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{This is true if the client loaded a new scene when connecting to the server.
         This is set before On\-Client\-Connect is called, so it can be checked there to perform different logic if a scene load occurred.} \\ \tabuphantomline
network\-Scene\-Name & public static & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The name of the current network scene.} \\ \tabuphantomline
start\-Positions & public static & List{\tt <}\-Transform\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{List of transforms populted by Network\-Start\-Position components found in the scene.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
num\-Players & public & int & \{ get; \} & Number of active player objects across all connections on the server.
         This is only valid on the host / server. \\
is\-Headless & public static & bool & \{ get; \} & headless mode detection \\
client & public & Network\-Client & \{ get; \} & Obsolete: Use  directly
         For example, use Network\-Client.Send(message) instead of Network\-Manager.client.Send(message) \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Is\-Client\-Connected & public & bool & () & Obsolete: Use  instead \\
Is\-Headless & public static & bool & () & Obsolete: Use  instead.
         This is a static property now. This method will be removed by summer 2019. \\
On\-Validate & public virtual & void & () & virtual so that inheriting classes' On\-Validate() can call base.On\-Validate() too \\
Awake & public virtual & void & () & virtual so that inheriting classes' Awake() can call base.Awake() too \\
Start & public virtual & void & () & virtual so that inheriting classes' Start() can call base.Start() too \\
Late\-Update & public virtual & void & () & virtual so that inheriting classes' Late\-Update() can call base.Late\-Update() too \\
Start\-Server & public & void & () & This starts a new server.
         This uses the network\-Port property as the listen port. \\
Start\-Client & public & void & () & This starts a network client. It uses the network\-Address and network\-Port properties as the address to connect to.
         This makes the newly created client connect to the server immediately. \\
Start\-Client & public & void & (Uri uri) & This starts a network client. It uses the network\-Address and network\-Port properties as the address to connect to.
         This makes the newly created client connect to the server immediately. \\
Start\-Host & public & void & () & This starts a network "host" - a server and client in the same application.
         The client returned from Start\-Host() is a special "local" client that communicates to the in-process server using a message queue instead of the real network. But in almost all other cases, it can be treated as a normal client. \\
Stop\-Host & public & void & () & This stops both the client and the server that the manager is using. \\
Stop\-Server & public & void & () & Stops the server that the manager is using. \\
Stop\-Client & public & void & () & Stops the client that the manager is using. \\
On\-Application\-Quit & public virtual & void & () & called when quitting the application by closing the window / pressing stop in the editor
         virtual so that inheriting classes' On\-Application\-Quit() can call base.On\-Application\-Quit() too \\
Configure\-Server\-Frame\-Rate & public virtual & void & () & Set the frame rate for a headless server.
         Override if you wish to disable the behavior or set your own tick rate. \\
Shutdown & public static & void & () & This is the only way to clear the singleton, so another instance can be created. \\
On\-Destroy & public virtual & void & () & virtual so that inheriting classes' On\-Destroy() can call base.On\-Destroy() too \\
Server\-Change\-Scene & public virtual & void & (string new\-Scene\-Name) & This causes the server to switch scenes and sets the network\-Scene\-Name.
         Clients that connect to this server will automatically switch to this scene. This is called autmatically if online\-Scene or offline\-Scene are set, but it can be called from user code to switch scenes again while the game is in progress. This automatically sets clients to be not-ready. The clients must call Network\-Client.Ready() again to participate in the new scene. \\
Register\-Start\-Position & public static & void & (Transform start) & Registers the transform of a game object as a player spawn location.
         This is done automatically by Network\-Start\-Position components, but can be done manually from user script code. \\
Un\-Register\-Start\-Position & public static & void & (Transform start) & Unregisters the transform of a game object as a player spawn location.
         This is done automatically by the Network\-Start\-Position component, but can be done manually from user code. \\
On\-Server\-Connect & public virtual & void & (Network\-Connection conn) & Called on the server when a new client connects.
         Unity calls this on the Server when a Client connects to the Server. Use an override to tell the Network\-Manager what to do when a client connects to the server. \\
On\-Server\-Disconnect & public virtual & void & (Network\-Connection conn) & Called on the server when a client disconnects.
         This is called on the Server when a Client disconnects from the Server. Use an override to decide what should happen when a disconnection is detected. \\
On\-Server\-Ready & public virtual & void & (Network\-Connection conn) & Called on the server when a client is ready.
         The default implementation of this function calls Network\-Server.Set\-Client\-Ready() to continue the network setup process. \\
On\-Server\-Add\-Player & public virtual & void & (Network\-Connection conn, Add\-Player\-Message extra\-Message) & Obsolete: Override  instead.
         See Custom Players for details. \\
On\-Server\-Add\-Player & public virtual & void & (Network\-Connection conn) & Called on the server when a client adds a new player with Client\-Scene.Add\-Player.
         The default implementation for this function creates a new player object from the player\-Prefab. \\
Get\-Start\-Position & public & Transform & () & This finds a spawn position based on Network\-Start\-Position objects in the scene.
         This is used by the default implementation of On\-Server\-Add\-Player. \\
On\-Server\-Remove\-Player & public virtual & void & (Network\-Connection conn, Network\-Identity player) & Called on the server when a client removes a player.
         The default implementation of this function destroys the corresponding player object. \\
On\-Server\-Error & public virtual & void & (Network\-Connection conn, int error\-Code) & Called on the server when a network error occurs for a client connection. \\
On\-Server\-Change\-Scene & public virtual & void & (string new\-Scene\-Name) & Called from Server\-Change\-Scene immediately before Scene\-Manager.Load\-Scene\-Async is executed
         This allows server to do work / cleanup / prep before the scene changes. \\
On\-Server\-Scene\-Changed & public virtual & void & (string scene\-Name) & Called on the server when a scene is completed loaded, when the scene load was initiated by the server with Server\-Change\-Scene(). \\
On\-Client\-Connect & public virtual & void & (Network\-Connection conn) & Called on the client when connected to a server.
         The default implementation of this function sets the client as ready and adds a player. Override the function to dictate what happens when the client connects. \\
On\-Client\-Disconnect & public virtual & void & (Network\-Connection conn) & Called on clients when disconnected from a server.
         This is called on the client when it disconnects from the server. Override this function to decide what happens when the client disconnects. \\
On\-Client\-Error & public virtual & void & (Network\-Connection conn, int error\-Code) & Called on clients when a network error occurs. \\
On\-Client\-Not\-Ready & public virtual & void & (Network\-Connection conn) & Called on clients when a servers tells the client it is no longer ready.
         This is commonly used when switching scenes. \\
On\-Client\-Change\-Scene & public virtual & void & (string new\-Scene\-Name) & Obsolete: Use  instead.). \\
On\-Client\-Change\-Scene & public virtual & void & (string new\-Scene\-Name, Scene\-Operation scene\-Operation) & Obsolete: Use  instead.). \\
On\-Client\-Change\-Scene & public virtual & void & (string new\-Scene\-Name, Scene\-Operation scene\-Operation, bool custom\-Handling) & Called from Client\-Change\-Scene immediately before Scene\-Manager.Load\-Scene\-Async is executed
         This allows client to do work / cleanup / prep before the scene changes. \\
On\-Client\-Scene\-Changed & public virtual & void & (Network\-Connection conn) & Called on clients when a scene has completed loaded, when the scene load was initiated by the server.
         Scene changes can cause player objects to be destroyed. The default implementation of On\-Client\-Scene\-Changed in the Network\-Manager is to add a player object for the connection if no player object exists. \\
On\-Start\-Host & public virtual & void & () & This is invoked when a host is started.
         Start\-Host has multiple signatures, but they all cause this hook to be called. \\
On\-Start\-Server & public virtual & void & () & This is invoked when a server is started - including when a host is started.
         Start\-Server has multiple signatures, but they all cause this hook to be called. \\
On\-Start\-Client & public virtual & void & (Network\-Client client) & Obsolete: Use  instead of On\-Start\-Client(Network\-Client client).
         All Network\-Client functions are static now, so you can use Network\-Client.Send(message) instead of client.Send(message) directly now. \\
On\-Start\-Client & public virtual & void & () & This is invoked when the client is started. \\
On\-Stop\-Server & public virtual & void & () & This is called when a server is stopped - including when a host is stopped. \\
On\-Stop\-Client & public virtual & void & () & This is called when a client is stopped. \\
On\-Stop\-Host & public virtual & void & () & This is called when a host is stopped. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkManagerHUD}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
show\-GUI & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Whether to show the default control HUD at runtime.} \\ \tabuphantomline
offset\-X & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The horizontal offset in pixels to draw the HUD runtime GUI at.} \\ \tabuphantomline
offset\-Y & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The vertical offset in pixels to draw the HUD runtime GUI at.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkServer}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
connections & public static & Dictionary{\tt <}\-int, Network\-Connection\-To\-Client\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{A list of local connections on the server.} \\ \tabuphantomline
handlers & static & Dictionary{\tt <}\-int, Network\-Message\-Delegate\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Dictionary of the message handlers registered with the server.
         The key to the dictionary is the message Id.} \\ \tabuphantomline
dont\-Listen & public static & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{If you enable this, the server will not listen for incoming connections on the regular network port.
         This can be used if the game is running in host mode and does not want external players to be able to connect - making it like a single-player game. Also this can be useful when using Add\-External\-Connection().} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
local\-Connection & public static & Network\-Connection\-To\-Client & \{ get; private set; \} & The connection to the host mode client (if any). \\
local\-Client\-Active & public static & bool & \{ get; \} & True is a local client is currently active on the server.
         This will be true for "Hosts" on hosted server games. \\
active & public static & bool & \{ get; private set; \} & Checks if the server has been started.
         This will be true after Network\-Server.Listen() has been called. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Reset & public static & void & () & Reset the Network\-Server singleton. \\
Shutdown & public static & void & () & This shuts down the server and disconnects all clients. \\
Listen & public static & void & (int max\-Conns) & Start the server, setting the maximum number of connections. \\
Add\-Connection & public static & bool & (Network\-Connection\-To\-Client conn) & This accepts a network connection and adds it to the server.
         This connection will use the callbacks registered with the server. \\
Remove\-Connection & public static & bool & (int connection\-Id) & This removes an external connection added with Add\-External\-Connection(). \\
Send\-To\-All & public static & bool & (int msg\-Type, Message\-Base msg, int channel\-Id = Channels.Default\-Reliable) & Obsolete: Use  instead. \\
Send\-To\-All & public static & bool & (T msg, int channel\-Id = Channels.Default\-Reliable) & Send a message structure with the given type number to all connected clients.
         This applies to clients that are ready and not-ready. \\
Send\-To\-Ready & public static & bool & (Network\-Identity identity, short msg\-Type, Message\-Base msg, int channel\-Id = Channels.Default\-Reliable) & Obsolete: Use  instead. \\
Send\-To\-Ready & public static & bool & (Network\-Identity identity, T msg, bool include\-Owner = true, int channel\-Id = Channels.Default\-Reliable) & Send a message structure with the given type number to only clients which are ready.
         See Networking.Network\-Client.Ready. \\
Send\-To\-Ready & public static & bool & (Network\-Identity identity, T msg, int channel\-Id = Channels.Default\-Reliable) & Send a message structure with the given type number to only clients which are ready.
         See Networking.Network\-Client.Ready. \\
Disconnect\-All & public static & void & () & Disconnect all currently connected clients, including the local connection.
         This can only be called on the server. Clients will receive the Disconnect message. \\
Disconnect\-All\-Connections & public static & void & () & Disconnect all currently connected clients except the local connection.
         This can only be called on the server. Clients will receive the Disconnect message. \\
Register\-Handler & public static & void & (int msg\-Type, Network\-Message\-Delegate handler) & Obsolete: Use  instead. \\
Register\-Handler & public static & void & (Msg\-Type msg\-Type, Network\-Message\-Delegate handler) & Obsolete: Use  instead. \\
Register\-Handler & public static & void & (Action{\tt <}\-Network\-Connection, T\-{\tt >} handler, bool require\-Authentication = true) & Register a handler for a particular message type.
         There are several system message types which you can add handlers for. You can also add your own message types. \\
Register\-Handler & public static & void & (Action{\tt <}\-T\-{\tt >} handler, bool require\-Authentication = true) & Register a handler for a particular message type.
         There are several system message types which you can add handlers for. You can also add your own message types. \\
Unregister\-Handler & public static & void & (int msg\-Type) & Obsolete: Use  instead. \\
Unregister\-Handler & public static & void & (Msg\-Type msg\-Type) & Obsolete: Use  instead. \\
Unregister\-Handler & public static & void & () & Unregisters a handler for a particular message type. \\
Clear\-Handlers & public static & void & () & Clear all registered callback handlers. \\
Send\-To\-Client & public static & void & (int connection\-Id, int msg\-Type, Message\-Base msg) & Obsolete: Use  instead. \\
Send\-To\-Client & public static & void & (int connection\-Id, T msg) & Obsolete: Use  instead. \\
Send\-To\-Client\-Of\-Player & public static & void & (Network\-Identity identity, int msg\-Type, Message\-Base msg) & Obsolete: Use  instead. \\
Send\-To\-Client\-Of\-Player & public static & void & (Network\-Identity identity, T msg, int channel\-Id = Channels.Default\-Reliable) & send this message to the player only \\
Replace\-Player\-For\-Connection & public static & bool & (Network\-Connection conn, Game\-Object player, Guid asset\-Id, bool keep\-Authority = false) & This replaces the player object for a connection with a different player object. The old player object is not destroyed.
         If a connection already has a player object, this can be used to replace that object with a different player object. This does NOT change the ready state of the connection, so it can safely be used while changing scenes. \\
Replace\-Player\-For\-Connection & public static & bool & (Network\-Connection conn, Game\-Object player, bool keep\-Authority = false) & This replaces the player object for a connection with a different player object. The old player object is not destroyed.
         If a connection already has a player object, this can be used to replace that object with a different player object. This does NOT change the ready state of the connection, so it can safely be used while changing scenes. \\
Add\-Player\-For\-Connection & public static & bool & (Network\-Connection conn, Game\-Object player, Guid asset\-Id) & When an Add\-Player message handler has received a request from a player, the server calls this to associate the player object with the connection.
         When a player is added for a connection, the client for that connection is made ready automatically. The player object is automatically spawned, so you do not need to call Network\-Server.Spawn for that object. This function is used for "adding" a player, not for "replacing" the player on a connection. If there is already a player on this player\-Controller\-Id for this connection, this will fail. \\
Add\-Player\-For\-Connection & public static & bool & (Network\-Connection conn, Game\-Object player) & When an Add\-Player message handler has received a request from a player, the server calls this to associate the player object with the connection.
         When a player is added for a connection, the client for that connection is made ready automatically. The player object is automatically spawned, so you do not need to call Network\-Server.Spawn for that object. This function is used for "adding" a player, not for "replacing" the player on a connection. If there is already a player on this player\-Controller\-Id for this connection, this will fail. \\
Set\-Client\-Ready & public static & void & (Network\-Connection conn) & Sets the client to be ready.
         When a client has signaled that it is ready, this method tells the server that the client is ready to receive spawned objects and state synchronization updates. This is usually called in a handler for the SYSTEM\_READY message. If there is not specific action a game needs to take for this message, relying on the default ready handler function is probably fine, so this call wont be needed. \\
Set\-All\-Clients\-Not\-Ready & public static & void & () & Marks all connected clients as no longer ready.
         All clients will no longer be sent state synchronization updates. The player's clients can call Client\-Manager.Ready() again to re-enter the ready state. This is useful when switching scenes. \\
Set\-Client\-Not\-Ready & public static & void & (Network\-Connection conn) & Sets the client of the connection to be not-ready.
         Clients that are not ready do not receive spawned objects or state synchronization updates. They client can be made ready again by calling Set\-Client\-Ready(). \\
Destroy\-Player\-For\-Connection & public static & void & (Network\-Connection conn) & This destroys all the player objects associated with a Network\-Connections on a server.
         This is used when a client disconnects, to remove the players for that client. This also destroys non-player objects that have client authority set for this connection. \\
Spawn & public static & void & (Game\-Object obj, Network\-Connection owner\-Connection = null) & Spawn the given game object on all clients which are ready.
         This will cause a new object to be instantiated from the registered prefab, or from a custom spawn function. \\
Spawn\-With\-Client\-Authority & public static & bool & (Game\-Object obj, Game\-Object player) & Obsolete: Use  instead. \\
Spawn & public static & void & (Game\-Object obj, Game\-Object player) & This spawns an object like Network\-Server.Spawn() but also assigns Client Authority to the specified client.
         This is the same as calling Network\-Identity.Assign\-Client\-Authority on the spawned object. \\
Spawn\-With\-Client\-Authority & public static & bool & (Game\-Object obj, Network\-Connection owner\-Connection) & Use  instead \\
Spawn\-With\-Client\-Authority & public static & bool & (Game\-Object obj, Guid asset\-Id, Network\-Connection owner\-Connection) & Use  instead \\
Spawn & public static & void & (Game\-Object obj, Guid asset\-Id, Network\-Connection owner\-Connection = null) & This spawns an object like Network\-Server.Spawn() but also assigns Client Authority to the specified client.
         This is the same as calling Network\-Identity.Assign\-Client\-Authority on the spawned object. \\
Destroy & public static & void & (Game\-Object obj) & Destroys this object and corresponding objects on all clients.
         In some cases it is useful to remove an object but not delete it on the server. For that, use Network\-Server.Un\-Spawn() instead of Network\-Server.Destroy(). \\
Un\-Spawn & public static & void & (Game\-Object obj) & This takes an object that has been spawned and un-spawns it.
         The object will be removed from clients that it was spawned on, or the custom spawn handler function on the client will be called for the object.
         Unlike when calling Network\-Server.Destroy(), on the server the object will NOT be destroyed. This allows the server to re-use the object, even spawn it again later. \\
Find\-Local\-Object & public static & Game\-Object & (uint net\-Id) & Obsolete: Use  instead. \\
Spawn\-Objects & public static & bool & () & This causes Network\-Identity objects in a scene to be spawned on a server.
         Network\-Identity objects in a scene are disabled by default. Calling Spawn\-Objects() causes these scene objects to be enabled and spawned. It is like calling Network\-Server.Spawn() for each of them. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkTime}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Ping\-Frequency & public static & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{how often are we sending ping messages
         used to calculate network time and RTT} \\ \tabuphantomline
Ping\-Window\-Size & public static & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{average out the last few results from Ping} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
time & public static & double & \{ get; \} & The time in seconds since the server started. \\
time\-Var & public static & double & \{ get; \} & Measurement of the variance of time.
         The higher the variance, the less accurate the time is \\
time\-Sd & public static & double & \{ get; \} & standard deviation of time.
         The higher the variance, the less accurate the time is \\
offset & public static & double & \{ get; \} & Clock difference in seconds between the client and the server \\
rtt & public static & double & \{ get; \} & how long in seconds does it take for a message to go
         to the server and come back \\
rtt\-Var & public static & double & \{ get; \} & measure variance of rtt
         the higher the number,  the less accurate rtt is \\
rtt\-Sd & public static & double & \{ get; \} & Measure the standard deviation of rtt
         the higher the number,  the less accurate rtt is \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Argument}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
NO\_SYNTAX\_ERRORS & public const & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SYNTAX\_ERROR\_OR\_STATUS\_UNKNOWN & public const & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ARGUMENT\_INITIAL\_VALUE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NOT\_FOUND & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
FREE\_ARGUMENT & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
DEPENDENT\_ARGUMENT & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
RECURSIVE\_ARGUMENT & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TYPE\_ID & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BODY\_RUNTIME & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BODY\_EXTENDED & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
argument\-Body\-Type & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
argument\-Extension & private & Argument\-Extension & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
description & private & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
argument\-Expression & internal & Expression & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
argument\-Name & private & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
argument\-Type & internal & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
argument\-Value & internal & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
n & protected & Argument & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Argument & public & (String argument\-Definition\-String, params Primitive\-Element[] elements) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Argument & public & (String argument\-Definition\-String, bool force\-Dependent, params Primitive\-Element[] elements) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Argument & public & (String argument\-Name, double argument\-Value) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Argument & public & (String argument\-Name, Argument\-Extension argument\-Extension) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Argument & public & (String argument\-Name, String argument\-Expression\-String, params Primitive\-Element[] elements) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
set\-Description & public & void & (String description) &  \\
get\-Description & public & String & () &  \\
set\-Verbose\-Mode & public & void & () &  \\
set\-Silent\-Mode & public & void & () &  \\
get\-Verbose\-Mode & public & bool & () &  \\
get\-Recursive\-Mode & public & bool & () &  \\
get\-Computing\-Time & public & double & () &  \\
set\-Argument\-Name & public & void & (String argument\-Name) &  \\
set\-Argument\-Expression\-String & public & void & (String argument\-Expression\-String) &  \\
get\-Argument\-Name & public & String & () &  \\
get\-Argument\-Expression\-String & public & String & () &  \\
get\-Argument\-Type & public & int & () &  \\
set\-Argument\-Value & public & void & (double argument\-Value) &  \\
get\-Argument\-Body\-Type & public & int & () &  \\
check\-Syntax & public & bool & () &  \\
get\-Error\-Message & public & String & () &  \\
get\-Argument\-Value & public & double & () &  \\
add\-Definitions & public & void & (params Primitive\-Element[] elements) &  \\
remove\-Definitions & public & void & (params Primitive\-Element[] elements) &  \\
add\-Arguments & public & void & (params Argument[] arguments) &  \\
define\-Arguments & public & void & (params String[] arguments\-Names) &  \\
define\-Argument & public & void & (String argument\-Name, double argument\-Value) &  \\
get\-Argument\-Index & public & int & (String argument\-Name) &  \\
get\-Argument & public & Argument & (String argument\-Name) &  \\
get\-Argument & public & Argument & (int argument\-Index) &  \\
get\-Arguments\-Number & public & int & () &  \\
remove\-Arguments & public & void & (params String[] arguments\-Names) &  \\
remove\-Arguments & public & void & (params Argument[] arguments) &  \\
remove\-All\-Arguments & public & void & () &  \\
add\-Constants & public & void & (params Constant[] constants) &  \\
define\-Constant & public & void & (String constant\-Name, double constant\-Value) &  \\
get\-Constant\-Index & public & int & (String constant\-Name) &  \\
get\-Constant & public & Constant & (String constant\-Name) &  \\
get\-Constant & public & Constant & (int constant\-Index) &  \\
get\-Constants\-Number & public & int & () &  \\
remove\-Constants & public & void & (params String[] constants\-Names) &  \\
remove\-Constants & public & void & (params Constant[] constants) &  \\
remove\-All\-Constants & public & void & () &  \\
add\-Functions & public & void & (params Function[] functions) &  \\
define\-Function & public & void & (String function\-Name, String  function\-Expression\-String,
				params String[] arguments\-Names) &  \\
get\-Function\-Index & public & int & (String function\-Name) &  \\
get\-Function & public & Function & (String function\-Name) &  \\
get\-Function & public & Function & (int function\-Index) &  \\
get\-Functions\-Number & public & int & () &  \\
remove\-Functions & public & void & (params String[] functions\-Names) &  \\
remove\-Functions & public & void & (params Function[] functions) &  \\
remove\-All\-Functions & public & void & () &  \\
add\-Related\-Expression & internal & void & (Expression expression) &  \\
remove\-Related\-Expression & internal & void & (Expression expression) &  \\
set\-Expression\-Modified\-Flags & internal & void & () &  \\
clone & public & Argument & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{<NotFound>}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Owner\-Script &  & Script & \{ get; \} & Gets the script owning this resource. \\
Name &  & string & \{ get; \} & Gets the name of the descriptor (usually, the name of the type described). \\
Type &  & Type & \{ get; \} & Gets the type this descriptor refers to \\
Name &  & string & \{ get; \} & Gets the name of the descriptor (usually, the name of the type described). \\
Type &  & Type & \{ get; \} & Gets the type this descriptor refers to \\
Member\-Type &  & User\-Data\-Member\-Type & \{ get; \} & Gets the type of the member. \\
action\-Bottom\-Row1 &  & IController\-Template\-Button & \{ get; \} & The "Action Bottom Row 1" element. \\
a &  & IController\-Template\-Button & \{ get; \} & The "Action Bottom Row 1" element.
         This is an alias for . \\
action\-Bottom\-Row2 &  & IController\-Template\-Button & \{ get; \} & The "Action Bottom Row 2" element. \\
b &  & IController\-Template\-Button & \{ get; \} & The "Action Bottom Row 2" element.
         This is an alias for . \\
action\-Bottom\-Row3 &  & IController\-Template\-Button & \{ get; \} & The "Action Bottom Row 3" element. \\
c &  & IController\-Template\-Button & \{ get; \} & The "Action Bottom Row 3" element.
         This is an alias for . \\
action\-Top\-Row1 &  & IController\-Template\-Button & \{ get; \} & The "Action Top Row 1" element. \\
x &  & IController\-Template\-Button & \{ get; \} & The "Action Top Row 1" element.
         This is an alias for . \\
action\-Top\-Row2 &  & IController\-Template\-Button & \{ get; \} & The "Action Top Row 2" element. \\
y &  & IController\-Template\-Button & \{ get; \} & The "Action Top Row 2" element.
         This is an alias for . \\
action\-Top\-Row3 &  & IController\-Template\-Button & \{ get; \} & The "Action Top Row 3" element. \\
z &  & IController\-Template\-Button & \{ get; \} & The "Action Top Row 3" element.
         This is an alias for . \\
left\-Shoulder1 &  & IController\-Template\-Button & \{ get; \} & The "Left Shoulder 1" element. \\
left\-Bumper &  & IController\-Template\-Button & \{ get; \} & The "Left Shoulder 1" element.
         This is an alias for . \\
left\-Shoulder2 &  & IController\-Template\-Axis & \{ get; \} & The "Left Shoulder 2" element. \\
left\-Trigger &  & IController\-Template\-Axis & \{ get; \} & The "Left Shoulder 2" element.
         This is an alias for . \\
right\-Shoulder1 &  & IController\-Template\-Button & \{ get; \} & The "Right Shoulder 1" element. \\
right\-Bumper &  & IController\-Template\-Button & \{ get; \} & The "Right Shoulder 1" element.
         This is an alias for . \\
right\-Shoulder2 &  & IController\-Template\-Axis & \{ get; \} & The "Right Shoulder 2" element. \\
right\-Trigger &  & IController\-Template\-Axis & \{ get; \} & The "Right Shoulder 2" element.
         This is an alias for . \\
center1 &  & IController\-Template\-Button & \{ get; \} & The "Center 1" element. \\
back &  & IController\-Template\-Button & \{ get; \} & The "Center 1" element.
         This is an alias for . \\
center2 &  & IController\-Template\-Button & \{ get; \} & The "Center 2" element. \\
start &  & IController\-Template\-Button & \{ get; \} & The "Center 2" element.
         This is an alias for . \\
center3 &  & IController\-Template\-Button & \{ get; \} & The "Center 3" element. \\
guide &  & IController\-Template\-Button & \{ get; \} & The "Center 3" element.
         This is an alias for . \\
left\-Stick &  & IController\-Template\-Thumb\-Stick & \{ get; \} & The "Left Stick" element. \\
right\-Stick &  & IController\-Template\-Thumb\-Stick & \{ get; \} & The "Right Stick" element. \\
d\-Pad &  & IController\-Template\-DPad & \{ get; \} & The "D-Pad" element. \\
wheel &  & IController\-Template\-Axis & \{ get; \} & The "Wheel" element. \\
accelerator &  & IController\-Template\-Axis & \{ get; \} & The "Accelerator" element. \\
brake &  & IController\-Template\-Axis & \{ get; \} & The "Brake" element. \\
clutch &  & IController\-Template\-Axis & \{ get; \} & The "Clutch" element. \\
shift\-Down &  & IController\-Template\-Button & \{ get; \} & The "Shift Down" element. \\
shift\-Up &  & IController\-Template\-Button & \{ get; \} & The "Shift Up" element. \\
wheel\-Button1 &  & IController\-Template\-Button & \{ get; \} & The "Wheel Button 1" element. \\
wheel\-Button2 &  & IController\-Template\-Button & \{ get; \} & The "Wheel Button 2" element. \\
wheel\-Button3 &  & IController\-Template\-Button & \{ get; \} & The "Wheel Button 3" element. \\
wheel\-Button4 &  & IController\-Template\-Button & \{ get; \} & The "Wheel Button 4" element. \\
wheel\-Button5 &  & IController\-Template\-Button & \{ get; \} & The "Wheel Button 5" element. \\
wheel\-Button6 &  & IController\-Template\-Button & \{ get; \} & The "Wheel Button 6" element. \\
wheel\-Button7 &  & IController\-Template\-Button & \{ get; \} & The "Wheel Button 7" element. \\
wheel\-Button8 &  & IController\-Template\-Button & \{ get; \} & The "Wheel Button 8" element. \\
wheel\-Button9 &  & IController\-Template\-Button & \{ get; \} & The "Wheel Button 9" element. \\
wheel\-Button10 &  & IController\-Template\-Button & \{ get; \} & The "Wheel Button 10" element. \\
console\-Button1 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 1" element. \\
console\-Button2 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 2" element. \\
console\-Button3 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 3" element. \\
console\-Button4 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 4" element. \\
console\-Button5 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 5" element. \\
console\-Button6 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 6" element. \\
console\-Button7 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 7" element. \\
console\-Button8 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 8" element. \\
console\-Button9 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 9" element. \\
console\-Button10 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 10" element. \\
shifter1 &  & IController\-Template\-Button & \{ get; \} & The "Shifter 1" element. \\
shifter2 &  & IController\-Template\-Button & \{ get; \} & The "Shifter 2" element. \\
shifter3 &  & IController\-Template\-Button & \{ get; \} & The "Shifter 3" element. \\
shifter4 &  & IController\-Template\-Button & \{ get; \} & The "Shifter 4" element. \\
shifter5 &  & IController\-Template\-Button & \{ get; \} & The "Shifter 5" element. \\
shifter6 &  & IController\-Template\-Button & \{ get; \} & The "Shifter 6" element. \\
shifter7 &  & IController\-Template\-Button & \{ get; \} & The "Shifter 7" element. \\
shifter8 &  & IController\-Template\-Button & \{ get; \} & The "Shifter 8" element. \\
shifter9 &  & IController\-Template\-Button & \{ get; \} & The "Shifter 9" element. \\
shifter10 &  & IController\-Template\-Button & \{ get; \} & The "Shifter 10" element. \\
reverse\-Gear &  & IController\-Template\-Button & \{ get; \} & The "Reverse Gear" element. \\
select &  & IController\-Template\-Button & \{ get; \} & The "Select" element. \\
start &  & IController\-Template\-Button & \{ get; \} & The "Start" element. \\
system\-Button &  & IController\-Template\-Button & \{ get; \} & The "System Button" element. \\
horn &  & IController\-Template\-Button & \{ get; \} & The "Horn" element. \\
d\-Pad &  & IController\-Template\-DPad & \{ get; \} & The "D-Pad" element. \\
stick\-Trigger &  & IController\-Template\-Button & \{ get; \} & The "Stick Trigger" element. \\
stick\-Trigger\-Stage2 &  & IController\-Template\-Button & \{ get; \} & The "Stick Trigger (Stage 2)" element. \\
stick\-Pinky\-Button &  & IController\-Template\-Button & \{ get; \} & The "Stick Pinky Button" element. \\
stick\-Pinky\-Trigger &  & IController\-Template\-Button & \{ get; \} & The "Stick Pinky Trigger" element. \\
stick\-Button1 &  & IController\-Template\-Button & \{ get; \} & The "Stick Button 1" element. \\
stick\-Button2 &  & IController\-Template\-Button & \{ get; \} & The "Stick Button 2" element. \\
stick\-Button3 &  & IController\-Template\-Button & \{ get; \} & The "Stick Button 3" element. \\
stick\-Button4 &  & IController\-Template\-Button & \{ get; \} & The "Stick Button 4" element. \\
stick\-Button5 &  & IController\-Template\-Button & \{ get; \} & The "Stick Button 5" element. \\
stick\-Button6 &  & IController\-Template\-Button & \{ get; \} & The "Stick Button 6" element. \\
stick\-Button7 &  & IController\-Template\-Button & \{ get; \} & The "Stick Button 7" element. \\
stick\-Button8 &  & IController\-Template\-Button & \{ get; \} & The "Stick Button 8" element. \\
stick\-Button9 &  & IController\-Template\-Button & \{ get; \} & The "Stick Button 9" element. \\
stick\-Button10 &  & IController\-Template\-Button & \{ get; \} & The "Stick Button 10" element. \\
stick\-Base\-Button1 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 1" element. \\
stick\-Base\-Button2 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 2" element. \\
stick\-Base\-Button3 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 3" element. \\
stick\-Base\-Button4 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 4" element. \\
stick\-Base\-Button5 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 5" element. \\
stick\-Base\-Button6 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 6" element. \\
stick\-Base\-Button7 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 7" element. \\
stick\-Base\-Button8 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 8" element. \\
stick\-Base\-Button9 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 9" element. \\
stick\-Base\-Button10 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 10" element. \\
stick\-Base\-Button11 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 11" element. \\
stick\-Base\-Button12 &  & IController\-Template\-Button & \{ get; \} & The "Stick Base Button 12" element. \\
mode1 &  & IController\-Template\-Button & \{ get; \} & The "Mode 1" element. \\
mode2 &  & IController\-Template\-Button & \{ get; \} & The "Mode 2" element. \\
mode3 &  & IController\-Template\-Button & \{ get; \} & The "Mode 3" element. \\
throttle\-Button1 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Button 1" element. \\
throttle\-Button2 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Button 2" element. \\
throttle\-Button3 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Button 3" element. \\
throttle\-Button4 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Button 4" element. \\
throttle\-Button5 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Button 5" element. \\
throttle\-Button6 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Button 6" element. \\
throttle\-Button7 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Button 7" element. \\
throttle\-Button8 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Button 8" element. \\
throttle\-Button9 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Button 9" element. \\
throttle\-Button10 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Button 10" element. \\
throttle\-Base\-Button1 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 1" element. \\
throttle\-Base\-Button2 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 2" element. \\
throttle\-Base\-Button3 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 3" element. \\
throttle\-Base\-Button4 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 4" element. \\
throttle\-Base\-Button5 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 5" element. \\
throttle\-Base\-Button6 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 6" element. \\
throttle\-Base\-Button7 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 7" element. \\
throttle\-Base\-Button8 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 8" element. \\
throttle\-Base\-Button9 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 9" element. \\
throttle\-Base\-Button10 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 10" element. \\
throttle\-Base\-Button11 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 11" element. \\
throttle\-Base\-Button12 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 12" element. \\
throttle\-Base\-Button13 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 13" element. \\
throttle\-Base\-Button14 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 14" element. \\
throttle\-Base\-Button15 &  & IController\-Template\-Button & \{ get; \} & The "Throttle Base Button 15" element. \\
throttle\-Slider1 &  & IController\-Template\-Axis & \{ get; \} & The "Throttle Slider 1" element. \\
throttle\-Slider2 &  & IController\-Template\-Axis & \{ get; \} & The "Throttle Slider 2" element. \\
throttle\-Slider3 &  & IController\-Template\-Axis & \{ get; \} & The "Throttle Slider 3" element. \\
throttle\-Slider4 &  & IController\-Template\-Axis & \{ get; \} & The "Throttle Slider 4" element. \\
throttle\-Dial1 &  & IController\-Template\-Axis & \{ get; \} & The "Throttle Dial 1" element. \\
throttle\-Dial2 &  & IController\-Template\-Axis & \{ get; \} & The "Throttle Dial 2" element. \\
throttle\-Dial3 &  & IController\-Template\-Axis & \{ get; \} & The "Throttle Dial 3" element. \\
throttle\-Dial4 &  & IController\-Template\-Axis & \{ get; \} & The "Throttle Dial 4" element. \\
throttle\-Wheel1Forward &  & IController\-Template\-Button & \{ get; \} & The "Throttle Wheel 1 Forward" element. \\
throttle\-Wheel1Back &  & IController\-Template\-Button & \{ get; \} & The "Throttle Wheel 1 Back" element. \\
throttle\-Wheel1Press &  & IController\-Template\-Button & \{ get; \} & The "Throttle Wheel 1 Press" element. \\
throttle\-Wheel2Forward &  & IController\-Template\-Button & \{ get; \} & The "Throttle Wheel 2 Forward" element. \\
throttle\-Wheel2Back &  & IController\-Template\-Button & \{ get; \} & The "Throttle Wheel 2 Back" element. \\
throttle\-Wheel2Press &  & IController\-Template\-Button & \{ get; \} & The "Throttle Wheel 2 Press" element. \\
throttle\-Wheel3Forward &  & IController\-Template\-Button & \{ get; \} & The "Throttle Wheel 3 Forward" element. \\
throttle\-Wheel3Back &  & IController\-Template\-Button & \{ get; \} & The "Throttle Wheel 3 Back" element. \\
throttle\-Wheel3Press &  & IController\-Template\-Button & \{ get; \} & The "Throttle Wheel 3 Press" element. \\
left\-Pedal &  & IController\-Template\-Axis & \{ get; \} & The "Left Pedal" element. \\
right\-Pedal &  & IController\-Template\-Axis & \{ get; \} & The "Right Pedal" element. \\
slide\-Pedals &  & IController\-Template\-Axis & \{ get; \} & The "Slide Pedals" element. \\
stick &  & IController\-Template\-Stick & \{ get; \} & The "Stick" element. \\
stick\-Mini\-Stick1 &  & IController\-Template\-Thumb\-Stick & \{ get; \} & The "Stick Mini Stick 1" element. \\
stick\-Mini\-Stick2 &  & IController\-Template\-Thumb\-Stick & \{ get; \} & The "Stick Mini Stick 2" element. \\
stick\-Hat1 &  & IController\-Template\-Hat & \{ get; \} & The "Stick Hat 1" element. \\
stick\-Hat2 &  & IController\-Template\-Hat & \{ get; \} & The "Stick Hat 2" element. \\
stick\-Hat3 &  & IController\-Template\-Hat & \{ get; \} & The "Stick Hat 3" element. \\
stick\-Hat4 &  & IController\-Template\-Hat & \{ get; \} & The "Stick Hat 4" element. \\
throttle1 &  & IController\-Template\-Throttle & \{ get; \} & The "Throttle 1" element. \\
throttle2 &  & IController\-Template\-Throttle & \{ get; \} & The "Throttle 2" element. \\
throttle\-Mini\-Stick &  & IController\-Template\-Thumb\-Stick & \{ get; \} & The "Throttle Mini Stick" element. \\
throttle\-Hat1 &  & IController\-Template\-Hat & \{ get; \} & The "Throttle Hat 1" element. \\
throttle\-Hat2 &  & IController\-Template\-Hat & \{ get; \} & The "Throttle Hat 2" element. \\
throttle\-Hat3 &  & IController\-Template\-Hat & \{ get; \} & The "Throttle Hat 3" element. \\
throttle\-Hat4 &  & IController\-Template\-Hat & \{ get; \} & The "Throttle Hat 4" element. \\
left\-Paddle &  & IController\-Template\-Button & \{ get; \} & The "Left Paddle" element. \\
right\-Paddle &  & IController\-Template\-Button & \{ get; \} & The "Right Paddle" element. \\
left\-Grip\-Button1 &  & IController\-Template\-Button & \{ get; \} & The "Left Grip Button 1" element. \\
left\-Grip\-Button2 &  & IController\-Template\-Button & \{ get; \} & The "Left Grip Button 2" element. \\
left\-Grip\-Button3 &  & IController\-Template\-Button & \{ get; \} & The "Left Grip Button 3" element. \\
left\-Grip\-Button4 &  & IController\-Template\-Button & \{ get; \} & The "Left Grip Button 4" element. \\
left\-Grip\-Button5 &  & IController\-Template\-Button & \{ get; \} & The "Left Grip Button 5" element. \\
left\-Grip\-Button6 &  & IController\-Template\-Button & \{ get; \} & The "Left Grip Button 6" element. \\
right\-Grip\-Button1 &  & IController\-Template\-Button & \{ get; \} & The "Right Grip Button 1" element. \\
right\-Grip\-Button2 &  & IController\-Template\-Button & \{ get; \} & The "Right Grip Button 2" element. \\
right\-Grip\-Button3 &  & IController\-Template\-Button & \{ get; \} & The "Right Grip Button 3" element. \\
right\-Grip\-Button4 &  & IController\-Template\-Button & \{ get; \} & The "Right Grip Button 4" element. \\
right\-Grip\-Button5 &  & IController\-Template\-Button & \{ get; \} & The "Right Grip Button 5" element. \\
right\-Grip\-Button6 &  & IController\-Template\-Button & \{ get; \} & The "Right Grip Button 6" element. \\
center\-Button1 &  & IController\-Template\-Button & \{ get; \} & The "Center Button 1" element. \\
center\-Button2 &  & IController\-Template\-Button & \{ get; \} & The "Center Button 2" element. \\
center\-Button3 &  & IController\-Template\-Button & \{ get; \} & The "Center Button 3" element. \\
center\-Button4 &  & IController\-Template\-Button & \{ get; \} & The "Center Button 4" element. \\
center\-Button5 &  & IController\-Template\-Button & \{ get; \} & The "Center Button 5" element. \\
center\-Button6 &  & IController\-Template\-Button & \{ get; \} & The "Center Button 6" element. \\
center\-Button7 &  & IController\-Template\-Button & \{ get; \} & The "Center Button 7" element. \\
center\-Button8 &  & IController\-Template\-Button & \{ get; \} & The "Center Button 8" element. \\
wheel1Up &  & IController\-Template\-Button & \{ get; \} & The "Wheel 1 Up" element. \\
wheel1Down &  & IController\-Template\-Button & \{ get; \} & The "Wheel 1 Down" element. \\
wheel1Press &  & IController\-Template\-Button & \{ get; \} & The "Wheel 1 Press" element. \\
wheel2Up &  & IController\-Template\-Button & \{ get; \} & The "Wheel 2 Up" element. \\
wheel2Down &  & IController\-Template\-Button & \{ get; \} & The "Wheel 2 Down" element. \\
wheel2Press &  & IController\-Template\-Button & \{ get; \} & The "Wheel 2 Press" element. \\
console\-Button1 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 1" element. \\
console\-Button2 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 2" element. \\
console\-Button3 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 3" element. \\
console\-Button4 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 4" element. \\
console\-Button5 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 5" element. \\
console\-Button6 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 6" element. \\
console\-Button7 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 7" element. \\
console\-Button8 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 8" element. \\
console\-Button9 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 9" element. \\
console\-Button10 &  & IController\-Template\-Button & \{ get; \} & The "Console Button 10" element. \\
mode1 &  & IController\-Template\-Button & \{ get; \} & The "Mode 1" element. \\
mode2 &  & IController\-Template\-Button & \{ get; \} & The "Mode 2" element. \\
mode3 &  & IController\-Template\-Button & \{ get; \} & The "Mode 3" element. \\
yoke &  & IController\-Template\-Yoke & \{ get; \} & The "Yoke" element. \\
lever1 &  & IController\-Template\-Throttle & \{ get; \} & The "Lever 1" element. \\
lever2 &  & IController\-Template\-Throttle & \{ get; \} & The "Lever 2" element. \\
lever3 &  & IController\-Template\-Throttle & \{ get; \} & The "Lever 3" element. \\
lever4 &  & IController\-Template\-Throttle & \{ get; \} & The "Lever 4" element. \\
lever5 &  & IController\-Template\-Throttle & \{ get; \} & The "Lever 5" element. \\
left\-Grip\-Hat &  & IController\-Template\-Hat & \{ get; \} & The "Left Grip Hat" element. \\
right\-Grip\-Hat &  & IController\-Template\-Hat & \{ get; \} & The "Right Grip Hat" element. \\
left\-Pedal &  & IController\-Template\-Axis & \{ get; \} & The "Left Pedal" element. \\
right\-Pedal &  & IController\-Template\-Axis & \{ get; \} & The "Right Pedal" element. \\
slide &  & IController\-Template\-Axis & \{ get; \} & The "Slide" element. \\
extra\-Axis1 &  & IController\-Template\-Axis & \{ get; \} & The "Extra Axis 1" element. \\
extra\-Axis2 &  & IController\-Template\-Axis & \{ get; \} & The "Extra Axis 2" element. \\
extra\-Axis3 &  & IController\-Template\-Axis & \{ get; \} & The "Extra Axis 3" element. \\
extra\-Axis4 &  & IController\-Template\-Axis & \{ get; \} & The "Extra Axis 4" element. \\
button1 &  & IController\-Template\-Button & \{ get; \} & The "Button 1" element. \\
button2 &  & IController\-Template\-Button & \{ get; \} & The "Button 2" element. \\
button3 &  & IController\-Template\-Button & \{ get; \} & The "Button 3" element. \\
button4 &  & IController\-Template\-Button & \{ get; \} & The "Button 4" element. \\
button5 &  & IController\-Template\-Button & \{ get; \} & The "Button 5" element. \\
button6 &  & IController\-Template\-Button & \{ get; \} & The "Button 6" element. \\
button7 &  & IController\-Template\-Button & \{ get; \} & The "Button 7" element. \\
button8 &  & IController\-Template\-Button & \{ get; \} & The "Button 8" element. \\
button9 &  & IController\-Template\-Button & \{ get; \} & The "Button 9" element. \\
button10 &  & IController\-Template\-Button & \{ get; \} & The "Button 10" element. \\
button11 &  & IController\-Template\-Button & \{ get; \} & The "Button 11" element. \\
button12 &  & IController\-Template\-Button & \{ get; \} & The "Button 12" element. \\
button13 &  & IController\-Template\-Button & \{ get; \} & The "Button 13" element. \\
button14 &  & IController\-Template\-Button & \{ get; \} & The "Button 14" element. \\
button15 &  & IController\-Template\-Button & \{ get; \} & The "Button 15" element. \\
button16 &  & IController\-Template\-Button & \{ get; \} & The "Button 16" element. \\
button17 &  & IController\-Template\-Button & \{ get; \} & The "Button 17" element. \\
button18 &  & IController\-Template\-Button & \{ get; \} & The "Button 18" element. \\
button19 &  & IController\-Template\-Button & \{ get; \} & The "Button 19" element. \\
button20 &  & IController\-Template\-Button & \{ get; \} & The "Button 20" element. \\
button21 &  & IController\-Template\-Button & \{ get; \} & The "Button 21" element. \\
button22 &  & IController\-Template\-Button & \{ get; \} & The "Button 22" element. \\
button23 &  & IController\-Template\-Button & \{ get; \} & The "Button 23" element. \\
button24 &  & IController\-Template\-Button & \{ get; \} & The "Button 24" element. \\
button25 &  & IController\-Template\-Button & \{ get; \} & The "Button 25" element. \\
button26 &  & IController\-Template\-Button & \{ get; \} & The "Button 26" element. \\
button27 &  & IController\-Template\-Button & \{ get; \} & The "Button 27" element. \\
button28 &  & IController\-Template\-Button & \{ get; \} & The "Button 28" element. \\
button29 &  & IController\-Template\-Button & \{ get; \} & The "Button 29" element. \\
button30 &  & IController\-Template\-Button & \{ get; \} & The "Button 30" element. \\
button31 &  & IController\-Template\-Button & \{ get; \} & The "Button 31" element. \\
button32 &  & IController\-Template\-Button & \{ get; \} & The "Button 32" element. \\
hat1 &  & IController\-Template\-Hat & \{ get; \} & The "Hat 1" element. \\
hat2 &  & IController\-Template\-Hat & \{ get; \} & The "Hat 2" element. \\
throttle1 &  & IController\-Template\-Throttle & \{ get; \} & The "Throttle 1" element. \\
throttle2 &  & IController\-Template\-Throttle & \{ get; \} & The "Throttle 2" element. \\
stick &  & IController\-Template\-Stick6D & \{ get; \} & The "Stick" element. \\
Is\-Static &  & bool & \{ get; \} & Gets a value indicating whether the described member is static. \\
Name &  & string & \{ get; \} & Gets the name of the member \\
Member\-Access &  & Member\-Descriptor\-Access & \{ get; \} & Gets the types of access supported by this member \\
Extension\-Method\-Type &  & Type & \{ get; \} & Gets the type which this extension method extends, null if this is not an extension method. \\
Parameters &  & Parameter\-Descriptor[] & \{ get; \} & Gets the type of the arguments of the underlying CLR function \\
Var\-Args\-Array\-Type &  & Type & \{ get; \} & Gets a value indicating the type of the Param\-Array parameter of a var-args function. If the function is not var-args,
		 null is returned. \\
Var\-Args\-Element\-Type &  & Type & \{ get; \} & Gets a value indicating the type of the elements of the Param\-Array parameter of a var-args function. If the function is not var-args,
		 null is returned. \\
Sort\-Discriminant &  & string & \{ get; \} & Gets a sort discriminant to give consistent overload resolution matching in case of perfectly equal scores \\
Target\-Type &  & Type & \{ get; \} & Gets the proxied type \\
Proxy\-Type &  & Type & \{ get; \} & Gets the proxy type \\
Max\-Size &  & int & \{ get; \} & Returns the maximum number of items that can be enqueued at once in this queue.  Once you hit this number (ie. once Count == Max\-Size),
         attempting to enqueue another item will cause undefined behavior. \\
First &  & TItem & \{ get; \} & Returns the head of the queue, without removing it (use Dequeue() for that). \\
Count &  & int & \{ get; \} & Returns the number of nodes in the queue. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
get\-Argument\-Value &  & double & () &  \\
clone &  & Argument\-Extension & () &  \\
get\-Parameters\-Number &  & int & () &  \\
set\-Parameter\-Value &  & void & (int parameter\-Index, double parameter\-Value) &  \\
get\-Parameter\-Name &  & String & (int parameter\-Index) &  \\
calculate &  & double & () &  \\
clone &  & Function\-Extension & () &  \\
calculate &  & double & (params double[] parameters) &  \\
clone &  & Function\-Extension\-Variadic & () &  \\
Get\-Debugger\-Caps &  & Debugger\-Caps & () & Gets the debugger caps. \\
Set\-Debug\-Service &  & void & (Debug\-Service debug\-Service) & Sets the debug service for this debugger \\
Set\-Source\-Code &  & void & (Source\-Code source\-Code) & Called by the script engine  when a source code is added or changed. \\
Set\-Byte\-Code &  & void & (string[] byte\-Code) & Called by the script engine  when the bytecode changes. \\
Is\-Pause\-Requested &  & bool & () & Called by the script engine at execution time to check if a break has 
		 been requested. Should return pretty fast as it's called A LOT. \\
Signal\-Runtime\-Exception &  & bool & (Script\-Runtime\-Exception ex) & Called by the script engine when a runtime error occurs. 
		 The debugger can return true to signal the engine that it wants to break 
		 into the source of the error. If it does so, it should also return true 
		 to subsequent calls to Is\-Pause\-Requested(). \\
Get\-Action &  & Debugger\-Action & (int ip, Source\-Ref sourceref) & Called by the script engine to get what action to do next. \\
Signal\-Execution\-Ended &  & void & () & Called by the script engine when the execution ends. \\
Update &  & void & (Watch\-Type watch\-Type, IEnumerable{\tt <}\-Watch\-Item\-{\tt >} items) & Called by the script engine to update watches of a given type. Note 
		 that this method is not called only for watches in the strictest term, 
		 but also for the stack, etc. \\
Get\-Watch\-Items &  & List{\tt <}\-Dynamic\-Expression\-{\tt >} & () & Called by the script engine to get which expressions are active 
		 watches in the debugger. \\
Refresh\-Breakpoints &  & void & (IEnumerable{\tt <}\-Source\-Ref\-{\tt >} refs) & Called by the script engine to refresh the breakpoint list. \\
Generate &  & IUser\-Data\-Descriptor & (Type type) & Generates a new descriptor for the specified type.
		 
		 The purpose is to allow a mechanism by which a type descriptor can replace itself with another
		 descriptor for a specific type. For example, descriptors can be created on the fly to support
		 generic types through this mechanism.
		 
		 The return value should be:
				null - if this descriptor is simply skipped for the specified type
				this - acts as if the descriptor was a vanilla descriptor
				a new descriptor - if a new descriptor should be used in place of this one
				
		 It's recommended that instances of descriptors are cached for future references. One possible way,
		 to do the caching is to have the generator register the descriptor through . 
		 In that case, it should query whether the type is exactly registered, through 
		 
		 NOTE-1 : the search for descriptors does NOT stop with the descriptor returned by this type, but 
		 other descriptors (e.g. for interfaces) might still be added.
		 
		 NOTE-2 : the descriptor generation mechanism is not triggered on an exact match of types.
		 
		 NOTE-3 : the method is called in the context of a lock over the descriptors registry so no unpredictable changes to the 
		 registry can come from other threads during the execution of this method. However this method should not take other 
		 locks, to avoid deadlocks. \\
Index &  & Dyn\-Value & (Script script, object obj, Dyn\-Value index, bool is\-Direct\-Indexing) & Performs an "index" "get" operation. \\
Set\-Index &  & bool & (Script script, object obj, Dyn\-Value index, Dyn\-Value value, bool is\-Direct\-Indexing) & Performs an "index" "set" operation. \\
As\-String &  & string & (object obj) & Converts this userdata to string \\
Meta\-Index &  & Dyn\-Value & (Script script, object obj, string metaname) & Gets a "meta" operation on this userdata. If a descriptor does not support this functionality,
		 it should return "null" (not a nil). 
		 
		 These standard metamethods can be supported (the return value should be a function accepting the
		 classic parameters of the corresponding metamethod):
		 \_\_add, \_\_sub, \_\_mul, \_\_div, \_\_div, \_\_pow, \_\_unm, \_\_eq, \_\_lt, \_\_le, \_\_lt, \_\_len, \_\_concat, 
		 \_\_pairs, \_\_ipairs, \_\_iterator, \_\_call
		 
		 These standard metamethods are supported through other calls for efficiency:
		 \_\_index, \_\_newindex, \_\_tostring \\
Is\-Type\-Compatible &  & bool & (Type type, object obj) & Determines whether the specified object is compatible with the specified type.
		 Unless a very specific behaviour is needed, the correct implementation is a 
		 simple " return type.Is\-Instance\-Of\-Type(obj); " \\
Get\-Value &  & Dyn\-Value & (Script script, object obj) & Gets the value of the member \\
Set\-Value &  & bool & (Script script, object obj, Dyn\-Value value) & Sets the value of the member \\
Index &  & Dyn\-Value & (Script script, Dyn\-Value index, bool is\-Direct\-Indexing) & Performs an "index" "get" operation. \\
Set\-Index &  & bool & (Script script, Dyn\-Value index, Dyn\-Value value, bool is\-Direct\-Indexing) & Performs an "index" "set" operation. \\
Meta\-Index &  & Dyn\-Value & (Script script, string metaname) & Gets a "meta" operation on this userdata. If a descriptor does not support this functionality,
		 it should return "null" (not a nil). 
		 
		 These standard metamethods can be supported (the return value should be a function accepting the
		 classic parameters of the corresponding metamethod):
		 \_\_add, \_\_sub, \_\_mul, \_\_div, \_\_div, \_\_pow, \_\_unm, \_\_eq, \_\_lt, \_\_le, \_\_lt, \_\_len, \_\_concat, 
		 \_\_pairs, \_\_ipairs, \_\_iterator, \_\_call
		 
		 These standard metamethods are supported through other calls for efficiency:
		 \_\_index, \_\_newindex, \_\_tostring \\
Prepare\-For\-Wiring &  & void & (Table t) & Prepares the descriptor for hard-wiring.
		 The descriptor fills the passed table with all the needed data for hardwire generators to generate the appropriate code. \\
Assign\-Object\-Unchecked &  & void & (object o, Table data) & Assigns the properties of the specified object without checking the type. \\
Load\-File &  & object & (string file, Table global\-Context) & Opens a file for reading the script code.
		 It can return either a string, a byte[] or a Stream.
		 If a byte[] is returned, the content is assumed to be a serialized (dumped) bytecode. If it's a string, it's
		 assumed to be either a script or the output of a string.dump call. If a Stream, autodetection takes place. \\
Resolve\-File\-Name &  & string & (string filename, Table global\-Context) & Resolves a filename [applying paths, etc.] \\
Resolve\-Module\-Name &  & string & (string modname, Table global\-Context) & Resolves the name of a module to a filename (which will later be passed to Open\-Script\-File) \\
Filter\-Supported\-Core\-Modules &  & Core\-Modules & (Core\-Modules module) & Filters the Core\-Modules enumeration to exclude non-supported operations \\
Get\-Environment\-Variable &  & string & (string envvarname) & Gets an environment variable. Must be implemented, but an implementation is allowed
		 to always return null if a more meaningful implementation cannot be achieved or is
		 not desired. \\
Is\-Running\-On\-AOT &  & bool & () & Determines whether the application is running in AOT (ahead-of-time) mode \\
Get\-Platform\-Name &  & string & () & Gets the name of the platform (used for debug purposes). \\
Default\-Print &  & void & (string content) & Default handler for 'print' calls. Can be customized in Script\-Options \\
Default\-Input &  & string & (string prompt) & Default handler for interactive line input calls. Can be customized in Script\-Options.
		 If a meaningful implementation cannot be provided, this method should return null. \\
IO\_Open\-File &  & Stream & (Script script, string filename, Encoding encoding, string mode) & A function used to open files in the 'io' module.
		 Can have an invalid implementation if 'io' module is filtered out.
		 It should return a correctly initialized Stream for the given file and access \\
IO\_Get\-Standard\-Stream &  & Stream & (Standard\-File\-Type type) & Gets a standard stream (stdin, stdout, stderr). \\
IO\_OS\_Get\-Temp\-Filename &  & string & () & Gets a temporary filename. Used in 'io' and 'os' modules.
		 Can have an invalid implementation if 'io' and 'os' modules are filtered out. \\
OS\_Exit\-Fast &  & void & (int exit\-Code) & Exits the process, returning the specified exit code.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_File\-Exists &  & bool & (string file) & Checks if a file exists. Used by the 'os' module.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_File\-Delete &  & void & (string file) & Deletes the specified file. Used by the 'os' module.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_File\-Move &  & void & (string src, string dst) & Moves the specified file. Used by the 'os' module.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_Execute &  & int & (string cmdline) & Executes the specified command line, returning the child process exit code and blocking in the meantime.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
Get\-Buffer &  & Memory\-Stream & () & Gets a Memory\-Stream built from a buffer plucked from a thread safe pool
         The pool grows automatically.
         Closing the memory stream clears the buffer and returns it to the pool \\
Send\-Ping &  & Task & (Array\-Segment{\tt <}\-byte\-{\tt >} payload, Cancellation\-Token cancellation) & Sends a ping frame \\
Connect\-Async &  & Task{\tt <}\-Web\-Socket\-{\tt >} & (Uri uri, Cancellation\-Token token = default(Cancellation\-Token)) & Connect with default options \\
Connect\-Async &  & Task{\tt <}\-Web\-Socket\-{\tt >} & (Uri uri, Web\-Socket\-Client\-Options options, Cancellation\-Token token = default(Cancellation\-Token)) & Connect with options specified \\
Connect\-Async &  & Task{\tt <}\-Web\-Socket\-{\tt >} & (Stream response\-Stream, string sec\-Web\-Socket\-Key, Web\-Socket\-Client\-Options options, Cancellation\-Token token = default(Cancellation\-Token)) & Connect with a stream that has already been opened and HTTP websocket upgrade request sent
         This function will check the handshake response from the server and proceed if successful
         Use this function if you have specific requirements to open a conenction like using special http headers and cookies
         You will have to build your own HTTP websocket upgrade request
         You may not even choose to use TCP/IP and this function will allow you to do that \\
Read\-Http\-Header\-From\-Stream\-Async &  & Task{\tt <}\-Web\-Socket\-Http\-Context\-{\tt >} & (Tcp\-Client client, Stream stream, Cancellation\-Token token = default(Cancellation\-Token)) & Reads a http header information from a stream and decodes the parts relating to the Web\-Socket protocot upgrade \\
Accept\-Web\-Socket\-Async &  & Task{\tt <}\-Web\-Socket\-{\tt >} & (Web\-Socket\-Http\-Context context, Cancellation\-Token token = default(Cancellation\-Token)) & Accept web socket with default options
         Call Read\-Http\-Header\-From\-Stream\-Async first to get Web\-Socket\-Http\-Context \\
Accept\-Web\-Socket\-Async &  & Task{\tt <}\-Web\-Socket\-{\tt >} & (Web\-Socket\-Http\-Context context, Web\-Socket\-Server\-Options options, Cancellation\-Token token = default(Cancellation\-Token)) & Accept web socket with options specified
         Call Read\-Http\-Header\-From\-Stream\-Async first to get Web\-Socket\-Http\-Context \\
Get\-Value &  & Dyn\-Value & (Script script, object obj) & Gets the value of this member as a  to be exposed to scripts.
		 Implementors should raise exceptions if the value cannot be read or if access to an
		 instance member through a static userdata is attempted. \\
Set\-Value &  & void & (Script script, object obj, Dyn\-Value value) & Sets the value of this member from a .
		 Implementors should raise exceptions if the value cannot be read or if access to an
		 instance member through a static userdata is attempted. \\
Optimize &  & void & () & Called by standard descriptors when background optimization or preoptimization needs to be performed. \\
Execute &  & Dyn\-Value & (Script script, object obj, Script\-Execution\-Context context, Callback\-Arguments args) & Invokes the member from script.
		 Implementors should raise exceptions if the value cannot be executed or if access to an
		 instance member through a static userdata is attempted. \\
Create\-Proxy\-Object &  & object & (object o) & Takes an instance of a target object and returns a proxy object wrapping it \\
Create\-Proxy\-Object &  & TProxy & (TTarget target) & Takes an instance of a target object and returns a proxy object wrapping it \\
Handle\-Registration &  & IUser\-Data\-Descriptor & (IUser\-Data\-Descriptor new\-Descriptor, IUser\-Data\-Descriptor old\-Descriptor) & Called to handle the registration or deregistration of a type descriptor. Must return the type descriptor to be registered, or null to remove the registration. \\
Allow\-Type\-Auto\-Registration &  & bool & (Type type) & Allows type automatic registration for the specified type.
		 NOTE: automatic type registration is NOT recommended. \\
Resize &  & void & (int max\-Nodes) & Resize the queue so it can accept more nodes.  All currently enqueued nodes are remain.
         Attempting to decrease the queue size to a size too small to hold the existing nodes results in undefined behavior \\
Reset\-Node &  & void & (TItem node) & By default, nodes that have been previously added to one queue cannot be added to another queue.
         If you need to do this, please call original\-Queue.Reset\-Node(node) before attempting to add it in the new queue \\
Enqueue &  & void & (TItem node, TPriority priority) & Enqueue a node to the priority queue.  Lower values are placed in front. Ties are broken by first-in-first-out.
         See implementation for how duplicates are handled. \\
Dequeue &  & TItem & () & Removes the head of the queue (node with minimum priority; ties are broken by order of insertion), and returns it. \\
Clear &  & void & () & Removes every node from the queue. \\
Contains &  & bool & (TItem node) & Returns whether the given node is in the queue. \\
Remove &  & void & (TItem node) & Removes a node from the queue.  The node does not need to be the head of the queue. \\
Update\-Priority &  & void & (TItem node, TPriority priority) & Call this method to change the priority of a node. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Constant}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
NOT\_FOUND & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TYPE\_ID & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NO\_SYNTAX\_ERRORS & public const & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
constant\-Name & private & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
constant\-Value & private & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
description & private & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
related\-Expressions\-List & private & List{\tt <}\-Expression\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
syntax\-Status & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
error\-Message & private & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Constant & public & (String constant\-Name, double constant\-Value) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Constant & public & (String constant\-Name, double constant\-Value, String description) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Constant & public & (String constant\-Definition\-String, params Primitive\-Element[] elements) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
get\-Constant\-Name & public & String & () &  \\
set\-Constant\-Name & public & void & (String constant\-Name) &  \\
set\-Constant\-Value & public & void & (double constant\-Value) &  \\
get\-Constant\-Value & public & double & () &  \\
get\-Description & public & String & () &  \\
set\-Description & public & void & (String description) &  \\
get\-Error\-Message & public & String & () &  \\
get\-Syntax\-Status & public & bool & () &  \\
add\-Related\-Expression & internal & void & (Expression expression) &  \\
remove\-Related\-Expression & internal & void & (Expression expression) &  \\
set\-Expression\-Modified\-Flags &  & void & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Expression}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
TYPE\_ID & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NOT\_FOUND & internal const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
INTERNAL & internal const & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
WITH\_EXP\_STR & private const & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NO\_SYNTAX\_ERRORS & public const & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
expression\-String & internal & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
arguments\-List & internal & List{\tt <}\-Argument\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
functions\-List & internal & List{\tt <}\-Function\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
constants\-List & internal & List{\tt <}\-Constant\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
key\-Words\-List & private & List{\tt <}\-Key\-Word\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
initial\-Tokens & private & List{\tt <}\-Token\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
tokens\-List & private & List{\tt <}\-Token\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
related\-Expressions\-List & internal & List{\tt <}\-Expression\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
computing\-Time & private & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
expression\-Was\-Modified & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
recursive\-Mode & internal & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
verbose\-Mode & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
disable\-Rounding & internal & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
syntax\-Status & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
error\-Message & private & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
recursion\-Call\-Pending & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
recursion\-Calls\-Counter & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
parser\-Key\-Words\-Only & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
UDFExpression & internal & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
UDFVariadic\-Params\-At\-Run\-Time & internal & List{\tt <}\-Double\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
internal\-Clone & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
options\-Changeset\-Number & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Expression & public & (params Primitive\-Element[] elements) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Expression & public & (String expression\-String, params Primitive\-Element[] elements) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Expression & internal & (String expression\-String, bool parser\-Key\-Words\-Only) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Expression & internal & (String expression\-String, List{\tt <}\-Token\-{\tt >} initial\-Tokens, List{\tt <}\-Argument\-{\tt >} arguments\-List,
				List{\tt <}\-Function\-{\tt >} functions\-List, List{\tt <}\-Constant\-{\tt >} constants\-List, bool disable\-Ulp\-Rounding,
				bool UDFExpression, List{\tt <}\-Double\-{\tt >} UDFVariadic\-Params\-At\-Run\-Time) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Expression & internal & (String expression\-String, List{\tt <}\-Argument\-{\tt >} arguments\-List,
				List{\tt <}\-Function\-{\tt >} functions\-List, List{\tt <}\-Constant\-{\tt >} constants\-List
				,bool i, bool UDFExpression, List{\tt <}\-Double\-{\tt >} UDFVariadic\-Params\-At\-Run\-Time) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Expression & private & (Expression expression) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
add\-Related\-Expression & internal & void & (Expression expression) &  \\
remove\-Related\-Expression & internal & void & (Expression expression) &  \\
show\-Related\-Expressions & internal & void & () &  \\
get\-Error\-Message & public & String & () &  \\
get\-Syntax\-Status & public & bool & () &  \\
set\-Syntax\-Status & internal & void & (bool syntax\-Status, String error\-Message) &  \\
set\-Expression\-Modified\-Flag & internal & void & () &  \\
expression\-Internal\-Vars\-Init & private & void & () &  \\
expression\-Init & private & void & () &  \\
set\-Expression\-String & public & void & (String expression\-String) &  \\
get\-Expression\-String & public & String & () &  \\
clear\-Expression\-String & public & void & () &  \\
set\-Description & public & void & (String description) &  \\
get\-Description & public & String & () &  \\
clear\-Description & public & void & () &  \\
set\-Verbose\-Mode & public & void & () &  \\
set\-Silent\-Mode & public & void & () &  \\
get\-Verbose\-Mode & public & bool & () &  \\
set\-Recursive\-Mode & internal & void & () &  \\
disable\-Recursive\-Mode & internal & void & () &  \\
get\-Recursive\-Mode & public & bool & () &  \\
get\-Computing\-Time & public & double & () &  \\
add\-Definitions & public & void & (params Primitive\-Element[] elements) &  \\
remove\-Definitions & public & void & (params Primitive\-Element[] elements) &  \\
add\-Arguments & public & void & (params Argument[] arguments) &  \\
define\-Arguments & public & void & (params String[] arguments\-Names) &  \\
define\-Argument & public & void & (String argument\-Name, double argument\-Value) &  \\
get\-Argument\-Index & public & int & (String argument\-Name) &  \\
get\-Argument & public & Argument & (String argument\-Name) &  \\
get\-Argument & public & Argument & (int argument\-Index) &  \\
get\-Arguments\-Number & public & int & () &  \\
set\-Argument\-Value & public & void & (String argument\-Name, double argument\-Value) &  \\
get\-Argument\-Value & public & double & (String argument\-Name) &  \\
remove\-Arguments & public & void & (params String[] arguments\-Names) &  \\
remove\-Arguments & public & void & (params Argument[] arguments) &  \\
remove\-All\-Arguments & public & void & () &  \\
add\-Constants & public & void & (params Constant[] constants) &  \\
define\-Constant & public & void & (String constant\-Name, double constant\-Value) &  \\
get\-Constant\-Index & public & int & (String constant\-Name) &  \\
get\-Constant & public & Constant & (String constant\-Name) &  \\
get\-Constant & public & Constant & (int constant\-Index) &  \\
get\-Constants\-Number & public & int & () &  \\
remove\-Constants & public & void & (params String[] constants\-Names) &  \\
remove\-Constants & public & void & (params Constant[] constants) &  \\
remove\-All\-Constants & public & void & () &  \\
add\-Functions & public & void & (params Function[] functions) &  \\
define\-Function & public & void & (String function\-Name, String  function\-Expression\-String,
					params String[] arguments\-Names) &  \\
get\-Function\-Index & public & int & (String function\-Name) &  \\
get\-Function & public & Function & (String function\-Name) &  \\
get\-Function & public & Function & (int function\-Index) &  \\
get\-Functions\-Number & public & int & () &  \\
remove\-Functions & public & void & (params String[] functions\-Names) &  \\
remove\-Functions & public & void & (params Function[] functions) &  \\
remove\-All\-Functions & public & void & () &  \\
set\-To\-Number & private & void & (int pos, double number, bool ulp\-Round) &  \\
f1Set\-Decrease\-Remove & private & void & (int pos, double result, bool ulp\-Round) &  \\
f2Set\-Decrease\-Remove & private & void & (int pos, double result, bool ulp\-Round) &  \\
f3Set\-Decrease\-Remove & private & void & (int pos, double result, bool ulp\-Round) &  \\
op\-Set\-Decrease\-Remove & private & void & (int pos, double result, bool ulp\-Round) &  \\
calc\-Set\-Decrease\-Remove & private & void & (int pos, double result, bool ulp\-Round) &  \\
variadic\-Set\-Decrease\-Remove & private & void & (int pos, double value, int length, bool ulp\-Round) &  \\
if\-Set\-Remove & private & void & (int pos, double if\-Condition, bool ulp\-Round) &  \\
create\-Initial\-Tokens & private & List{\tt <}\-Token\-{\tt >} & (int start\-Pos,
				int end\-Pos,
				List{\tt <}\-Token\-{\tt >} tokens\-List) &  \\
get\-Parameters\-Number & private & int & (int pos) &  \\
get\-Function\-Parameters & private & List{\tt <}\-Function\-Parameter\-{\tt >} & (int pos, List{\tt <}\-Token\-{\tt >} tokens\-List) &  \\
get\-Param\-Argument & private & Argument\-Parameter & (String argument\-Name) &  \\
clear\-Param\-Argument & private & void & (Argument\-Parameter arg\-Param) &  \\
FREE\_ARGUMENT & private & void & (int pos) &  \\
DEPENDENT\_ARGUMENT & private & void & (int pos) &  \\
USER\_FUNCTION & private & void & (int pos) &  \\
USER\_CONSTANT & private & void & (int pos) &  \\
RECURSIVE\_ARGUMENT & private & void & (int pos) &  \\
CONSTANT & private & void & (int pos) &  \\
UNIT & private & void & (int pos) &  \\
RANDOM\_VARIABLE & private & void & (int pos) &  \\
get\-Token\-Value & private & double & (int token\-Index) &  \\
TETRATION & private & void & (int pos) &  \\
POWER & private & void & (int pos) &  \\
MODULO & private & void & (int pos) &  \\
DIVIDE & private & void & (int pos) &  \\
MULTIPLY & private & void & (int pos) &  \\
PLUS & private & void & (int pos) &  \\
MINUS & private & void & (int pos) &  \\
AND & private & void & (int pos) &  \\
OR & private & void & (int pos) &  \\
NAND & private & void & (int pos) &  \\
NOR & private & void & (int pos) &  \\
XOR & private & void & (int pos) &  \\
IMP & private & void & (int pos) &  \\
CIMP & private & void & (int pos) &  \\
NIMP & private & void & (int pos) &  \\
CNIMP & private & void & (int pos) &  \\
EQV & private & void & (int pos) &  \\
NEG & private & void & (int pos) &  \\
EQ & private & void & (int pos) &  \\
NEQ & private & void & (int pos) &  \\
LT & private & void & (int pos) &  \\
GT & private & void & (int pos) &  \\
LEQ & private & void & (int pos) &  \\
GEQ & private & void & (int pos) &  \\
BITWISE\_COMPL & private & void & (int pos) &  \\
BITWISE\_AND & private & void & (int pos) &  \\
BITWISE\_OR & private & void & (int pos) &  \\
BITWISE\_XOR & private & void & (int pos) &  \\
BITWISE\_LEFT\_SHIFT & private & void & (int pos) &  \\
BITWISE\_RIGHT\_SHIFT & private & void & (int pos) &  \\
SIN & private & void & (int pos) &  \\
COS & private & void & (int pos) &  \\
TAN & private & void & (int pos) &  \\
CTAN & private & void & (int pos) &  \\
SEC & private & void & (int pos) &  \\
COSEC & private & void & (int pos) &  \\
ASIN & private & void & (int pos) &  \\
ACOS & private & void & (int pos) &  \\
ATAN & private & void & (int pos) &  \\
ACTAN & private & void & (int pos) &  \\
LN & private & void & (int pos) &  \\
LOG2 & private & void & (int pos) &  \\
LOG10 & private & void & (int pos) &  \\
RAD & private & void & (int pos) &  \\
EXP & private & void & (int pos) &  \\
SQRT & private & void & (int pos) &  \\
SINH & private & void & (int pos) &  \\
COSH & private & void & (int pos) &  \\
TANH & private & void & (int pos) &  \\
COTH & private & void & (int pos) &  \\
SECH & private & void & (int pos) &  \\
CSCH & private & void & (int pos) &  \\
DEG & private & void & (int pos) &  \\
ABS & private & void & (int pos) &  \\
SGN & private & void & (int pos) &  \\
FLOOR & private & void & (int pos) &  \\
CEIL & private & void & (int pos) &  \\
ARSINH & private & void & (int pos) &  \\
ARCOSH & private & void & (int pos) &  \\
ARTANH & private & void & (int pos) &  \\
ARCOTH & private & void & (int pos) &  \\
ARSECH & private & void & (int pos) &  \\
ARCSCH & private & void & (int pos) &  \\
SA & private & void & (int pos) &  \\
SINC & private & void & (int pos) &  \\
BELL\_NUMBER & private & void & (int pos) &  \\
LUCAS\_NUMBER & private & void & (int pos) &  \\
FIBONACCI\_NUMBER & private & void & (int pos) &  \\
HARMONIC\_NUMBER & private & void & (int pos) &  \\
IS\_PRIME & private & void & (int pos) &  \\
PRIME\_COUNT & private & void & (int pos) &  \\
EXP\_INT & private & void & (int pos) &  \\
LOG\_INT & private & void & (int pos) &  \\
OFF\_LOG\_INT & private & void & (int pos) &  \\
FACT & private & void & (int pos) &  \\
PERC & private & void & (int pos) &  \\
NOT & private & void & (int pos) &  \\
GAUSS\_ERF & private & void & (int pos) &  \\
GAUSS\_ERFC & private & void & (int pos) &  \\
GAUSS\_ERF\_INV & private & void & (int pos) &  \\
GAUSS\_ERFC\_INV & private & void & (int pos) &  \\
ULP & private & void & (int pos) &  \\
ISNAN & private & void & (int pos) &  \\
NDIG10 & private & void & (int pos) &  \\
NFACT & private & void & (int pos) &  \\
ARCSEC & private & void & (int pos) &  \\
ARCCSC & private & void & (int pos) &  \\
GAMMA & private & void & (int pos) &  \\
LAMBERT\_W0 & private & void & (int pos) &  \\
LAMBERT\_W1 & private & void & (int pos) &  \\
SGN\_GAMMA & private & void & (int pos) &  \\
LOG\_GAMMA & private & void & (int pos) &  \\
DI\_GAMMA & private & void & (int pos) &  \\
UDF\_PARAM & private & void & (int pos) &  \\
LOG & private & void & (int pos) &  \\
get\-Numbers & private & List{\tt <}\-Double\-{\tt >} & (int pos) &  \\
MOD & private & void & (int pos) &  \\
BINOM\_COEFF & private & void & (int pos) &  \\
PERMUTATIONS & private & void & (int pos) &  \\
BETA & private & void & (int pos) &  \\
LOG\_BETA & private & void & (int pos) &  \\
BERNOULLI\_NUMBER & private & void & (int pos) &  \\
STIRLING1\_NUMBER & private & void & (int pos) &  \\
STIRLING2\_NUMBER & private & void & (int pos) &  \\
WORPITZKY\_NUMBER & private & void & (int pos) &  \\
EULER\_NUMBER & private & void & (int pos) &  \\
KRONECKER\_DELTA & private & void & (int pos) &  \\
EULER\_POLYNOMIAL & private & void & (int pos) &  \\
HARMONIC2\_NUMBER & private & void & (int pos) &  \\
ROUND & private & void & (int pos) &  \\
RND\_VAR\_UNIFORM\_CONT & private & void & (int pos) &  \\
RND\_VAR\_UNIFORM\_DISCR & private & void & (int pos) &  \\
RND\_NORMAL & private & void & (int pos) &  \\
NDIG & private & void & (int pos) &  \\
DIGIT10 & private & void & (int pos) &  \\
FACTVAL & private & void & (int pos) &  \\
FACTEXP & private & void & (int pos) &  \\
ROOT & private & void & (int pos) &  \\
INC\_GAMMA\_LOWER & private & void & (int pos) &  \\
INC\_GAMMA\_UPPER & private & void & (int pos) &  \\
REG\_GAMMA\_LOWER & private & void & (int pos) &  \\
REG\_GAMMA\_UPPER & private & void & (int pos) &  \\
IF\_CONDITION & private & void & (int pos) &  \\
IFF & private & void & (int pos) &  \\
IF & private & void & (int pos) &  \\
CHI & private & void & (int pos) &  \\
CHI\_LR & private & void & (int pos) &  \\
CHI\_L & private & void & (int pos) &  \\
CHI\_R & private & void & (int pos) &  \\
PDF\_UNIFORM\_CONT & private & void & (int pos) &  \\
CDF\_UNIFORM\_CONT & private & void & (int pos) &  \\
QNT\_UNIFORM\_CONT & private & void & (int pos) &  \\
PDF\_NORMAL & private & void & (int pos) &  \\
CDF\_NORMAL & private & void & (int pos) &  \\
QNT\_NORMAL & private & void & (int pos) &  \\
DIGIT & private & void & (int pos) &  \\
INC\_BETA & private & void & (int pos) &  \\
REG\_BETA & private & void & (int pos) &  \\
update\-Missing\-Tokens & private & void & (List{\tt <}\-Token\-{\tt >} tokens, String key\-Word, int token\-Id, int token\-Type\-Id) &  \\
update\-Missing\-Tokens & private & void & (Argument\-Parameter index, Iterative\-Operator\-Parameters iter\-Params) &  \\
eval\-From\-To\-Delta\-Parameters & private & void & (Argument\-Parameter index, Iterative\-Operator\-Parameters iter\-Params) &  \\
SUM & private & void & (int pos) &  \\
PROD & private & void & (int pos) &  \\
MIN & private & void & (int pos) &  \\
MAX & private & void & (int pos) &  \\
AVG & private & void & (int pos) &  \\
VAR & private & void & (int pos) &  \\
STD & private & void & (int pos) &  \\
DERIVATIVE\_NTH & private & void & (int pos, int derivative\-Type) &  \\
INTEGRAL & private & void & (int pos) &  \\
INTEGRAL & private & void & (int pos) &  \\
SOLVE & private & void & (int pos) &  \\
SOLVE & private & void & (int pos) &  \\
FORWARD\_DIFFERENCE & private & void & (int pos) &  \\
BACKWARD\_DIFFERENCE & private & void & (int pos) &  \\
MIN\_VARIADIC & private & void & (int pos) &  \\
MAX\_VARIADIC & private & void & (int pos) &  \\
SUM\_VARIADIC & private & void & (int pos) &  \\
PROD\_VARIADIC & private & void & (int pos) &  \\
AVG\_VARIADIC & private & void & (int pos) &  \\
VAR\_VARIADIC & private & void & (int pos) &  \\
STD\_VARIADIC & private & void & (int pos) &  \\
CONTINUED\_FRACTION & private & void & (int pos) &  \\
CONTINUED\_POLYNOMIAL & private & void & (int pos) &  \\
GCD & private & void & (int pos) &  \\
LCM & private & void & (int pos) &  \\
RND\_LIST & private & void & (int pos) &  \\
COALESCE & private & void & (int pos) &  \\
OR\_VARIADIC & private & void & (int pos) &  \\
AND\_VARIADIC & private & void & (int pos) &  \\
XOR\_VARIADIC & private & void & (int pos) &  \\
ARGMIN\_VARIADIC & private & void & (int pos) &  \\
ARGMAX\_VARIADIC & private & void & (int pos) &  \\
MEDIAN\_VARIADIC & private & void & (int pos) &  \\
MODE\_VARIADIC & private & void & (int pos) &  \\
BASE\_VARIADIC & private & void & (int pos) &  \\
NDIST\_VARIADIC & private & void & (int pos) &  \\
COMMA & private & void & (int pos) &  \\
PARENTHESES & private & void & (int l\-Pos, int r\-Pos) &  \\
check\-Lex\-Syntax & public & bool & () &  \\
check\-Syntax & public & bool & () &  \\
check\-Calculus\-Parameter & private & int & (String param) &  \\
check\-If\-Known\-Argument & private & bool & (Function\-Parameter param) &  \\
check\-If\-Unknown\-Token & private & bool & (Function\-Parameter param) &  \\
check\-Syntax & private & bool & (String level, bool function\-With\-Body\-Ext) &  \\
calculate & public & double & () &  \\
f1Arg\-Calc & private & void & (int pos) &  \\
f2Arg\-Calc & private & void & (int pos) &  \\
f3Arg\-Calc & private & void & (int pos) &  \\
variadic\-Fun\-Calc & private & void & (int pos) &  \\
calculus\-Calc & private & void & (int pos) &  \\
bol\-Calc & private & void & (int pos) &  \\
bitwise\-Calc & private & void & (int pos) &  \\
add\-UDFSpecific\-Parser\-Key\-Words & private & void & () &  \\
add\-Parser\-Key\-Words & private & void & () &  \\
add\-Arguments\-Key\-Words & private & void & () &  \\
add\-Functions\-Key\-Words & private & void & () &  \\
add\-Constants\-Key\-Words & private & void & () &  \\
validate\-Parser\-Key\-Words & private & void & () &  \\
add\-Key\-Word & private & void & (String word\-String, String word\-Description, int word\-Id, String word\-Syntax, String word\-Since, int word\-Type\-Id) &  \\
check\-Other\-Number\-Bases & private & void & (Token token) &  \\
check\-Fraction & private & void & (Token token) &  \\
add\-Token & private & void & (String token\-Str, Key\-Word key\-Word) &  \\
tokenize\-Expression\-String & private & void & () &  \\
evaluate\-Tokens\-Levels & private & void & () &  \\
copy\-Initial\-Tokens & private & void & () &  \\
get\-Copy\-Of\-Initial\-Tokens & public & List{\tt <}\-Token\-{\tt >} & () &  \\
get\-Missing\-User\-Defined\-Arguments & public & String[] & () &  \\
get\-Missing\-User\-Defined\-Units & public & String[] & () &  \\
get\-Missing\-User\-Defined\-Functions & public & String[] & () &  \\
get\-Initial\-Tokens & internal & List{\tt <}\-Token\-{\tt >} & () &  \\
show\-Parsing & private & void & (int l\-Pos, int r\-Pos) &  \\
show\-Key\-Words &  & void & () &  \\
get\-Help & public & String & () &  \\
get\-Help & public & String & (String word) &  \\
get\-Key\-Words & public & List{\tt <}\-Key\-Word\-{\tt >} & () &  \\
get\-Key\-Words & public & List{\tt <}\-Key\-Word\-{\tt >} & (String query) &  \\
show\-Initial\-Tokens &  & void & () &  \\
print\-System\-Info & private & void & (String info, bool with\-Expression\-String) &  \\
clone & internal & Expression & () &  \\
Primary\-Exp & internal static & Expression & (Script\-Loading\-Context lcontext) & Primaries the exp. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Function}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
NO\_SYNTAX\_ERRORS & public const & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SYNTAX\_ERROR\_OR\_STATUS\_UNKNOWN & public const & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NOT\_FOUND & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TYPE\_ID & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BODY\_RUNTIME & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BODY\_EXTENDED & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
function\-Body\-Type & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
function\-Expression & internal & Expression & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
function\-Name & private & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
description & private & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
is\-Variadic & internal & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
parameters\-Number & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
function\-Extension & private & Function\-Extension & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
function\-Extension\-Variadic & private & Function\-Extension\-Variadic & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Function & public & (String function\-Name
						,String  function\-Expression\-String, params Primitive\-Element[] elements) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Function & public & (String function\-Name
						,String  function\-Expression\-String
						,params String[] arguments\-Names ) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Function & public & (String function\-Definition\-String, params Primitive\-Element[] elements) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Function & public & (String function\-Name, Function\-Extension function\-Extension) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Function & public & (String function\-Name, Function\-Extension\-Variadic function\-Extension\-Variadic) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Function & private & (Function function) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
set\-Function & public & void & (String function\-Definition\-String, params Primitive\-Element[] elements) &  \\
set\-Description & public & void & (String description) &  \\
get\-Description & public & String & () &  \\
get\-Function\-Name & public & String & () &  \\
get\-Function\-Expression\-String & public & String & () &  \\
set\-Function\-Name & public & void & (String function\-Name) &  \\
set\-Argument\-Value & public & void & (int argument\-Index, double argument\-Value) &  \\
get\-Function\-Body\-Type & public & int & () &  \\
check\-Syntax & public & bool & () &  \\
get\-Error\-Message & public & String & () &  \\
clone & internal & Function & () &  \\
calculate & public & double & () &  \\
calculate & public & double & (params double[] parameters) &  \\
calculate & public & double & (params Argument[] arguments) &  \\
add\-Definitions & public & void & (params Primitive\-Element[] elements) &  \\
remove\-Definitions & public & void & (params Primitive\-Element[] elements) &  \\
add\-Arguments & public & void & (params Argument[] arguments) &  \\
define\-Arguments & public & void & (params String[] arguments\-Names) &  \\
define\-Argument & public & void & (String argument\-Name, double argument\-Value) &  \\
get\-Argument\-Index & public & int & (String argument\-Name) &  \\
get\-Argument & public & Argument & (String argument\-Name) &  \\
get\-Argument & public & Argument & (int argument\-Index) &  \\
get\-Parameters\-Number & public & int & () &  \\
set\-Parameters\-Number & public & void & (int parameters\-Number) &  \\
get\-Parameter\-Name & public & String & (int parameter\-Index) &  \\
get\-Arguments\-Number & public & int & () &  \\
remove\-Arguments & public & void & (params String[] arguments\-Names) &  \\
remove\-Arguments & public & void & (params Argument[] arguments) &  \\
remove\-All\-Arguments & public & void & () &  \\
add\-Constants & public & void & (params Constant[] constants) &  \\
define\-Constant & public & void & (String constant\-Name, double constant\-Value) &  \\
get\-Constant\-Index & public & int & (String constant\-Name) &  \\
get\-Constant & public & Constant & (String constant\-Name) &  \\
get\-Constant & public & Constant & (int constant\-Index) &  \\
get\-Constants\-Number & public & int & () &  \\
remove\-Constants & public & void & (params String[] constants\-Names) &  \\
remove\-Constants & public & void & (params Constant[] constants) &  \\
remove\-All\-Constants & public & void & () &  \\
add\-Functions & public & void & (params Function[] functions) &  \\
define\-Function & public & void & (String function\-Name, String  function\-Expression\-String,
				params String[] arguments\-Names) &  \\
get\-Function\-Index & public & int & (String function\-Name) &  \\
get\-Function & public & Function & (String function\-Name) &  \\
get\-Function & public & Function & (int function\-Index) &  \\
get\-Functions\-Number & public & int & () &  \\
remove\-Functions & public & void & (params String[] functions\-Names) &  \\
remove\-Functions & public & void & (params Function[] functions) &  \\
remove\-All\-Functions & public & void & () &  \\
set\-Verbose\-Mode & public & void & () &  \\
set\-Silent\-Mode & public & void & () &  \\
get\-Verbose\-Mode & public & bool & () &  \\
check\-Recursive\-Mode & internal & void & () &  \\
get\-Recursive\-Mode & public & bool & () &  \\
get\-Computing\-Time & public & double & () &  \\
add\-Related\-Expression & internal & void & (Expression expression) &  \\
remove\-Related\-Expression & internal & void & (Expression expression) &  \\
set\-Expression\-Modified\-Flags & internal & void & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{KwStrComparator}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Compare & public & int & (Key\-Word kw1, Key\-Word kw2) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DescKwLenComparator}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Compare & public & int & (Key\-Word kw1, Key\-Word kw2) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{KwTypeComparator}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Compare & public & int & (Key\-Word kw1, Key\-Word kw2) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{mXparser}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
VERSION & public const & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NOT\_FOUND & internal const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CONSOLE\_OUTPUT & private static volatile & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
primes\-Cache & public static & Primes\-Cache & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
THREADS\_NUMBER & private static & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
m\-Xparser\-Exp & internal static volatile & Expression & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ulp\-Rounding & internal volatile static & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
canonical\-Rounding & internal volatile static & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
almost\-Int\-Rounding & internal volatile static & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MAX\_RECURSION\_CALLS & internal volatile static & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
tokens\-To\-Remove & internal volatile static & List{\tt <}\-String\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
tokens\-To\-Modify & internal volatile static & List{\tt <}\-Token\-Modification\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
degrees\-Mode & internal volatile static & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
override\-Builtin\-Tokens & internal volatile static & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
options\-Changeset\-Number & internal volatile static & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
cancel\-Current\-Calculation\-Flag & private static volatile & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LICENSE & public const & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
init\-Primes\-Cache & public static & void & () &  \\
is\-Init\-Primes\-Cache\-Successful & public static & bool & () &  \\
init\-Primes\-Cache & public static & void & (int mximum\-Number\-In\-Cache) &  \\
init\-Primes\-Cache & public static & void & (Primes\-Cache primes\-Cache) &  \\
set\-No\-Primes\-Cache & public static & void & () &  \\
get\-Max\-Num\-In\-Primes\-Cache & public static & int & () &  \\
get\-Threads\-Number & public static & int & () &  \\
set\-Default\-Threads\-Number & public static & void & () &  \\
set\-Threads\-Number & public static & void & (int threads\-Number) &  \\
get\-Function\-Value & public static & double & (Expression f, Argument x, double x0) &  \\
array\-List2double & public static & double[] & (List{\tt <}\-Double\-{\tt >} numbers) &  \\
get\-Function\-Values & public static & double[] & (Expression f, Argument index, double from, double to, double delta) &  \\
set\-Random\-Generator & public static & void & (Random random\-Generator) &  \\
set\-Exact\-Comparison & public static & void & () &  \\
set\-Epsilon\-Comparison & public static & void & () &  \\
set\-Epsilon & public static & void & (double epsilon) &  \\
set\-Default\-Epsilon & public static & void & () &  \\
get\-Epsilon & public static & double & () &  \\
check\-If\-Epsilon\-Mode & public static & bool & () &  \\
check\-If\-Exact\-Mode & public static & bool & () &  \\
enable\-Ulp\-Rounding & public static & void & () &  \\
disable\-Ulp\-Rounding & public static & void & () &  \\
set\-Ulp\-Rounding & public static & void & (bool ulp\-Rounding\-State) &  \\
check\-If\-Ulp\-Rounding & public static & bool & () &  \\
enable\-Canonical\-Rounding & public static & void & () &  \\
disable\-Canonical\-Rounding & public static & void & () &  \\
set\-Canonical\-Rounding & public static & void & (bool canonical\-Rounding\-State) &  \\
check\-If\-Canonical\-Rounding & public static & bool & () &  \\
enable\-Almost\-Int\-Rounding & public static & void & () &  \\
disable\-Almost\-Int\-Rounding & public static & void & () &  \\
set\-Almost\-Int\-Rounding & public static & void & (bool almost\-Int\-Rounding\-State) &  \\
check\-If\-Almost\-Int\-Rounding & public static & bool & () &  \\
set\-Max\-Allowed\-Recursion\-Depth & public static & void & (int max\-Allowed\-Recursion\-Depth) &  \\
get\-Max\-Allowed\-Recursion\-Depth & public static & int & () &  \\
set\-Radians\-Mode & public static & void & () &  \\
set\-Degrees\-Mode & public static & void & () &  \\
check\-If\-Radians\-Mode & public static & bool & () &  \\
check\-If\-Degrees\-Mode & public static & bool & () &  \\
set\-To\-Fraction\-Init\-Search\-Size & public static & void & (long n) &  \\
get\-To\-Fraction\-Init\-Search\-Size & public static & long & () &  \\
remove\-Builtin\-Tokens & public static & void & (params String[] tokens) &  \\
unremove\-Builtin\-Tokens & public static & void & (params String[] tokens) &  \\
unremove\-All\-Builtin\-Tokens & public static & void & () &  \\
get\-Builtin\-Tokens\-To\-Remove & public static & String[] & () &  \\
modify\-Builtin\-Token & public static & void & (String current\-Token, String new\-Token) &  \\
modify\-Builtin\-Token & public static & void & (String current\-Token, String new\-Token, String new\-Token\-Description) &  \\
unmodify\-Builtin\-Tokens & public static & void & (params String[] current\-Or\-New\-Tokens) &  \\
unmodify\-All\-Builtin\-Tokens & public static & void & () &  \\
get\-Builtin\-Tokens\-To\-Modify & public static & String[,] & () &  \\
set\-To\-Override\-Builtin\-Tokens & public static & void & () &  \\
set\-Not\-To\-Override\-Builtin\-Tokens & public static & void & () &  \\
check\-Ifset\-To\-Override\-Builtin\-Tokens & public static & bool & () &  \\
set\-Default\-Options & public static & void & () &  \\
get\-Token\-Type\-Description & public static & String & (int token\-Type\-Id) &  \\
number\-To\-Hex\-String & public static & String & (int number) &  \\
number\-To\-Hex\-String & public static & String & (long number) &  \\
number\-To\-Hex\-String & public static & String & (double number) &  \\
hex\-String2Ascii\-String & public static & String & (String hex\-String) &  \\
number\-To\-Ascii\-String & public static & String & (int number) &  \\
number\-To\-Ascii\-String & public static & String & (long number) &  \\
number\-To\-Ascii\-String & public static & String & (double number) &  \\
conv\-Oth\-Base2Decimal & public static & double & (String number\-Literal, int numeral\-System\-Base) &  \\
conv\-Oth\-Base2Decimal & public static & double & (String number\-Literal) &  \\
conv\-Oth\-Base2Decimal & public static & double & (int numeral\-System\-Base, params int[] digits) &  \\
conv\-Oth\-Base2Decimal & public static & double & (double numeral\-System\-Base, params double[] digits) &  \\
conv\-Decimal2Oth\-Base & public static & String & (double decimal\-Number, int numeral\-System\-Base) &  \\
conv\-Decimal2Oth\-Base & public static & String & (double decimal\-Number, int numeral\-System\-Base, int format) &  \\
to\-Fraction & public static & double[] & (double value) &  \\
to\-Mixed\-Fraction & public static & double[] & (double value) &  \\
fraction\-To\-String & public static & String & (double[] fraction) &  \\
to\-Fraction\-String & public static & String & (double value) &  \\
to\-Mixed\-Fraction\-String & public static & String & (double value) &  \\
console\-Println & public static & void & (Object o) &  \\
console\-Println & public static & void & (String[] string\-Array) &  \\
console\-Println & public static & void & () &  \\
console\-Print & public static & void & (Object o) &  \\
reset\-Console\-Output & public static & void & () &  \\
set\-Default\-Console\-Prefix & public static & void & () &  \\
set\-Default\-Console\-Output\-Prefix & public static & void & () &  \\
set\-Console\-Prefix & public static & void & (String console\-Prefix) &  \\
set\-Console\-Output\-Prefix & public static & void & (String console\-Output\-Prefix) &  \\
get\-Console\-Output & public static & String & () &  \\
get\-Help & public static & String & () &  \\
get\-Help & public static & String & (String word) &  \\
console\-Print\-Help & public static & void & () &  \\
console\-Print\-Help & public static & void & (String word) &  \\
get\-Key\-Words & public static & List{\tt <}\-Key\-Word\-{\tt >} & () &  \\
get\-Key\-Words & public static & List{\tt <}\-Key\-Word\-{\tt >} & (String query) &  \\
regex\-Match & public static & bool & (String str, String pattern) &  \\
console\-Print\-Tokens & public static & void & (List{\tt <}\-Token\-{\tt >} tokens) &  \\
get\-License & public static & String & () &  \\
wait & public static & void & (int n) &  \\
cancel\-Current\-Calculation & public static & void & () &  \\
reset\-Cancel\-Current\-Calculation\-Flag & public static & void & () &  \\
is\-Current\-Calculation\-Cancelled & public static & bool & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PrimitiveElement}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
my\-Type\-Id & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Primitive\-Element & public & (int type\-Id) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
get\-My\-Type\-Id & public & int & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RecursiveArgument}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
TYPE\_ID\_RECURSIVE & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
base\-Values & private & List{\tt <}\-Double\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
recursive\-Counter & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Recursive\-Argument & public & (String argument\-Name, String recursive\-Expression\-String, String index\-Name) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Recursive\-Argument & public & (String argument\-Name, String recursive\-Expression\-String, Argument n, params Primitive\-Element[] elements) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Recursive\-Argument & public & (String argument\-Definition\-String, params Primitive\-Element[] elements) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
add\-Base\-Case & public & void & (int index, double value) &  \\
reset\-All\-Cases & public & void & () &  \\
get\-Argument\-Value & public & double & (double index) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Inheritance}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Register & public static & void & (Tyd\-Collection node) & Registers a single node.
         When we resolve later, we'll be able to use this node as a source. \\
Register\-All\-Roots & public static & void & (Tyd\-Document doc) & Registers all root nodes in a doc.
         When we resolve later, we'll be able to use the nodes in this document as a sources. \\
Resolve\-All & public static & void & () & Resolves all registered nodes. \\
Reset & public static & void & () & Reset the inheritance system to its initial state. Generally, this should only be used to recover from errors. \\
Link\-All\-Inheritance\-Nodes & private static & void & () & Link all unresolved nodes to their sources and heirs. \\
Resolve\-All\-Unresolved\-Inheritance\-Nodes & private static & void & () & Merge all unresolved nodes with their source nodes. \\
Resolve\-Inheritance\-Node\-And\-Heirs & private static & void & (Inheritance\-Node node) & Resolves given node and then all its heir nodes recursively using DFS. \\
Apply\-Inheritance & private static & void & (Tyd\-Node source, Tyd\-Node heir) & Copies all child nodes from source into heir, recursively.
         -If a node appears only in source or only in heir, it is included.
         -If a list appears in both source and heir, source's entries are appended to heir's entries.
         -If a non-list node appears in both source and heir, heir's node is overwritten. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TydFile}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
From\-Document & public static & Tyd\-File & (Tyd\-Document doc, string file\-Path = null) & Create a new Tyd\-File from a Tyd\-Document. \\
From\-File & public static & Tyd\-File & (string file\-Path, bool treat\-Xml\-As\-One\-Object = false) & Create a new Tyd\-File by loading data from a file at the given path. \\
Save & public & void & (string path = null) & Write to a file, overwriting any file present.
         If a path is provided, the file's path is changed to that new path before saving. Otherwise, the current path is used. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TydFromText}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Parse & private static & IEnumerable{\tt <}\-Tyd\-Node\-{\tt >} & (string text, int start\-Index, Tyd\-Node parent, bool expect\-Names = true) & Recursively parses the string 'text' starting at char index 'start\-Index' and ending when there is an unmatched closing bracket or EOF.
         text should have any opening bracket already stripped off.
         This recursive method is used both for parsing files, as well as for parsing specific entries inside files. \\
Resolve\-Escape\-Chars & private static & string & (string input) & Take the input string and replace any escape sequences with the final chars they correspond to.
         This can be opimized \\
Next\-Substance\-Index & private static & int & (string text, int p) & Returns the index of the next char after p that is not whitespace or part of a comment.
         If there is no more substance in the text, this returns an index just after the end of the text. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TydToText}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Write & public static & string & (Tyd\-Node node, int indent = 0) & Writes a given Tyd\-Node, along with all its descendants, as a string, at a given indent level.
         This method is recursive. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TydXml}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Tyd\-Node\-From\-Xml\-Document & public static & Tyd\-Node & ( Xml\-Document xml\-Document ) & Read an XML document and convert it to a single Tyd node.
     This treats the XML root as the root of a single table. \\
Tyd\-Nodes\-From\-Xml\-Document & public static & IEnumerable{\tt <}\-Tyd\-Node\-{\tt >} & ( Xml\-Document xml\-Document ) & Read an XML document and convert it to a sequence of Tyd nodes.
     This ignores the XML root and treats each of the root's children as a separate Tyd table. \\
Tyd\-Node\-From\-Xml\-Node & public static & Tyd\-Node & ( Xml\-Node xml\-Root, Tyd\-Node tyd\-Parent ) & Convert a single XML tree into a Tyd tree.
     If expect\-Name is false, it'll be parsed as a list item. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{EnterableBuilding}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add & public & void & (Actor actor) & Adds an actor to the building.
         The actor will be confined to the building until Remove() is called on the same actor. \\
Remove & public & void & (Actor actor) & Removes an actor from the building. \\
Contains & public & bool & (Actor actor) & Checks if the building contains an actor. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CentralIntelligence}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
groups & public & List{\tt <}\-Group\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{List of groups(which is a list of drones)} \\ \tabuphantomline
\_drone\-Prefab &  & Game\-Object & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The prefab to use when instatiating new drones.} \\ \tabuphantomline
NUMOFACTIONS & private const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The number of actions the AI is capable of doing in total. NOTE, when you add more actions this needs to be increased.} \\ \tabuphantomline
AIDECISIONTIME & private const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Seconds between each time the AI tries to reselect an action} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Drones & public & List{\tt <}\-Drone\-{\tt >} & \{ get; protected set; \} & All drones under CI's control. \\
Drone\-Type\-Count & public & Dictionary{\tt <}\-string, int\-{\tt >} & \{ get; protected set; \} & Drones of each type under the CI's control. \\
Last\-Time\-Chunk\-Was\-Scouted & public & Dictionary{\tt <}\-Vector2Int, float\-{\tt >} & \{ get; protected set; \} & Maps chunks to the last time the chunk was scouted. \\
Drone\-Count & public & int & \{ get =\-{\tt >} Drones.Count; \} public  & Total number of drones present in the army \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Awake &  & void & () & Drone building \\
Awake &  & void & () & Need a fighter group \\
Awake &  & void & () & Need a worker group \\
Awake &  & void & () & Need a scout group \\
Add\-Drone & public & void & (Drone drone) & Adds a drone to the CI's hivemind. \\
Set\-Last\-Time\-Scouted & public & void & (Vector2Int chunk, float time) & Updates the last time a chunk was scouted. \\
read\-Utility\-Function\-From\-File & private & string & (string filepath) & Reads a utility function from the provided lua filepath. \\
Create\-Group & public & void & () & Create the drone groups \\
Add\-Drone\-To\-Group & private & List{\tt <}\-Drone\-{\tt >} & () & assign drones to groups, this is where utility happens and drones are added to the list based on their usability \\
Get\-Fighter\-Groups & public & List{\tt <}\-Group\-{\tt >} & () & Get all the drone groups of a particular type \\
Add\-Group & public & void & (Group.Group\-Type group\-Type) & Add groups of a particular type to the army \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Command}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Do & public abstract & void & () & Does the command. \\
Undo & public abstract & void & () & Undoes the command. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CommandManager}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_undo\-Stack & private & Stack{\tt <}\-Command\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Stack of commands that have been performed and can be undone.} \\ \tabuphantomline
\_redo\-Stack & private & Stack{\tt <}\-Command\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Stack of commands that have been undone and can be redone.} \\ \tabuphantomline
On\-Do & public & Action{\tt <}\-Command\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Action invoked when Command\-Manager.Do() is called.} \\ \tabuphantomline
On\-Undo & public & Action{\tt <}\-Command\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Action invoked when Command\-Manager.Undo() is called with a non-empty undo stack.} \\ \tabuphantomline
On\-Redo & public & Action{\tt <}\-Command\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Action invoked when Command\-Manager.Redo() is called with a non-empty redo stack.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Command\-Manager & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Command\-Manager.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Do & public & void & (Command command) & Performs a command and adds it to the Command\-Manager's undo stack.
         Note: This will also clear the redo stack as non-linear command histories are not supported. \\
Undo & public & void & (int amount = 1) & Undoes the last command handled by the Command\-Manager. \\
Redo & public & void & (int amount = 1) & Redoes the last command undone by the Command\-Manager. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Drone}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_next\-Id & private static & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The id to assign to the next instantiated drone.} \\ \tabuphantomline
personal\-Channel\-Dictionary & public & Dictionary{\tt <}\-string, Unity\-Event\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Each channel needs to store their own messages on dictionaries} \\ \tabuphantomline
message\-List & public & List{\tt <}\-string\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{List of all the messages the drone will me listening after} \\ \tabuphantomline
message &  & string[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{String used for listening to messages contained in the message list} \\ \tabuphantomline
group\-ID & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Drone Group and it's ID} \\ \tabuphantomline
power\-Level & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The absolute strength of the drone} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
ID & public & int & \{ get; protected set; \} & Unique ID of the drone \\
Central\-Intelligence & public & Central\-Intelligence & \{ get; set; \} & The drone's central intelligence. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Setup\-Group &  & void & () & set the group script's id to match that of the drone \\
Initialize & public & void & (string type, int id) & Reads the drone's stats from lua. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Miner}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Setup & public & void & (string lua\-File) & Set mining related values to those found in the given lua file. \\
Mine & public & bool & () & Mines target, adds resources to inventory. \\
Set\-Target\-Resource & public & void & (Game\-Object target) & Sets the target resource to parameter game object \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Resource}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Mine & public & int & (int amount) & Takes a request of how much to mine the resource for. Returns how much you managed to mine. \\
Die & public & void & () & Destroy object and delete it from lists. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Group}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
group\-ID & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{the unique ID of the group} \\ \tabuphantomline
group\-Size & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Number of members of the group in question} \\ \tabuphantomline
message &  & string[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{String used for listening to messages contained in the message list} \\ \tabuphantomline
leader\-Status & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Leader status for the drone in question} \\ \tabuphantomline
group\-Members & public & List{\tt <}\-Game\-Object\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{All the group members in the group} \\ \tabuphantomline
group\-Message\-List & public & List{\tt <}\-string\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{A list of all messages currently sent to the group} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Construct\-Enemy\-List &  & void & () & Construct the list of enemies visible to the group \\
Leader\-Start\-Listening &  & void & () & Make the leader listen in on the channel \\
Assign\-New\-Leader &  & void & () & assign a new leader to the group, presumably because the previous one is dead. \\
Create\-Target\-Bounds & public & void & () & Create the radius of all the targets the group members are currently assigned to
     this is used for flanking behaviour \\
Assign\-Alpha\-Drones & private & void & () & Assign drones to the alpha unit, the primary fighting force of the group. Everyone starts in this unit and are diverged
     into sub-units later as needed \\
Assign\-Bravo\-Drones & private & void & () & Assign drones to the bravo unit, these are the second-most powerful force of the group, and the primary backup unit for flanking \\
Assign\-Charlie\-Drones & private & void & () & Assign drones to the charlie unit, the second weakest unit of the group, they provide support for bravo unit \\
Assign\-Delta\-Drones & private & void & () & Assign drones to the delta unit, the smallest and weakest unit of the group, they're dependant on the others for success in maneuvers \\
Divide\-Army & public & void & (int divisions) & For use in two-way flanking maneuvers, divide the army up into different tactical units up to four times \\
Get\-Group\-Units & public & List{\tt <}\-Game\-Object\-{\tt >} & (Drone.Group\-Unit unit) & return the group unit specified in the argument \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RTSLuaManager}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Create\-Script & public override & Script & () & Creates a Moon\-Sharp.Interpreter.Script set up to accept our awesome scripting API. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{EventManager}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_global\-Channel\-Dictionary & protected & Dictionary{\tt <}\-string, Unity\-Event\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Each channel needs to store their own messages on dictionaries
     Personal channel dictionaries for the drones are located in Drone.cs
     Each group needs to store their messages in a dictionary as well} \\ \tabuphantomline
no\-ID & const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The default value of the IDs} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Start\-Listening & protected static & void & (string event\-Name, Unity\-Action listener, Message\-Channel channel, int ID = no\-ID) &  \\
Stop\-Listening & protected static & void & (string event\-Name, Unity\-Action listener, Message\-Channel channel, int drone\-ID = no\-ID) & Stop listening in on the specified channel event \\
Trigger\-Event & protected static & void & (string event\-Name, Message\-Channel channel, int drone\-ID = no\-ID) & Trigger the event on the specified channel, actually sending the message to the listeners. \\
Add\-Private\-Channel & protected static & void & (Dictionary{\tt <}\-string, Unity\-Event\-{\tt >} channel) & Add a private channel to the list of Private Channels \\
Remove\-Private\-Channel & protected static & void & (Dictionary{\tt <}\-string, Unity\-Event\-{\tt >} channel) & Remove a private channel from the Private Channel list \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ListenToChannel}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Listen\-To\-Message & public & void & (string message) & Listen continually for messages on the channel provided in the enumerator \\
Message\-List & private & List{\tt <}\-string\-{\tt >} & () & The list of messages individual drones can listen to \\
Group\-Message\-List & private & List{\tt <}\-string\-{\tt >} & () & The list of messages a group can listen to \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SendMessageToChannel}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Send & public & void & (string message, Message\-Channel channel, int ID = -1) & Send a message to the channel specified, ID is optional \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RTSNetworkRoomManager}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Room\-Start\-Server & public override & void & () & This is called on the server when the server is started - including when a host is started. \\
On\-Room\-Start\-Host & public override & void & () & This is called on the host when a host is started. \\
On\-Room\-Stop\-Host & public override & void & () & This is called on the host when the host is stopped. \\
On\-Room\-Server\-Connect & public override & void & (Network\-Connection conn) & This is called on the server when a new client connects to the server. \\
On\-Room\-Server\-Disconnect & public override & void & (Network\-Connection conn) & This is called on the server when a client disconnects. \\
On\-Room\-Server\-Scene\-Changed & public override & void & (string scene\-Name) & This is called on the server when a networked scene finishes loading. \\
On\-Room\-Server\-Create\-Room\-Player & public override & Game\-Object & (Network\-Connection conn) & This allows customization of the creation of the room-player object on the server.
         By default the room\-Player\-Prefab is used to create the room-player, but this function allows that behaviour to be customized. \\
On\-Room\-Server\-Create\-Game\-Player & public override & Game\-Object & (Network\-Connection conn, Game\-Object room\-Player) & This allows customization of the creation of the Game\-Player object on the server.
         By default the game\-Player\-Prefab is used to create the game-player, but this function allows that behaviour to be customized. The object returned from the function will be used to replace the room-player on the connection. \\
On\-Room\-Server\-Add\-Player & public override & void & (Network\-Connection conn) & This allows customization of the creation of the Game\-Player object on the server.
         This is only called for subsequent Game\-Play scenes after the first one.
         See On\-Room\-Server\-Create\-Game\-Player to customize the player object for the initial Game\-Play scene. \\
On\-Room\-Server\-Scene\-Loaded\-For\-Player & public override & bool & (Network\-Connection conn, Game\-Object room\-Player, Game\-Object game\-Player) & This is called on the server when it is told that a client has finished switching from the room scene to a game player scene.
         When switching from the room, the room-player is replaced with a game-player object. This callback function gives an opportunity to apply state from the room-player to the game-player object. \\
On\-Room\-Server\-Players\-Ready & public override & void & () & This is called on the server when all the players in the room are ready.
         The default implementation of this function uses Server\-Change\-Scene() to switch to the game player scene. By implementing this callback you can customize what happens when all the players in the room are ready, such as adding a countdown or a confirmation for a group leader. \\
On\-Room\-Client\-Enter & public override & void & () & This is a hook to allow custom behaviour when the game client enters the room. \\
On\-Room\-Client\-Exit & public override & void & () & This is a hook to allow custom behaviour when the game client exits the room. \\
On\-Room\-Client\-Connect & public override & void & (Network\-Connection conn) & This is called on the client when it connects to server. \\
On\-Room\-Client\-Disconnect & public override & void & (Network\-Connection conn) & This is called on the client when disconnected from a server. \\
On\-Room\-Start\-Client & public override & void & () & This is called on the client when a client is started. \\
On\-Room\-Stop\-Client & public override & void & () & This is called on the client when the client stops. \\
On\-Room\-Client\-Scene\-Changed & public override & void & (Network\-Connection conn) & This is called on the client when the client is finished loading a new networked scene. \\
On\-Room\-Client\-Add\-Player\-Failed & public override & void & () & Called on the client when adding a player to the room fails.
         This could be because the room is full, or the connection is not allowed to have more players. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{LaserWeapon}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Laser\-Line & public & Line\-Renderer & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Draws a straight line between points given to it.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Shoot\-Laser & private & void & () & Shoots A laser form the gun\-End of the owner to its owners target. \\
Shoot\-Laser\-Coroutine & protected & IEnumerator & () & Draws the laser line \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Factory}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Order\-Drone &  & void & (string drone\-Type, float build\-Time) & Order a drone of the specific type to be built. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{AssignedDronePercentage}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Assigned\-Drone\-Percentage & public & (Central\-Intelligence CI, string function, string drone\-Name, string task) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructor} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DronePower}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Drone\-Power & public & (Central\-Intelligence CI, int ID, string function) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructor} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NeedDefenseGroup}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_central\-Intelligence &  & Central\-Intelligence & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The instance of central intelligence the factor will be applied to} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NeedFighterGroup}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_central\-Intelligence &  & Central\-Intelligence & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The Central Intelligence instance the factor will be applied to} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NeedMixedGroup}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_central\-Intelligence &  & Central\-Intelligence & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The Central Intelligence instance the factor will be applied to} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ResourceAmount}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Resource\-Amount & public & (Central\-Intelligence CI, string resource, string function) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructor.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviourTree}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Editor\-Save\-Data & public & Bbbt\-Behaviour\-Tree\-Editor\-Save\-Data & \{ get; protected set; \} & The data needed to reconstruct the tree in the editor. \\
Save\-Data & public & Bbbt\-Behaviour\-Tree\-Save\-Data & \{ get; protected set; \} & The data needed to functionally reconstruct the behaviour tree. \\
Root\-Behaviour & public & Bbbt\-Behaviour & \{ get; protected set; \} & The entry point of the behaviour tree. \\
Behaviours & public & List{\tt <}\-Bbbt\-Behaviour\-{\tt >} & \{ get; protected set; \} & A list of all the behaviours in the tree. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Save & public & void & (Bbbt\-Behaviour\-Tree\-Editor\-Save\-Data editor\-Save\-Data, Bbbt\-Behaviour\-Tree\-Save\-Data save\-Data) & Saves the behaviour tree's data to a json file of the same name as the tree. \\
Load\-Save\-Data & public & void & (Bbbt\-Behaviour\-Tree source\-Tree = null) & Loads the behaviour tree save data from the json file of the same name in the json directory. \\
Build\-Tree & private & void & () & Builds a functional behaviour tree from the save data. \\
Find\-Behaviour\-Tree\-With\-Name & public static & Bbbt\-Behaviour\-Tree & (string query) & Tries to find a beahaviour tree that matches a given query (case insensitive). \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviourTreeComponent}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Tree & public & Bbbt\-Behaviour\-Tree & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The unique tree belonging to this component.} \\ \tabuphantomline
\_root\-Node & private & Bbbt\-Behaviour & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The entry point of the behaviour tree.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Update & private & void & () & Called every frame. \\
Set\-Behaviour\-Tree & public & void & (string tree\-Name) & Awake is called before Start. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviourTreeEditorSaveData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Nodes & public & Bbbt\-Node\-Save\-Data[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The save data for the nodes belonging to the behaviour tree.} \\ \tabuphantomline
Connections & public & Bbbt\-Connection\-Save\-Data[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The save data for the connections between the nodes in the behaviour tree.} \\ \tabuphantomline
Window\-Offset\-X & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The amount by which the behaviour tree has been offset from the centre of the editor window in the x axis.} \\ \tabuphantomline
Window\-Offset\-Y & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The amount by which the behaviour tree has been offset from the centre of the editor window in the y axis.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Behaviour\-Tree\-Editor\-Save\-Data & public & (
            Bbbt\-Node\-Save\-Data[] nodes,
            Bbbt\-Connection\-Save\-Data[] connections,
            float window\-Offset\-X,
            float window\-Offset\-Y) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a Bbbt\-Behaviour\-Tree\-Save\-Data object.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviourTreeSaveData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Root & public & Bbbt\-Root & \{ get; protected set; \} & The data needed to load the root behaviour. \\
Root & public & Bbbt\-Root & \{ get; protected set; \} & The root of the behaviour tree. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Behaviour\-Tree\-Save\-Data & public & (/*Bbbt\-Root\-Save\-Data root\-Save\-Data*/ Bbbt\-Root root) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Bbbt\-Behaviour\-Tree\-Save\-Data object.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtConnectionSaveData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
In\-Node\-Id & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The id of the node to which the connection leads.} \\ \tabuphantomline
Out\-Node\-Id & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The id of the node from which the connection leads.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Connection\-Save\-Data & public & (int in\-Node\-Id, int out\-Node\-Id) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a Bbbt\-Connection\-Save\-Data object.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtNodeSaveData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Id & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Unique ID used to identify the node.} \\ \tabuphantomline
Base\-Behaviour & public & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The name of the node's base behaviour.} \\ \tabuphantomline
Base\-Behaviour\-Instance\-Id & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The instance id of the node's base behaviour.} \\ \tabuphantomline
Behaviour & public & Bbbt\-Behaviour & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The behaviour attached to the node.} \\ \tabuphantomline
X & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The node's X position.} \\ \tabuphantomline
Y & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The node's Y position.} \\ \tabuphantomline
Is\-Selected & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Whether the node is selected.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Node\-Save\-Data & public & (
            int id,
            string base\-Behaviour,
            int base\-Behaviour\-Instance\-Id,
            Bbbt\-Behaviour behaviour,
            float x,
            float y,
            bool is\-Selected) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a Bbbt\-Node\-Save\-Data object.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtConstants}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Json\-Directory & public static & string & \{ get; \} & The directory which contains behaviour tree json save data. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DOTweenModuleAudio}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
DOFade & public static & Tweener\-Core{\tt <}\-float, float, Float\-Options\-{\tt >} & (this Audio\-Source target, float end\-Value, float duration) & Tweens an Audio\-Source's volume to the given value.
         Also stores the Audio\-Source as the tween's target so it can be used for filtered operations \\
DOPitch & public static & Tweener\-Core{\tt <}\-float, float, Float\-Options\-{\tt >} & (this Audio\-Source target, float end\-Value, float duration) & Tweens an Audio\-Source's pitch to the given value.
         Also stores the Audio\-Source as the tween's target so it can be used for filtered operations \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DOTweenModulePhysics}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
DOMove & public static & Tweener\-Core{\tt <}\-Vector3, Vector3, Vector\-Options\-{\tt >} & (this Rigidbody target, Vector3 end\-Value, float duration, bool snapping = false) & Tweens a Rigidbody's position to the given value.
         Also stores the rigidbody as the tween's target so it can be used for filtered operations \\
DOMove\-X & public static & Tweener\-Core{\tt <}\-Vector3, Vector3, Vector\-Options\-{\tt >} & (this Rigidbody target, float end\-Value, float duration, bool snapping = false) & Tweens a Rigidbody's X position to the given value.
         Also stores the rigidbody as the tween's target so it can be used for filtered operations \\
DOMove\-Y & public static & Tweener\-Core{\tt <}\-Vector3, Vector3, Vector\-Options\-{\tt >} & (this Rigidbody target, float end\-Value, float duration, bool snapping = false) & Tweens a Rigidbody's Y position to the given value.
         Also stores the rigidbody as the tween's target so it can be used for filtered operations \\
DOMove\-Z & public static & Tweener\-Core{\tt <}\-Vector3, Vector3, Vector\-Options\-{\tt >} & (this Rigidbody target, float end\-Value, float duration, bool snapping = false) & Tweens a Rigidbody's Z position to the given value.
         Also stores the rigidbody as the tween's target so it can be used for filtered operations \\
DORotate & public static & Tweener\-Core{\tt <}\-Quaternion, Vector3, Quaternion\-Options\-{\tt >} & (this Rigidbody target, Vector3 end\-Value, float duration, Rotate\-Mode mode = Rotate\-Mode.Fast) & Tweens a Rigidbody's rotation to the given value.
         Also stores the rigidbody as the tween's target so it can be used for filtered operations \\
DOLook\-At & public static & Tweener\-Core{\tt <}\-Quaternion, Vector3, Quaternion\-Options\-{\tt >} & (this Rigidbody target, Vector3 towards, float duration, Axis\-Constraint axis\-Constraint = Axis\-Constraint.None, Vector3? up = null) & Tweens a Rigidbody's rotation so that it will look towards the given position.
         Also stores the rigidbody as the tween's target so it can be used for filtered operations \\
DOJump & public static & Sequence & (this Rigidbody target, Vector3 end\-Value, float jump\-Power, int num\-Jumps, float duration, bool snapping = false) & Tweens a Rigidbody's position to the given value, while also applying a jump effect along the Y axis.
         Returns a Sequence instead of a Tweener.
         Also stores the Rigidbody as the tween's target so it can be used for filtered operations \\
DOPath & public static & Tweener\-Core{\tt <}\-Vector3, Path, Path\-Options\-{\tt >} & (
            this Rigidbody target, Vector3[] path, float duration, Path\-Type path\-Type = Path\-Type.Linear,
            Path\-Mode path\-Mode = Path\-Mode.Full3D, int resolution = 10, Color? gizmo\-Color = null
        ) & Tweens a Rigidbody's position through the given path waypoints, using the chosen path algorithm.
         Also stores the Rigidbody as the tween's target so it can be used for filtered operations.
         NOTE: to tween a rigidbody correctly it should be set to kinematic at least while being tweened.
         BEWARE: doesn't work on Windows Phone store (waiting for Unity to fix their own bug).
         If you plan to publish there you should use a regular transform.DOPath. \\
DOLocal\-Path & public static & Tweener\-Core{\tt <}\-Vector3, Path, Path\-Options\-{\tt >} & (
            this Rigidbody target, Vector3[] path, float duration, Path\-Type path\-Type = Path\-Type.Linear,
            Path\-Mode path\-Mode = Path\-Mode.Full3D, int resolution = 10, Color? gizmo\-Color = null
        ) & Tweens a Rigidbody's local\-Position through the given path waypoints, using the chosen path algorithm.
         Also stores the Rigidbody as the tween's target so it can be used for filtered operations
         NOTE: to tween a rigidbody correctly it should be set to kinematic at least while being tweened.
         BEWARE: doesn't work on Windows Phone store (waiting for Unity to fix their own bug).
         If you plan to publish there you should use a regular transform.DOLocal\-Path. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DOTweenModuleUtils}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Init & public static & void & () & Called via Reflection by DOTween\-Component on Awake \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkDiscovery}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Process\-Request & protected override & Server\-Response & (Server\-Request request, IPEnd\-Point endpoint) & Process the request from a client \\
Get\-Request & protected override & Server\-Request & () & Create a message that will be broadcasted on the network to discover servers \\
Process\-Response & protected override & void & (Server\-Response response, IPEnd\-Point endpoint) & Process the answer from a server \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkDiscoveryBase}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Start & public virtual & void & () & virtual so that inheriting classes' Start() can call base.Start() too \\
Advertise\-Server & public & void & () & Advertise this server in the local network \\
Process\-Client\-Request & protected virtual & void & (Request request, IPEnd\-Point endpoint) & Reply to the client to inform it of this server \\
Process\-Request & protected abstract & Response & (Request request, IPEnd\-Point endpoint) & Process the request from a client \\
Start\-Discovery & public & void & () & Start Active Discovery \\
Stop\-Discovery & public & void & () & Stop Active Discovery \\
Client\-Listen\-Async & public async & Task & () & Awaits for server response \\
Broadcast\-Discovery\-Request & public & void & () & Sends discovery request from client \\
Get\-Request & protected virtual & Request & () & Create a message that will be broadcasted on the network to discover servers \\
Process\-Response & protected abstract & void & (Response response, IPEnd\-Point endpoint) & Process the answer from a server \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Transport}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
active\-Transport & public static & Transport & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The current transport used by Mirror.} \\ \tabuphantomline
On\-Client\-Connected & public & Unity\-Event & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Notify subscribers when when this client establish a successful connection to the server} \\ \tabuphantomline
On\-Client\-Data\-Received & public & Client\-Data\-Received\-Event & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Notify subscribers when this client receive data from the server} \\ \tabuphantomline
On\-Client\-Error & public & Unity\-Event\-Exception & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Notify subscribers when this clianet encounters an error communicating with the server} \\ \tabuphantomline
On\-Client\-Disconnected & public & Unity\-Event & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Notify subscribers when this client disconnects from the server} \\ \tabuphantomline
On\-Server\-Connected & public & Unity\-Event\-Int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Notify subscribers when a client connects to this server} \\ \tabuphantomline
On\-Server\-Data\-Received & public & Server\-Data\-Received\-Event & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Notify subscribers when this server receives data from the client} \\ \tabuphantomline
On\-Server\-Error & public & Unity\-Event\-Int\-Exception & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Notify subscribers when this server has some problem communicating with the client} \\ \tabuphantomline
On\-Server\-Disconnected & public & Unity\-Event\-Int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Notify subscribers when a client disconnects from this server} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Available & public abstract & bool & () & Is this transport available in the current platform?
         Some transports might only be available in mobile
         Many will not work in webgl
         Example usage: return Application.platform == Runtime\-Platform.Web\-GLPlayer \\
Client\-Connected & public abstract & bool & () & Determines if we are currently connected to the server \\
Client\-Connect & public abstract & void & (string address) & Establish a connection to a server \\
Client\-Connect & public virtual & void & (Uri uri) & Establish a connection to a server \\
Client\-Send & public abstract & bool & (int channel\-Id, Array\-Segment{\tt <}\-byte\-{\tt >} segment) & Send data to the server \\
Client\-Disconnect & public abstract & void & () & Disconnect this client from the server \\
Server\-Uri & public abstract & Uri & () & Retrieves the address of this server.
         Useful for network discovery \\
Server\-Active & public abstract & bool & () & Determines if the server is up and running \\
Server\-Start & public abstract & void & () & Start listening for clients \\
Server\-Send & public abstract & bool & (List{\tt <}\-int\-{\tt >} connection\-Ids, int channel\-Id, Array\-Segment{\tt <}\-byte\-{\tt >} segment) & Send data to one or multiple clients. We provide a list, so that transports can make use
         of multicasting, and avoid allocations where possible.
        
         We don't provide a single Server\-Send function to reduce complexity. Simply overwrite this
         one in your Transport. \\
Server\-Disconnect & public abstract & bool & (int connection\-Id) & Disconnect a client from this server.  Useful to kick people out. \\
Get\-Connection\-Info & public virtual & bool & (int connection\-Id, out string address) & Obsolete: Use  instead \\
Server\-Get\-Client\-Address & public abstract & string & (int connection\-Id) & Get the client address \\
Server\-Stop & public abstract & void & () & Stop listening for clients and disconnect all existing clients \\
Get\-Max\-Packet\-Size & public abstract & int & (int channel\-Id = Channels.Default\-Reliable) & The maximum packet size for a given channel.  Unreliable transports
         usually can only deliver small packets. Reliable fragmented channels
         can usually deliver large ones.
        
         Get\-Max\-Packet\-Size needs to return a value at all times. Even if the
         Transport isn't running, or isn't Available(). This is because
         Fallback and Multiplex transports need to find the smallest possible
         packet size at runtime. \\
Shutdown & public abstract & void & () & Shut down the transport, both as client and server \\
On\-Application\-Quit & public virtual & void & () & called when quitting the application by closing the window / pressing stop in the editor
         virtual so that inheriting classes' On\-Application\-Quit() can call base.On\-Application\-Quit() too \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoonSharpVsCodeDebugServer}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Current\-Id & public & int? & \{ get set var current = (m\_Debugger\-List.First\-Or\-Default(d =\-{\tt >} d.Id == value)); if (current == null) throw new Argument\-Exception("Cannot find debugger with given Id."); m\_Current = current; \} \} \} & Gets or sets the current script by ID (see Get\-Attached\-Debuggers\-By\-Id\-And\-Name). 
		 New vscode connections will attach to this debugger ID. Changing the current ID does NOT disconnect
		 connected clients. \\
Current & public & Script & \{ get set var current = (m\_Debugger\-List.First\-Or\-Default(d =\-{\tt >} d.Script == value)); if (current == null) throw new Argument\-Exception("Cannot find debugger with given script associated."); m\_Current = current; \} \} \} & Gets or sets the current script. New vscode connections will attach to this script. Changing the current script does NOT disconnect
		 connected clients. \\
Logger & public & Action{\tt <}\-string\-{\tt >} & \{ get; set; \} & Gets or sets a delegate which will be called when logging messages are generated \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Moon\-Sharp\-Vs\-Code\-Debug\-Server & public & (int port = 41912) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Moon\-Sharp\-Vs\-Code\-Debug\-Server & public & (Script script, int port, Func{\tt <}\-Source\-Code, string\-{\tt >} source\-Finder = null) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class with a default script.
		 Note that for this specific script, it will NOT attach the debugger to the script.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Attach\-To\-Script & public & void & (Script script, string name, Func{\tt <}\-Source\-Code, string\-{\tt >} source\-Finder = null) & Attaches the specified script to the debugger \\
Get\-Attached\-Debuggers\-By\-Id\-And\-Name & public & IEnumerable{\tt <}\-Key\-Value\-Pair{\tt <}\-int, string\-{\tt >}\-{\tt >} & () & Gets a list of the attached debuggers by id and name \\
Detach & public & void & (Script script) & Detaches the specified script. The debugger attached to that script will get disconnected. \\
Get\-Debugger & public & IDebugger & () & Gets the debugger object. Obsolete, use the new interface using the Attach method instead. \\
Dispose & public & void & () & Stops listening \\
Start & public & Moon\-Sharp\-Vs\-Code\-Debug\-Server & () & Starts listening on the localhost for incoming connections. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{LinqHelpers}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Convert & public static & IEnumerable{\tt <}\-T\-{\tt >} & (this IEnumerable{\tt <}\-Dyn\-Value\-{\tt >} enumerable, Data\-Type type) & Converts the specified enumerable dynvalues of a given script type to objects of a given type \\
Of\-Data\-Type & public static & IEnumerable{\tt <}\-Dyn\-Value\-{\tt >} & (this IEnumerable{\tt <}\-Dyn\-Value\-{\tt >} enumerable, Data\-Type type) & Filters an enumeration for items of the given script type \\
As\-Objects & public static & IEnumerable{\tt <}\-object\-{\tt >} & (this IEnumerable{\tt <}\-Dyn\-Value\-{\tt >} enumerable) & Converts the elements to CLR objects \\
As\-Objects & public static & IEnumerable{\tt <}\-T\-{\tt >} & (this IEnumerable{\tt <}\-Dyn\-Value\-{\tt >} enumerable) & Converts the elements to CLR objects of the desired type \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Script}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
VERSION & public const & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The version of the Moon\-Sharp engine} \\ \tabuphantomline
LUA\_VERSION & public const & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The Lua version being supported} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Default\-Options & public static & Script\-Options & \{ get; private set; \} & Gets or sets the script loader which will be used as the value of the
		 Script\-Loader property for all newly created scripts. \\
Options & public & Script\-Options & \{ get; private set; \} & Gets access to the script options. \\
Global\-Options & public static & Script\-Global\-Options & \{ get; private set; \} & Gets the global options, that is options which cannot be customized per-script. \\
Performance\-Stats & public & Performance\-Statistics & \{ get; private set; \} & Gets access to performance statistics. \\
Globals & public & Table & \{ get \} & Gets the default global table for this script. Unless a different table is intentionally passed (or setfenv has been used)
		 execution uses this table. \\
Debugger\-Enabled & public & bool & \{ get set \} & Gets or sets a value indicating whether the debugger is enabled.
		 Note that unless a debugger attached, this property returns a 
		 value which might not reflect the real status of the debugger.
		 Use this property if you want to disable the debugger for some 
		 executions. \\
Source\-Code\-Count & public & int & \{ get \} & Gets the source code count. \\
Registry & public & Table & \{ get; private set; \} & Moon\-Sharp (like Lua itself) provides a registry, a predefined table that can be used by any CLR code to 
		 store whatever Lua values it needs to store. 
		 Any CLR code can store data into this table, but it should take care to choose keys 
		 that are different from those used by other libraries, to avoid collisions. 
		 Typically, you should use as key a string GUID, a string containing your library name, or a 
		 userdata with the address of a CLR object in your code. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Script & static & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes the  class.} \\ \tabuphantomline
Script & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  clas.s} \\ \tabuphantomline
Script & public & (Core\-Modules core\-Modules) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Load\-Function & public & Dyn\-Value & (string code, Table global\-Table = null, string func\-Friendly\-Name = null) & Loads a string containing a Lua/Moon\-Sharp function. \\
Load\-String & public & Dyn\-Value & (string code, Table global\-Table = null, string code\-Friendly\-Name = null) & Loads a string containing a Lua/Moon\-Sharp script. \\
Load\-Stream & public & Dyn\-Value & (Stream stream, Table global\-Table = null, string code\-Friendly\-Name = null) & Loads a Lua/Moon\-Sharp script from a System.IO.Stream. NOTE: This will *NOT* close the stream! \\
Dump & public & void & (Dyn\-Value function, Stream stream) & Dumps on the specified stream. \\
Load\-File & public & Dyn\-Value & (string filename, Table global\-Context = null, string friendly\-Filename = null) & Loads a string containing a Lua/Moon\-Sharp script. \\
Do\-String & public & Dyn\-Value & (string code, Table global\-Context = null, string code\-Friendly\-Name = null) & Loads and executes a string containing a Lua/Moon\-Sharp script. \\
Do\-Stream & public & Dyn\-Value & (Stream stream, Table global\-Context = null, string code\-Friendly\-Name = null) & Loads and executes a stream containing a Lua/Moon\-Sharp script. \\
Do\-File & public & Dyn\-Value & (string filename, Table global\-Context = null, string code\-Friendly\-Name = null) & Loads and executes a file containing a Lua/Moon\-Sharp script. \\
Run\-File & public static & Dyn\-Value & (string filename) & Runs the specified file with all possible defaults for quick experimenting. \\
Run\-String & public static & Dyn\-Value & (string code) & Runs the specified code with all possible defaults for quick experimenting. \\
Make\-Closure & private & Dyn\-Value & (int address, Table env\-Table = null) & Creates a closure from a bytecode address. \\
Call & public & Dyn\-Value & (Dyn\-Value function) & Calls the specified function. \\
Call & public & Dyn\-Value & (Dyn\-Value function, params Dyn\-Value[] args) & Calls the specified function. \\
Call & public & Dyn\-Value & (Dyn\-Value function, params object[] args) & Calls the specified function. \\
Call & public & Dyn\-Value & (object function) & Calls the specified function. \\
Call & public & Dyn\-Value & (object function, params object[] args) & Calls the specified function. \\
Create\-Coroutine & public & Dyn\-Value & (Dyn\-Value function) & Creates a coroutine pointing at the specified function. \\
Create\-Coroutine & public & Dyn\-Value & (object function) & Creates a coroutine pointing at the specified function. \\
Attach\-Debugger & public & void & (IDebugger debugger) & Attaches a debugger. This usually should be called by the debugger itself and not by user code. \\
Get\-Source\-Code & public & Source\-Code & (int source\-Code\-ID) & Gets the source code. \\
Require\-Module & public & Dyn\-Value & (string modname, Table global\-Context = null) & Loads a module as per the "require" Lua function. http://www.lua.org/pil/8.1.html \\
Get\-Type\-Metatable & public & Table & (Data\-Type type) & Gets a type metatable. \\
Set\-Type\-Metatable & public & void & (Data\-Type type, Table metatable) & Sets a type metatable. \\
Warm\-Up & public static & void & () & Warms up the parser/lexer structures so that Moon\-Sharp operations start faster. \\
Create\-Dynamic\-Expression & public & Dynamic\-Expression & (string code) & Creates a new dynamic expression. \\
Create\-Constant\-Dynamic\-Expression & public & Dynamic\-Expression & (string code, Dyn\-Value constant) & Creates a new dynamic expression which is actually quite static, returning always the same constant value. \\
Create\-Dynamic\-Execution\-Context & internal & Script\-Execution\-Context & (Callback\-Function func = null) & Gets an execution context exposing only partial functionality, which should be used for
		 those cases where the execution engine is not really running - for example for dynamic expression
		 or calls from CLR to CLR callbacks \\
Get\-Banner & public static & string & (string subproduct = null) & Gets a banner string with copyright info, link to website, version, etc. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ScriptGlobalOptions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Custom\-Converters & public & Custom\-Converters\-Collection & \{ get; set; \} & Gets or sets the custom converters. \\
Platform & public & IPlatform\-Accessor & \{ get; set; \} & Gets or sets the platform abstraction to use. \\
Rethrow\-Exception\-Nested & public & bool & \{ get; set; \} & Gets or sets a value indicating whether interpreter exceptions should be 
		 re-thrown as nested exceptions. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ScriptOptions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Script\-Loader & public & IScript\-Loader & \{ get; set; \} & Gets or sets the current script-loader. \\
Debug\-Print & public & Action{\tt <}\-string\-{\tt >} & \{ get; set; \} & Gets or sets the debug print handler \\
Debug\-Input & public & Func{\tt <}\-string, string\-{\tt >} & \{ get; set; \} & Gets or sets the debug input handler (takes a prompt as an input, for interactive interpreters, like debug.debug). \\
Use\-Lua\-Error\-Locations & public & bool & \{ get; set; \} & Gets or sets a value indicating whether error messages will use Lua error locations instead of Moon\-Sharp 
		 improved ones. Use this for compatibility with legacy Lua code which parses error messages. \\
Colon\-Operator\-Clr\-Callback\-Behaviour & public & Colon\-Operator\-Behaviour & \{ get; set; \} & Gets or sets a value which dictates the behaviour of the colon (':') operator in callbacks to CLR code. \\
Stdin & public & Stream & \{ get; set; \} & Gets or sets the stream used as stdin. If null, a default stream is used. \\
Stdout & public & Stream & \{ get; set; \} & Gets or sets the stream used as stdout. If null, a default stream is used. \\
Stderr & public & Stream & \{ get; set; \} & Gets or sets the stream used as stderr. If null, a default stream is used. \\
Tail\-Call\-Optimization\-Threshold & public & int & \{ get; set; \} & Gets or sets the stack depth threshold at which Moon\-Sharp starts doing
		 tail call optimizations.
		 TCOs can provide the little benefit of avoiding stack overflows in corner case
		 scenarios, at the expense of losing debug information and error stack traces 
		 in all other, more common scenarios. Moon\-Sharp choice is to start performing
		 TCOs only after a certain threshold of stack usage is reached - by default
		 half the current stack depth (128K entries), thus 64K entries, on either
		 the internal stacks.
		 Set this to int.Max\-Value to disable TCOs entirely, or to 0 to always have
		 TCOs enabled. \\
Check\-Thread\-Access & public & bool & \{ get; set; \} & Gets or sets a value indicating whether the thread check is enabled.
		 A "lazy" thread check is performed everytime execution is entered to ensure that no two threads
		 calls Moon\-Sharp execution concurrently. However 1) the check is performed best effort (thus, it might
		 not detect all issues) and 2) it might trigger in very odd legal situations (like, switching threads 
		 inside a CLR-callback without actually having concurrency.
		 
		 Disable this option if the thread check is giving problems in your scenario, but please check that
		 you are not calling Moon\-Sharp execution concurrently as it is not supported. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{AstronomicalConstants}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
LIGHT\_YEAR & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ASTRONOMICAL\_UNIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PARSEC & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILOPARSEC & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EARTH\_RADIUS\_EQUATORIAL & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EARTH\_RADIUS\_POLAR & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EARTH\_RADIUS\_MEAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EARTH\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EARTH\_SEMI\_MAJOR\_AXIS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MOON\_RADIUS\_MEAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MOON\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MONN\_SEMI\_MAJOR\_AXIS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SOLAR\_RADIUS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SOLAR\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MERCURY\_RADIUS\_MEAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MERCURY\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MERCURY\_SEMI\_MAJOR\_AXIS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
VENUS\_RADIUS\_MEAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
VENUS\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
VENUS\_SEMI\_MAJOR\_AXIS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MARS\_RADIUS\_MEAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MARS\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MARS\_SEMI\_MAJOR\_AXIS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
JUPITER\_RADIUS\_MEAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
JUPITER\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
JUPITER\_SEMI\_MAJOR\_AXIS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SATURN\_RADIUS\_MEAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SATURN\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SATURN\_SEMI\_MAJOR\_AXIS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
URANUS\_RADIUS\_MEAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
URANUS\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
URANUS\_SEMI\_MAJOR\_AXIS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NEPTUNE\_RADIUS\_MEAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NEPTUNE\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NEPTUNE\_SEMI\_MAJOR\_AXIS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BinaryRelations}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
DEFAULT\_COMPARISON\_EPSILON & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
epsilon & internal static & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
epsilon\-Comparison & internal static & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
set\-Exact\-Comparison & public static & void & () &  \\
set\-Epsilon\-Comparison & public static & void & () &  \\
set\-Epsilon & public static & void & (double epsilon) &  \\
set\-Default\-Epsilon & public static & void & () &  \\
get\-Epsilon & public static & double & () &  \\
check\-If\-Epsilon\-Mode & public static & bool & () &  \\
check\-If\-Exact\-Mode & public static & bool & () &  \\
eq & public static & double & (double a, double b) &  \\
neq & public static & double & (double a, double b) &  \\
lt & public static & double & (double a, double b) &  \\
gt & public static & double & (double a, double b) &  \\
leq & public static & double & (double a, double b) &  \\
geq & public static & double & (double a, double b) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BooleanAlgebra}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
FALSE & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TRUE & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NULL & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
F & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
T & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
N & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
AND\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NAND\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
OR\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NOR\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
XOR\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
XNOR\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
IMP\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CIMP\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EQV\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NIMP\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CNIMP\_TRUTH\_TABLE & public static readonly & double[,] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NOT\_TRUTH\_TABLE & public static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
double2Int\-Boolean & public static & int & (double a) &  \\
and & public static & double & (double a, double b) &  \\
or & public static & double & (double a, double b) &  \\
xor & public static & double & (double a, double b) &  \\
nand & public static & double & (double a, double b) &  \\
nor & public static & double & (double a, double b) &  \\
xnor & public static & double & (double a, double b) &  \\
imp & public static & double & (double a, double b) &  \\
eqv & public static & double & (double a, double b) &  \\
not & public static & double & (double a) &  \\
cimp & public static & double & (double a, double b) &  \\
nimp & public static & double & (double a, double b) &  \\
cnimp & public static & double & (double a, double b) &  \\
and\-Variadic & public static & double & (params double[] values) &  \\
or\-Variadic & public static & double & (params double[] values) &  \\
xor\-Variadic & public static & double & (params double[] values) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Calculus}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
LEFT\_DERIVATIVE & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
integral\-Trapezoid & public static & double & (Expression f, Argument x, double a, double b,
				double eps, int max\-Steps) &  \\
derivative & public static & double & (Expression f, Argument x, double x0,
				int der\-Type, double eps, int max\-Steps) &  \\
derivative\-Nth & public static & double & (Expression f, double n, Argument x,
				double x0, int der\-Type, double eps, int max\-Steps) &  \\
forward\-Difference & public static & double & (Expression f, Argument x, double x0) &  \\
forward\-Difference & public static & double & (Expression f, Argument x) &  \\
backward\-Difference & public static & double & (Expression f, Argument x, double x0) &  \\
backward\-Difference & public static & double & (Expression f, Argument x) &  \\
forward\-Difference & public static & double & (Expression f, double h, Argument x, double x0) &  \\
forward\-Difference & public static & double & (Expression f, double h, Argument x) &  \\
backward\-Difference & public static & double & (Expression f, double h, Argument x, double x0) &  \\
backward\-Difference & public static & double & (Expression f, double h, Argument x) &  \\
solve\-Brent & public static & double & (Expression f, Argument x, double a, double b, double eps, double max\-Steps) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Coefficients}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
erf\-Imp\-An & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Ad & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Bn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Bd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Cn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Cd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Dn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Dd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-En & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Ed & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Fn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Fd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Gn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Gd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Hn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Hd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-In & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Id & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Jn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Jd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Kn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Kd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Ln & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Ld & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Mn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Md & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Nn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erf\-Imp\-Nd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-An & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Ad & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Bn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Bd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Cn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Cd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Dn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Dd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-En & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Ed & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Fn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Fd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Gn & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
erv\-Inv\-Imp\-Gd & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EI & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
lanchos\-Gamma & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
log\-Gamma\-A & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
log\-Gamma\-B & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
log\-Gamma\-C & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
lambert\-Wq\-Near\-Zero & internal static readonly & double[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Evaluate}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
polynomial & public static & double & (double x, double[] coefficients) &  \\
p1evl & public static & double & (double x, double[] coef, int n) &  \\
polevl & public static & double & (double x, double[] coef, int n) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MathConstants}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
PI & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PIBY2 & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
E & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EULER\_MASCHERONI & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GOLDEN\_RATIO & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PLASTIC & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EMBREE\_TREFETHEN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
FEIGENBAUM\_DELTA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
FEIGENBAUM\_ALFA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TWIN\_PRIME & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MEISSEL\_MERTEENS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BRAUN\_TWIN\_PRIME & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BRAUN\_PRIME\_QUADR & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BRUIJN\_NEWMAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CATALAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LANDAU\_RAMANUJAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
VISWANATH & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LEGENDRE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
RAMANUJAN\_SOLDNER & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ERDOS\_BORWEIN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BERNSTEIN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GAUSS\_KUZMIN\_WIRSING & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
HAFNER\_SARNAK\_MCCURLEY & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GOLOMB\_DICKMAN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CAHEN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LAPLACE\_LIMIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ALLADI\_GRINSTEAD & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LENGYEL & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LEVY & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
APERY & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILLS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BACKHOUSE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PORTER & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LIEB\_QUARE\_ICE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NIVEN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SIERPINSKI & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KHINCHIN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
FRANSEN\_ROBINSON & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LANDAU & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PARABOLIC & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
OMEGA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MRB & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LI2 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GOMPERTZ & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SQRT2 & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SQRTPi & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SQRT2Pi & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LNPI & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EXP\_MINUS\_E & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EXP\_1\_OVER\_E & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EXP\_MINUS\_1 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LN\_SQRT2 & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SQRT2BY2 & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SQRT3 & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SQRT3BY2 & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
D2BYSQRT3 & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SQRT3BY3 & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NOT\_A\_NUMBER & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MathFunctions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
plus & public static & double & (double a, double b) &  \\
minus & public static & double & (double a, double b) &  \\
multiply & public static & double & (double a, double b) &  \\
div & public static & double & (double a, double b) &  \\
bell\-Number & public static & double & (int n) &  \\
bell\-Number & public static & double & (double n) &  \\
euler\-Number & public static & double & (int n, int k) &  \\
euler\-Number & public static & double & (double n, double k) &  \\
factorial & public static & double & (int n) &  \\
factorial & public static & double & (double n) &  \\
binom\-Coeff & public static & double & (double n, long k) &  \\
binom\-Coeff & public static & double & (double n, double k) &  \\
number\-Of\-Permutations & public static & double & (double n, long k) &  \\
number\-Of\-Permutations & public static & double & (double n, double k) &  \\
bernoulli\-Number & public static & double & (int m, int n) &  \\
bernoulli\-Number & public static & double & (double m, double n) &  \\
Stirling1Number & public static & double & (int n, int k) &  \\
Stirling1Number & public static & double & (double n, double k) &  \\
Stirling2Number & public static & double & (int n, int k) &  \\
Stirling2Number & public static & double & (double n, double k) &  \\
worpitzky\-Number & public static & double & (int n, int k) &  \\
worpitzky\-Number & public static & double & (double n, double k) &  \\
harmonic\-Number & public static & double & (int n) &  \\
harmonic\-Number & public static & double & (double n) &  \\
harmonic\-Number & public static & double & (double x, int n) &  \\
harmonic\-Number & public static & double & (double x, double n) &  \\
catalan\-Number & public static & double & (int n) &  \\
catalan\-Number & public static & double & (double n) &  \\
fibonacci\-Number & public static & double & (int n) &  \\
fibonacci\-Number & public static & double & (double n) &  \\
lucas\-Number & public static & double & (int n) &  \\
lucas\-Number & public static & double & (double n) &  \\
kronecker\-Delta & public static & double & (double i, double j) &  \\
kronecker\-Delta & public static & double & (int i, int j) &  \\
continued\-Fraction & public static & double & (params double[] sequence) &  \\
continued\-Polynomial & private static & double & (int n, double[] x) &  \\
continued\-Polynomial & public static & double & (params double[] x) &  \\
euler\-Polynomial & public static & double & (int m, double x) &  \\
euler\-Polynomial & public static & double & (double m, double x) &  \\
chi & public static & double & (double x, double a, double b) &  \\
chi\_LR & public static & double & (double x, double a, double b) &  \\
chi\_L & public static & double & (double x, double a, double b) &  \\
chi\_R & public static & double & (double x, double a, double b) &  \\
is\-Almost\-Int & public static & bool & (double a) &  \\
pow\-Int & private static & double & (double a, int n) &  \\
power & public static & double & (double a, double b) &  \\
root & public static & double & (double n, double x) &  \\
tetration & public static & double & (double a, double n) &  \\
mod & public static & double & (double a, double b) &  \\
sin & public static & double & (double a) &  \\
sin & public static & double & (double a) &  \\
cos & public static & double & (double a) &  \\
tan & public static & double & (double a) &  \\
ctan & public static & double & (double a) &  \\
sec & public static & double & (double a) &  \\
cosec & public static & double & (double a) &  \\
int\-If\-Almost\-Int\-Otherwise\-Orig & private static & double & (double val) &  \\
asin & public static & double & (double a) &  \\
acos & public static & double & (double a) &  \\
atan & public static & double & (double a) &  \\
actan & public static & double & (double a) &  \\
asec & public static & double & (double a) &  \\
acosec & public static & double & (double a) &  \\
ln & public static & double & (double a) &  \\
log2 & public static & double & (double a) &  \\
log10 & public static & double & (double a) &  \\
rad & public static & double & (double a) &  \\
exp & public static & double & (double a) &  \\
sqrt & public static & double & (double a) &  \\
sinh & public static & double & (double a) &  \\
cosh & public static & double & (double a) &  \\
tanh & public static & double & (double a) &  \\
coth & public static & double & (double a) &  \\
sech & public static & double & (double a) &  \\
csch & public static & double & (double a) &  \\
deg & public static & double & (double a) &  \\
abs & public static & double & (double a) &  \\
sgn & public static & double & (double a) &  \\
floor & public static & double & (double a) &  \\
ceil & public static & double & (double a) &  \\
arsinh & public static & double & (double a) &  \\
arcosh & public static & double & (double a) &  \\
artanh & public static & double & (double a) &  \\
arcoth & public static & double & (double a) &  \\
arsech & public static & double & (double a) &  \\
arcsch & public static & double & (double a) &  \\
sa & public static & double & (double a) &  \\
sinc & public static & double & (double a) &  \\
log & public static & double & (double a, double b) &  \\
round & public static & double & (double value, int places) &  \\
round\-Half\-Up & public static & double & (double value, int places) &  \\
round\-Down & public static & double & (double value, int places) &  \\
round\-Ulp & public static & double & (double number) &  \\
integer\-Part & public static & double & (double x) &  \\
decimal\-Digits\-Before & public static & int & (double value) &  \\
ulp & public static & double & (double value) &  \\
ulp\-Decimal\-Digits\-Before & public static & int & (double value) &  \\
coalesce & public static & double & (double[] values) &  \\
is\-Integer & public static & bool & (double x) &  \\
almost\-Equal & public static & bool & (double a, double b) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NumberTheory}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
TO\_FRACTION\_INIT\_SEARCH\_SIZE & private static & long & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
set\-To\-Fraction\-Init\-Search\-Size & public static & void & (long n) &  \\
get\-To\-Fraction\-Init\-Search\-Size & public static & long & () &  \\
min & public static & double & (double a, double b) &  \\
min & public static & double & (params double[] numbers) &  \\
argmin & public static & double & (params double[] numbers) &  \\
max & public static & double & (double a, double b) &  \\
max & public static & double & (params double[] numbers) &  \\
argmax & public static & double & (params double[] numbers) &  \\
sort\-Asc & private static & void & (double[] array, int[] init\-Order, int left\-Index, int right\-Index) &  \\
sort\-Asc & public static & int[] & (double[] array) &  \\
get\-Dist\-Values & public static & double[,] & (double[] array, bool return\-Order\-By\-Desc\-Freq\-And\-Asc\-Orig\-Pos) &  \\
number\-Of\-Dist\-Values & public static & double & (params double[] numbers) &  \\
gcd & public static & long & (long a, long b) &  \\
gcd & public static & double & (double a, double b) &  \\
gcd & public static & long & (params long[] numbers) &  \\
gcd & public static & double & (params double[] numbers) &  \\
lcm & public static & long & (long a, long b) &  \\
lcm & public static & double & (double a, double b) &  \\
lcm & public static & long & (params long[] numbers) &  \\
lcm & public static & double & (params double[] numbers) &  \\
sum & public static & double & (params double[] numbers) &  \\
prod & public static & double & (params double[] numbers) &  \\
prime\-Test & public static & bool & (long n) &  \\
prime\-Test & public static & double & (double n) &  \\
prime\-Count & public static & long & (long n) &  \\
prime\-Count & public static & double & (double n) &  \\
sigma\-Summation & public static & double & (Expression f, Argument index, double from, double to, double delta) &  \\
pi\-Product & public static & double & (Expression f, Argument index, double from, double to, double delta) &  \\
min & public static & double & (Expression f, Argument index, double from, double to, double delta) &  \\
max & public static & double & (Expression f, Argument index, double from, double to, double delta) &  \\
get\-Reg\-Exp\-For\-Numeral\-System & private static & String & (int numeral\-System\-Base) &  \\
digit\-Index & public static & int & (char digit\-Char) &  \\
digit\-Char & public static & char & (int digit\-Index) &  \\
get\-Numeral\-System\-Base & public static & int & (String number\-Literal) &  \\
conv\-Oth\-Base2Decimal & public static & double & (String number\-Literal, int numeral\-System\-Base) &  \\
conv\-Oth\-Base2Decimal & public static & double & (String number\-Literal) &  \\
conv\-Oth\-Base2Decimal & public static & double & (int numeral\-System\-Base, params int[] digits) &  \\
conv\-Oth\-Base2Decimal & public static & double & (double numeral\-System\-Base, params double[] digits) &  \\
conv\-Oth\-Base2Decimal & public static & double & (int[] base\-And\-Digits) &  \\
conv\-Oth\-Base2Decimal & public static & double & (double[] base\-And\-Digits) &  \\
conv\-Decimal2Oth\-Base & public static & String & (double decimal\-Number, int numeral\-System\-Base) &  \\
conv\-Decimal2Oth\-Base & public static & String & (double decimal\-Number, int numeral\-System\-Base, int format) &  \\
number\-Of\-Digits & public static & int & (long number) &  \\
number\-Of\-Digits & public static & double & (double number) &  \\
number\-Of\-Digits & public static & long & (long number, long numeral\-System\-Base) &  \\
number\-Of\-Digits & public static & double & (double number, double numeral\-System\-Base) &  \\
digit\-At\-Position & public static & int & (long number, int position, int numeral\-System\-Base) &  \\
digit\-At\-Position & public static & int & (long number, int position) &  \\
digit\-At\-Position & public static & double & (double number, double position, double numeral\-System\-Base) &  \\
digit\-At\-Position & public static & double & (double number, double position) &  \\
prime\-Factors & public static & long[] & (long number) &  \\
prime\-Factors & public static & double[] & (double number) &  \\
number\-Of\-Prime\-Factors & public static & double & (double number) &  \\
prime\-Factor\-Value & public static & double & (double number, double id) &  \\
prime\-Factor\-Exponent & public static & double & (double number, double id) &  \\
fraction\-To\-Double\-Array & private static & double[] & (double sign, double numerator, double denominator) &  \\
mixed\-Fraction\-To\-Double\-Array & private static & double[] & (double sign, double whole, double numerator, double denominator) &  \\
to\-Fraction & public static & double[] & (double value) &  \\
to\-Mixed\-Fraction & public static & double[] & (double value) &  \\
fraction\-To\-String & public static & String & (double[] fraction) &  \\
to\-Fraction\-String & public static & String & (double value) &  \\
to\-Mixed\-Fraction\-String & public static & String & (double value) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PhysicalConstants}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
LIGHT\_SPEED & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GRAVITATIONAL\_CONSTANT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GRAVIT\_ACC\_EARTH & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PLANCK\_CONSTANT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PLANCK\_CONSTANT\_REDUCED & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PLANCK\_LENGTH & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PLANCK\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PLANCK\_TIME & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
N\_A & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
R & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BOLTZMANN\_CONSTANT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NEUTRON\_REST\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NEUTRON\_EQUIVALENT\_REST\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PROTON\_REST\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PROTON\_EQUIVALENT\_REST\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ELEMENTARY\_CHARGE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ELECTRON\_REST\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ELECTRON\_EQUIVALENT\_REST\_MASS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
VACUUM\_PERMITTIVITY & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
VACUUM\_PERMEABILITY & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PrimesCache}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
DEFAULT\_MAX\_NUM\_IN\_CACHE & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CACHE\_EMPTY & public const & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CACHING\_FINISHED & public const & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
IS\_PRIME & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
IS\_NOT\_PRIME & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NOT\_IN\_CACHE & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
max\-Num\-In\-Cache & internal & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
number\-Of\-Primes & internal & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
computing\-Time & internal & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
cache\-Status & internal & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
is\-Prime & internal & bool[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
init\-Successful &  & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Primes\-Cache & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Primes\-Cache & public & (int max\-Num\-In\-Cache) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Eratosthenes\-Sieve & private & void & () &  \\
count\-Primes & private & void & () &  \\
get\-Computing\-Time & public & double & () &  \\
get\-Cache\-Status & public & bool & () &  \\
get\-Number\-Of\-Primes & public & int & () &  \\
get\-Max\-Num\-In\-Cache & public & int & () &  \\
prime\-Test & public & int & (int n) &  \\
is\-Init\-Successful & public & bool & () &  \\
get\-Primes &  & bool[] & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ProbabilityDistributions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
random\-Generator & public static & Random & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
rnd\-Uniform\-Continuous & public static & double & (double a, double b, Random rnd) &  \\
rnd\-Uniform\-Continuous & public static & double & (double a, double b) &  \\
rnd\-Uniform\-Continuous & public static & double & (Random rnd) &  \\
random\-Uniform\-Continuous & public static & double & () &  \\
pdf\-Uniform\-Continuous & public static & double & (double x, double a, double b) &  \\
cdf\-Uniform\-Continuous & public static & double & (double x, double a, double b) &  \\
qnt\-Uniform\-Continuous & public static & double & (double q, double a, double b) &  \\
rnd\-Integer & public static & double & (int a, int b, Random rnd) &  \\
rnd\-Integer & public static & double & (int a, int b) &  \\
rnd\-Integer & public static & int & (Random rnd) &  \\
rnd\-Index & public static & int & (int n, Random rnd) &  \\
rnd\-Index & public static & int & (int n) &  \\
rnd\-Integer & public static & int & () &  \\
rnd\-Normal & public static & double & (double mean, double stddev, Random rnd) &  \\
rnd\-Normal & public static & double & (double mean, double stddev) &  \\
pdf\-Normal & public static & double & (double x, double mean, double stddev) &  \\
cdf\-Normal & public static & double & (double x, double mean, double stddev) &  \\
qnt\-Normal & public static & double & (double q, double mean, double stddev) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SpecialFunctions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
EI\_DBL\_EPSILON & private static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
exponential\-Integral\-Ei & public static & double & (double x) &  \\
continued\-Fraction\-Ei & private static & double & (double x) &  \\
power\-Series\-Ei & private static & double & (double x) &  \\
argument\-Addition\-Series\-Ei & private static & double & (double x) &  \\
logarithmic\-Integral\-Li & public static & double & (double x) &  \\
offset\-Logarithmic\-Integral\-Li & public static & double & (double x) &  \\
erf & public static & double & (double x) &  \\
erfc & public static & double & (double x) &  \\
erf\-Inv & public static & double & (double x) &  \\
erf\-Imp & private static & double & (double z, bool invert) &  \\
erfc\-Inv & public static & double & (double z) &  \\
erf\-Inv\-Impl & private static & double & (double p, double q, double s) &  \\
gamma\-Int & private static & double & (long n) &  \\
gamma & public static & double & (double x) &  \\
lanchos\-Gamma & public static & double & (double x) &  \\
log\-Gamma & public static & double & (double x) &  \\
sgn\-Gamma & public static & double & (double x) &  \\
regularized\-Gamma\-Lower\-P & public static & double & (double s, double x) &  \\
incomplete\-Gamma\-Lower & public static & double & (double s, double x) &  \\
regularized\-Gamma\-Upper\-Q & public static & double & (double s, double x) &  \\
incomplete\-Gamma\-Upper & public static & double & (double s, double x) &  \\
di\-Gamma & public static & double & (double x) &  \\
log\-Beta & public static & double & (double x, double y) &  \\
beta & public static & double & (double x, double y) &  \\
incomplete\-Beta & public static & double & (double a, double b, double x) &  \\
regularized\-Beta & public static & double & (double a, double b, double x) &  \\
halley\-Iteration & private static & double & (double x, double w\-Initial, int max\-Iter) &  \\
series\-Eval & private static & double & (double r) &  \\
lambert\-W0 & private static & double & (double x) &  \\
lambert\-W1 & private static & double & (double x) &  \\
lambert\-W & public static & double & (double x, double branch) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SpecialValue}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
EPSILON & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
x & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
x\-From & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
x\-To & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
fv & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
fvdeg & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Special\-Value & public & (double x, double fv) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Special\-Value & public & (double x, double fv, double fvdeg) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SpecialValueTrigonometric}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
EPSILON & public static readonly & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
values\-List\-Trig & public static & Special\-Value\-Trigonometric[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
values\-List\-Asin & public static & List{\tt <}\-Special\-Value\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
values\-List\-Acos & public static & List{\tt <}\-Special\-Value\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
values\-List\-Atan & public static & List{\tt <}\-Special\-Value\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
values\-List\-Actan & public static & List{\tt <}\-Special\-Value\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
values\-List\-Asec & public static & List{\tt <}\-Special\-Value\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
values\-List\-Acsc & public static & List{\tt <}\-Special\-Value\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
factor & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
xrad & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
xdeg & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
xrad\-From & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
xrad\-To & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
sin & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
cos & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
tan & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ctan & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
sec & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
csc & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Special\-Value\-Trigonometric & public & (double factor, double sin, double cos, double tan, double ctan, double sec, double csc) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Special\-Value\-Trigonometric & public & (double factor, double sin, double cos, double tan, double ctan, double sec, double csc) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Special\-Value\-Trigonometric & public & (double factor, double sin, double cos, double tan, double ctan, double sec, double csc) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
get\-Special\-Value\-Trigonometric & public static & Special\-Value\-Trigonometric & (double xrad) &  \\
get\-Special\-Value\-Asin & public static & Special\-Value & (double x) &  \\
get\-Special\-Value\-Acos & public static & Special\-Value & (double x) &  \\
get\-Special\-Value\-Atan & public static & Special\-Value & (double x) &  \\
get\-Special\-Value\-Actan & public static & Special\-Value & (double x) &  \\
get\-Special\-Value\-Asec & public static & Special\-Value & (double x) &  \\
get\-Special\-Value\-Acsc & public static & Special\-Value & (double x) &  \\
get\-Special\-Value & private static & Special\-Value & (double x, List{\tt <}\-Special\-Value\-{\tt >} values\-List) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Statistics}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
avg & public static & double & (Expression f, Argument index, double from, double to, double delta) &  \\
var & public static & double & (Expression f, Argument index, double from, double to, double delta) &  \\
std & public static & double & (Expression f, Argument index, double from, double to, double delta) &  \\
avg & public static & double & (params double[] numbers) &  \\
var & public static & double & (params double[] numbers) &  \\
std & public static & double & (params double[] numbers) &  \\
median & public static & double & (params double[] numbers) &  \\
mode & public static & double & (params double[] numbers) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Units}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
PERC & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PROMIL & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
YOTTA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ZETTA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EXA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PETA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TERA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GIGA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MEGA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILO & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
HECTO & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
DECA & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
DECI & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CENTI & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILLI & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MICRO & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NANO & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PICO & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
FEMTO & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ATTO & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ZEPTO & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
YOCTO & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
METRE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILOMETRE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CENTIMETRE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILLIMETRE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
INCH & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
YARD & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
FEET & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
NAUTICAL\_MILE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
METRE2 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CENTIMETRE2 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILLIMETRE2 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ARE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
HECTARE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILOMETRE2 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ACRE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILLIMETRE3 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CENTIMETRE3 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
METRE3 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILOMETRE3 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILLILITRE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LITRE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GALLON & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PINT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SECOND & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILLISECOND & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MINUTE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
HOUR & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
DAY & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
WEEK & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
JULIAN\_YEAR & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILOGRAM & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GRAM & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILLIGRAM & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
DECAGRAM & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TONNE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
OUNCE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
POUND & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
COULOMB & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
AMPERE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KELVIN & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
CELCIUS & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
FARENHEIGHT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILOBIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MEGABIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GIGABIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TERABIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PETABIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EXABIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ZETTABIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
YOTTABIT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
BYTE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILOBYTE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MEGABYTE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GIGABYTE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TERABYTE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PETABYTE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
EXABYTE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ZETTABYTE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
YOTTABYTE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
JOULE & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
ELECTRONO\_VOLT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILO\_ELECTRONO\_VOLT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MEGA\_ELECTRONO\_VOLT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
GIGA\_ELECTRONO\_VOLT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TERA\_ELECTRONO\_VOLT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
METRE\_PER\_SECOND & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILOMETRE\_PER\_HOUR & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILE\_PER\_HOUR & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KNOT & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
METRE\_PER\_SECOND2 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
KILOMETRE\_PER\_HOUR2 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MILE\_PER\_HOUR2 & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
RADIAN\_ARC & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
DEGREE\_ARC & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
MINUTE\_ARC & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
SECOND\_ARC & public const & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{KeyWord}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Key\-Word & public & (String word\-String, String description, int word\-Id, String syntax, String since, int word\-Type\-Id) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ParserSymbol}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
DIGIT & public const & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
TYPE\_ID & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LEFT\_PARENTHESES\_ID & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LEFT\_PARENTHESES\_STR & public const & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Token}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
NOT\_MATCHED & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
token\-Str & public & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
key\-Word & public & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
token\-Id & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
token\-Type\-Id & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
token\-Level & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
token\-Value & public & double & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
looks\-Like & public & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
kind & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
begin\-Line & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
begin\-Column & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
end\-Line & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
end\-Column & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
image & public & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
next & public & Token & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
special\-Token & public & Token & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Token & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Token & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Token & public & (int kind) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Token & public & (int kind, String image) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
clone & public & Token & () &  \\
To\-String & public override & String & () &  \\
new\-Token & public static & Token & (int of\-Kind, String img) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PerformanceTests}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
tests & private static & Performance\-Test\-Result[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
create\-Run\-Join\-Threads & static & void & (Performance\-Test\-Result test, int class\-Id) &  \\
test000 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test001 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test002 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test003 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test004 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test005 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test006 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test007 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test008 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test009 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test010 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test011 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test012 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test013 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test014 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test015 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test016 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test017 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test018 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test019 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
test020 & static & void & (Performance\-Test\-Result test, int test\-Id) &  \\
Start & public static & int & (int threads\-Num) &  \\
Start & public static & int & () &  \\
Main & public static & void & (string[] args) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TestThread}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
iter\-Num & protected & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
test & protected & Performance\-Test\-Result & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Test\-Thread & internal & (Performance\-Test\-Result test) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
test\-Scenario & protected abstract & void & () &  \\
run & public & void & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RegTestExpression}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Start & public static & int & (int num\-Of\-Tests) &  \\
Start & public static & int & () &  \\
Main & public static & void & (string[] args) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RegTestExpressionAPI}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Start & public static & int & (int fraction\-Iterations) &  \\
Start & public static & int & () &  \\
Main & public static & void & (string[] args) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RegTestSyntax}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Start & public static & int & (int num\-Of\-Tests) &  \\
Start & public static & int & () &  \\
Main & public static & void & (string[] args) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RunTest}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Start & public static & int & (params string[] args) &  \\
Main & public static & void & (string[] args) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ParseException}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
special\-Constructor & protected & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
current\-Token & public & Token & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
expected\-Token\-Sequences & public & long[][] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
token\-Image & public & String[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
eol & protected & String & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Message & public override & String & \{ get System.Text.String\-Builder expected = new System.Text.String\-Builder(); int max\-Size = 0; for (int i = 0; i {\tt <}\- expected\-Token\-Sequences.Length; i++) \{ if (max\-Size {\tt <}\- expected\-Token\-Sequences[i].Length) \{ max\-Size = expected\-Token\-Sequences[i].Length; \} for (int j = 0; j {\tt <}\- expected\-Token\-Sequences[i].Length; j++) \{ expected.Append(token\-Image[expected\-Token\-Sequences[i][j]]).Append(" "); \} if (expected\-Token\-Sequences[i][expected\-Token\-Sequences[i].Length - 1] != 0) \{ expected.Append("..."); \} expected.Append(eol).Append(" "); \} String retval = "Encountered \textbackslash\{\}""; Token tok = current\-Token.next; for (int i = 0; i {\tt <}\- max\-Size; i++) \{ if (i != 0) retval += " "; if (tok.kind == 0) \{ retval += token\-Image[0]; break; \} retval += add\_escapes(tok.image); tok = tok.next; \} retval += "\textbackslash\{\}" at line " + current\-Token.next.begin\-Line + ", column " + current\-Token.next.begin\-Column; retval += "." + eol; if (expected\-Token\-Sequences.Length == 1) \{ retval += "Was expecting:" + eol + " "; \} else \{ retval += "Was expecting one of:" + eol + " "; \} retval += expected.To\-String(); return retval; \} \} &  \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Parse\-Exception & public & (Token current\-Token\-Val,
                        long[][] expected\-Token\-Sequences\-Val,
                        String[] token\-Image\-Val
                       ) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Parse\-Exception & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
add\_escapes & protected & String & (String str) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SimpleCharStream}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
get\-Column & public & int & () &  \\
get\-Line & public & int & () &  \\
adjust\-Begin\-Line\-Column & public & void & (int new\-Line, int new\-Col) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TokenMgrError}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
LEXICAL\_ERROR & public static & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
STATIC\_LEXER\_ERROR & public static & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
INVALID\_LEXICAL\_STATE & public static & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
LOOP\_DETECTED & public static & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
error\-Code &  & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Message & public override & String & \{ get \} &  \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
add\-Escapes & public static & String & (String str) &  \\
Lexical\-Error & protected static & String & (bool EOFSeen, int lex\-State, int error\-Line, int error\-Column, String error\-After, char cur\-Char) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TydDocument}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Tyd\-Document & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Create a new empty Tyd\-Document.} \\ \tabuphantomline
Tyd\-Document & public & (IEnumerable{\tt <}\-Tyd\-Node\-{\tt >} nodes) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Create a new Tyd\-Document from a list of Tyd\-Nodes.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BBInput}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Load\-Profiles & public static & void & () & Loads all input profiles from the defs. \\
Initialize & public static & void & () & Initialises the input system. Call after Load\-Profiles. \\
Add\-On\-Axis\-Pressed & public static & void & (string axis\-Name, Action action, int priority = 0) & Adds an action to be called when an axis is pressed. \\
Add\-On\-Axis\-Pressed & public static & void & (string axis\-Name, Dyn\-Value action, int priority = 0) & Adds an action to be called when an axis is pressed. \\
Add\-On\-Axis\-Held & public static & void & (string axis\-Name, Action action, int priority = 0) & Adds an action to be called when an axis is held. \\
Add\-On\-Axis\-Held & public static & void & (string axis\-Name, Dyn\-Value action, int priority = 0) & Adds an action to be called when an axis is held. \\
Add\-On\-Axis\-Released & public static & void & (string axis\-Name, Action action, int priority = 0) & Adds an action to be called when an axis is released. \\
Add\-On\-Axis\-Released & public static & void & (string axis\-Name, Dyn\-Value action, int priority = 0) & Adds an action to be called when an axis is released. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BBInputAxis}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_on\-Pressed & private & Sorted\-List{\tt <}\-int, Action\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Triggered when a button in the axis is pressed.} \\ \tabuphantomline
\_on\-Held & private & Sorted\-List{\tt <}\-int, Action\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Triggered when a button in the axis is held.} \\ \tabuphantomline
\_on\-Released & private & Sorted\-List{\tt <}\-int, Action\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Triggered when a button in the axis is released.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; private set; \} & The name used to refer to the key in scripts. \\
Label & public & string & \{ get; private set; \} & The name of the key as it appears in the game.
     Example: An axis controls left-right movement.
     The label should be something like "Horizontal", or "Horizontal movement", or "Move horizontally", etc. \\
Positive\-Label & public & string & \{ get; private set; \} & The name of the positive axis direction as it appears in the game.
     Example: An axis controls left-right movement.
     The positive label should be something like "Move right" or "Right", etc. \\
Negative\-Label & public & string & \{ get; private set; \} & The name of the positive axis direction as it appears in the game.
     Example: An axis controls left-right movement.
     The positive label should be something like "Move left" or "left", etc. \\
Description & public & string & \{ get; private set; \} & The description of the key. \\
Priority & public & int & \{ get; private set; \} & The priority of the axis. The higher the number, the sooner it gets checked by the input system.
     This allows you to have two axes bound to the same key, assign one to a higher priority, and have the
     axis with the higher priority use up and "eat" the key (i.e. make it so no one else can use it for the
     duration of the current frame). \\
Enabled & public & bool & \{ get; private set; \} & Whether or not this axis is enabled. An axis is only checked if enabled. \\
Was\-Pressed\-This\-Frame & public & bool & \{ get =\-{\tt >} \_was\-Pressed\-This\-Frame; set \} \} \} /// {\tt <}\-summary\-{\tt >} /// Whether the axis is currently held. /// {\tt <}\-/summary\-{\tt >} public  & Whether the axis was pressed this frame. \\
Was\-Pressed\-This\-Frame & public & bool & \{ get =\-{\tt >} \_was\-Pressed\-This\-Frame; set \} \} \} /// {\tt <}\-summary\-{\tt >} /// Whether the axis is currently held. /// {\tt <}\-/summary\-{\tt >} public  & Whether the axis is currently held. \\
Is\-Held &  & bool & \{ get =\-{\tt >} \_is\-Held; set \} \} \} /// {\tt <}\-summary\-{\tt >} /// Whether the axis was released this frame. /// {\tt <}\-/summary\-{\tt >} public  & Whether the axis was released this frame. \\
Was\-Released\-This\-Frame &  & bool & \{ get =\-{\tt >} \_was\-Released\-This\-Frame; set \} \} \} /// {\tt <}\-summary\-{\tt >} /// The Unity key codes bound to the positive axis direction. /// This is a list of lists which each contain a combination of key codes /// which must all be pressed to trigger the key. /// Example as it appears in a .tyd file: /// positive\-Key\-Codes [[A]; [Left\-Shift; M]] /// The above would mean that the key is triggered by /// 1. Pressing A. /// and/or /// 2. Pressing left shift and M at the same time. /// {\tt <}\-/summary\-{\tt >} public List{\tt <}\-List{\tt <}\-Key\-Code\-{\tt >}\-{\tt >} Positive\-Key\-Codes \{ get; private set; \} & The Unity key codes bound to the positive axis direction.
     This is a list of lists which each contain a combination of key codes
     which must all be pressed to trigger the key.
     Example as it appears in a .tyd file:
     positive\-Key\-Codes [[A]; [Left\-Shift; M]]
     The above would mean that the key is triggered by
     1. Pressing A.
     and/or
     2. Pressing left shift and M at the same time. \\
Negative\-Key\-Codes & public & List{\tt <}\-List{\tt <}\-Key\-Code\-{\tt >}\-{\tt >} & \{ get; private set; \} & NOTE: Not implemented
     The Unity key codes bound to the negative axis direction.
     This is a list of lists which each contain a combination of key codes
     which must all be pressed to trigger the key.
     Example as it appears in a .tyd file:
     key\-Codes [[D]; [Right\-Shift; M]]
     The above would mean that the key is triggered by
     1. Pressing D.
     and/or
     2. Pressing right shift and M at the same time. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add\-On\-Pressed & public & void & (Action action, int priority = 0) & Adds an action to be called when the axis is pressed. \\
Add\-On\-Held & public & void & (Action action, int priority = 0) & Adds an action to be called when the axis is held. \\
Add\-On\-Released & public & void & (Action action, int priority = 0) & Adds an action to be called when the axis is released. \\
From\-Tyd\-Table & public static & BBInput\-Axis & (Tyd\-Table table) & Constructs a new BBInput\-Axis from A Tyd\-Table. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BBInputProfile}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; private set; \} & The name of the profile when referenced in code. \\
Enabled & public & bool & \{ get; set; \} & Whether the profile is enabled.
     If it is not enabled the axes cannot be \\
Always\-Enabled & public & bool & \{ get; private set; \} & Whether the profile is always enabled.
     A profile with this property set to true can never be disabled under any circumstances. \\
Axes & public & List{\tt <}\-BBInput\-Axis\-{\tt >} & \{ get; private set; \} &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pb_MissingScriptEditor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
index & static & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
total & static & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
do\-Fix & static & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
unfixable & static & List{\tt <}\-Game\-Object\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\_mono\_pb & static & Mono\-Script & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\_mono\_pe & static & Mono\-Script & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\_mono\_dummy & static & Mono\-Script & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PB\_OBJECT\_SCRIPT\_PROPERTIES &  & List{\tt <}\-string\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
PB\_ENTITY\_SCRIPT\_PROPERTIES &  & List{\tt <}\-string\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Load\-Mono\-Script & static & void & () &  \\
Load\-Mono\-Script & static & void & () &  \\
Next & static & void & () &  \\
Delete\-Dummy\-Scripts & static & void & () &  \\
Serialized\-Object\-To\-String & static & string & (Serialized\-Object serialized\-Object) &  \\
Serialized\-Property\-Value & static & string & (Serialized\-Property sp) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pb_Preferences}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Preferences\-GUI & private static & void & () &  \\
Preferences\-GUI & private static & void & () &  \\
Preferences\-GUI & private static & void & () &  \\
Preferences\-GUI & private static & void & () &  \\
Preferences\-GUI & private static & void & () &  \\
Preferences\-GUI & private static & void & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pb_ScenePostProcessor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Postprocess\-Scene & public static & void & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pg_Enum}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Inverse\-Axis\-Mask & public static & Vector3 & (Vector3 v, Axis axis) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pg_Util}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Type & private static & Type & (string type, string assembly = null) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pg_Initializer}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
pg\_Initializer & static & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pg_Editor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
grid\-Color\-X & public & Color & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
grid\-Color\-Y & public & Color & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
grid\-Color\-Z & public & Color & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Draw\-Scene\-GUI &  & void & () &  \\
On\-Scene\-GUI & public & void & (Scene\-View scnview) &  \\
Draw\-Grid\-Orthographic & private & void & (Camera cam, Axis cam\-Axis, Color primary\-Color, Color secondary\-Color) &  \\
Draw\-Grid\-Orthographic & private & void & (Camera cam, Axis cam\-Axis, Color primary\-Color, Color secondary\-Color) &  \\
Draw\-Grid\-Orthographic & private & void & (Camera cam, Axis cam\-Axis, Color primary\-Color, Color secondary\-Color) &  \\
Draw\-Grid\-Orthographic & private & void & (Camera cam, Axis cam\-Axis, Color primary\-Color, Color secondary\-Color) &  \\
Set\-Snap\-Value & public & void & (Snap\-Unit su, float val, int multiplier) &  \\
Use\-Axis\-Constraints & public static & bool & () &  \\
Snap\-Value & public static & float & () &  \\
Snap\-Enabled & public static & bool & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pg_GridRenderer}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Init & public static & void & () &  \\
Draw\-Plane & public static & float & (Camera cam, Vector3 pivot, Vector3 tangent, Vector3 bitangent, float snap\-Value, Color color, float alpha\-Bump) &  \\
Draw\-Full\-Grid & private static & void & (Camera cam, Vector3 pivot, Vector3 tan, Vector3 bitan, float increment, int iterations, int div, Color secondary, float alpha\-Bump) &  \\
Get\-Distance\-To\-Frustum\-Planes & private static & float[] & (Camera cam, Vector3 pivot, Vector3 tan, Vector3 bitan, float min\-Dist) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pg_Preferences}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
GRID\_COLOR\_X & public static & Color & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PlayerPointerEventData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
player\-Id & public & int & \{ get; set; \} & The Player id of the Player that generated this event. \\
input\-Source\-Index & public & int & \{ get; set; \} & The index of the mouse/touch input source owned by the Player that generated this event. \\
mouse\-Source & public & IMouse\-Input\-Source & \{ get; set; \} & The mouse that generated this event. \\
touch\-Source & public & ITouch\-Input\-Source & \{ get; set; \} & The touch source that generated this event. \\
source\-Type & public & Pointer\-Event\-Type & \{ get; set; \} & The input source type that generated this event. \\
button\-Index & public & int & \{ get; set; \} & The index of the button that generated this event. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RewiredPointerInputModule}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Mouse\-Input\-Source & public & IMouse\-Input\-Source & (int player\-Id, int mouse\-Index) & Gets or sets the input source used for mouse input. \\
Remove\-Mouse\-Input\-Source & public & void & (IMouse\-Input\-Source source) & Removes the mouse input source. \\
Add\-Mouse\-Input\-Source & public & void & (IMouse\-Input\-Source source) & Adds the mouse input source. \\
Get\-Mouse\-Input\-Source\-Count & public & int & (int player\-Id) & Returns the number of possible pointers.
         Does not count the number actually assigned. \\
Get\-Touch\-Input\-Source & public & ITouch\-Input\-Source & (int player\-Id, int source\-Index) & Gets or sets the input source used for touch input. \\
Remove\-Touch\-Input\-Source & public & void & (ITouch\-Input\-Source source) & Removes the touch input source. \\
Add\-Touch\-Input\-Source & public & void & (ITouch\-Input\-Source source) & Adds the touch input source. \\
Get\-Touch\-Input\-Source\-Count & public & int & (int player\-Id) & Returns the number of possible pointers.
         Does not count the number actually assigned. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RewiredStandaloneInputModule}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
use\-All\-Rewired\-Game\-Players & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Allow all Rewired game Players to control the UI. This does not include the System Player. If enabled, this setting overrides individual Player Ids set in Rewired Player Ids.} \\ \tabuphantomline
use\-Rewired\-System\-Player & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Allow the Rewired System Player to control the UI.} \\ \tabuphantomline
rewired\-Player\-Ids & private & int[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{A list of Player Ids that are allowed to control the UI. If Use All Rewired Game Players = True, this list will be ignored.} \\ \tabuphantomline
use\-Playing\-Players\-Only & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Allow only Players with Player.is\-Playing = true to control the UI.} \\ \tabuphantomline
player\-Mice & private & List{\tt <}\-Rewired.Components.Player\-Mouse\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Player Mice allowed to interact with the UI.} \\ \tabuphantomline
move\-One\-Element\-Per\-Axis\-Press & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Makes an axis press always move only one UI selection. Enable if you do not want to allow scrolling through UI elements by holding an axis direction.} \\ \tabuphantomline
set\-Actions\-By\-Id & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{If enabled, Action Ids will be used to set the Actions. If disabled, string names will be used to set the Actions.} \\ \tabuphantomline
horizontal\-Action\-Id & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Name of the horizontal axis for movement (if axis events are used).} \\ \tabuphantomline
vertical\-Action\-Id & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Name of the vertical axis for movement (if axis events are used).} \\ \tabuphantomline
submit\-Action\-Id & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Name of the action used to submit.} \\ \tabuphantomline
cancel\-Action\-Id & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Name of the action used to cancel.} \\ \tabuphantomline
m\_Horizontal\-Axis & private & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Name of the horizontal axis for movement (if axis events are used).} \\ \tabuphantomline
m\_Vertical\-Axis & private & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Name of the vertical axis for movement (if axis events are used).} \\ \tabuphantomline
m\_Submit\-Button & private & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Name of the action used to submit.} \\ \tabuphantomline
m\_Cancel\-Button & private & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Name of the action used to cancel.} \\ \tabuphantomline
m\_Input\-Actions\-Per\-Second & private & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Number of selection changes allowed per second when a movement button/axis is held in a direction.} \\ \tabuphantomline
m\_Repeat\-Delay & private & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Delay in seconds before vertical/horizontal movement starts repeating continouously when a movement direction is held.} \\ \tabuphantomline
m\_allow\-Mouse\-Input & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Allows the mouse to be used to select elements.} \\ \tabuphantomline
m\_allow\-Mouse\-Input\-If\-Touch\-Supported & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Allows the mouse to be used to select elements if the device also supports touch control.} \\ \tabuphantomline
m\_allow\-Touch\-Input & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Allows touch input to be used to select elements.} \\ \tabuphantomline
m\_deselect\-If\-Background\-Clicked & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Deselects the current selection on mouse/touch click when the pointer is not over a selectable object.} \\ \tabuphantomline
m\_deselect\-Before\-Selecting & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Deselects the current selection on mouse/touch click before selecting the next object.} \\ \tabuphantomline
m\_Force\-Module\-Active & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Forces the module to always be active.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Rewired\-Input\-Manager & public & Input\-Manager\_Base & \{ get set \} & (Optional) Link the Rewired Input Manager here for easier access to Player ids, etc. \\
Use\-All\-Rewired\-Game\-Players & public & bool & \{ get set \} & Allow all Rewired game Players to control the UI. This does not include the System Player. If enabled, this setting overrides individual Player Ids set in Rewired Player Ids. \\
Use\-Rewired\-System\-Player & public & bool & \{ get set \} & Allow the Rewired System Player to control the UI. \\
Rewired\-Player\-Ids & public & int[] & \{ get set \} & A list of Player Ids that are allowed to control the UI. If Use All Rewired Game Players = True, this list will be ignored.
         Returns a clone of the array. \\
Use\-Playing\-Players\-Only & public & bool & \{ get set \} & Allow only Players with Player.is\-Playing = true to control the UI. \\
Player\-Mice & public & List{\tt <}\-Rewired.Components.Player\-Mouse\-{\tt >} & \{ get set player\-Mice = new List{\tt <}\-Rewired.Components.Player\-Mouse\-{\tt >}(value); Setup\-Rewired\-Vars(); \} \} & Player Mice allowed to interact with the UI.
         Each Player that owns a Player Mouse must also be allowed to control the UI or the Player Mouse will not function. \\
Move\-One\-Element\-Per\-Axis\-Press & public & bool & \{ get set \} & Makes an axis press always move only one UI selection. Enable if you do not want to allow scrolling through UI elements by holding an axis direction. \\
allow\-Mouse\-Input & public & bool & \{ get set \} & Allows the mouse to be used to select elements. \\
allow\-Mouse\-Input\-If\-Touch\-Supported & public & bool & \{ get set \} & Allows the mouse to be used to select elements if the device also supports touch control. \\
allow\-Touch\-Input & public & bool & \{ get set \} & Allows touch input to be used to select elements. \\
deselect\-If\-Background\-Clicked & public & bool & \{ get set \} & Deselects the current selection on mouse/touch click when the pointer is not over a selectable object. \\
deselect\-Before\-Selecting & private & bool & \{ get set \} & Deselects the current selection on mouse/touch click before selecting the next object. \\
Set\-Actions\-By\-Id & public & bool & \{ get set \} & If enabled, Action Ids will be used to set the Actions. If disabled, string names will be used to set the Actions. \\
Horizontal\-Action\-Id & public & int & \{ get set \} \} & Name of the horizontal axis for movement (if axis events are used). \\
Vertical\-Action\-Id & public & int & \{ get set \} \} & Name of the vertical axis for movement (if axis events are used). \\
Submit\-Action\-Id & public & int & \{ get set \} \} & Name of the action used to submit. \\
Cancel\-Action\-Id & public & int & \{ get set \} \} & Name of the action used to cancel. \\
allow\-Activation\-On\-Mobile\-Device & public & bool & \{ get set \} & Allows the module to control UI input on mobile devices.. \\
force\-Module\-Active & public & bool & \{ get set \} & Forces the module to always be active. \\
input\-Actions\-Per\-Second & public & float & \{ get set \} &  \\
repeat\-Delay & public & float & \{ get set \} & Delay in seconds before vertical/horizontal movement starts repeating continouously when a movement direction is held. \\
horizontal\-Axis & public & string & \{ get set \} \} & Name of the horizontal axis for movement (if axis events are used). \\
vertical\-Axis & public & string & \{ get set \} \} & Name of the vertical axis for movement (if axis events are used). \\
submit\-Button & public & string & \{ get set \} \} & Name of the action used to submit. \\
cancel\-Button & public & string & \{ get set \} \} & Name of the action used to cancel. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Send\-Submit\-Event\-To\-Selected\-Object & private & bool & () & Process submit keys. \\
Send\-Move\-Event\-To\-Selected\-Object & private & bool & () & Process keyboard events. \\
Process\-Mouse\-Event & private & void & (int player\-Id, int pointer\-Index) & Process all mouse events. \\
Process\-Mouse\-Press & private & void & (Mouse\-Button\-Event\-Data data) & Process the current mouse press. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CIGatherResource}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Init & public & void & (string resource\-Type) & Initialize the action \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DroneTestFactory}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Build\-Drone\-For\-Free & public & void & (string type) & Builds a drone. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CameraController}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Camera\-Mode & public & TCamera\-Mode & () & Returns a Camera\-Mode of the passed in type, if one exists. Null otherwise. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CFX_LightIntensityFade}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
final\-Intensity & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CFX_SpawnSystem}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
All\-Objects\-Loaded & static public & bool & \{ get \} & Gets a value indicating whether all objects defined in the Editor are loaded or not. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Next\-Object & static public & Game\-Object & (Game\-Object source\-Obj, bool activate\-Object = true) & Get the next available preloaded Object. \\
Preload\-Object & static public & void & (Game\-Object source\-Obj, int pool\-Size = 1) & Preloads an object a number of times in the pool. \\
Unload\-Objects & static public & void & (Game\-Object source\-Obj) & Unloads all the preloaded objects from a source Object. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviourTreeAssetHandler}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Open\-Asset & public static & bool & (int instance\-ID, int line) & Called when an instance of Bbbt\-Behaviour\-Tree is selected in the project hierarchy. \\
On\-Will\-Delete\-Asset & private static & Asset\-Delete\-Result & (string asset\-Path, Remove\-Asset\-Options options) & Called when the asset will be deleted. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviourTreeCallerBehaviourEditor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Inspector\-GUI & public override & void & () & Called when a Bbbt\-Behaviour\-Tree\-Caller\-Behaviour is shown in the inspector. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviourTreeComponentEditor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Inspector\-GUI & public override & void & () & Called when a Bbbt\-Behaviour\-Tree\-Component is shown in the inspector. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtConnection}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
In\-Point & public & Bbbt\-Connection\-Point & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The connection point leading that this connection leads in to.} \\ \tabuphantomline
Out\-Point & public & Bbbt\-Connection\-Point & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The connection point that this connection leads out from.} \\ \tabuphantomline
\_on\-Click\-Remove\-Connection & private & Action{\tt <}\-Bbbt\-Connection\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Action invoked when the button to remove the connection is clicked.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Connection & public & (
            Bbbt\-Connection\-Point in\-Point,
            Bbbt\-Connection\-Point out\-Point,
            Action{\tt <}\-Bbbt\-Connection\-{\tt >} on\-Click\-Remove\-Connection) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Bbbt\-Connection.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Draw & public & void & () & Draws the connection. \\
To\-Save\-Data & public & Bbbt\-Connection\-Save\-Data & () & Generates save data from this connection. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtConnectionPoint}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Rect & public & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The connection point's rect.} \\ \tabuphantomline
Node & public & Bbbt\-Node & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The node to which the connection point belongs.} \\ \tabuphantomline
Type & public & Bbbt\-Connection\-Point\-Type & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The type (in or out) of the connection point.} \\ \tabuphantomline
\_style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The connection point's GUIStyle.} \\ \tabuphantomline
\_on\-Click & private & Action{\tt <}\-Bbbt\-Connection\-Point\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Action invoked when the connection point is clicked on.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Connection\-Point & public & (
            Bbbt\-Node node,
            Bbbt\-Connection\-Point\-Type type,
            GUIStyle style,
            Action{\tt <}\-Bbbt\-Connection\-Point\-{\tt >} on\-Click) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a Bbbt\-Connection\-Point.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Draw & public & void & (Rect \_node\-Rect) & Draws the connection point. \\
Draw & public & void & (Rect \_node\-Rect) &  \\
Drag & public & void & (Vector2 delta) & Moves the connection point. Should only be called from Bbbt\-Node.Draw(). \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtConnectionPreview}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_point & private & Bbbt\-Connection\-Point & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The point from which to draw the preview.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Connection\-Preview & public & (Bbbt\-Connection\-Point point) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a Bbbt\-Connection\-Preview.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Draw & public & void & () & Draws the connection point preview from its associated point to the cursor position. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtNode}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_type\-Icon\-Rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The rect used to show the icon for the node's type.} \\ \tabuphantomline
\_label\-Rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The rect used for positioning the node's label.} \\ \tabuphantomline
\_style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The node's GUIStyle.} \\ \tabuphantomline
\_type\-Icon\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style of the rect which displays the icon for the node's type.} \\ \tabuphantomline
\_selected\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style used for the node when selected.} \\ \tabuphantomline
In\-Point & public & Bbbt\-Connection\-Point & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The connection point that leads in to this node.} \\ \tabuphantomline
Out\-Point & public & Bbbt\-Connection\-Point & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The connection point that leads out from this node.} \\ \tabuphantomline
\_is\-Dragged & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Whether the node is currently being dragged.} \\ \tabuphantomline
\_drag\-Start\-Position & private & Vector2 & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The position on which we started dragging the node.} \\ \tabuphantomline
\_on\-Click\-Remove\-Node & private & Action{\tt <}\-Bbbt\-Node\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Action invoked when the node is removed.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Id & public & int & \{ get; protected set; \} & A unique id used to reference the node. \\
Base\-Behaviour & public & Bbbt\-Behaviour & \{ get; protected set; \} & The behaviour used as a base for the node's behaviour. \\
Behaviour & public & Bbbt\-Behaviour & \{ get; set; \} & The behaviour instance specific to this node. \\
Rect & public & Rect & \{ get; protected set; \} & The node's rect. \\
Tab & public & Bbbt\-Window\-Tab & \{ get; protected set; \} & The tab the node belongs to. \\
Is\-Selected & public & bool & \{ get; set; \} & Whether the node is currently selected. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Setup & public & void & (
            int id,
            Bbbt\-Behaviour base\-Behaviour,
            Vector2 position,
            Bbbt\-Window\-Tab tab,
            float width,
            float height,
            GUIStyle style,
            GUIStyle selected\-Style,
            GUIStyle in\-Point\-Style,
            GUIStyle out\-Point\-Style,
            Action{\tt <}\-Bbbt\-Connection\-Point\-{\tt >} in\-Point\-On\-Click,
            Action{\tt <}\-Bbbt\-Connection\-Point\-{\tt >} out\-Point\-On\-Click,
            Action{\tt <}\-Bbbt\-Node\-{\tt >} on\-Click\-Remove\-Node,
            bool is\-Selected = false,
            //Bbbt\-Behaviour\-Save\-Data behaviour\-Save\-Data = null
            Bbbt\-Behaviour behaviour = null) & Sets up a new Bbbt\-Node. \\
Drag & public & void & (Vector2 delta) & Moves the node. Used when the node is being dragged with the mouse. \\
Draw & public & void & () & Draws the node. \\
Draw\-Label & public & void & () & Draws the node's label undearneath the node. \\
Process\-Events & public & bool & (Bbbt\-Window window, Event e) & Processes events. \\
Create\-Context\-Menu & private & void & () & Creates a context menu for actions related to the node. \\
On\-Click\-Remove\-Node & private & void & () & Removes the node. \\
To\-Save\-Data & public & Bbbt\-Node\-Save\-Data & () & Generates a Bbbt\-Node\-Save\-Data from this node. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtPrompt}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The prompt's rect.} \\ \tabuphantomline
\_text\-Rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The prompt's text rect.} \\ \tabuphantomline
\_text & private & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The text to display in the prompt.} \\ \tabuphantomline
\_options & private & List{\tt <}\-Bbbt\-Prompt\-Option\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The options available for selection in the prompt.} \\ \tabuphantomline
\_window & private & Bbbt\-Window & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The window the prompt should be displayed in.} \\ \tabuphantomline
\_style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The prompt's gui style.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Prompt & public & (string text, List{\tt <}\-Bbbt\-Prompt\-Option\-{\tt >} options) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Bbbt\-Prompt.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Draw & public & bool & () & Draws the prompt to the screen. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtPromptOption}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_text & private & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The text to display in the button.} \\ \tabuphantomline
\_on\-Click & private & Action & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Action invoked when the button is clicked.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Rect & public & Rect & \{ get; protected set; \} & The rect for drawing the prompt's button. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Prompt\-Option & public & (string text, Action on\-Click) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Bbbt\-Prompt\-Option.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Draw & public & bool & (Vector2 position) & Draws the button to the screen. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtWindow}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Tree\-To\-Load & public & Bbbt\-Behaviour\-Tree & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Used to tell the editor to load a tree.
         Used to avoid loading a new tree in the middle of processing events.} \\ \tabuphantomline
Tab\-To\-Remove & public & Bbbt\-Window\-Tab & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Used to tell the editor to remove a tab.
         Used to avoid removing a tab in the middle of processing events.} \\ \tabuphantomline
\_tabs & private & List{\tt <}\-Bbbt\-Window\-Tab\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Tabs currently loaded into the Bbbt\-Window.} \\ \tabuphantomline
\_prompt & private & Bbbt\-Prompt & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The currently open prompt if any.
         If this is not null all other input should be blocked until the prompt is dealt with.} \\ \tabuphantomline
\_background & private static & Texture2D & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The texture for the editor window's background.} \\ \tabuphantomline
\_node\-To\-Open\-In\-Inspector & private & Bbbt\-Node & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{A node that was just selected and has yet to be display in the inspector.} \\ \tabuphantomline
\_connection\-Preview & private & Bbbt\-Connection\-Preview & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The preview of the connection currently being created.} \\ \tabuphantomline
\_node\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The GUIStyle used for drawing nodes.} \\ \tabuphantomline
\_selected\-Node\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The GUIStyle used for drawing selected nodes.} \\ \tabuphantomline
\_in\-Point\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style of connection points leading in to a node.} \\ \tabuphantomline
\_out\-Point\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style of connection points leading out from a node.} \\ \tabuphantomline
\_top\-Bar\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The GUIStyle of the top bar.} \\ \tabuphantomline
\_tab\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style of the tabs in the top bar.} \\ \tabuphantomline
\_selected\-In\-Point & private & Bbbt\-Connection\-Point & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The ingoing selection point that has been selected.} \\ \tabuphantomline
\_selected\-Out\-Point & private & Bbbt\-Connection\-Point & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The outgoing selection point that has been selected.} \\ \tabuphantomline
\_drag & private & Vector3 & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The amount by which to drag the canvas on a given frame.} \\ \tabuphantomline
\_grid\-Offset & private & Vector3 & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The amount by which to offset the lines when drawing the grid.} \\ \tabuphantomline
\_top\-Bar\-Rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The rect of the top bar.} \\ \tabuphantomline
\_last\-Is\-Playing & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Application.is\-Playing last time we checked.} \\ \tabuphantomline
\_side\-Panel & private & Bbbt\-Side\-Panel & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The window's side panel.} \\ \tabuphantomline
\_always\-Show\-Node\-Labels & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Whether node labels should always be shown.} \\ \tabuphantomline
\_resize\-With\-Side\-Panel & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Whether the window should resize with the side panel.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Current\-Tab & public & Bbbt\-Window\-Tab & \{ get; protected set; \} & The currently selected tab. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Open\-Window & public static & void & () & Opens a bb\-BT window. \\
On\-Enable & private & void & () & Called when the editor window is enabled. \\
On\-GUI & private & void & () & Called more or less when something needs to change in the editor. \\
Generate\-Background & private static & void & () & Generates the background texture for the editor window. \\
Draw\-Background & private & void & () & Draws the background of the editor window. \\
Draw\-Grid & private & void & (float line\-Distance, float opacity, Color line\-Color) & Draws a grid across the whole editor window. \\
Draw\-Top\-Bar & private & void & () & Draws the top bar of the editor window. \\
Draw\-Tabs & private & void & () & Draws the tabs in the top bar. \\
Close\-Tab & private & void & (Bbbt\-Window\-Tab tab, bool force = false) & Closes a tab. \\
Draw\-Nodes & private & void & () & Draws all nodes in the window. \\
Draw\-Node\-Labels & private & void & () & Draws all node labe. \\
Draw\-Connections & private & void & () & Draws all connections in the behaviour tree. \\
Process\-Events & private & void & (Event e) & Processes events. \\
Drag\-Window & private & void & (Vector2 delta) & Drags the entire window. \\
Process\-Node\-Events & private & void & (Event e) & Processes node events. \\
Process\-Tab\-Events & private & void & (Event e) & Processes tab events. \\
Select\-Node & public & void & (Bbbt\-Node node) & Selects a node. \\
Create\-Context\-Menu & private & void & (Vector2 position) & Creates a context menu. \\
Add\-Node & public & Bbbt\-Node & (
            int id,
            Bbbt\-Behaviour base\-Behaviour,
            Vector2 position,
            bool is\-Selected = false,
            //Bbbt\-Behaviour\-Save\-Data behaviour\-Save\-Data = null,
            Bbbt\-Behaviour behaviour = null) & Adds a new node to the behaviour tree. \\
Add\-Node & public & Bbbt\-Node & (
            int id,
            Bbbt\-Behaviour base\-Behaviour,
            Vector2 position,
            bool is\-Selected = false,
            //Bbbt\-Behaviour\-Save\-Data behaviour\-Save\-Data = null,
            Bbbt\-Behaviour behaviour = null) &  \\
On\-Click\-In\-Point & private & void & (Bbbt\-Connection\-Point in\-Point) & Called when an ingoing connection point is clicked. \\
On\-Click\-Out\-Point & private & void & (Bbbt\-Connection\-Point out\-Point) & Called when an outgoing connection point is clicked. \\
Create\-Connection & public & void & () & Creates a connection from the selected out point to the selected in point. \\
Create\-Connection & public & void & (Bbbt\-Node from, Bbbt\-Node to) & Creates a connection between two nodes. \\
Clear\-Connection\-Selection & private & void & () & Clears the selection of in point and out point. \\
Find\-Connection\-To\-Point & private & Bbbt\-Connection & (Bbbt\-Connection\-Point point) & Finds a connection leading to/from a connection point. \\
Is\-Connection\-Point\-At\-Max\-Capacity & private & bool & (Bbbt\-Connection\-Point point) & Checks whether a connection is currently unable to support more connections. \\
Remove\-Node & private & void & (Bbbt\-Node node) & Removes a node. \\
Find\-Selected\-Node & private & Bbbt\-Node & () & Finds the currently selected node, if any. \\
Set\-Unsaved\-Changes\-Tab\-Title & public & void & (Bbbt\-Window\-Tab tab, bool is\-Unsaved = true) & Adds an asterisk to the window title. \\
Decrement\-Tab\-Index & public & void & (Bbbt\-Window\-Tab tab) & Decrements the index of  in the tab list if possible.
         This has the effect of moving it to the left in the top bar. \\
Increment\-Tab\-Index & public & void & (Bbbt\-Window\-Tab tab) & Increments the index of  in the tab list if possible.
         This has the effect of moving it to the right in the top bar. \\
Save\-Tree & private & void & () & Saves the behaviour tree in the current tab to a file. \\
Save\-Tab & private & void & (Bbbt\-Window\-Tab tab) & Saves the contents of a tab. \\
Load\-Tree & public & void & (Bbbt\-Behaviour\-Tree tree) & Loads a behaviour tree from a Bbbt\-Behaviour\-Tree scriptable object. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtWindowTab}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The tab's rect.} \\ \tabuphantomline
Last\-Node\-ID & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The id of the last created node.} \\ \tabuphantomline
Tree & public & Bbbt\-Behaviour\-Tree & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The behaviour tree currently loaded into the editor window.} \\ \tabuphantomline
Nodes & public & List{\tt <}\-Bbbt\-Node\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The nodes that make up the behaviour tree.} \\ \tabuphantomline
Connections & public & List{\tt <}\-Bbbt\-Connection\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The current connections between nodes.} \\ \tabuphantomline
Window\-Offset & public & Vector3 & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The amount by which the entire window has been dragged from its initial position.} \\ \tabuphantomline
Is\-Unsaved & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Whether the tab has unsaved changes.} \\ \tabuphantomline
\_is\-Dragged & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Whether the tab is being dragged.} \\ \tabuphantomline
\_tab\-Moved\-Position & private & Vector2 & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The position at which the tab previously moved. A non-zero value indicates that we should reference this
         value when deciding whether to move the tab back to its previous position.} \\ \tabuphantomline
\_tab\-Moved\-Delta & private & Vector2 & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The mouse delta when the tab previously moved.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Command\-Manager & public & Command\-Manager & \{ get; protected set; \} & The tab's command manager. \\
Command\-History & public & Bbbt\-Tab\-Command\-History & \{ get; protected set; \} & The tab's command history. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Window\-Tab & public & (Bbbt\-Behaviour\-Tree tree, GUIStyle style) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiates a new Bbbt\-Window\-Tab.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Draw & public & void & (Rect top\-Bar\-Rect, List{\tt <}\-Bbbt\-Window\-Tab\-{\tt >} tabs, bool is\-Active = false) & Draws the tab. \\
Process\-Events & public & bool & (Event e) & Processes events. \\
Create\-Context\-Menu & private & void & (Vector2 position) & Creates a context menu \\
Close\-Tab & private & void & () & Closes the tab. \\
Drag & private & void & (Vector2 mouse\-Position, Vector2 delta) & Drags the tab. \\
Reset\-Commands & public & void & () & Resets the Command\-Manager/command strings for this tab. \\
Set\-Behaviour\-Children & public & void & () & Sets the behaviour children according to the nodes' position in the editor. \\
Find\-Node\-With\-Id & public & Bbbt\-Node & (int id) & Finds a node in the tab with a given id. \\
Find\-Parent\-Node & public & Bbbt\-Node & (Bbbt\-Node node) & Finds the node which the given node is a child of. \\
Does\-Root\-Exist & public & bool & () & Checks if a root node exists in the tab. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviour}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Save\-Data\-Type & public abstract & string & \{ get; \} & The name of the save data type used for identifying type during serialisation. \\
Status & public & Bbbt\-Behaviour\-Status & \{ get; protected set; \} & The current status of the behaviour. \\
Node\-Id & public & int & \{ get; set; \} & The id of the node that contains the behaviour in the editor.
         We need this to get direct behaviour references when opening behaviour trees in the editor in debug mode. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Tick & public & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Tick gets called every time the behaviour tree reaches the node containing this behaviour. \\
On\-Initialize & protected abstract & void & (Game\-Object game\-Object) & On\-Initialize is called once, immediately before the first call to the behavior's update method \\
Update\-Behaviour & protected abstract & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Update is called once each time the behavior tree is updated,
         until it signals it has terminated thanks to its return status \\
On\-Terminate & protected abstract & void & (Game\-Object game\-Object, Bbbt\-Behaviour\-Status status) & On\-Terminate is called once, immediately after the previous update signals it's no longer running. \\
Add\-Child & public abstract & void & (Bbbt\-Behaviour child) & Adds a child to the node. \\
Remove\-Children & public abstract & void & () & Removes all of the behaviour's children. \\
Reset & public & void & () & Resets the behaviour to its initial state. \\
Abort & public & void & (Game\-Object game\-Object) & Gracefully aborts the behaviour. \\
Is\-Terminated & public & bool & () & Checks whether the behaviour has terminated. \\
Find\-Behaviour\-With\-Name & public static & Bbbt\-Behaviour & (string query) & Tries to find a behaviour that matches a given query. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtCompositeBehaviour}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Children & public & List{\tt <}\-Bbbt\-Behaviour\-{\tt >} & \{ get; protected set; \} & The child behaviours of this node. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add\-Child & public override & void & (Bbbt\-Behaviour child) & Adds a child behaviour. \\
Remove\-Children & public override & void & () & Removes all of the behaviour's children. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtDecoratorBehaviour}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Child & public & Bbbt\-Behaviour & \{ get; protected set; \} & The decorator's child behaviour. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add\-Child & public override & void & (Bbbt\-Behaviour child) & Adds a child to the node. \\
Remove\-Children & public override & void & () & Removes all of the behaviour's children. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtLeafBehaviour}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add\-Child & public override & void & (Bbbt\-Behaviour child) & Adds a child to the node. \\
Remove\-Children & public override & void & () & Removes all of the behaviour's children. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtRoot}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Child & public & Bbbt\-Behaviour & \{ get; protected set; \} & The node that the Bbbt\-Root points to as the real root of the behaviour tree. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Initialize & protected override & void & (Game\-Object game\-Object) & Bbbt\-Root doesn't have any initialisation logic.
         This should never be called as the root node isn't actually a part of a built behaviour tree. \\
On\-Terminate & protected override & void & (Game\-Object game\-Object, Bbbt\-Behaviour\-Status status) & Bbbt\-Root doesn't have any termination logic.
         This should never be called as the root node isn't actually a part of a built behaviour tree. \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Bbbt\-Root doesn't have any update logic.
         This should never be called as the root node isn't actually a part of a built behaviour tree. \\
Add\-Child & public override & void & (Bbbt\-Behaviour child) & Adds a child to the node. \\
Remove\-Children & public override & void & () & Removes all of the behaviour's children. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtInverter}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Inverts the result of the child behavior \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtRepeater}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Count & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Number of times to repeat the child succsessfully} \\ \tabuphantomline
\_success\-Count & private & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{how many time the child has repeated} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Executes the repeaters child node untill it has succsessfully executed a set number of times (Count variable). \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtRepeatUntilFail}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviourSaveData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Save\-Data\-Type & public abstract & string & \{ get; \} & The name of the save data type used for identifying type during serialisation. \\
Node\-Id & public & int & \{ get; set; \} & The id of the node that contains the behaviour in the editor.
         We need this to get direct behaviour references when opening behaviour trees in the editor in debug mode. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviourTreeCallerBehaviourSaveData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Save\-Data\-Type & public override & string & \{ get; \} & The name of the save data type used for identifying type during serialisation. \\
Behaviour\-Tree\-Name & public & string & \{ get; protected set; \} & The name of the behaviour tree to call. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Behaviour\-Tree\-Caller\-Behaviour\-Save\-Data & public & (int node\-Id, string behaviour\-Tree\-Name) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Bbbt\-Behaviour\-Tree\-Caller\-Behaviour\-Save\-Data object.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtDebugLogBehaviourSaveData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Save\-Data\-Type & public override & string & \{ get; \} & The name of the save data type used for identifying type during serialisation. \\
Message & public & string & \{ get; protected set; \} & The message to be displayed by the behaviour. \\
Log\-Type & public & Log\-Type & \{ get; protected set; \} & The type of message to log. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Debug\-Log\-Behaviour\-Save\-Data & public & (int node\-Id, string message, Log\-Type log\-Type) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Bbbt\-Debug\-Log\-Behaviour\-Save\-Data object.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtRootSaveData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Save\-Data\-Type & public override & string & \{ get; \} & The name of the save data type used for identifying type during serialisation. \\
Child\-Save\-Data & public & Bbbt\-Behaviour\-Save\-Data & \{ get; protected set; \} & The root behaviour's child. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Root\-Save\-Data & public & (int node\-Id, Bbbt\-Behaviour\-Save\-Data child\-Save\-Data) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Bbbt\-Root\-Save\-Data object.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtSelectorSaveData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Save\-Data\-Type & public override & string & \{ get; \} & The name of the save data type used for identifying type during serialisation. \\
Child\-Save\-Data & public & Bbbt\-Behaviour\-Save\-Data[] & \{ get; protected set; \} & The behaviour's children. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Selector\-Save\-Data & public & (int node\-Id, Bbbt\-Behaviour\-Save\-Data[] child\-Save\-Data) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Bbbt\-Selector\-Save\-Data object.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtSequencerSaveData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Save\-Data\-Type & public override & string & \{ get; \} & The name of the save data type used for identifying type during serialisation. \\
Child\-Save\-Data & public & Bbbt\-Behaviour\-Save\-Data[] & \{ get; protected set; \} & The behaviour's children. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Sequencer\-Save\-Data & public & (int node\-Id, Bbbt\-Behaviour\-Save\-Data[] child\-Save\-Data) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Bbbt\-Sequencer\-Save\-Data object.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SyncDictionaryProcessor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Process & public static & void & (Type\-Definition td) & Generates serialization methods for synclists \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SyncListProcessor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Process & public static & void & (Type\-Definition td) & Generates serialization methods for synclists \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SyncObjectProcessor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Generate\-Serialization & public static & void & (Type\-Definition td, int generic\-Argument, string serialize\-Method, string deserialize\-Method) & Generates the serialization and deserialization methods for a specified generic argument \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NetworkRoomManagerExt}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Room\-Server\-Scene\-Loaded\-For\-Player & public override & bool & (Network\-Connection conn, Game\-Object room\-Player, Game\-Object game\-Player) & Called just after Game\-Player object is instantiated and just before it replaces Room\-Player object.
         This is the ideal point to pass any data like player name, credentials, tokens, colors, etc.
         into the Game\-Player object as it is about to enter the Online scene. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Utilities}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Make\-Relative\-Path & public static & string & (string dir\-Path, string abs\-Path) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Extension_Methods}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Or\-Default & public static & TValue & (this Dictionary{\tt <}\-TKey, TValue\-{\tt >} dictionary, TKey key) & Gets a value from the dictionary or returns the default value \\
Get\-Or\-Create & public static & TValue & (this Dictionary{\tt <}\-TKey, TValue\-{\tt >} dictionary, TKey key, Func{\tt <}\-TValue\-{\tt >} creator) & Gets a value from the dictionary or creates it \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{LinkedListIndex}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Linked\-List\-Index & public & (Linked\-List{\tt <}\-TValue\-{\tt >} linked\-List) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Find & public & Linked\-List\-Node{\tt <}\-TValue\-{\tt >} & (TKey key) & Finds the node indexed by the specified key, or null. \\
Set & public & TValue & (TKey key, TValue value) & Updates or creates a new node in the linked list, indexed by the specified key. \\
Add & public & void & (TKey key, TValue value) & Creates a new node in the linked list, indexed by the specified key. \\
Remove & public & bool & (TKey key) & Removes the specified key from the index, and the node indexed by the key from the linked list. \\
Contains\-Key & public & bool & (TKey key) & Determines whether the index contains the specified key. \\
Clear & public & void & () & Clears this instance (removes all elements) \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MultiDictionary}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Keys & public & IEnumerable{\tt <}\-K\-{\tt >} & \{ get \} & Gets the keys. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Multi\-Dictionary & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Multi\-Dictionary & public & (IEquality\-Comparer{\tt <}\-K\-{\tt >} eq\-Comparer) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add & public & bool & (K key, V value) & Adds the specified key. Returns true if this is the first value for a given key \\
Find & public & IEnumerable{\tt <}\-V\-{\tt >} & (K key) & Finds all the values associated with the specified key. 
		 An empty collection is returned if not found. \\
Contains\-Key & public & bool & (K key) & Determines whether this contains the specified key \\
Clear & public & void & () & Clears this instance. \\
Remove & public & void & (K key) & Removes the specified key and all its associated values from the multidictionary \\
Remove\-Value & public & bool & (K key, V value) & Removes the value. Returns true if the removed value was the last of a given key \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Slice}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
From & public & int & \{ get \} & Gets the index from which the slice starts \\
Count & public & int & \{ get \} & Gets the number of elements contained in the . \\
Reversed & public & bool & \{ get \} & Gets a value indicating whether this  operates in a reversed direction. \\
Is\-Read\-Only & public & bool & \{ get \} & Gets a value indicating whether the  is read-only. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Slice & public & (IList{\tt <}\-T\-{\tt >} list, int from, int length, bool reversed) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Calc\-Real\-Index & private & int & (int index) & Calculates the real index in the underlying collection \\
Get\-Enumerator & public & IEnumerator{\tt <}\-T\-{\tt >} & () & Returns an enumerator that iterates through the collection. \\
Get\-Enumerator &  & System.Collections.IEnumerator & () & Returns an enumerator that iterates through a collection. \\
To\-Array & public & T[] & () & Converts to an array. \\
To\-List & public & List{\tt <}\-T\-{\tt >} & () & Converts to an list. \\
Index\-Of & public & int & (T item) & Determines the index of a specific item in the . \\
Insert & public & void & (int index, T item) & Inserts an item to the  at the specified index. \\
Remove\-At & public & void & (int index) & Removes the  item at the specified index. \\
Add & public & void & (T item) & Adds an item to the . \\
Clear & public & void & () & Removes all items from the . \\
Contains & public & bool & (T item) & Determines whether the  contains a specific value. \\
Copy\-To & public & void & (T[] array, int array\-Index) & Copies to. \\
Remove & public & bool & (T item) & Removes the first occurrence of a specific object from the . \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CallbackArguments}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Count & public & int & \{ get \} & Gets the count of arguments \\
Is\-Method\-Call & public & bool & \{ get; private set; \} & Gets or sets a value indicating whether this is a method call. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Callback\-Arguments & public & (IList{\tt <}\-Dyn\-Value\-{\tt >} args, bool is\-Method\-Call) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Raw\-Get & public & Dyn\-Value & (int index, bool translate\-Voids) & Gets the  at the specified index, or null. \\
Get\-Array & public & Dyn\-Value[] & (int skip = 0) & Converts the arguments to an array \\
As\-Type & public & Dyn\-Value & (int arg\-Num, string func\-Name, Data\-Type type, bool allow\-Nil = false) & Gets the specified argument as as an argument of the specified type. If not possible,
		 an exception is raised. \\
As\-User\-Data & public & T & (int arg\-Num, string func\-Name, bool allow\-Nil = false) & Gets the specified argument as as an argument of the specified user data type. If not possible,
		 an exception is raised. \\
As\-Int & public & int & (int arg\-Num, string func\-Name) & Gets the specified argument as an integer \\
As\-Long & public & long & (int arg\-Num, string func\-Name) & Gets the specified argument as a long integer \\
As\-String\-Using\-Meta & public & string & (Script\-Execution\-Context execution\-Context, int arg\-Num, string func\-Name) & Gets the specified argument as a string, calling the \_\_tostring metamethod if needed, in a NON
		 yield-compatible way. \\
Skip\-Method\-Call & public & Callback\-Arguments & () & Returns a copy of Callback\-Arguments where the first ("self") argument is skipped if this was a method call,
		 otherwise returns itself. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CallbackFunction}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; private set; \} & Gets the name of the function \\
Clr\-Callback & public & Func{\tt <}\-Script\-Execution\-Context, Callback\-Arguments, Dyn\-Value\-{\tt >} & \{ get; private set; \} & Gets the call back. \\
Default\-Access\-Mode & public static & Interop\-Access\-Mode & \{ get set \} & Gets or sets the default access mode used when marshalling delegates \\
Additional\-Data & public & object & \{ get; set; \} & Gets or sets an object used as additional data to the callback function (available in the execution context). \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Callback\-Function & public & (Func{\tt <}\-Script\-Execution\-Context, Callback\-Arguments, Dyn\-Value\-{\tt >} call\-Back, string name = null) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Invoke & public & Dyn\-Value & (Script\-Execution\-Context execution\-Context, IList{\tt <}\-Dyn\-Value\-{\tt >} args, bool is\-Method\-Call = false) & Invokes the callback function \\
From\-Delegate & public static & Callback\-Function & (Script script, Delegate del, Interop\-Access\-Mode access\-Mode = Interop\-Access\-Mode.Default) & Creates a Callback\-Function from a delegate. \\
From\-Method\-Info & public static & Callback\-Function & (Script script, System.Reflection.Method\-Info mi, object obj = null, Interop\-Access\-Mode access\-Mode = Interop\-Access\-Mode.Default) & Creates a Callback\-Function from a Method\-Info relative to a function. \\
Check\-Callback\-Signature & public static & bool & (System.Reflection.Method\-Info mi, bool require\-Public\-Visibility) & Checks the callback signature of a method is compatible for callbacks \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Closure}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
empty\-Closure & private static & Closure\-Context & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Shortcut for an empty closure} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Entry\-Point\-Byte\-Code\-Location & public & int & \{ get; private set; \} & Gets the entry point location in bytecode . \\
Owner\-Script & public & Script & \{ get; private set; \} & Gets the script owning this function \\
Closure\-Context & internal & Closure\-Context & \{ get; private set; \} & The current closure context \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Closure & internal & (Script script, int idx, Symbol\-Ref[] symbols, IEnumerable{\tt <}\-Dyn\-Value\-{\tt >} resolved\-Locals) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Call & public & Dyn\-Value & () & Calls this function with the specified args \\
Call & public & Dyn\-Value & (params object[] args) & Calls this function with the specified args \\
Call & public & Dyn\-Value & (params Dyn\-Value[] args) & Calls this function with the specified args \\
Get\-Delegate & public & Script\-Function\-Delegate & () & Gets a delegate wrapping calls to this scripted function \\
Get\-Delegate & public & Script\-Function\-Delegate{\tt <}\-T\-{\tt >} & () & Gets a delegate wrapping calls to this scripted function \\
Get\-Upvalues\-Count & public & int & () & Gets the number of upvalues in this closure \\
Get\-Upvalue\-Name & public & string & (int idx) & Gets the name of the specified upvalue. \\
Get\-Upvalue & public & Dyn\-Value & (int idx) & Gets the value of an upvalue. To set the value, use Get\-Upvalue(idx).Assign(...); \\
Get\-Upvalues\-Type & public & Upvalues\-Type & () & Gets the type of the upvalues contained in this closure \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Coroutine}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Type & public & Coroutine\-Type & \{ get; private set; \} & Gets the type of coroutine \\
State & public & Coroutine\-State & \{ get \} & Gets the coroutine state. \\
Owner\-Script & public & Script & \{ get; private set; \} & Gets the script owning this resource. \\
Auto\-Yield\-Counter & public & long & \{ get set \} & Gets or sets the automatic yield counter. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
As\-Typed\-Enumerable & public & IEnumerable{\tt <}\-Dyn\-Value\-{\tt >} & () & Gets this coroutine as a typed enumerable which can be looped over for resuming.
		 Returns its result as Dyn\-Value(s) \\
As\-Enumerable & public & IEnumerable{\tt <}\-object\-{\tt >} & () & Gets this coroutine as a typed enumerable which can be looped over for resuming.
		 Returns its result as System.Object. Only the first element of tuples is returned.
		 Only non-CLR coroutines can be resumed with this method. Use an overload of the Resume method accepting a Script\-Execution\-Context instead. \\
As\-Enumerable & public & IEnumerable{\tt <}\-T\-{\tt >} & () & Gets this coroutine as a typed enumerable which can be looped over for resuming.
		 Returns its result as the specified type. Only the first element of tuples is returned.
		 Only non-CLR coroutines can be resumed with this method. Use an overload of the Resume method accepting a Script\-Execution\-Context instead. \\
As\-Unity\-Coroutine & public & System.Collections.IEnumerator & () & The purpose of this method is to convert a Moon\-Sharp/Lua coroutine to a Unity3D coroutine.
		 This loops over the coroutine, discarding returned values, and returning null for each invocation.
		 This means however that the coroutine will be invoked each frame.
		 Only non-CLR coroutines can be resumed with this method. Use an overload of the Resume method accepting a Script\-Execution\-Context instead. \\
Resume & public & Dyn\-Value & (params Dyn\-Value[] args) & Resumes the coroutine.
		 Only non-CLR coroutines can be resumed with this overload of the Resume method. Use the overload accepting a Script\-Execution\-Context instead. \\
Resume & public & Dyn\-Value & (Script\-Execution\-Context context, params Dyn\-Value[] args) & Resumes the coroutine. \\
Resume & public & Dyn\-Value & () & Resumes the coroutine.
		 Only non-CLR coroutines can be resumed with this overload of the Resume method. Use the overload accepting a Script\-Execution\-Context instead. \\
Resume & public & Dyn\-Value & (Script\-Execution\-Context context) & Resumes the coroutine. \\
Resume & public & Dyn\-Value & (params object[] args) & Resumes the coroutine.
		 Only non-CLR coroutines can be resumed with this overload of the Resume method. Use the overload accepting a Script\-Execution\-Context instead. \\
Resume & public & Dyn\-Value & (Script\-Execution\-Context context, params object[] args) & Resumes the coroutine \\
Get\-Stack\-Trace & public & Watch\-Item[] & (int skip, Source\-Ref entry\-Source\-Ref = null) & Gets the coroutine stack trace for debug purposes \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{LuaTypeExtensions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Can\-Have\-Type\-Metatables & public static & bool & (this Data\-Type type) & Determines whether this data type can have type metatables. \\
To\-Error\-Type\-String & public static & string & (this Data\-Type type) & Converts the Data\-Type to the string returned by the "type(...)" Lua function \\
To\-Lua\-Debugger\-String & public static & string & (this Data\-Type type) & Converts the Data\-Type to the string returned by the "type(...)" Lua function, with additional values
		 to support debuggers \\
To\-Lua\-Type\-String & public static & string & (this Data\-Type type) & Converts the Data\-Type to the string returned by the "type(...)" Lua function \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DynValue}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Reference\-ID & public & int & \{ get \} & Gets a unique reference identifier. This is guaranteed to be unique only for dynvalues created in a single thread as it's not thread-safe. \\
Type & public & Data\-Type & \{ get \} & Gets the type of the value. \\
Function & public & Closure & \{ get \} & Gets the function (valid only if the  is ) \\
Number & public & double & \{ get \} & Gets the numeric value (valid only if the  is ) \\
Tuple & public & Dyn\-Value[] & \{ get \} & Gets the values in the tuple (valid only if the  is Tuple).
		 This field is currently also used to hold arguments in values whose  is . \\
Coroutine & public & Coroutine & \{ get \} & Gets the coroutine handle. (valid only if the  is Thread). \\
Table & public & Table & \{ get \} & Gets the table (valid only if the  is ) \\
Boolean & public & bool & \{ get \} & Gets the boolean value (valid only if the  is ) \\
String & public & string & \{ get \} & Gets the string value (valid only if the  is ) \\
Callback & public & Callback\-Function & \{ get \} & Gets the CLR callback (valid only if the  is ) \\
Tail\-Call\-Data & public & Tail\-Call\-Data & \{ get \} & Gets the tail call data. \\
Yield\-Request & public & Yield\-Request & \{ get \} & Gets the yield request data. \\
User\-Data & public & User\-Data & \{ get \} & Gets the tail call data. \\
Read\-Only & public & bool & \{ get \} & Returns true if this instance is write protected. \\
Void & public static & Dyn\-Value & \{ get; private set; \} & A preinitialized, readonly instance, equaling Void \\
Nil & public static & Dyn\-Value & \{ get; private set; \} & A preinitialized, readonly instance, equaling Nil \\
True & public static & Dyn\-Value & \{ get; private set; \} & A preinitialized, readonly instance, equaling True \\
False & public static & Dyn\-Value & \{ get; private set; \} & A preinitialized, readonly instance, equaling False \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
New\-Nil & public static & Dyn\-Value & () & Creates a new writable value initialized to Nil. \\
New\-Boolean & public static & Dyn\-Value & (bool v) & Creates a new writable value initialized to the specified boolean. \\
New\-Number & public static & Dyn\-Value & (double num) & Creates a new writable value initialized to the specified number. \\
New\-String & public static & Dyn\-Value & (string str) & Creates a new writable value initialized to the specified string. \\
New\-String & public static & Dyn\-Value & (String\-Builder sb) & Creates a new writable value initialized to the specified String\-Builder. \\
New\-String & public static & Dyn\-Value & (string format, params object[] args) & Creates a new writable value initialized to the specified string using String.Format like syntax \\
New\-Coroutine & public static & Dyn\-Value & (Coroutine coroutine) & Creates a new writable value initialized to the specified coroutine.
		 Internal use only, for external use, see Script.Coroutine\-Create \\
New\-Closure & public static & Dyn\-Value & (Closure function) & Creates a new writable value initialized to the specified closure (function). \\
New\-Callback & public static & Dyn\-Value & (Func{\tt <}\-Script\-Execution\-Context, Callback\-Arguments, Dyn\-Value\-{\tt >} call\-Back, string name = null) & Creates a new writable value initialized to the specified CLR callback. \\
New\-Callback & public static & Dyn\-Value & (Callback\-Function function) & Creates a new writable value initialized to the specified CLR callback.
		 See also Callback\-Function.From\-Delegate and Callback\-Function.From\-Method\-Info factory methods. \\
New\-Table & public static & Dyn\-Value & (Table table) & Creates a new writable value initialized to the specified table. \\
New\-Prime\-Table & public static & Dyn\-Value & () & Creates a new writable value initialized to an empty prime table (a 
		 prime table is a table made only of numbers, strings, booleans and other
		 prime tables). \\
New\-Table & public static & Dyn\-Value & (Script script) & Creates a new writable value initialized to an empty table. \\
New\-Table & public static & Dyn\-Value & (Script script, params Dyn\-Value[] array\-Values) & Creates a new writable value initialized to with array contents. \\
New\-Tail\-Call\-Req & public static & Dyn\-Value & (Dyn\-Value tail\-Fn, params Dyn\-Value[] args) & Creates a new request for a tail call. This is the preferred way to execute Lua/Moon\-Sharp code from a callback,
		 although it's not always possible to use it. When a function (callback or script closure) returns a
		 Tail\-Call\-Request, the bytecode processor immediately executes the function contained in the request.
		 By executing script in this way, a callback function ensures it's not on the stack anymore and thus a number
		 of functionality (state savings, coroutines, etc) keeps working at full power. \\
New\-Tail\-Call\-Req & public static & Dyn\-Value & (Tail\-Call\-Data tail\-Call\-Data) & Creates a new request for a tail call. This is the preferred way to execute Lua/Moon\-Sharp code from a callback,
		 although it's not always possible to use it. When a function (callback or script closure) returns a
		 Tail\-Call\-Request, the bytecode processor immediately executes the function contained in the request.
		 By executing script in this way, a callback function ensures it's not on the stack anymore and thus a number
		 of functionality (state savings, coroutines, etc) keeps working at full power. \\
New\-Yield\-Req & public static & Dyn\-Value & (Dyn\-Value[] args) & Creates a new request for a yield of the current coroutine. \\
New\-Forced\-Yield\-Req & internal static & Dyn\-Value & () & Creates a new request for a yield of the current coroutine. \\
New\-Tuple & public static & Dyn\-Value & (params Dyn\-Value[] values) & Creates a new tuple initialized to the specified values. \\
New\-Tuple\-Nested & public static & Dyn\-Value & (params Dyn\-Value[] values) & Creates a new tuple initialized to the specified values - which can be potentially other tuples \\
New\-User\-Data & public static & Dyn\-Value & (User\-Data user\-Data) & Creates a new userdata value \\
As\-Read\-Only & public & Dyn\-Value & () & Returns this value as readonly - eventually cloning it in the process if it isn't readonly to start with. \\
Clone & public & Dyn\-Value & () & Clones this instance. \\
Clone & public & Dyn\-Value & (bool read\-Only) & Clones this instance, overriding the "readonly" status. \\
Clone\-As\-Writable & public & Dyn\-Value & () & Clones this instance, returning a writable copy. \\
To\-Print\-String & public & string & () & Returns a string which is what it's expected to be output by the print function applied to this value. \\
To\-Debug\-Print\-String & public & string & () & Returns a string which is what it's expected to be output by debuggers. \\
To\-String & public override & string & () & Returns a  that represents this instance. \\
Get\-Hash\-Code & public override & int & () & Returns a hash code for this instance. \\
Equals & public override & bool & (object obj) & Determines whether the specified , is equal to this instance. \\
Cast\-To\-String & public & string & () & Casts this Dyn\-Value to string, using coercion if the type is number. \\
Cast\-To\-Number & public & double? & () & Casts this Dyn\-Value to a double, using coercion if the type is string. \\
Cast\-To\-Bool & public & bool & () & Casts this Dyn\-Value to a bool \\
Get\-As\-Private\-Resource & public & IScript\-Private\-Resource & () & Returns this Dyn\-Value as an instance of , if possible,
		 null otherwise \\
To\-Scalar & public & Dyn\-Value & () & Converts a tuple to a scalar value. If it's already a scalar value, this function returns "this". \\
Assign & public & void & (Dyn\-Value value) & Performs an assignment, overwriting the value with the specified one. \\
Get\-Length & public & Dyn\-Value & () & Gets the length of a string or table value. \\
Is\-Nil & public & bool & () & Determines whether this instance is nil or void \\
Is\-Not\-Nil & public & bool & () & Determines whether this instance is not nil or void \\
Is\-Void & public & bool & () & Determines whether this instance is void \\
Is\-Not\-Void & public & bool & () & Determines whether this instance is not void \\
Is\-Nil\-Or\-Nan & public & bool & () & Determines whether is nil, void or Na\-N (and thus unsuitable for using as a table key). \\
Assign\-Number & internal & void & (double num) & Changes the numeric value of a number Dyn\-Value. \\
From\-Object & public static & Dyn\-Value & (Script script, object obj) & Creates a new Dyn\-Value from a CLR object \\
To\-Object & public & object & () & Converts this Moon\-Sharp Dyn\-Value to a CLR object. \\
To\-Object & public & object & (Type desired\-Type) & Converts this Moon\-Sharp Dyn\-Value to a CLR object of the specified type. \\
To\-Object & public & T & () & Converts this Moon\-Sharp Dyn\-Value to a CLR object of the specified type. \\
Check\-Type & public & Dyn\-Value & (string func\-Name, Data\-Type desired\-Type, int arg\-Num = -1, Type\-Validation\-Flags flags = Type\-Validation\-Flags.Default) & Checks the type of this value corresponds to the desired type. A propert Script\-Runtime\-Exception is thrown
		 if the value is not of the specified type or - considering the Type\-Validation\-Flags - is not convertible
		 to the specified type. \\
Check\-User\-Data\-Type & public & T & (string func\-Name, int arg\-Num = -1, Type\-Validation\-Flags flags = Type\-Validation\-Flags.Default) & Checks if the type is a specific userdata type, and returns it or throws. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RefIdObject}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Reference\-ID & public & int & \{ get \} & Gets the reference identifier. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Format\-Type\-String & public & string & (string type\-String) & Formats a string with a type name and a ref-id \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SymbolRef}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Type & public & Symbol\-Ref\-Type & \{ get \} & Gets the type of this symbol reference \\
Index & public & int & \{ get \} & Gets the index of this symbol in its scope context \\
Name & public & string & \{ get \} & Gets the name of this symbol \\
Environment & public & Symbol\-Ref & \{ get \} & Gets the environment this symbol refers to (for global symbols only) \\
Default\-Env & public static & Symbol\-Ref & \{ get \} & Gets the default \_ENV. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Global & public static & Symbol\-Ref & (string name, Symbol\-Ref env\-Symbol) & Creates a new symbol reference pointing to a global var \\
Local & internal static & Symbol\-Ref & (string name, int index) & Creates a new symbol reference pointing to a local var \\
Upvalue & internal static & Symbol\-Ref & (string name, int index) & Creates a new symbol reference pointing to an upvalue var \\
To\-String & public override & string & () & Returns a  that represents this instance. \\
Write\-Binary & internal & void & (Binary\-Writer bw) & Writes this instance to a binary stream \\
Read\-Binary & internal static & Symbol\-Ref & (Binary\-Reader br) & Reads a symbolref from a binary stream \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Table}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Owner\-Script & public & Script & \{ get \} & Gets the script owning this resource. \\
Length & public & int & \{ get return m\_Cached\-Length; \} \} & Gets the length of the "array part". \\
Meta\-Table & public & Table & \{ get set \} & Gets the meta-table associated with this instance. \\
Pairs & public & IEnumerable{\tt <}\-Table\-Pair\-{\tt >} & \{ get \} & Enumerates the key/value pairs. \\
Keys & public & IEnumerable{\tt <}\-Dyn\-Value\-{\tt >} & \{ get \} & Enumerates the keys. \\
Values & public & IEnumerable{\tt <}\-Dyn\-Value\-{\tt >} & \{ get \} & Enumerates the values \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Table & public & (Script owner) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Table & public & (Script owner, params Dyn\-Value[] array\-Values) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Clear & public & void & () & Removes all items from the Table. \\
Get\-Integral\-Key & private & int & (double d) & Gets the integral key from a double. \\
Append & public & void & (Dyn\-Value value) & Append the value to the table using the next available integer index. \\
Set & public & void & (string key, Dyn\-Value value) & Sets the value associated to the specified key. \\
Set & public & void & (int key, Dyn\-Value value) & Sets the value associated to the specified key. \\
Set & public & void & (Dyn\-Value key, Dyn\-Value value) & Sets the value associated to the specified key. \\
Set & public & void & (object key, Dyn\-Value value) & Sets the value associated with the specified key. \\
Set & public & void & (object[] keys, Dyn\-Value value) & Sets the value associated with the specified keys.
		 Multiple keys can be used to access subtables. \\
Get & public & Dyn\-Value & (string key) & Gets the value associated with the specified key. \\
Get & public & Dyn\-Value & (int key) & Gets the value associated with the specified key. \\
Get & public & Dyn\-Value & (Dyn\-Value key) & Gets the value associated with the specified key. \\
Get & public & Dyn\-Value & (object key) & Gets the value associated with the specified key.
		 (expressed as a ). \\
Get & public & Dyn\-Value & (params object[] keys) & Gets the value associated with the specified keys (expressed as an 
		 array of ).
		 This will marshall CLR and Moon\-Sharp objects in the best possible way.
		 Multiple keys can be used to access subtables. \\
Raw\-Get & public & Dyn\-Value & (string key) & Gets the value associated with the specified key,
		 without bringing to Nil the non-existant values. \\
Raw\-Get & public & Dyn\-Value & (int key) & Gets the value associated with the specified key,
		 without bringing to Nil the non-existant values. \\
Raw\-Get & public & Dyn\-Value & (Dyn\-Value key) & Gets the value associated with the specified key,
		 without bringing to Nil the non-existant values. \\
Raw\-Get & public & Dyn\-Value & (object key) & Gets the value associated with the specified key,
		 without bringing to Nil the non-existant values. \\
Raw\-Get & public & Dyn\-Value & (params object[] keys) & Gets the value associated with the specified keys (expressed as an
		 array of ).
		 This will marshall CLR and Moon\-Sharp objects in the best possible way.
		 Multiple keys can be used to access subtables. \\
Remove & public & bool & (string key) & Remove the value associated with the specified key from the table. \\
Remove & public & bool & (int key) & Remove the value associated with the specified key from the table. \\
Remove & public & bool & (Dyn\-Value key) & Remove the value associated with the specified key from the table. \\
Remove & public & bool & (object key) & Remove the value associated with the specified key from the table. \\
Remove & public & bool & (params object[] keys) & Remove the value associated with the specified keys from the table.
		 Multiple keys can be used to access subtables. \\
Collect\-Dead\-Keys & public & void & () & Collects the dead keys. This frees up memory but invalidates pending iterators.
		 It's called automatically internally when the semantics of Lua tables allow, but can be forced
		 externally if it's known that no iterators are pending. \\
Next\-Key & public & Table\-Pair? & (Dyn\-Value v) & Returns the next pair from a value \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TablePair}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Key & public & Dyn\-Value & \{ get private set \} & Gets the key. \\
Value & public & Dyn\-Value & \{ get set \} & Gets or sets the value. \\
Nil & public static & Table\-Pair & \{ get \} & Gets the nil pair \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Table\-Pair & public & (Dyn\-Value key, Dyn\-Value val) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  struct.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TailCallData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Function & public & Dyn\-Value & \{ get; set; \} & Gets or sets the function to call \\
Args & public & Dyn\-Value[] & \{ get; set; \} & Gets or sets the arguments to the function \\
Continuation & public & Callback\-Function & \{ get; set; \} & Gets or sets the callback to be used as a continuation. \\
Error\-Handler & public & Callback\-Function & \{ get; set; \} & Gets or sets the callback to be used in case of errors. \\
Error\-Handler\-Before\-Unwind & public & Dyn\-Value & \{ get; set; \} & Gets or sets the error handler to be called before stack unwinding \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{UserData}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
User\-Value & public & Dyn\-Value & \{ get; set; \} & Gets or sets the "uservalue". See debug.getuservalue and debug.setuservalue.
		 http://www.lua.org/manual/5.2/manual.html\#pdf-debug.setuservalue \\
Object & public & object & \{ get; private set; \} & Gets the object associated to this userdata (null for statics) \\
Descriptor & public & IUser\-Data\-Descriptor & \{ get; private set; \} & Gets the type descriptor of this userdata \\
Registration\-Policy & public static & IRegistration\-Policy & \{ get set \} & Gets or sets the registration policy to be used in the whole application \\
Default\-Access\-Mode & public static & Interop\-Access\-Mode & \{ get set \} & Gets or sets the default access mode to be used in the whole application \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Register\-Type & public static & IUser\-Data\-Descriptor & (Interop\-Access\-Mode access\-Mode = Interop\-Access\-Mode.Default, string friendly\-Name = null) & Registers a type for userdata interop \\
Register\-Type & public static & IUser\-Data\-Descriptor & (Type type, Interop\-Access\-Mode access\-Mode = Interop\-Access\-Mode.Default, string friendly\-Name = null) & Registers a type for userdata interop \\
Register\-Proxy\-Type & public static & IUser\-Data\-Descriptor & (IProxy\-Factory proxy\-Factory, Interop\-Access\-Mode access\-Mode = Interop\-Access\-Mode.Default, string friendly\-Name = null) & Registers a proxy type. \\
Register\-Proxy\-Type & public static & IUser\-Data\-Descriptor & (Func{\tt <}\-TTarget, TProxy\-{\tt >} wrap\-Delegate, Interop\-Access\-Mode access\-Mode = Interop\-Access\-Mode.Default, string friendly\-Name = null) & Registers a proxy type using a delegate. \\
Register\-Type & public static & IUser\-Data\-Descriptor & (IUser\-Data\-Descriptor custom\-Descriptor) & Registers a type with a custom userdata descriptor \\
Register\-Type & public static & IUser\-Data\-Descriptor & (Type type, IUser\-Data\-Descriptor custom\-Descriptor) & Registers a type with a custom userdata descriptor \\
Register\-Type & public static & IUser\-Data\-Descriptor & (IUser\-Data\-Descriptor custom\-Descriptor) & Registers a type with a custom userdata descriptor \\
Register\-Assembly & public static & void & (Assembly asm = null, bool include\-Extension\-Types = false) & Registers all types marked with a Moon\-Sharp\-User\-Data\-Attribute that ar contained in an assembly. \\
Is\-Type\-Registered & public static & bool & (Type t) & Determines whether the specified type is registered. Note that this should be used only to check if a descriptor
		 has been registered EXACTLY. For many types a descriptor can still be created, for example through the descriptor
		 of a base type or implemented interfaces. \\
Is\-Type\-Registered & public static & bool & () & Determines whether the specified type is registered. Note that this should be used only to check if a descriptor
		 has been registered EXACTLY. For many types a descriptor can still be created, for example through the descriptor
		 of a base type or implemented interfaces. \\
Unregister\-Type & public static & void & () & Unregisters a type. 
		 WARNING: unregistering types at runtime is a dangerous practice and may cause unwanted errors.
		 Use this only for testing purposes or to re-register the same type in a slightly different way.
		 Additionally, it's a good practice to discard all previous loaded scripts after calling this method. \\
Unregister\-Type & public static & void & (Type t) & Unregisters a type.
		 WARNING: unregistering types at runtime is a dangerous practice and may cause unwanted errors.
		 Use this only for testing purposes or to re-register the same type in a slightly different way.
		 Additionally, it's a good practice to discard all previous loaded scripts after calling this method. \\
Create & public static & Dyn\-Value & (object o, IUser\-Data\-Descriptor descr) & Creates a userdata Dyn\-Value from the specified object, using a specific descriptor \\
Create & public static & Dyn\-Value & (object o) & Creates a userdata Dyn\-Value from the specified object \\
Create\-Static & public static & Dyn\-Value & (IUser\-Data\-Descriptor descr) & Creates a static userdata Dyn\-Value from the specified IUser\-Data\-Descriptor \\
Create\-Static & public static & Dyn\-Value & (Type t) & Creates a static userdata Dyn\-Value from the specified Type \\
Create\-Static & public static & Dyn\-Value & () & Creates a static userdata Dyn\-Value from the specified Type \\
Register\-Extension\-Type & public static & void & (Type type, Interop\-Access\-Mode mode = Interop\-Access\-Mode.Default) & Registers an extension Type (that is a type containing extension methods) \\
Get\-Extension\-Methods\-By\-Name\-And\-Type & public static & List{\tt <}\-IOverloadable\-Member\-Descriptor\-{\tt >} & (string name, Type extended\-Type) & Gets all the extension methods which can match a given name and extending a given Type \\
Get\-Extension\-Methods\-Change\-Version & public static & int & () & Gets a number which gets incremented everytime the extension methods registry changes.
		 Use this to invalidate caches based on extension methods \\
Get\-Descriptor\-For\-Type & public static & IUser\-Data\-Descriptor & (bool search\-Interfaces) & Gets the best possible type descriptor for a specified CLR type. \\
Get\-Descriptor\-For\-Type & public static & IUser\-Data\-Descriptor & (Type type, bool search\-Interfaces) & Gets the best possible type descriptor for a specified CLR type. \\
Get\-Descriptor\-For\-Object & public static & IUser\-Data\-Descriptor & (object o) & Gets the best possible type descriptor for a specified CLR object. \\
Get\-Description\-Of\-Registered\-Types & public static & Table & (bool use\-Historical\-Data = false) & Gets a table with the description of registered types. \\
Get\-Registered\-Types & public static & IEnumerable{\tt <}\-Type\-{\tt >} & (bool use\-Historical\-Data = false) & Gets all the registered types. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WellKnownSymbols}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
VARARGS & public const & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The variadic argument symbol ("...")} \\ \tabuphantomline
ENV & public const & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The environment symbol ("\_ENV")} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{YieldRequest}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Return\-Values & public & Dyn\-Value[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The return values of the coroutine} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Forced & public & bool & \{ get; internal set; \} & Gets or sets a value indicating whether this  is a forced yield. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DebuggerAction}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Action & public & Action\-Type & \{ get; set; \} & The type of action \\
Time\-Stamp\-UTC & public & Date\-Time & \{ get; private set; \} & Gets the time stamp UTC of this action \\
Source\-ID & public & int & \{ get; set; \} & Gets or sets the source identifier this action refers to. \\
Source\-Line & public & int & \{ get; set; \} & Gets or sets the source line this action refers to. \\
Source\-Col & public & int & \{ get; set; \} & Gets or sets the source column this action refers to. \\
Lines & public & int[] & \{ get; set; \} & Gets or sets the lines. This is used for the Reset\-Breakpoints and sets line-based bps only. \\
Age & public & Time\-Span & \{ get \} & Gets the age of this debugger action \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Debugger\-Action & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
To\-String & public override & string & () & Returns a  that represents this instance. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DebugService}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Owner\-Script & public & Script & \{ get; private set; \} & Gets the script owning this resource. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Reset\-Break\-Points & public & Hash\-Set{\tt <}\-int\-{\tt >} & (Source\-Code src, Hash\-Set{\tt <}\-int\-{\tt >} lines) & Resets the break points for a given file. Supports only line-based breakpoints. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SourceCode}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; private set; \} & Gets the name of the source code \\
Code & public & string & \{ get; private set; \} & Gets the source code as a string \\
Lines & public & string[] & \{ get; private set; \} & Gets the source code lines. \\
Owner\-Script & public & Script & \{ get; private set; \} & Gets the script owning this resource. \\
Source\-ID & public & int & \{ get; private set; \} & Gets the source identifier inside a script \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Code\-Snippet & public & string & (Source\-Ref source\-Code\-Ref) & Gets the code snippet represented by a source ref \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SourceRef}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Breakpoint & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Gets a value indicating whether this instance is a breakpoint} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Is\-Clr\-Location & public & bool & \{ get; private set; \} & Gets a value indicating whether this location is inside CLR . \\
Source\-Idx & public & int & \{ get; private set; \} & Gets the index of the source. \\
From\-Char & public & int & \{ get; private set; \} & Gets from which column the source code ref starts \\
To\-Char & public & int & \{ get; private set; \} & Gets to which column the source code ref ends \\
From\-Line & public & int & \{ get; private set; \} & Gets from which line the source code ref starts \\
To\-Line & public & int & \{ get; private set; \} & Gets to which line the source code ref ends \\
Is\-Step\-Stop & public & bool & \{ get; private set; \} & Gets a value indicating whether this instance is a stop "step" in source mode \\
Cannot\-Breakpoint & public & bool & \{ get; private set; \} & Gets a value indicating whether this instance cannot be set as a breakpoint \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
To\-String & public override & string & () & Returns a  that represents this instance. \\
Includes\-Location & public & bool & (int source\-Idx, int line, int col) & Gets whether the source ref includes the specified location \\
Set\-No\-Break\-Point & public & Source\-Ref & () & Sets the Cannot\-Breakpoint flag. \\
Format\-Location & public & string & (Script script, bool force\-Classic\-Format = false) & Formats the location according to script preferences \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WatchItem}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Address & public & int & \{ get; set; \} & Gets or sets the address of the item \\
Base\-Ptr & public & int & \{ get; set; \} & Gets or sets the base pointer (base value of v-stack at entering the function).
		 Valid only for call-stack items \\
Ret\-Address & public & int & \{ get; set; \} & Gets or sets the return address.
		 Valid only for call-stack items \\
Name & public & string & \{ get; set; \} & Gets or sets the name of the item \\
Value & public & Dyn\-Value & \{ get; set; \} & Gets or sets the value of the item \\
LValue & public & Symbol\-Ref & \{ get; set; \} & Gets or sets the symbol reference of the item \\
Is\-Error & public & bool & \{ get; set; \} & Gets or sets a value indicating whether this instance is generating an error. \\
Location & public & Source\-Ref & \{ get; set; \} & Gets or sets the source location this item refers to. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
To\-String & public override & string & () & Returns a  that represents this instance. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PerformanceResult}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; internal set; \} & Gets the name of the performance counter which generated this result. \\
Counter & public & long & \{ get; internal set; \} & Gets the quantity monitored - see Type to understand what this field contains \\
Instances & public & int & \{ get; internal set; \} & Gets the number of instances which led to the specified counter being incremented - e.g. the times a specific
		 code is executed, or object instanced \\
Global & public & bool & \{ get; internal set; \} & Gets a value indicating whether this  is global or relative to the resource
		 for which it's called. \\
Type & public & Performance\-Counter\-Type & \{ get; internal set; \} & Gets the unit of measure of the Counter field. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
To\-String & public override & string & () & Returns a  that represents this instance. \\
Performance\-Counter\-Type\-To\-String & public static & string & (Performance\-Counter\-Type Type) & Converts a Performance\-Counter\-Type to a string. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PerformanceStatistics}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Enabled & public & bool & \{ get set else if (!value \&\& m\_Enabled) \{ m\_Stopwatches = new IPerformance\-Stopwatch[(int)Performance\-Counter.Last\-Value]; m\_Global\-Stopwatches = new IPerformance\-Stopwatch[(int)Performance\-Counter.Last\-Value]; \} m\_Enabled = value; \} \} & Gets or sets a value indicating whether this collection of performance stats is enabled. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Performance\-Counter\-Result & public & Performance\-Result & (Performance\-Counter pc) & Gets the result of the specified performance counter . \\
Start\-Stopwatch & internal & IDisposable & (Performance\-Counter pc) & Starts a stopwatch. \\
Start\-Global\-Stopwatch & internal static & IDisposable & (Performance\-Counter pc) & Starts a stopwatch. \\
Get\-Performance\-Log & public & string & () & Gets a string with a complete performance log. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DynamicExpressionException}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Dynamic\-Expression\-Exception & public & (string format, params object[] args) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Dynamic\-Expression\-Exception & public & (string message) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{InterpreterException}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Instruction\-Ptr & public & int & \{ get; internal set; \} & Gets the instruction pointer of the execution (if it makes sense) \\
Call\-Stack & public & IList{\tt <}\-Moon\-Sharp.Interpreter.Debugging.Watch\-Item\-{\tt >} & \{ get; internal set; \} & Gets the interpreter call stack. \\
Decorated\-Message & public & string & \{ get; internal set; \} & Gets the decorated message (error message plus error location in script) if possible. \\
Do\-Not\-Decorate\-Message & public & bool & \{ get; set; \} & Gets or sets a value indicating whether the message should not be decorated \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Interpreter\-Exception & protected & (Exception ex, string message) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Interpreter\-Exception & protected & (Exception ex) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Interpreter\-Exception & protected & (string message) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Interpreter\-Exception & protected & (string format, params object[] args) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Rethrow & public virtual & void & () & Rethrows this instance if \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ScriptRuntimeException}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Script\-Runtime\-Exception & public & (Exception ex) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Script\-Runtime\-Exception & public & (Script\-Runtime\-Exception ex) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Script\-Runtime\-Exception & public & (string message) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Script\-Runtime\-Exception & public & (string format, params object[] args) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Arithmetic\-On\-Non\-Number & public static & Script\-Runtime\-Exception & (Dyn\-Value l, Dyn\-Value r = null) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 an arithmetic operation was attempted on non-numbers \\
Concat\-On\-Non\-String & public static & Script\-Runtime\-Exception & (Dyn\-Value l, Dyn\-Value r) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a concat operation was attempted on non-strings \\
Len\-On\-Invalid\-Type & public static & Script\-Runtime\-Exception & (Dyn\-Value r) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a len operator was applied on an invalid operand \\
Compare\-Invalid\-Type & public static & Script\-Runtime\-Exception & (Dyn\-Value l, Dyn\-Value r) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a comparison operator was applied on an invalid combination of operand types \\
Bad\-Argument & public static & Script\-Runtime\-Exception & (int arg\-Num, string func\-Name, string message) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a function was called with a bad argument \\
Bad\-Argument\-User\-Data & public static & Script\-Runtime\-Exception & (int arg\-Num, string func\-Name, Type expected, object got, bool allow\-Nil) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a function was called with a bad userdata argument \\
Bad\-Argument & public static & Script\-Runtime\-Exception & (int arg\-Num, string func\-Name, Data\-Type expected, Data\-Type got, bool allow\-Nil) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a function was called with a bad argument \\
Bad\-Argument & public static & Script\-Runtime\-Exception & (int arg\-Num, string func\-Name, string expected, string got, bool allow\-Nil) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a function was called with a bad argument \\
Bad\-Argument\-No\-Value & public static & Script\-Runtime\-Exception & (int arg\-Num, string func\-Name, Data\-Type expected) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a function was called with no value when a value was required.
		 
		 This function creates a message like "bad argument \#xxx to 'yyy' (zzz expected, got no value)"
		 while  creates a message like "bad argument \#xxx to 'yyy' (value expected)" \\
Bad\-Argument\-Index\-Out\-Of\-Range & public static & Script\-Runtime\-Exception & (string func\-Name, int arg\-Num) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 an out of range index was specified \\
Bad\-Argument\-No\-Negative\-Numbers & public static & Script\-Runtime\-Exception & (int arg\-Num, string func\-Name) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a function was called with a negative number when a positive one was expected. \\
Bad\-Argument\-Value\-Expected & public static & Script\-Runtime\-Exception & (int arg\-Num, string func\-Name) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a function was called with no value when a value was required.
		 This function creates a message like "bad argument \#xxx to 'yyy' (value expected)"
		 while  creates a message like "bad argument \#xxx to 'yyy' (zzz expected, got no value)" \\
Index\-Type & public static & Script\-Runtime\-Exception & (Dyn\-Value obj) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 an invalid attempt to index the specified object was made \\
Loop\-In\-Index & public static & Script\-Runtime\-Exception & () & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a loop was detected when performing \_\_index over metatables. \\
Loop\-In\-New\-Index & public static & Script\-Runtime\-Exception & () & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a loop was detected when performing \_\_newindex over metatables. \\
Loop\-In\-Call & public static & Script\-Runtime\-Exception & () & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a loop was detected when performing \_\_call over metatables. \\
Table\-Index\-Is\-Nil & public static & Script\-Runtime\-Exception & () & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a table indexing operation used nil as the key. \\
Table\-Index\-Is\-Na\-N & public static & Script\-Runtime\-Exception & () & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a table indexing operation used a Na\-N as the key. \\
Convert\-To\-Number\-Failed & public static & Script\-Runtime\-Exception & (int stage) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a conversion to number failed. \\
Convert\-Object\-Failed & public static & Script\-Runtime\-Exception & (object obj) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a conversion of a CLR type to a Lua type has failed. \\
Convert\-Object\-Failed & public static & Script\-Runtime\-Exception & (Data\-Type t) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a conversion of a Lua type to a CLR type has failed. \\
Convert\-Object\-Failed & public static & Script\-Runtime\-Exception & (Data\-Type t, Type t2) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a constrained conversion of a Lua type to a CLR type has failed. \\
User\-Data\-Argument\-Type\-Mismatch & public static & Script\-Runtime\-Exception & (Data\-Type t, Type clr\-Type) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 a userdata of a specific CLR type was expected and a non-userdata type was passed. \\
User\-Data\-Missing\-Field & public static & Script\-Runtime\-Exception & (string typename, string fieldname) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 an attempt to index an invalid member of a userdata was done. \\
Cannot\-Resume\-Not\-Suspended & public static & Script\-Runtime\-Exception & (Coroutine\-State state) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 an attempt resume a coroutine in an invalid state was done. \\
Cannot\-Yield & public static & Script\-Runtime\-Exception & () & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 an attempt to yield across a CLR boundary was made. \\
Cannot\-Yield\-Main & public static & Script\-Runtime\-Exception & () & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 an attempt to yield from the main coroutine was made. \\
Attempt\-To\-Call\-Non\-Func & public static & Script\-Runtime\-Exception & (Data\-Type type, string debug\-Text = null) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 an attempt to call a non-function was made \\
Access\-Instance\-Member\-On\-Statics & public static & Script\-Runtime\-Exception & (IMember\-Descriptor desc) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 an attempt to access a non-static member from a static userdata was made \\
Access\-Instance\-Member\-On\-Statics & public static & Script\-Runtime\-Exception & (IUser\-Data\-Descriptor type\-Descr, IMember\-Descriptor desc) & Creates a Script\-Runtime\-Exception with a predefined error message specifying that
		 an attempt to access a non-static member from a static userdata was made \\
Rethrow & public override & void & () & Rethrows this instance if \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SyntaxErrorException}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Is\-Premature\-Stream\-Termination & public & bool & \{ get; set; \} & Gets or sets a value indicating whether this exception was caused by premature stream termination (that is, unexpected EOF).
		 This can be used in REPL interfaces to tell between unrecoverable errors and those which can be recovered by extra input. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Rethrow & public override & void & () & Rethrows this instance if \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DynamicExpression}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Expression\-Code & public readonly & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The code which generated this expression} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Owner\-Script & public & Script & \{ get; private set; \} & Gets the script owning this resource. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Evaluate & public & Dyn\-Value & (Script\-Execution\-Context context = null) & Evaluates the expression \\
Find\-Symbol & public & Symbol\-Ref & (Script\-Execution\-Context context) & Finds a symbol in the expression \\
Is\-Constant & public & bool & () & Determines whether this instance is a constant expression \\
Get\-Hash\-Code & public override & int & () & Returns a hash code for this instance. \\
Equals & public override & bool & (object obj) & Determines whether the specified , is equal to this instance. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ScriptExecutionContext}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Is\-Dynamic\-Execution & public & bool & \{ get; private set; \} & Gets a value indicating whether this instance is running a dynamic execution.
		 Under a dynamic execution, most methods of Script\-Execution\-Context are not reliable as the
		 processing engine of the script is not "really" running or is not available. \\
Calling\-Location & public & Source\-Ref & \{ get; private set; \} & Gets the location of the code calling back \\
Additional\-Data & public & object & \{ get set \} & Gets or sets the additional data associated to this CLR function call. \\
Current\-Global\-Env & public & Table & \{ get \} & Gets the current global env, or null if not found. \\
Owner\-Script & public & Script & \{ get \} & Gets the script owning this resource. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Metatable & public & Table & (Dyn\-Value value) & Gets the metatable associated with the given value. \\
Get\-Metamethod & public & Dyn\-Value & (Dyn\-Value value, string metamethod) & Gets the specified metamethod associated with the given value. \\
Get\-Metamethod\-Tail\-Call & public & Dyn\-Value & (Dyn\-Value value, string metamethod, params Dyn\-Value[] args) & prepares a tail call request for the specified metamethod, or null if no metamethod is found. \\
Get\-Binary\-Metamethod & public & Dyn\-Value & (Dyn\-Value op1, Dyn\-Value op2, string event\-Name) & Gets the metamethod to be used for a binary operation using op1 and op2. \\
Get\-Script & public & Script & () & Gets the script object associated with this request \\
Get\-Calling\-Coroutine & public & Coroutine & () & Gets the coroutine which is performing the call \\
Emulate\-Classic\-Call & public & Dyn\-Value & (Callback\-Arguments args, string function\-Name, Func{\tt <}\-Lua\-State, int\-{\tt >} callback) & Calls a callback function implemented in "classic way". 
		 Useful to port C code from Lua, or C\# code from Uni\-Lua and Kopi\-Lua.
		 Lua : http://www.lua.org/
		 Uni\-Lua : http://github.com/xebecnan/Uni\-Lua
		 Kopi\-Lua : http://github.com/NLua/Kopi\-Lua \\
Call & public & Dyn\-Value & (Dyn\-Value func, params Dyn\-Value[] args) & Calls the specified function, supporting most cases. The called function must not yield. \\
Evaluate\-Symbol & public & Dyn\-Value & (Symbol\-Ref symref) & Tries to get the reference of a symbol in the current execution state \\
Evaluate\-Symbol\-By\-Name & public & Dyn\-Value & (string symbol) & Tries to get the value of a symbol in the current execution state \\
Find\-Symbol\-By\-Name & public & Symbol\-Ref & (string symbol) & Finds a symbol by name in the current execution state \\
Perform\-Message\-Decoration\-Before\-Unwind & public & void & (Dyn\-Value message\-Handler, Script\-Runtime\-Exception exception) & Performs a message decoration before unwinding after an error. To be used in the implementation of xpcall like functions. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CustomConvertersCollection}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Set\-Script\-To\-Clr\-Custom\-Conversion & public & void & (Data\-Type script\-Data\-Type, Type clr\-Data\-Type, Func{\tt <}\-Dyn\-Value, object\-{\tt >} converter = null) & Sets a custom converter from a script data type to a CLR data type. Set null to remove a previous custom converter. \\
Get\-Script\-To\-Clr\-Custom\-Conversion & public & Func{\tt <}\-Dyn\-Value, object\-{\tt >} & (Data\-Type script\-Data\-Type, Type clr\-Data\-Type) & Gets a custom converter from a script data type to a CLR data type, or null \\
Set\-Clr\-To\-Script\-Custom\-Conversion & public & void & (Type clr\-Data\-Type, Func{\tt <}\-Script, object, Dyn\-Value\-{\tt >} converter = null) & Sets a custom converter from a CLR data type. Set null to remove a previous custom converter. \\
Set\-Clr\-To\-Script\-Custom\-Conversion & public & void & (Func{\tt <}\-Script, T, Dyn\-Value\-{\tt >} converter = null) & Sets a custom converter from a CLR data type. Set null to remove a previous custom converter. \\
Get\-Clr\-To\-Script\-Custom\-Conversion & public & Func{\tt <}\-Script, object, Dyn\-Value\-{\tt >} & (Type clr\-Data\-Type) & Gets a custom converter from a CLR data type, or null \\
Set\-Clr\-To\-Script\-Custom\-Conversion & public & void & (Type clr\-Data\-Type, Func{\tt <}\-object, Dyn\-Value\-{\tt >} converter = null) &  \\
Set\-Clr\-To\-Script\-Custom\-Conversion & public & void & (Func{\tt <}\-T, Dyn\-Value\-{\tt >} converter = null) & Sets a custom converter from a CLR data type. Set null to remove a previous custom converter. \\
Clear & public & void & () & Removes all converters. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DescriptorHelpers}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Visibility\-From\-Attributes & public static & bool? & (this Member\-Info mi) & Determines whether a
		  or a   is changing visibility of a member
		 to scripts. \\
Get\-Clr\-Visibility & public static & string & (this Type type) & Gets the visibility of the type as a string \\
Get\-Clr\-Visibility & public static & string & (this Field\-Info info) & Gets a string representing visibility of the given member type \\
Get\-Clr\-Visibility & public static & string & (this Property\-Info info) & Gets a string representing visibility of the given member type \\
Get\-Clr\-Visibility & public static & string & (this Method\-Base info) & Gets a string representing visibility of the given member type \\
Is\-Property\-Info\-Public & public static & bool & (this Property\-Info pi) & Determines whether the specified Property\-Info is visible publicly (either the getter or the setter is public). \\
Get\-Meta\-Names\-From\-Attributes & public static & List{\tt <}\-string\-{\tt >} & (this Method\-Info mi) & Gets the list of metamethod names from attributes - in practice the list of metamethods declared through
		  . \\
Safe\-Get\-Types & public static & Type[] & (this Assembly asm) & Gets the Types implemented in the assembly, catching the Reflection\-Type\-Load\-Exception just in case.. \\
Get\-Conversion\-Method\-Name & public static & string & (this Type type) & Gets the name of a conversion method to be exposed to Lua scripts \\
Get\-All\-Implemented\-Types & public static & IEnumerable{\tt <}\-Type\-{\tt >} & (this Type t) & Gets all implemented types by a given type \\
Is\-Valid\-Simple\-Identifier & public static & bool & (string str) & Determines whether the string is a valid simple identifier (starts with letter or underscore
		 and contains only letters, digits and underscores). \\
To\-Valid\-Simple\-Identifier & public static & string & (string str) & Converts the string to a valid simple identifier (starts with letter or underscore
		 and contains only letters, digits and underscores). \\
Camelify & public static & string & (string name) & Converts the specified name from underscore\_case to camel\-Case. \\
Upper\-First\-Letter & public static & string & (string name) & Converts the specified name to one with an uppercase first letter (something to Something). \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{InteropRegistrationPolicy}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Default & public static & IRegistration\-Policy & \{ get\} & The default registration policy used by Moon\-Sharp unless explicitely replaced.
		 Deregistrations are allowed, but registration of a new descriptor are not allowed
		 if a descriptor is already registered for that type.
		 
		 Types must be explicitly registered. \\
Explicit & public static & IRegistration\-Policy & \{ get \} & The default registration policy used by Moon\-Sharp unless explicitely replaced.
		 Deregistrations are allowed, but registration of a new descriptor are not allowed
		 if a descriptor is already registered for that type.
		 
		 Types must be explicitly registered. \\
Automatic & public static & IRegistration\-Policy & \{ get \} & Types are automatically registered if not found in the registry. This is easier to use but potentially unsafe. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PropertyTableAssigner}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Property\-Table\-Assigner & public & (params string[] expected\-Missing\-Properties) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Property\-Table\-Assigner & public & (Type type, params string[] expected\-Missing\-Properties) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add\-Expected\-Missing\-Property & public & void & (string name) & Adds an expected missing property, that is an expected field in the table with no corresponding property in the object. \\
Assign\-Object & public & void & (T obj, Table data) & Assigns properties from tables to an object. \\
Get\-Type\-Unsafe\-Assigner & public & Property\-Table\-Assigner & () & Gets the type-unsafe assigner corresponding to this object. \\
Set\-Subassigner\-For\-Type & public & void & (Type property\-Type, IProperty\-Table\-Assigner assigner) & Sets the subassigner for the given type. Pass null to remove usage of subassigner for the given type. \\
Set\-Subassigner & public & void & (Property\-Table\-Assigner{\tt <}\-Subassigner\-Type\-{\tt >} assigner) & Sets the subassigner for the given type \\
Assign\-Object\-Unchecked &  & void & (object o, Table data) & Assigns the properties of the specified object without checking the type. \\
Add\-Expected\-Missing\-Property & public & void & (string name) & Adds an expected missing property, that is an expected field in the table with no corresponding property in the object. \\
Assign\-Object & public & void & (object obj, Table data) & Assigns properties from tables to an object. \\
Set\-Subassigner\-For\-Type & public & void & (Type property\-Type, IProperty\-Table\-Assigner assigner) & Sets the subassigner for the given type. Pass null to remove usage of subassigner for the given type. \\
Assign\-Object\-Unchecked &  & void & (object obj, Table data) & Assigns the properties of the specified object without checking the type. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{EmbeddedResourcesScriptLoader}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Embedded\-Resources\-Script\-Loader & public & (Assembly resource\-Assembly = null) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Script\-File\-Exists & public override & bool & (string name) & Checks if a script file exists. \\
Load\-File & public override & object & (string file, Table global\-Context) & Opens a file for reading the script code.
		 It can return either a string, a byte[] or a Stream.
		 If a byte[] is returned, the content is assumed to be a serialized (dumped) bytecode. If it's a string, it's
		 assumed to be either a script or the output of a string.dump call. If a Stream, autodetection takes place. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{FileSystemScriptLoader}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Script\-File\-Exists & public override & bool & (string name) & Checks if a script file exists. \\
Load\-File & public override & object & (string file, Table global\-Context) & Opens a file for reading the script code.
		 It can return either a string, a byte[] or a Stream.
		 If a byte[] is returned, the content is assumed to be a serialized (dumped) bytecode. If it's a string, it's
		 assumed to be either a script or the output of a string.dump call. If a Stream, autodetection takes place. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ScriptLoaderBase}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Module\-Paths & public & string[] & \{ get; set; \} & Gets or sets the modules paths used by the "require" function. If null, the default paths are used (using
		 environment variables etc.). \\
Ignore\-Lua\-Path\-Global & public & bool & \{ get; set; \} & Gets or sets a value indicating whether the LUA\_PATH global is checked or not to get the path where modules are contained.
		 If true, the LUA\_PATH global is NOT checked. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Script\-File\-Exists & public abstract & bool & (string name) & Checks if a script file exists. \\
Load\-File & public abstract & object & (string file, Table global\-Context) & Opens a file for reading the script code.
		 It can return either a string, a byte[] or a Stream.
		 If a byte[] is returned, the content is assumed to be a serialized (dumped) bytecode. If it's a string, it's
		 assumed to be either a script or the output of a string.dump call. If a Stream, autodetection takes place. \\
Resolve\-Module\-Name & protected virtual & string & (string modname, string[] paths) & Resolves the name of a module on a set of paths. \\
Resolve\-Module\-Name & public virtual & string & (string modname, Table global\-Context) & Resolves the name of a module to a filename (which will later be passed to Open\-Script\-File).
		 The resolution happens first on paths included in the LUA\_PATH global variable (if and only if
		 the Ignore\-Lua\-Path\-Global is false), and - if the variable does not exist - by consulting the
		 Script\-Options.Modules\-Paths array. Override to provide a different behaviour. \\
Unpack\-String\-Paths & public static & string[] & (string str) & Unpacks a string path in a form like "?;?.lua" to an array \\
Get\-Default\-Environment\-Paths & public static & string[] & () & Gets the default environment paths. \\
Resolve\-File\-Name & public virtual & string & (string filename, Table global\-Context) & Resolves a filename [applying paths, etc.] \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{StreamingAssetsScriptLoader}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Script\-File\-Exists & public override & bool & (string name) & Checks if a script file exists. \\
Load\-File & public override & object & (string path, Table global\-Context) & Opens a file for reading the script code.
		 It can return either a string, a byte[] or a Stream.
		 If a byte[] is returned, the content is assumed to be a serialized (dumped) bytecode. If it's a string, it's
		 assumed to be either a script or the output of a string.dump call. If a Stream, autodetection takes place. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{UnityAssetsScriptLoader}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
DEFAULT\_PATH & public const & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The default path where scripts are meant to be stored (if not changed)} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Unity\-Assets\-Script\-Loader & public & (string assets\-Path = null) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Unity\-Assets\-Script\-Loader & public & (Dictionary{\tt <}\-string, string\-{\tt >} script\-To\-Code\-Map) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Load\-File & public override & object & (string file, Table global\-Context) & Opens a file for reading the script code.
		 It can return either a string, a byte[] or a Stream.
		 If a byte[] is returned, the content is assumed to be a serialized (dumped) bytecode. If it's a string, it's
		 assumed to be either a script or the output of a string.dump call. If a Stream, autodetection takes place. \\
Script\-File\-Exists & public override & bool & (string file) & Checks if a given file exists \\
Get\-Loaded\-Scripts & public & string[] & () & Gets the list of loaded scripts filenames (useful for debugging purposes). \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ModuleRegister}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Register\-Core\-Modules & public static & Table & (this Table table, Core\-Modules modules) & Register the core modules to a table \\
Register\-Constants & public static & Table & (this Table table) & Registers the standard constants (\_G, \_VERSION, \_MOONSHARP) to a table \\
Register\-Module\-Type & public static & Table & (this Table gtable, Type t) & Registers a module type to the specified table \\
Register\-Module\-Type & public static & Table & (this Table table) & Registers a module type to the specified table \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoonSharpModuleAttribute}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Namespace & public & string & \{ get; set; \} & Gets or sets the namespace, that is the name of the table which will contain the defined functions.
		 Can be null to be in the global table. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoonSharpModuleConstantAttribute}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; set; \} & Gets or sets the name of the constant - if different from the name of the field itself \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoonSharpModuleMethodAttribute}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; set; \} & Gets or sets the name of the function in the module (defaults to member name) \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{LimitedPlatformAccessor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Environment\-Variable & public override & string & (string envvarname) & Gets an environment variable. Must be implemented, but an implementation is allowed
		 to always return null if a more meaningful implementation cannot be achieved or is
		 not desired. \\
Filter\-Supported\-Core\-Modules & public override & Core\-Modules & (Core\-Modules module) & Filters the Core\-Modules enumeration to exclude non-supported operations \\
IO\_Open\-File & public override & System.IO.Stream & (Script script, string filename, Encoding encoding, string mode) & A function used to open files in the 'io' module. 
		 Limited\-Platform\-Accessor\-Base does NOT offer a meaningful implementation of this method and
		 thus does not support 'io' and 'os' modules. \\
IO\_Get\-Standard\-Stream & public override & System.IO.Stream & (Standard\-File\-Type type) & Gets a standard stream (stdin, stdout, stderr).
		 Limited\-Platform\-Accessor\-Base does NOT offer a meaningful implementation of this method and
		 thus does not support 'io' and 'os' modules. \\
IO\_OS\_Get\-Temp\-Filename & public override & string & () & Gets a temporary filename. Used in 'io' and 'os' modules.
		 Limited\-Platform\-Accessor\-Base does NOT offer a meaningful implementation of this method and
		 thus does not support 'io' and 'os' modules. \\
OS\_Exit\-Fast & public override & void & (int exit\-Code) & Exits the process, returning the specified exit code.
		 Limited\-Platform\-Accessor\-Base does NOT offer a meaningful implementation of this method and
		 thus does not support 'io' and 'os' modules. \\
OS\_File\-Exists & public override & bool & (string file) & Checks if a file exists. Used by the 'os' module.
		 Limited\-Platform\-Accessor\-Base does NOT offer a meaningful implementation of this method and
		 thus does not support 'io' and 'os' modules. \\
OS\_File\-Delete & public override & void & (string file) & Deletes the specified file. Used by the 'os' module.
		 Limited\-Platform\-Accessor\-Base does NOT offer a meaningful implementation of this method and
		 thus does not support 'io' and 'os' modules. \\
OS\_File\-Move & public override & void & (string src, string dst) & Moves the specified file. Used by the 'os' module.
		 Limited\-Platform\-Accessor\-Base does NOT offer a meaningful implementation of this method and
		 thus does not support 'io' and 'os' modules. \\
OS\_Execute & public override & int & (string cmdline) & Executes the specified command line, returning the child process exit code and blocking in the meantime.
		 Limited\-Platform\-Accessor\-Base does NOT offer a meaningful implementation of this method and
		 thus does not support 'io' and 'os' modules. \\
Get\-Platform\-Name\-Prefix & public override & string & () & Gets the platform name prefix \\
Default\-Print & public override & void & (string content) & Default handler for 'print' calls. Can be customized in Script\-Options \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PlatformAccessorBase}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Platform\-Name\-Prefix & public abstract & string & () & Gets the platform name prefix \\
Get\-Platform\-Name & public & string & () & Gets the name of the platform (used for debug purposes). \\
Default\-Print & public abstract & void & (string content) & Default handler for 'print' calls. Can be customized in Script\-Options \\
Default\-Input & public virtual & string & () & DEPRECATED.
		 This is kept for backward compatibility, see the overload taking a prompt as an input parameter.
		 
		 Default handler for interactive line input calls. Can be customized in Script\-Options.
		 If an inheriting class whants to give a meaningful implementation, this method MUST be overridden. \\
Default\-Input & public virtual & string & (string prompt) & Default handler for interactive line input calls. Can be customized in Script\-Options.
		 If an inheriting class whants to give a meaningful implementation, this method MUST be overridden. \\
IO\_Open\-File & public abstract & Stream & (Script script, string filename, Encoding encoding, string mode) & A function used to open files in the 'io' module. 
		 Can have an invalid implementation if 'io' module is filtered out.
		 It should return a correctly initialized Stream for the given file and access \\
IO\_Get\-Standard\-Stream & public abstract & Stream & (Standard\-File\-Type type) & Gets a standard stream (stdin, stdout, stderr). \\
IO\_OS\_Get\-Temp\-Filename & public abstract & string & () & Gets a temporary filename. Used in 'io' and 'os' modules.
		 Can have an invalid implementation if 'io' and 'os' modules are filtered out. \\
OS\_Exit\-Fast & public abstract & void & (int exit\-Code) & Exits the process, returning the specified exit code.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_File\-Exists & public abstract & bool & (string file) & Checks if a file exists. Used by the 'os' module.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_File\-Delete & public abstract & void & (string file) & Deletes the specified file. Used by the 'os' module.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_File\-Move & public abstract & void & (string src, string dst) & Moves the specified file. Used by the 'os' module.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_Execute & public abstract & int & (string cmdline) & Executes the specified command line, returning the child process exit code and blocking in the meantime.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
Filter\-Supported\-Core\-Modules & public abstract & Core\-Modules & (Core\-Modules module) & Filters the Core\-Modules enumeration to exclude non-supported operations \\
Get\-Environment\-Variable & public abstract & string & (string envvarname) & Gets an environment variable. Must be implemented, but an implementation is allowed
		 to always return null if a more meaningful implementation cannot be achieved or is
		 not desired. \\
Is\-Running\-On\-AOT & public virtual & bool & () & Determines whether the application is running in AOT (ahead-of-time) mode \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PlatformAutoDetector}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Is\-Running\-On\-Mono & public static & bool & \{ get; private set; \} & Gets a value indicating whether this instance is running on mono. \\
Is\-Running\-On\-Clr4 & public static & bool & \{ get; private set; \} & Gets a value indicating whether this instance is running on a CLR4 compatible implementation \\
Is\-Running\-On\-Unity & public static & bool & \{ get; private set; \} & Gets a value indicating whether this instance is running on Unity-3D \\
Is\-Portable\-Framework & public static & bool & \{ get; private set; \} & Gets a value indicating whether this instance has been built as a Portable Class Library \\
Is\-Unity\-Native & public static & bool & \{ get; private set; \} & Gets a value indicating whether this instance has been compiled natively in Unity (as opposite to importing a DLL). \\
Is\-Unity\-IL2CPP & public static & bool & \{ get; private set; \} & Gets a value indicating whether this instance has been compiled natively in Unity AND is using IL2CPP \\
Is\-Running\-On\-AOT & public static & bool & \{ // We do a lazy eval here, so we can wire out this code by not calling it, if necessary.. get catch (Exception) \{ m\_Is\-Running\-On\-AOT = true; \} \} return m\_Is\-Running\-On\-AOT.Value; \#endif \} \} & Gets a value indicating whether this instance is running a system using Ahead-Of-Time compilation 
		 and not supporting JIT. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{StandardPlatformAccessor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Parse\-File\-Access & public static & File\-Access & (string mode) & Converts a Lua string access mode to a File\-Access enum \\
Parse\-File\-Mode & public static & File\-Mode & (string mode) & Converts a Lua string access mode to a Parse\-File\-Mode enum \\
IO\_Open\-File & public override & Stream & (Script script, string filename, Encoding encoding, string mode) & A function used to open files in the 'io' module. 
		 Can have an invalid implementation if 'io' module is filtered out.
		 It should return a correctly initialized Stream for the given file and access \\
Get\-Environment\-Variable & public override & string & (string envvarname) & Gets an environment variable. Must be implemented, but an implementation is allowed
		 to always return null if a more meaningful implementation cannot be achieved or is
		 not desired. \\
IO\_Get\-Standard\-Stream & public override & Stream & (Standard\-File\-Type type) & Gets a standard stream (stdin, stdout, stderr). \\
Default\-Print & public override & void & (string content) & Default handler for 'print' calls. Can be customized in Script\-Options \\
IO\_OS\_Get\-Temp\-Filename & public override & string & () & Gets a temporary filename. Used in 'io' and 'os' modules.
		 Can have an invalid implementation if 'io' and 'os' modules are filtered out. \\
OS\_Exit\-Fast & public override & void & (int exit\-Code) & Exits the process, returning the specified exit code.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_File\-Exists & public override & bool & (string file) & Checks if a file exists. Used by the 'os' module.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_File\-Delete & public override & void & (string file) & Deletes the specified file. Used by the 'os' module.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_File\-Move & public override & void & (string src, string dst) & Moves the specified file. Used by the 'os' module.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
OS\_Execute & public override & int & (string cmdline) & Executes the specified command line, returning the child process exit code and blocking in the meantime.
		 Can have an invalid implementation if the 'os' module is filtered out. \\
Filter\-Supported\-Core\-Modules & public override & Core\-Modules & (Core\-Modules module) & Filters the Core\-Modules enumeration to exclude non-supported operations \\
Get\-Platform\-Name\-Prefix & public override & string & () & Gets the platform name prefix \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ReplHistoryInterpreter}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Repl\-History\-Interpreter & public & (Script script, int history\-Size) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Evaluate & public override & Dyn\-Value & (string input) & Evaluate a REPL command.
		 This method returns the result of the computation, or null if more input is needed for having valid code.
		 In case of errors, exceptions are propagated to the caller. \\
History\-Prev & public & string & () & Gets the previous item in history, or null \\
History\-Next & public & string & () & Gets the next item in history, or null \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ReplInterpreter}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Handle\-Dynamic\-Exprs & public & bool & \{ get; set; \} & Gets or sets a value indicating whether this instances handle inputs starting with a "?" as a 
		 dynamic expression to evaluate instead of script code (likely invalid) \\
Handle\-Classic\-Exprs\-Syntax & public & bool & \{ get; set; \} & Gets or sets a value indicating whether this instances handle inputs starting with a "=" as a 
		 non-dynamic expression to evaluate (just like the Lua interpreter does by default). \\
Has\-Pending\-Command & public virtual & bool & \{ get \} & Gets a value indicating whether this instance has a pending command \\
Current\-Pending\-Command & public virtual & string & \{ get \} & Gets the current pending command. \\
Classic\-Prompt & public virtual & string & \{ get \} & Gets the classic prompt ("\-{\tt >}" or "\-{\tt >}\-{\tt >}") given the current state of the interpreter \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Repl\-Interpreter & public & (Script script) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Evaluate & public virtual & Dyn\-Value & (string input) & Evaluate a REPL command.
		 This method returns the result of the computation, or null if more input is needed for having valid code.
		 In case of errors, exceptions are propagated to the caller. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ReplInterpreterScriptLoader}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Repl\-Interpreter\-Script\-Loader & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Resolve\-Module\-Name & public override & string & (string modname, Table global\-Context) & Resolves the name of a module to a filename (which will later be passed to Open\-Script\-File).
		 The resolution happens first on paths included in the LUA\_PATH global variable, and -
		 if the variable does not exist - by consulting the
		 Script\-Options.Modules\-Paths array. Override to provide a different behaviour. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{AudioLoader}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Load\-Files & public & void & (List{\tt <}\-Audio\-Meta\-Data\-{\tt >} files) & Loads audio files. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DebugConsoleInputField}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
On\-Command\-Done & public & Action{\tt <}\-string\-{\tt >} & \{ get; set; \} & Invoked when a command entered into the input field has been parsed and run. \\
On\-BBInput\-Focus\-Stolen & public & Action & \{ get; set; \} & Invoked when Debug\-Console\-Input\-Field has loc BBInput.
         This is so that other classes can bypass the eaten keys if needed. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DebugConsoleSuggestionsPanel}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_input\-Field & private & Input\-Field & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The input field to listen to.} \\ \tabuphantomline
\_suggestions\-Panel\-Entry\-Prefab & private & Game\-Object & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The prefab to instantiate when we add a suggestion to the panel.} \\ \tabuphantomline
\_debug\-Console\-Input\-Field & private & Debug\-Console\-Input\-Field & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Load\-Bindings & private & void & () & Loads the Lua bindings from Bindings.generated.lua \\
Suggest & private & void & (string text) & Prints bindings that start with the text in the input field. \\
Clear & private & void & () & Removes all children. \\
Auto\-Complete & private & void & () & Completes the current word. \\
Disable & private & void & () & Disables the suggestion panel. \\
On\-Debug\-Console\-Input\-Field\-Command\-Done & private & void & (string command) & Called when the is done with a command. \\
Get\-Words & private & string[] & (string text) & Gets the last word in a string.
         Class is one word.
         Class.Method is one word.
         Namespace.Class.Method is one word.
         Class.Method(Class.Method) is two words. \\
Get\-Last\-Word & private & string & (string text) & Gets the last word in a string.
         Class is one word.
         Class.Method is one word.
         Namespace.Class.Method is one word.
         Class.Method(Class.Method) is two words. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{JsonMenuItem}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Create\-Json\-Script & public static & void & () & Creates a Json in the assets folder. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{LuaMenuItem}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Create\-Lua\-Script & public static & void & () & Creates a Lua Script in the assets folder. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TxtMenuItem}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Create\-Lua\-Script & public static & void & () & Creates a txt file in the assets folder. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TydMenuItem}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Create\-Tyd\-File & public static & void & () & Creates a .Ty\-D in the assets folder. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{XmlMenuItem}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Create\-Xml\-File & public static & void & () & Creates a Xml in the assets folder. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{LuaManager}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Active\-Lua\-Manager & public static & Lua\-Manager & \{ get; set; \} & The active Lua\-Manager is the lua manager that we use to execute scripts and build lua objects. \\
Load\-Update\-Each\-Frame & public static & bool & \{ get =\-{\tt >} Active\-Lua\-Manager.\_load\-Update\-Each\-Frame; set =\-{\tt >} Active\-Lua\-Manager.\_load\-Update\-Each\-Frame = value; \} /// {\tt <}\-summary\-{\tt >} /// Used so that stuff can be shared essentially. /// {\tt <}\-/summary\-{\tt >} protected Script \_global\-Script; protected  & Used so that stuff can be shared essentially. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Setup\-Lua\-Object & public static & void & (Lua\-Object\-Component lua\-Object) & Sets up a Lua\-Object\-Component. \\
Add\-On\-Value\-Set\-Listener & public static & void & (int id, string key, Action{\tt <}\-Dyn\-Value\-{\tt >} action) & Adds an action to be performed when a value is a associated with a given key for a
         Lua\-Object with a given id. \\
Add\-On\-Value\-Set\-Listener & public static & void & (int id, string key, Dyn\-Value action) & Adds an action to be performed when a value is a associated with a given key for a
         Lua\-Object with a given id. \\
Set & public static & void & (int id, string key, Dyn\-Value value) & Sets a table value in a Lua\-Object. \\
Get & public static & Dyn\-Value & (int id, string key) & Gets a table value in a Lua\-Object. \\
Get\-Lua\-Object\-Id & public static & Dyn\-Value & (int id) & Gets the Lua\-Object id of a Game\-Object. \\
Do\-String & public static & Dyn\-Value & (string code) & Loads and executes a string. \\
Call & public static & Dyn\-Value & (Dyn\-Value function) & Executes a function. \\
Call & public static & Dyn\-Value & (Dyn\-Value function, params Dyn\-Value[] args) & Executes a function. \\
Create\-Script & public virtual & Script & () & Creates a script set up with the globals we need. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{LuaObjectComponent}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get & public & Dyn\-Value & (string key) & Gets a value from the Actor's table. \\
Get\-Table\-Pairs & public & IEnumerable{\tt <}\-Table\-Pair\-{\tt >} & () & Returns every pair in the actor's table. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoonSharpAliasAttribute}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Aliases & public & string[] & \{ get; private set; \} & The aliases used for the class in Lua. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Moon\-Sharp\-Alias\-Attribute & public & (string alias) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Moon\-Sharp\-Alias\-Attribute & public & (string[] aliases) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{YeeterScriptLoader}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Script\-File\-Exists & public override & bool & (string name) & Checks if a script file exists. \\
Load\-File & public override & object & (string key, Table global\-Context) & Opens a file for reading the script code.
		 It can return either a string, a byte[] or a Stream.
		 If a byte[] is returned, the content is assumed to be a serialized (dumped) bytecode. If it's a string, it's
		 assumed to be either a script or the output of a string.dump call. If a Stream, autodetection takes place. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SliderSetting}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Set\-Key & public & void & (string setting\-Key) & Sets the settings key that the slider will read from/write to. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pb_AboutWindow}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Init & public static & bool & (bool from\-Menu) &  \\
Horizontal\-Line &  & void & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pb_VersionInfo}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
From\-String & public static & pb\_Version\-Info & (string str) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pb_VersionUtil}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-About\-Entry & public static & bool & (out pb\_About\-Entry about) &  \\
Format\-Changelog & public static & bool & (string raw, out pb\_Version\-Info version, out string formatted\_changes) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{HighlightNearestFace}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Face\-Center & private & Vector3 & (pb\_Object pb, pb\_Face face) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pg_AboutWindow}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
ABOUT\_ROOT & const & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
advertisements & public static & Advertisement\-Thumb[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
advertisements & public static & Advertisement\-Thumb[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Init & public static & bool & (string about\-Entry\-Path, bool from\-Menu) &  \\
Horizontal\-Line &  & void & () &  \\
Populate\-Data\-Fields &  & void & (string entry\-Path) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CustomControllersTiltDemo}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Input\-Update & private & void & () & This will be called each time input updates. Use this to push values into the Custom Controller axes. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{UIPointer}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
auto\-Sort & public & bool & \{ get set \} & Sets the pointer to the last sibling in the parent hierarchy. Do not enable this on multiple UIPointers under the same parent transform or they will constantly fight each other for dominance. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Screen\-Position\-Changed & public & void & (Vector2 screen\-Position) & Updates the pointer position. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CalibrationWindow}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
min\-Sensitivity & private & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{This value prevents the user from lowering the axis sensitivity so far that the axis is unusable.
         This is very important for the axes used for menu navigation, otherwise the user could permanently
         disable their ability to navigate the menu on a console with no mouse/keyboard.
         This value will be drawn from the Input\-Behavior(s) assigned to the menu horizontal and vertical axes} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CanvasScalerExt}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Force\-Refresh & public & void & () & Force a refresh on the canvas scaler. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{GamepadTemplate}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
type\-Guid & public static readonly & System.Guid & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The type Guid of the Controller Template.} \\ \tabuphantomline
element\-Id\_left\-Stick\-X & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Stick X".} \\ \tabuphantomline
element\-Id\_left\-Stick\-Y & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Stick Y".} \\ \tabuphantomline
element\-Id\_right\-Stick\-X & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Stick X".} \\ \tabuphantomline
element\-Id\_right\-Stick\-Y & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Stick Y".} \\ \tabuphantomline
element\-Id\_action\-Bottom\-Row1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Bottom Row 1".} \\ \tabuphantomline
element\-Id\_a & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Bottom Row 1".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_action\-Bottom\-Row2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Bottom Row 2".} \\ \tabuphantomline
element\-Id\_b & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Bottom Row 2".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_action\-Bottom\-Row3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Bottom Row 3".} \\ \tabuphantomline
element\-Id\_c & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Bottom Row 3".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_action\-Top\-Row1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Top Row 1".} \\ \tabuphantomline
element\-Id\_x & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Top Row 1".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_action\-Top\-Row2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Top Row 2".} \\ \tabuphantomline
element\-Id\_y & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Top Row 2".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_action\-Top\-Row3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Top Row 3".} \\ \tabuphantomline
element\-Id\_z & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Action Top Row 3".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_left\-Shoulder1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Shoulder 1".} \\ \tabuphantomline
element\-Id\_left\-Bumper & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Shoulder 1".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_left\-Shoulder2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Shoulder 2".} \\ \tabuphantomline
element\-Id\_left\-Trigger & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Shoulder 2".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_right\-Shoulder1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Shoulder 1".} \\ \tabuphantomline
element\-Id\_right\-Bumper & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Shoulder 1".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_right\-Shoulder2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Shoulder 2".} \\ \tabuphantomline
element\-Id\_right\-Trigger & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Shoulder 2".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_center1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center 1".} \\ \tabuphantomline
element\-Id\_back & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center 1".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_center2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center 2".} \\ \tabuphantomline
element\-Id\_start & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center 2".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_center3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center 3".} \\ \tabuphantomline
element\-Id\_guide & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center 3".
         This is an alias for .} \\ \tabuphantomline
element\-Id\_left\-Stick\-Button & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Stick Button".} \\ \tabuphantomline
element\-Id\_right\-Stick\-Button & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Stick Button".} \\ \tabuphantomline
element\-Id\_d\-Pad\-Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "D-Pad Up".} \\ \tabuphantomline
element\-Id\_d\-Pad\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "D-Pad Right".} \\ \tabuphantomline
element\-Id\_d\-Pad\-Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "D-Pad Down".} \\ \tabuphantomline
element\-Id\_d\-Pad\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "D-Pad Left".} \\ \tabuphantomline
element\-Id\_left\-Stick & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Stick".} \\ \tabuphantomline
element\-Id\_right\-Stick & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Stick".} \\ \tabuphantomline
element\-Id\_d\-Pad & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "D-Pad".} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
action\-Bottom\-Row1 &  & IController\-Template\-Button & \{ get \} & The "Action Bottom Row 1" element. \\
a &  & IController\-Template\-Button & \{ get \} & The "Action Bottom Row 1" element.
         This is an alias for . \\
action\-Bottom\-Row2 &  & IController\-Template\-Button & \{ get \} & The "Action Bottom Row 2" element. \\
b &  & IController\-Template\-Button & \{ get \} & The "Action Bottom Row 2" element.
         This is an alias for . \\
action\-Bottom\-Row3 &  & IController\-Template\-Button & \{ get \} & The "Action Bottom Row 3" element. \\
c &  & IController\-Template\-Button & \{ get \} & The "Action Bottom Row 3" element.
         This is an alias for . \\
action\-Top\-Row1 &  & IController\-Template\-Button & \{ get \} & The "Action Top Row 1" element. \\
x &  & IController\-Template\-Button & \{ get \} & The "Action Top Row 1" element.
         This is an alias for . \\
action\-Top\-Row2 &  & IController\-Template\-Button & \{ get \} & The "Action Top Row 2" element. \\
y &  & IController\-Template\-Button & \{ get \} & The "Action Top Row 2" element.
         This is an alias for . \\
action\-Top\-Row3 &  & IController\-Template\-Button & \{ get \} & The "Action Top Row 3" element. \\
z &  & IController\-Template\-Button & \{ get \} & The "Action Top Row 3" element.
         This is an alias for . \\
left\-Shoulder1 &  & IController\-Template\-Button & \{ get \} & The "Left Shoulder 1" element. \\
left\-Bumper &  & IController\-Template\-Button & \{ get \} & The "Left Shoulder 1" element.
         This is an alias for . \\
left\-Shoulder2 &  & IController\-Template\-Axis & \{ get \} & The "Left Shoulder 2" element. \\
left\-Trigger &  & IController\-Template\-Axis & \{ get \} & The "Left Shoulder 2" element.
         This is an alias for . \\
right\-Shoulder1 &  & IController\-Template\-Button & \{ get \} & The "Right Shoulder 1" element. \\
right\-Bumper &  & IController\-Template\-Button & \{ get \} & The "Right Shoulder 1" element.
         This is an alias for . \\
right\-Shoulder2 &  & IController\-Template\-Axis & \{ get \} & The "Right Shoulder 2" element. \\
right\-Trigger &  & IController\-Template\-Axis & \{ get \} & The "Right Shoulder 2" element.
         This is an alias for . \\
center1 &  & IController\-Template\-Button & \{ get \} & The "Center 1" element. \\
back &  & IController\-Template\-Button & \{ get \} & The "Center 1" element.
         This is an alias for . \\
center2 &  & IController\-Template\-Button & \{ get \} & The "Center 2" element. \\
start &  & IController\-Template\-Button & \{ get \} & The "Center 2" element.
         This is an alias for . \\
center3 &  & IController\-Template\-Button & \{ get \} & The "Center 3" element. \\
guide &  & IController\-Template\-Button & \{ get \} & The "Center 3" element.
         This is an alias for . \\
left\-Stick &  & IController\-Template\-Thumb\-Stick & \{ get \} & The "Left Stick" element. \\
right\-Stick &  & IController\-Template\-Thumb\-Stick & \{ get \} & The "Right Stick" element. \\
d\-Pad &  & IController\-Template\-DPad & \{ get \} & The "D-Pad" element. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Gamepad\-Template & public & (object payload) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new instance of this class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RacingWheelTemplate}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
type\-Guid & public static readonly & System.Guid & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The type Guid of the Controller Template.} \\ \tabuphantomline
element\-Id\_wheel & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel".} \\ \tabuphantomline
element\-Id\_accelerator & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Accelerator".} \\ \tabuphantomline
element\-Id\_brake & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Brake".} \\ \tabuphantomline
element\-Id\_clutch & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Clutch".} \\ \tabuphantomline
element\-Id\_shift\-Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shift Down".} \\ \tabuphantomline
element\-Id\_shift\-Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shift Up".} \\ \tabuphantomline
element\-Id\_wheel\-Button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel Button 1".} \\ \tabuphantomline
element\-Id\_wheel\-Button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel Button 2".} \\ \tabuphantomline
element\-Id\_wheel\-Button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel Button 3".} \\ \tabuphantomline
element\-Id\_wheel\-Button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel Button 4".} \\ \tabuphantomline
element\-Id\_wheel\-Button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel Button 5".} \\ \tabuphantomline
element\-Id\_wheel\-Button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel Button 6".} \\ \tabuphantomline
element\-Id\_wheel\-Button7 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel Button 7".} \\ \tabuphantomline
element\-Id\_wheel\-Button8 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel Button 8".} \\ \tabuphantomline
element\-Id\_wheel\-Button9 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel Button 9".} \\ \tabuphantomline
element\-Id\_wheel\-Button10 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel Button 10".} \\ \tabuphantomline
element\-Id\_console\-Button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 1".} \\ \tabuphantomline
element\-Id\_console\-Button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 2".} \\ \tabuphantomline
element\-Id\_console\-Button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 3".} \\ \tabuphantomline
element\-Id\_console\-Button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 4".} \\ \tabuphantomline
element\-Id\_console\-Button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 5".} \\ \tabuphantomline
element\-Id\_console\-Button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 6".} \\ \tabuphantomline
element\-Id\_console\-Button7 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 7".} \\ \tabuphantomline
element\-Id\_console\-Button8 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 8".} \\ \tabuphantomline
element\-Id\_console\-Button9 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 9".} \\ \tabuphantomline
element\-Id\_console\-Button10 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 10".} \\ \tabuphantomline
element\-Id\_shifter1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shifter 1".} \\ \tabuphantomline
element\-Id\_shifter2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shifter 2".} \\ \tabuphantomline
element\-Id\_shifter3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shifter 3".} \\ \tabuphantomline
element\-Id\_shifter4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shifter 4".} \\ \tabuphantomline
element\-Id\_shifter5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shifter 5".} \\ \tabuphantomline
element\-Id\_shifter6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shifter 6".} \\ \tabuphantomline
element\-Id\_shifter7 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shifter 7".} \\ \tabuphantomline
element\-Id\_shifter8 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shifter 8".} \\ \tabuphantomline
element\-Id\_shifter9 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shifter 9".} \\ \tabuphantomline
element\-Id\_shifter10 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Shifter 10".} \\ \tabuphantomline
element\-Id\_reverse\-Gear & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Reverse Gear".} \\ \tabuphantomline
element\-Id\_select & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Select".} \\ \tabuphantomline
element\-Id\_start & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Start".} \\ \tabuphantomline
element\-Id\_system\-Button & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "System Button".} \\ \tabuphantomline
element\-Id\_horn & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Horn".} \\ \tabuphantomline
element\-Id\_d\-Pad\-Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "D-Pad Up".} \\ \tabuphantomline
element\-Id\_d\-Pad\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "D-Pad Right".} \\ \tabuphantomline
element\-Id\_d\-Pad\-Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "D-Pad Down".} \\ \tabuphantomline
element\-Id\_d\-Pad\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "D-Pad Left".} \\ \tabuphantomline
element\-Id\_d\-Pad & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "D-Pad".} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
wheel &  & IController\-Template\-Axis & \{ get \} & The "Wheel" element. \\
accelerator &  & IController\-Template\-Axis & \{ get \} & The "Accelerator" element. \\
brake &  & IController\-Template\-Axis & \{ get \} & The "Brake" element. \\
clutch &  & IController\-Template\-Axis & \{ get \} & The "Clutch" element. \\
shift\-Down &  & IController\-Template\-Button & \{ get \} & The "Shift Down" element. \\
shift\-Up &  & IController\-Template\-Button & \{ get \} & The "Shift Up" element. \\
wheel\-Button1 &  & IController\-Template\-Button & \{ get \} & The "Wheel Button 1" element. \\
wheel\-Button2 &  & IController\-Template\-Button & \{ get \} & The "Wheel Button 2" element. \\
wheel\-Button3 &  & IController\-Template\-Button & \{ get \} & The "Wheel Button 3" element. \\
wheel\-Button4 &  & IController\-Template\-Button & \{ get \} & The "Wheel Button 4" element. \\
wheel\-Button5 &  & IController\-Template\-Button & \{ get \} & The "Wheel Button 5" element. \\
wheel\-Button6 &  & IController\-Template\-Button & \{ get \} & The "Wheel Button 6" element. \\
wheel\-Button7 &  & IController\-Template\-Button & \{ get \} & The "Wheel Button 7" element. \\
wheel\-Button8 &  & IController\-Template\-Button & \{ get \} & The "Wheel Button 8" element. \\
wheel\-Button9 &  & IController\-Template\-Button & \{ get \} & The "Wheel Button 9" element. \\
wheel\-Button10 &  & IController\-Template\-Button & \{ get \} & The "Wheel Button 10" element. \\
console\-Button1 &  & IController\-Template\-Button & \{ get \} & The "Console Button 1" element. \\
console\-Button2 &  & IController\-Template\-Button & \{ get \} & The "Console Button 2" element. \\
console\-Button3 &  & IController\-Template\-Button & \{ get \} & The "Console Button 3" element. \\
console\-Button4 &  & IController\-Template\-Button & \{ get \} & The "Console Button 4" element. \\
console\-Button5 &  & IController\-Template\-Button & \{ get \} & The "Console Button 5" element. \\
console\-Button6 &  & IController\-Template\-Button & \{ get \} & The "Console Button 6" element. \\
console\-Button7 &  & IController\-Template\-Button & \{ get \} & The "Console Button 7" element. \\
console\-Button8 &  & IController\-Template\-Button & \{ get \} & The "Console Button 8" element. \\
console\-Button9 &  & IController\-Template\-Button & \{ get \} & The "Console Button 9" element. \\
console\-Button10 &  & IController\-Template\-Button & \{ get \} & The "Console Button 10" element. \\
shifter1 &  & IController\-Template\-Button & \{ get \} & The "Shifter 1" element. \\
shifter2 &  & IController\-Template\-Button & \{ get \} & The "Shifter 2" element. \\
shifter3 &  & IController\-Template\-Button & \{ get \} & The "Shifter 3" element. \\
shifter4 &  & IController\-Template\-Button & \{ get \} & The "Shifter 4" element. \\
shifter5 &  & IController\-Template\-Button & \{ get \} & The "Shifter 5" element. \\
shifter6 &  & IController\-Template\-Button & \{ get \} & The "Shifter 6" element. \\
shifter7 &  & IController\-Template\-Button & \{ get \} & The "Shifter 7" element. \\
shifter8 &  & IController\-Template\-Button & \{ get \} & The "Shifter 8" element. \\
shifter9 &  & IController\-Template\-Button & \{ get \} & The "Shifter 9" element. \\
shifter10 &  & IController\-Template\-Button & \{ get \} & The "Shifter 10" element. \\
reverse\-Gear &  & IController\-Template\-Button & \{ get \} & The "Reverse Gear" element. \\
select &  & IController\-Template\-Button & \{ get \} & The "Select" element. \\
start &  & IController\-Template\-Button & \{ get \} & The "Start" element. \\
system\-Button &  & IController\-Template\-Button & \{ get \} & The "System Button" element. \\
horn &  & IController\-Template\-Button & \{ get \} & The "Horn" element. \\
d\-Pad &  & IController\-Template\-DPad & \{ get \} & The "D-Pad" element. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Racing\-Wheel\-Template & public & (object payload) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new instance of this class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{HOTASTemplate}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
type\-Guid & public static readonly & System.Guid & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The type Guid of the Controller Template.} \\ \tabuphantomline
element\-Id\_stick\-X & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick X".} \\ \tabuphantomline
element\-Id\_stick\-Y & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Y".} \\ \tabuphantomline
element\-Id\_stick\-Rotate & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Rotate".} \\ \tabuphantomline
element\-Id\_stick\-Mini\-Stick1X & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Mini Stick 1 X".} \\ \tabuphantomline
element\-Id\_stick\-Mini\-Stick1Y & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Mini Stick 1 Y".} \\ \tabuphantomline
element\-Id\_stick\-Mini\-Stick1Press & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Mini Stick 1 Press".} \\ \tabuphantomline
element\-Id\_stick\-Mini\-Stick2X & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Mini Stick 2 X".} \\ \tabuphantomline
element\-Id\_stick\-Mini\-Stick2Y & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Mini Stick 2 Y".} \\ \tabuphantomline
element\-Id\_stick\-Mini\-Stick2Press & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Mini Stick 2 Press".} \\ \tabuphantomline
element\-Id\_stick\-Trigger & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Trigger".} \\ \tabuphantomline
element\-Id\_stick\-Trigger\-Stage2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Trigger (Stage 2)".} \\ \tabuphantomline
element\-Id\_stick\-Pinky\-Button & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Pinky Button".} \\ \tabuphantomline
element\-Id\_stick\-Pinky\-Trigger & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Pinky Trigger".} \\ \tabuphantomline
element\-Id\_stick\-Button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Button 1".} \\ \tabuphantomline
element\-Id\_stick\-Button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Button 2".} \\ \tabuphantomline
element\-Id\_stick\-Button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Button 3".} \\ \tabuphantomline
element\-Id\_stick\-Button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Button 4".} \\ \tabuphantomline
element\-Id\_stick\-Button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Button 5".} \\ \tabuphantomline
element\-Id\_stick\-Button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Button 6".} \\ \tabuphantomline
element\-Id\_stick\-Button7 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Button 7".} \\ \tabuphantomline
element\-Id\_stick\-Button8 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Button 8".} \\ \tabuphantomline
element\-Id\_stick\-Button9 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Button 9".} \\ \tabuphantomline
element\-Id\_stick\-Button10 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Button 10".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 1".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 2".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 3".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 4".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 5".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 6".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button7 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 7".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button8 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 8".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button9 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 9".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button10 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 10".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button11 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 11".} \\ \tabuphantomline
element\-Id\_stick\-Base\-Button12 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Base Button 12".} \\ \tabuphantomline
element\-Id\_stick\-Hat1Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 1 Up".} \\ \tabuphantomline
element\-Id\_stick\-Hat1Up\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 1 Up-Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat1Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 1 Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat1Down\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 1 Down-Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat1Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 1 Down".} \\ \tabuphantomline
element\-Id\_stick\-Hat1Down\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 1 Down-Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat1Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 1 Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat1Up\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 1 Up-Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat2Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 2 Up".} \\ \tabuphantomline
element\-Id\_stick\-Hat2Up\_right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 2 Up-right".} \\ \tabuphantomline
element\-Id\_stick\-Hat2Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 2 Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat2Down\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 2 Down-Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat2Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 2 Down".} \\ \tabuphantomline
element\-Id\_stick\-Hat2Down\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 2 Down-Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat2Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 2 Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat2Up\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 2 Up-Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat3Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 3 Up".} \\ \tabuphantomline
element\-Id\_stick\-Hat3Up\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 3 Up-Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat3Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 3 Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat3Down\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 3 Down-Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat3Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 3 Down".} \\ \tabuphantomline
element\-Id\_stick\-Hat3Down\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 3 Down-Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat3Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 3 Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat3Up\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 3 Up-Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat4Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 4 Up".} \\ \tabuphantomline
element\-Id\_stick\-Hat4Up\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 4 Up-Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat4Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 4 Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat4Down\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 4 Down-Right".} \\ \tabuphantomline
element\-Id\_stick\-Hat4Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 4 Down".} \\ \tabuphantomline
element\-Id\_stick\-Hat4Down\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 4 Down-Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat4Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 4 Left".} \\ \tabuphantomline
element\-Id\_stick\-Hat4Up\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 4 Up-Left".} \\ \tabuphantomline
element\-Id\_mode1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Mode 1".} \\ \tabuphantomline
element\-Id\_mode2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Mode 2".} \\ \tabuphantomline
element\-Id\_mode3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Mode 3".} \\ \tabuphantomline
element\-Id\_throttle1Axis & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 1".} \\ \tabuphantomline
element\-Id\_throttle2Axis & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 2".} \\ \tabuphantomline
element\-Id\_throttle1Min\-Detent & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 1 Min Detent".} \\ \tabuphantomline
element\-Id\_throttle2Min\-Detent & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 2 Min Detent".} \\ \tabuphantomline
element\-Id\_throttle\-Button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Button 1".} \\ \tabuphantomline
element\-Id\_throttle\-Button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Button 2".} \\ \tabuphantomline
element\-Id\_throttle\-Button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Button 3".} \\ \tabuphantomline
element\-Id\_throttle\-Button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Button 4".} \\ \tabuphantomline
element\-Id\_throttle\-Button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Button 5".} \\ \tabuphantomline
element\-Id\_throttle\-Button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Button 6".} \\ \tabuphantomline
element\-Id\_throttle\-Button7 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Button 7".} \\ \tabuphantomline
element\-Id\_throttle\-Button8 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Button 8".} \\ \tabuphantomline
element\-Id\_throttle\-Button9 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Button 9".} \\ \tabuphantomline
element\-Id\_throttle\-Button10 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Button 10".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 1".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 2".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 3".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 4".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 5".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 6".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button7 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 7".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button8 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 8".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button9 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 9".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button10 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 10".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button11 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 11".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button12 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 12".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button13 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 13".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button14 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 14".} \\ \tabuphantomline
element\-Id\_throttle\-Base\-Button15 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Base Button 15".} \\ \tabuphantomline
element\-Id\_throttle\-Slider1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Slider 1".} \\ \tabuphantomline
element\-Id\_throttle\-Slider2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Slider 2".} \\ \tabuphantomline
element\-Id\_throttle\-Slider3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Slider 3".} \\ \tabuphantomline
element\-Id\_throttle\-Slider4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Slider 4".} \\ \tabuphantomline
element\-Id\_throttle\-Dial1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Dial 1".} \\ \tabuphantomline
element\-Id\_throttle\-Dial2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Dial 2".} \\ \tabuphantomline
element\-Id\_throttle\-Dial3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Dial 3".} \\ \tabuphantomline
element\-Id\_throttle\-Dial4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Dial 4".} \\ \tabuphantomline
element\-Id\_throttle\-Mini\-Stick\-X & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Mini Stick X".} \\ \tabuphantomline
element\-Id\_throttle\-Mini\-Stick\-Y & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Mini Stick Y".} \\ \tabuphantomline
element\-Id\_throttle\-Mini\-Stick\-Press & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Mini Stick Press".} \\ \tabuphantomline
element\-Id\_throttle\-Wheel1Forward & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Wheel 1 Forward".} \\ \tabuphantomline
element\-Id\_throttle\-Wheel1Back & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Wheel 1 Back".} \\ \tabuphantomline
element\-Id\_throttle\-Wheel1Press & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Wheel 1 Press".} \\ \tabuphantomline
element\-Id\_throttle\-Wheel2Forward & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Wheel 2 Forward".} \\ \tabuphantomline
element\-Id\_throttle\-Wheel2Back & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Wheel 2 Back".} \\ \tabuphantomline
element\-Id\_throttle\-Wheel2Press & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Wheel 2 Press".} \\ \tabuphantomline
element\-Id\_throttle\-Wheel3Forward & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Wheel 3 Forward".} \\ \tabuphantomline
element\-Id\_throttle\-Wheel3Back & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Wheel 3 Back".} \\ \tabuphantomline
element\-Id\_throttle\-Wheel3Press & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Wheel 3 Press".} \\ \tabuphantomline
element\-Id\_throttle\-Hat1Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 1 Up".} \\ \tabuphantomline
element\-Id\_throttle\-Hat1Up\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 1 Up-Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat1Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 1 Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat1Down\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 1 Down-Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat1Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 1 Down".} \\ \tabuphantomline
element\-Id\_throttle\-Hat1Down\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 1 Down-Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat1Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 1 Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat1Up\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 1 Up-Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat2Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 2 Up".} \\ \tabuphantomline
element\-Id\_throttle\-Hat2Up\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 2 Up-Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat2Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 2 Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat2Down\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 2 Down-Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat2Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 2 Down".} \\ \tabuphantomline
element\-Id\_throttle\-Hat2Down\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 2 Down-Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat2Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 2 Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat2Up\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 2 Up-Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat3Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 3 Up".} \\ \tabuphantomline
element\-Id\_throttle\-Hat3Up\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 3 Up-Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat3Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 3 Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat3Down\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 3 Down-Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat3Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 3 Down".} \\ \tabuphantomline
element\-Id\_throttle\-Hat3Down\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 3 Down-Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat3Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 3 Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat3Up\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 3 Up-Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat4Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 4 Up".} \\ \tabuphantomline
element\-Id\_throttle\-Hat4Up\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 4 Up-Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat4Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 4 Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat4Down\_Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 4 Down-Right".} \\ \tabuphantomline
element\-Id\_throttle\-Hat4Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 4 Down".} \\ \tabuphantomline
element\-Id\_throttle\-Hat4Down\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 4 Down-Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat4Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 4 Left".} \\ \tabuphantomline
element\-Id\_throttle\-Hat4Up\_Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 4 Up-Left".} \\ \tabuphantomline
element\-Id\_left\-Pedal & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Pedal".} \\ \tabuphantomline
element\-Id\_right\-Pedal & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Pedal".} \\ \tabuphantomline
element\-Id\_slide\-Pedals & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Slide Pedals".} \\ \tabuphantomline
element\-Id\_stick & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick".} \\ \tabuphantomline
element\-Id\_stick\-Mini\-Stick1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Mini Stick 1".} \\ \tabuphantomline
element\-Id\_stick\-Mini\-Stick2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Mini Stick 2".} \\ \tabuphantomline
element\-Id\_stick\-Hat1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 1".} \\ \tabuphantomline
element\-Id\_stick\-Hat2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 2".} \\ \tabuphantomline
element\-Id\_stick\-Hat3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 3".} \\ \tabuphantomline
element\-Id\_stick\-Hat4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick Hat 4".} \\ \tabuphantomline
element\-Id\_throttle1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 1".} \\ \tabuphantomline
element\-Id\_throttle2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 2".} \\ \tabuphantomline
element\-Id\_throttle\-Mini\-Stick & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Mini Stick".} \\ \tabuphantomline
element\-Id\_throttle\-Hat1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 1".} \\ \tabuphantomline
element\-Id\_throttle\-Hat2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 2".} \\ \tabuphantomline
element\-Id\_throttle\-Hat3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 3".} \\ \tabuphantomline
element\-Id\_throttle\-Hat4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle Hat 4".} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
stick\-Trigger &  & IController\-Template\-Button & \{ get \} & The "Stick Trigger" element. \\
stick\-Trigger\-Stage2 &  & IController\-Template\-Button & \{ get \} & The "Stick Trigger (Stage 2)" element. \\
stick\-Pinky\-Button &  & IController\-Template\-Button & \{ get \} & The "Stick Pinky Button" element. \\
stick\-Pinky\-Trigger &  & IController\-Template\-Button & \{ get \} & The "Stick Pinky Trigger" element. \\
stick\-Button1 &  & IController\-Template\-Button & \{ get \} & The "Stick Button 1" element. \\
stick\-Button2 &  & IController\-Template\-Button & \{ get \} & The "Stick Button 2" element. \\
stick\-Button3 &  & IController\-Template\-Button & \{ get \} & The "Stick Button 3" element. \\
stick\-Button4 &  & IController\-Template\-Button & \{ get \} & The "Stick Button 4" element. \\
stick\-Button5 &  & IController\-Template\-Button & \{ get \} & The "Stick Button 5" element. \\
stick\-Button6 &  & IController\-Template\-Button & \{ get \} & The "Stick Button 6" element. \\
stick\-Button7 &  & IController\-Template\-Button & \{ get \} & The "Stick Button 7" element. \\
stick\-Button8 &  & IController\-Template\-Button & \{ get \} & The "Stick Button 8" element. \\
stick\-Button9 &  & IController\-Template\-Button & \{ get \} & The "Stick Button 9" element. \\
stick\-Button10 &  & IController\-Template\-Button & \{ get \} & The "Stick Button 10" element. \\
stick\-Base\-Button1 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 1" element. \\
stick\-Base\-Button2 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 2" element. \\
stick\-Base\-Button3 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 3" element. \\
stick\-Base\-Button4 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 4" element. \\
stick\-Base\-Button5 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 5" element. \\
stick\-Base\-Button6 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 6" element. \\
stick\-Base\-Button7 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 7" element. \\
stick\-Base\-Button8 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 8" element. \\
stick\-Base\-Button9 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 9" element. \\
stick\-Base\-Button10 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 10" element. \\
stick\-Base\-Button11 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 11" element. \\
stick\-Base\-Button12 &  & IController\-Template\-Button & \{ get \} & The "Stick Base Button 12" element. \\
mode1 &  & IController\-Template\-Button & \{ get \} & The "Mode 1" element. \\
mode2 &  & IController\-Template\-Button & \{ get \} & The "Mode 2" element. \\
mode3 &  & IController\-Template\-Button & \{ get \} & The "Mode 3" element. \\
throttle\-Button1 &  & IController\-Template\-Button & \{ get \} & The "Throttle Button 1" element. \\
throttle\-Button2 &  & IController\-Template\-Button & \{ get \} & The "Throttle Button 2" element. \\
throttle\-Button3 &  & IController\-Template\-Button & \{ get \} & The "Throttle Button 3" element. \\
throttle\-Button4 &  & IController\-Template\-Button & \{ get \} & The "Throttle Button 4" element. \\
throttle\-Button5 &  & IController\-Template\-Button & \{ get \} & The "Throttle Button 5" element. \\
throttle\-Button6 &  & IController\-Template\-Button & \{ get \} & The "Throttle Button 6" element. \\
throttle\-Button7 &  & IController\-Template\-Button & \{ get \} & The "Throttle Button 7" element. \\
throttle\-Button8 &  & IController\-Template\-Button & \{ get \} & The "Throttle Button 8" element. \\
throttle\-Button9 &  & IController\-Template\-Button & \{ get \} & The "Throttle Button 9" element. \\
throttle\-Button10 &  & IController\-Template\-Button & \{ get \} & The "Throttle Button 10" element. \\
throttle\-Base\-Button1 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 1" element. \\
throttle\-Base\-Button2 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 2" element. \\
throttle\-Base\-Button3 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 3" element. \\
throttle\-Base\-Button4 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 4" element. \\
throttle\-Base\-Button5 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 5" element. \\
throttle\-Base\-Button6 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 6" element. \\
throttle\-Base\-Button7 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 7" element. \\
throttle\-Base\-Button8 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 8" element. \\
throttle\-Base\-Button9 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 9" element. \\
throttle\-Base\-Button10 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 10" element. \\
throttle\-Base\-Button11 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 11" element. \\
throttle\-Base\-Button12 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 12" element. \\
throttle\-Base\-Button13 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 13" element. \\
throttle\-Base\-Button14 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 14" element. \\
throttle\-Base\-Button15 &  & IController\-Template\-Button & \{ get \} & The "Throttle Base Button 15" element. \\
throttle\-Slider1 &  & IController\-Template\-Axis & \{ get \} & The "Throttle Slider 1" element. \\
throttle\-Slider2 &  & IController\-Template\-Axis & \{ get \} & The "Throttle Slider 2" element. \\
throttle\-Slider3 &  & IController\-Template\-Axis & \{ get \} & The "Throttle Slider 3" element. \\
throttle\-Slider4 &  & IController\-Template\-Axis & \{ get \} & The "Throttle Slider 4" element. \\
throttle\-Dial1 &  & IController\-Template\-Axis & \{ get \} & The "Throttle Dial 1" element. \\
throttle\-Dial2 &  & IController\-Template\-Axis & \{ get \} & The "Throttle Dial 2" element. \\
throttle\-Dial3 &  & IController\-Template\-Axis & \{ get \} & The "Throttle Dial 3" element. \\
throttle\-Dial4 &  & IController\-Template\-Axis & \{ get \} & The "Throttle Dial 4" element. \\
throttle\-Wheel1Forward &  & IController\-Template\-Button & \{ get \} & The "Throttle Wheel 1 Forward" element. \\
throttle\-Wheel1Back &  & IController\-Template\-Button & \{ get \} & The "Throttle Wheel 1 Back" element. \\
throttle\-Wheel1Press &  & IController\-Template\-Button & \{ get \} & The "Throttle Wheel 1 Press" element. \\
throttle\-Wheel2Forward &  & IController\-Template\-Button & \{ get \} & The "Throttle Wheel 2 Forward" element. \\
throttle\-Wheel2Back &  & IController\-Template\-Button & \{ get \} & The "Throttle Wheel 2 Back" element. \\
throttle\-Wheel2Press &  & IController\-Template\-Button & \{ get \} & The "Throttle Wheel 2 Press" element. \\
throttle\-Wheel3Forward &  & IController\-Template\-Button & \{ get \} & The "Throttle Wheel 3 Forward" element. \\
throttle\-Wheel3Back &  & IController\-Template\-Button & \{ get \} & The "Throttle Wheel 3 Back" element. \\
throttle\-Wheel3Press &  & IController\-Template\-Button & \{ get \} & The "Throttle Wheel 3 Press" element. \\
left\-Pedal &  & IController\-Template\-Axis & \{ get \} & The "Left Pedal" element. \\
right\-Pedal &  & IController\-Template\-Axis & \{ get \} & The "Right Pedal" element. \\
slide\-Pedals &  & IController\-Template\-Axis & \{ get \} & The "Slide Pedals" element. \\
stick &  & IController\-Template\-Stick & \{ get \} & The "Stick" element. \\
stick\-Mini\-Stick1 &  & IController\-Template\-Thumb\-Stick & \{ get \} & The "Stick Mini Stick 1" element. \\
stick\-Mini\-Stick2 &  & IController\-Template\-Thumb\-Stick & \{ get \} & The "Stick Mini Stick 2" element. \\
stick\-Hat1 &  & IController\-Template\-Hat & \{ get \} & The "Stick Hat 1" element. \\
stick\-Hat2 &  & IController\-Template\-Hat & \{ get \} & The "Stick Hat 2" element. \\
stick\-Hat3 &  & IController\-Template\-Hat & \{ get \} & The "Stick Hat 3" element. \\
stick\-Hat4 &  & IController\-Template\-Hat & \{ get \} & The "Stick Hat 4" element. \\
throttle1 &  & IController\-Template\-Throttle & \{ get \} & The "Throttle 1" element. \\
throttle2 &  & IController\-Template\-Throttle & \{ get \} & The "Throttle 2" element. \\
throttle\-Mini\-Stick &  & IController\-Template\-Thumb\-Stick & \{ get \} & The "Throttle Mini Stick" element. \\
throttle\-Hat1 &  & IController\-Template\-Hat & \{ get \} & The "Throttle Hat 1" element. \\
throttle\-Hat2 &  & IController\-Template\-Hat & \{ get \} & The "Throttle Hat 2" element. \\
throttle\-Hat3 &  & IController\-Template\-Hat & \{ get \} & The "Throttle Hat 3" element. \\
throttle\-Hat4 &  & IController\-Template\-Hat & \{ get \} & The "Throttle Hat 4" element. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
HOTASTemplate & public & (object payload) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new instance of this class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{FlightYokeTemplate}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
type\-Guid & public static readonly & System.Guid & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The type Guid of the Controller Template.} \\ \tabuphantomline
element\-Id\_rotate\-Yoke & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Rotate Yoke".} \\ \tabuphantomline
element\-Id\_yoke\-Z & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Yoke Z".} \\ \tabuphantomline
element\-Id\_left\-Paddle & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Paddle".} \\ \tabuphantomline
element\-Id\_right\-Paddle & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Paddle".} \\ \tabuphantomline
element\-Id\_lever1Axis & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 1".} \\ \tabuphantomline
element\-Id\_lever1Min\-Detent & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 1 Min Detent".} \\ \tabuphantomline
element\-Id\_lever2Axis & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 2".} \\ \tabuphantomline
element\-Id\_lever2Min\-Detent & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 2 Min Detent".} \\ \tabuphantomline
element\-Id\_lever3Axis & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 3".} \\ \tabuphantomline
element\-Id\_lever3Min\-Detent & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 3 Min Detent".} \\ \tabuphantomline
element\-Id\_lever4Axis & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 4".} \\ \tabuphantomline
element\-Id\_lever4Min\-Detent & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 4 Min Detent".} \\ \tabuphantomline
element\-Id\_lever5Axis & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 5".} \\ \tabuphantomline
element\-Id\_lever5Min\-Detent & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 5 Min Detent".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Button 1".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Button 2".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Button 3".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Button 4".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Button 5".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Button 6".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Button 1".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Button 2".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Button 3".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Button 4".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Button 5".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Button 6".} \\ \tabuphantomline
element\-Id\_center\-Button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center Button 1".} \\ \tabuphantomline
element\-Id\_center\-Button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center Button 2".} \\ \tabuphantomline
element\-Id\_center\-Button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center Button 3".} \\ \tabuphantomline
element\-Id\_center\-Button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center Button 4".} \\ \tabuphantomline
element\-Id\_center\-Button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center Button 5".} \\ \tabuphantomline
element\-Id\_center\-Button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center Button 6".} \\ \tabuphantomline
element\-Id\_center\-Button7 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center Button 7".} \\ \tabuphantomline
element\-Id\_center\-Button8 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Center Button 8".} \\ \tabuphantomline
element\-Id\_wheel1Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel 1 Up".} \\ \tabuphantomline
element\-Id\_wheel1Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel 1 Down".} \\ \tabuphantomline
element\-Id\_wheel1Press & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel 1 Press".} \\ \tabuphantomline
element\-Id\_wheel2Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel 2 Up".} \\ \tabuphantomline
element\-Id\_wheel2Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel 2 Down".} \\ \tabuphantomline
element\-Id\_wheel2Press & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Wheel 2 Press".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Hat\-Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Hat Up".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Hat\-Up\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Hat Up-Right".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Hat\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Hat Right".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Hat\-Down\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Hat Down-Right".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Hat\-Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Hat Down".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Hat\-Down\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Hat Down-Left".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Hat\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Hat Left".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Hat\-Up\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Hat Up-Left".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Hat\-Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Hat Up".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Hat\-Up\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Hat Up-Right".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Hat\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Hat Right".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Hat\-Down\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Hat Down-Right".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Hat\-Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Hat Down".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Hat\-Down\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Hat Down-Left".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Hat\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Hat Left".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Hat\-Up\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Hat Up-Left".} \\ \tabuphantomline
element\-Id\_console\-Button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 1".} \\ \tabuphantomline
element\-Id\_console\-Button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 2".} \\ \tabuphantomline
element\-Id\_console\-Button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 3".} \\ \tabuphantomline
element\-Id\_console\-Button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 4".} \\ \tabuphantomline
element\-Id\_console\-Button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 5".} \\ \tabuphantomline
element\-Id\_console\-Button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 6".} \\ \tabuphantomline
element\-Id\_console\-Button7 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 7".} \\ \tabuphantomline
element\-Id\_console\-Button8 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 8".} \\ \tabuphantomline
element\-Id\_console\-Button9 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 9".} \\ \tabuphantomline
element\-Id\_console\-Button10 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Console Button 10".} \\ \tabuphantomline
element\-Id\_mode1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Mode 1".} \\ \tabuphantomline
element\-Id\_mode2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Mode 2".} \\ \tabuphantomline
element\-Id\_mode3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Mode 3".} \\ \tabuphantomline
element\-Id\_yoke & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Yoke".} \\ \tabuphantomline
element\-Id\_lever1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 1".} \\ \tabuphantomline
element\-Id\_lever2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 2".} \\ \tabuphantomline
element\-Id\_lever3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 3".} \\ \tabuphantomline
element\-Id\_lever4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 4".} \\ \tabuphantomline
element\-Id\_lever5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Lever 5".} \\ \tabuphantomline
element\-Id\_left\-Grip\-Hat & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Grip Hat".} \\ \tabuphantomline
element\-Id\_right\-Grip\-Hat & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Grip Hat".} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
left\-Paddle &  & IController\-Template\-Button & \{ get \} & The "Left Paddle" element. \\
right\-Paddle &  & IController\-Template\-Button & \{ get \} & The "Right Paddle" element. \\
left\-Grip\-Button1 &  & IController\-Template\-Button & \{ get \} & The "Left Grip Button 1" element. \\
left\-Grip\-Button2 &  & IController\-Template\-Button & \{ get \} & The "Left Grip Button 2" element. \\
left\-Grip\-Button3 &  & IController\-Template\-Button & \{ get \} & The "Left Grip Button 3" element. \\
left\-Grip\-Button4 &  & IController\-Template\-Button & \{ get \} & The "Left Grip Button 4" element. \\
left\-Grip\-Button5 &  & IController\-Template\-Button & \{ get \} & The "Left Grip Button 5" element. \\
left\-Grip\-Button6 &  & IController\-Template\-Button & \{ get \} & The "Left Grip Button 6" element. \\
right\-Grip\-Button1 &  & IController\-Template\-Button & \{ get \} & The "Right Grip Button 1" element. \\
right\-Grip\-Button2 &  & IController\-Template\-Button & \{ get \} & The "Right Grip Button 2" element. \\
right\-Grip\-Button3 &  & IController\-Template\-Button & \{ get \} & The "Right Grip Button 3" element. \\
right\-Grip\-Button4 &  & IController\-Template\-Button & \{ get \} & The "Right Grip Button 4" element. \\
right\-Grip\-Button5 &  & IController\-Template\-Button & \{ get \} & The "Right Grip Button 5" element. \\
right\-Grip\-Button6 &  & IController\-Template\-Button & \{ get \} & The "Right Grip Button 6" element. \\
center\-Button1 &  & IController\-Template\-Button & \{ get \} & The "Center Button 1" element. \\
center\-Button2 &  & IController\-Template\-Button & \{ get \} & The "Center Button 2" element. \\
center\-Button3 &  & IController\-Template\-Button & \{ get \} & The "Center Button 3" element. \\
center\-Button4 &  & IController\-Template\-Button & \{ get \} & The "Center Button 4" element. \\
center\-Button5 &  & IController\-Template\-Button & \{ get \} & The "Center Button 5" element. \\
center\-Button6 &  & IController\-Template\-Button & \{ get \} & The "Center Button 6" element. \\
center\-Button7 &  & IController\-Template\-Button & \{ get \} & The "Center Button 7" element. \\
center\-Button8 &  & IController\-Template\-Button & \{ get \} & The "Center Button 8" element. \\
wheel1Up &  & IController\-Template\-Button & \{ get \} & The "Wheel 1 Up" element. \\
wheel1Down &  & IController\-Template\-Button & \{ get \} & The "Wheel 1 Down" element. \\
wheel1Press &  & IController\-Template\-Button & \{ get \} & The "Wheel 1 Press" element. \\
wheel2Up &  & IController\-Template\-Button & \{ get \} & The "Wheel 2 Up" element. \\
wheel2Down &  & IController\-Template\-Button & \{ get \} & The "Wheel 2 Down" element. \\
wheel2Press &  & IController\-Template\-Button & \{ get \} & The "Wheel 2 Press" element. \\
console\-Button1 &  & IController\-Template\-Button & \{ get \} & The "Console Button 1" element. \\
console\-Button2 &  & IController\-Template\-Button & \{ get \} & The "Console Button 2" element. \\
console\-Button3 &  & IController\-Template\-Button & \{ get \} & The "Console Button 3" element. \\
console\-Button4 &  & IController\-Template\-Button & \{ get \} & The "Console Button 4" element. \\
console\-Button5 &  & IController\-Template\-Button & \{ get \} & The "Console Button 5" element. \\
console\-Button6 &  & IController\-Template\-Button & \{ get \} & The "Console Button 6" element. \\
console\-Button7 &  & IController\-Template\-Button & \{ get \} & The "Console Button 7" element. \\
console\-Button8 &  & IController\-Template\-Button & \{ get \} & The "Console Button 8" element. \\
console\-Button9 &  & IController\-Template\-Button & \{ get \} & The "Console Button 9" element. \\
console\-Button10 &  & IController\-Template\-Button & \{ get \} & The "Console Button 10" element. \\
mode1 &  & IController\-Template\-Button & \{ get \} & The "Mode 1" element. \\
mode2 &  & IController\-Template\-Button & \{ get \} & The "Mode 2" element. \\
mode3 &  & IController\-Template\-Button & \{ get \} & The "Mode 3" element. \\
yoke &  & IController\-Template\-Yoke & \{ get \} & The "Yoke" element. \\
lever1 &  & IController\-Template\-Throttle & \{ get \} & The "Lever 1" element. \\
lever2 &  & IController\-Template\-Throttle & \{ get \} & The "Lever 2" element. \\
lever3 &  & IController\-Template\-Throttle & \{ get \} & The "Lever 3" element. \\
lever4 &  & IController\-Template\-Throttle & \{ get \} & The "Lever 4" element. \\
lever5 &  & IController\-Template\-Throttle & \{ get \} & The "Lever 5" element. \\
left\-Grip\-Hat &  & IController\-Template\-Hat & \{ get \} & The "Left Grip Hat" element. \\
right\-Grip\-Hat &  & IController\-Template\-Hat & \{ get \} & The "Right Grip Hat" element. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Flight\-Yoke\-Template & public & (object payload) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new instance of this class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{FlightPedalsTemplate}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
type\-Guid & public static readonly & System.Guid & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The type Guid of the Controller Template.} \\ \tabuphantomline
element\-Id\_left\-Pedal & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Left Pedal".} \\ \tabuphantomline
element\-Id\_right\-Pedal & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Right Pedal".} \\ \tabuphantomline
element\-Id\_slide & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Slide".} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
left\-Pedal &  & IController\-Template\-Axis & \{ get \} & The "Left Pedal" element. \\
right\-Pedal &  & IController\-Template\-Axis & \{ get \} & The "Right Pedal" element. \\
slide &  & IController\-Template\-Axis & \{ get \} & The "Slide" element. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Flight\-Pedals\-Template & public & (object payload) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new instance of this class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SixDofControllerTemplate}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
type\-Guid & public static readonly & System.Guid & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The type Guid of the Controller Template.} \\ \tabuphantomline
element\-Id\_position\-X & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Horizontal".} \\ \tabuphantomline
element\-Id\_position\-Y & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Vertical".} \\ \tabuphantomline
element\-Id\_position\-Z & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Forward/Back".} \\ \tabuphantomline
element\-Id\_rotation\-X & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Rotate X".} \\ \tabuphantomline
element\-Id\_rotation\-Y & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Rotate Y".} \\ \tabuphantomline
element\-Id\_rotation\-Z & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Rotate Z".} \\ \tabuphantomline
element\-Id\_throttle1Axis & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 1".} \\ \tabuphantomline
element\-Id\_throttle1Min\-Detent & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 1 Min Detent".} \\ \tabuphantomline
element\-Id\_throttle2Axis & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 2".} \\ \tabuphantomline
element\-Id\_throttle2Min\-Detent & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 2 Min Detent".} \\ \tabuphantomline
element\-Id\_extra\-Axis1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Extra Axis 1".} \\ \tabuphantomline
element\-Id\_extra\-Axis2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Extra Axis 2".} \\ \tabuphantomline
element\-Id\_extra\-Axis3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Extra Axis 3".} \\ \tabuphantomline
element\-Id\_extra\-Axis4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Extra Axis 4".} \\ \tabuphantomline
element\-Id\_button1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 1".} \\ \tabuphantomline
element\-Id\_button2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 2".} \\ \tabuphantomline
element\-Id\_button3 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 3".} \\ \tabuphantomline
element\-Id\_button4 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 4".} \\ \tabuphantomline
element\-Id\_button5 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 5".} \\ \tabuphantomline
element\-Id\_button6 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 6".} \\ \tabuphantomline
element\-Id\_button7 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 7".} \\ \tabuphantomline
element\-Id\_button8 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 8".} \\ \tabuphantomline
element\-Id\_button9 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 9".} \\ \tabuphantomline
element\-Id\_button10 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 10".} \\ \tabuphantomline
element\-Id\_button11 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 11".} \\ \tabuphantomline
element\-Id\_button12 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 12".} \\ \tabuphantomline
element\-Id\_button13 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 13".} \\ \tabuphantomline
element\-Id\_button14 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 14".} \\ \tabuphantomline
element\-Id\_button15 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 15".} \\ \tabuphantomline
element\-Id\_button16 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 16".} \\ \tabuphantomline
element\-Id\_button17 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 17".} \\ \tabuphantomline
element\-Id\_button18 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 18".} \\ \tabuphantomline
element\-Id\_button19 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 19".} \\ \tabuphantomline
element\-Id\_button20 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 20".} \\ \tabuphantomline
element\-Id\_button21 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 21".} \\ \tabuphantomline
element\-Id\_button22 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 22".} \\ \tabuphantomline
element\-Id\_button23 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 23".} \\ \tabuphantomline
element\-Id\_button24 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 24".} \\ \tabuphantomline
element\-Id\_button25 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 25".} \\ \tabuphantomline
element\-Id\_button26 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 26".} \\ \tabuphantomline
element\-Id\_button27 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 27".} \\ \tabuphantomline
element\-Id\_button28 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 28".} \\ \tabuphantomline
element\-Id\_button29 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 29".} \\ \tabuphantomline
element\-Id\_button30 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 30".} \\ \tabuphantomline
element\-Id\_button31 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 31".} \\ \tabuphantomline
element\-Id\_button32 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Button 32".} \\ \tabuphantomline
element\-Id\_hat1Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 1 Up".} \\ \tabuphantomline
element\-Id\_hat1Up\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 1 Up-Right".} \\ \tabuphantomline
element\-Id\_hat1Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 1 Right".} \\ \tabuphantomline
element\-Id\_hat1Down\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 1 Down-Right".} \\ \tabuphantomline
element\-Id\_hat1Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 1 Down".} \\ \tabuphantomline
element\-Id\_hat1Down\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 1 Down-Left".} \\ \tabuphantomline
element\-Id\_hat1Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 1 Left".} \\ \tabuphantomline
element\-Id\_hat1Up\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 1 Up-Left".} \\ \tabuphantomline
element\-Id\_hat2Up & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 2 Up".} \\ \tabuphantomline
element\-Id\_hat2Up\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 2 Up-Right".} \\ \tabuphantomline
element\-Id\_hat2Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 2 Right".} \\ \tabuphantomline
element\-Id\_hat2Down\-Right & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 2 Down-Right".} \\ \tabuphantomline
element\-Id\_hat2Down & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 2 Down".} \\ \tabuphantomline
element\-Id\_hat2Down\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 2 Down-Left".} \\ \tabuphantomline
element\-Id\_hat2Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 2 Left".} \\ \tabuphantomline
element\-Id\_hat2Up\-Left & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 2 Up-Left".} \\ \tabuphantomline
element\-Id\_hat1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 1".} \\ \tabuphantomline
element\-Id\_hat2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Hat 2".} \\ \tabuphantomline
element\-Id\_throttle1 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 1".} \\ \tabuphantomline
element\-Id\_throttle2 & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Throttle 2".} \\ \tabuphantomline
element\-Id\_stick & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Element identifier id for "Stick".} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
extra\-Axis1 &  & IController\-Template\-Axis & \{ get \} & The "Extra Axis 1" element. \\
extra\-Axis2 &  & IController\-Template\-Axis & \{ get \} & The "Extra Axis 2" element. \\
extra\-Axis3 &  & IController\-Template\-Axis & \{ get \} & The "Extra Axis 3" element. \\
extra\-Axis4 &  & IController\-Template\-Axis & \{ get \} & The "Extra Axis 4" element. \\
button1 &  & IController\-Template\-Button & \{ get \} & The "Button 1" element. \\
button2 &  & IController\-Template\-Button & \{ get \} & The "Button 2" element. \\
button3 &  & IController\-Template\-Button & \{ get \} & The "Button 3" element. \\
button4 &  & IController\-Template\-Button & \{ get \} & The "Button 4" element. \\
button5 &  & IController\-Template\-Button & \{ get \} & The "Button 5" element. \\
button6 &  & IController\-Template\-Button & \{ get \} & The "Button 6" element. \\
button7 &  & IController\-Template\-Button & \{ get \} & The "Button 7" element. \\
button8 &  & IController\-Template\-Button & \{ get \} & The "Button 8" element. \\
button9 &  & IController\-Template\-Button & \{ get \} & The "Button 9" element. \\
button10 &  & IController\-Template\-Button & \{ get \} & The "Button 10" element. \\
button11 &  & IController\-Template\-Button & \{ get \} & The "Button 11" element. \\
button12 &  & IController\-Template\-Button & \{ get \} & The "Button 12" element. \\
button13 &  & IController\-Template\-Button & \{ get \} & The "Button 13" element. \\
button14 &  & IController\-Template\-Button & \{ get \} & The "Button 14" element. \\
button15 &  & IController\-Template\-Button & \{ get \} & The "Button 15" element. \\
button16 &  & IController\-Template\-Button & \{ get \} & The "Button 16" element. \\
button17 &  & IController\-Template\-Button & \{ get \} & The "Button 17" element. \\
button18 &  & IController\-Template\-Button & \{ get \} & The "Button 18" element. \\
button19 &  & IController\-Template\-Button & \{ get \} & The "Button 19" element. \\
button20 &  & IController\-Template\-Button & \{ get \} & The "Button 20" element. \\
button21 &  & IController\-Template\-Button & \{ get \} & The "Button 21" element. \\
button22 &  & IController\-Template\-Button & \{ get \} & The "Button 22" element. \\
button23 &  & IController\-Template\-Button & \{ get \} & The "Button 23" element. \\
button24 &  & IController\-Template\-Button & \{ get \} & The "Button 24" element. \\
button25 &  & IController\-Template\-Button & \{ get \} & The "Button 25" element. \\
button26 &  & IController\-Template\-Button & \{ get \} & The "Button 26" element. \\
button27 &  & IController\-Template\-Button & \{ get \} & The "Button 27" element. \\
button28 &  & IController\-Template\-Button & \{ get \} & The "Button 28" element. \\
button29 &  & IController\-Template\-Button & \{ get \} & The "Button 29" element. \\
button30 &  & IController\-Template\-Button & \{ get \} & The "Button 30" element. \\
button31 &  & IController\-Template\-Button & \{ get \} & The "Button 31" element. \\
button32 &  & IController\-Template\-Button & \{ get \} & The "Button 32" element. \\
hat1 &  & IController\-Template\-Hat & \{ get \} & The "Hat 1" element. \\
hat2 &  & IController\-Template\-Hat & \{ get \} & The "Hat 2" element. \\
throttle1 &  & IController\-Template\-Throttle & \{ get \} & The "Throttle 1" element. \\
throttle2 &  & IController\-Template\-Throttle & \{ get \} & The "Throttle 2" element. \\
stick &  & IController\-Template\-Stick6D & \{ get \} & The "Stick" element. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Six\-Dof\-Controller\-Template & public & (object payload) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new instance of this class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ControllerTemplateFactory}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
template\-Types & public static & Type[] & \{ get \} & Controller Template types. \\
template\-Interface\-Types & public static & Type[] & \{ get \} & Controller Template interface types. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Create & public static & IController\-Template & (Guid type\-Guid, object payload) & Creates a Controller Template instance. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{UserDataStore_PlayerPrefs}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Is\-Enabled & public & bool & \{ get set \} & Should this script be used? If disabled, nothing will be saved or loaded. \\
Load\-Data\-On\-Start & public & bool & \{ get set \} & Should saved data be loaded on start? \\
Load\-Joystick\-Assignments & public & bool & \{ get set \} & Should Player Joystick assignments be saved and loaded? This is not totally reliable for all Joysticks on all platforms.
         Some platforms/input sources do not provide enough information to reliably save assignments from session to session
         and reboot to reboot. \\
Load\-Keyboard\-Assignments & public & bool & \{ get set \} & Should Player Keyboard assignments be saved and loaded? \\
Load\-Mouse\-Assignments & public & bool & \{ get set \} & Should Player Mouse assignments be saved and loaded? \\
Player\-Prefs\-Key\-Prefix & public & string & \{ get set \} & The Player\-Prefs key prefix. Change this to change how keys are stored in Player\-Prefs. Changing this will make saved data already stored with the old key no longer accessible. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Save & public override & void & () & Save all data now. \\
Save\-Controller\-Data & public override & void & (int player\-Id, Controller\-Type controller\-Type, int controller\-Id) & Save all data for a specific controller for a Player. \\
Save\-Controller\-Data & public override & void & (Controller\-Type controller\-Type, int controller\-Id) & Save all data for a specific controller. Does not save Player data. \\
Save\-Player\-Data & public override & void & (int player\-Id) & Save all data for a specific Player. \\
Save\-Input\-Behavior & public override & void & (int player\-Id, int behavior\-Id) & Save all data for a specific Input\-Behavior for a Player. \\
Load & public override & void & () & Load all data now. \\
Load\-Controller\-Data & public override & void & (int player\-Id, Controller\-Type controller\-Type, int controller\-Id) & Load all data for a specific controller for a Player. \\
Load\-Controller\-Data & public override & void & (Controller\-Type controller\-Type, int controller\-Id) & Load all data for a specific controller. Does not load Player data. \\
Load\-Player\-Data & public override & void & (int player\-Id) & Load all data for a specific Player. \\
Load\-Input\-Behavior & public override & void & (int player\-Id, int behavior\-Id) & Load all data for a specific Input\-Behavior for a Player. \\
On\-Initialize & protected override & void & () & Called when Save\-Data\-Store is initialized. \\
On\-Controller\-Connected & protected override & void & (Controller\-Status\-Changed\-Event\-Args args) & Called when a controller is connected. \\
On\-Controller\-Pre\-Disconnect & protected override & void & (Controller\-Status\-Changed\-Event\-Args args) & Calls after a controller has been disconnected. \\
On\-Controller\-Disconnected & protected override & void & (Controller\-Status\-Changed\-Event\-Args args) & Called when a controller is disconnected. \\
Save\-Controller\-Map & public override & void & (int player\-Id, Controller\-Map controller\-Map) & Saves a Controller Map. \\
Load\-Controller\-Map & public override & Controller\-Map & (int player\-Id, Controller\-Identifier controller\-Identifier, int category\-Id, int layout\-Id) & Loads a Controller Map for a Controller. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CollectionExtension}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Is\-Enumerable\-Null\-Or\-Empty & public static & bool & (this IEnumerable{\tt <}\-T\-{\tt >} collection) & Is\-Null\-Or\-Empty alternative for generic enumerables \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{FPSCounter}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Update\-Interval & public & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The frequency at which the FPS counter should update (in seconds)} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Start & protected virtual & void & () & On Start(), we get the Text component and initialize our counter \\
Update & protected virtual & void & () & On Update, we increment our various counters, and if we've reached our Update\-Interval, we update our FPS counter
	 with the number of frames displayed since the last counter update \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{AStar}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Search & public static & List{\tt <}\-Grid\-Tile\-{\tt >} & (Grid\-Tile start, Grid\-Tile goal) & Returns the best path as a List of Nodes \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{GridPathfinder}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
m\_Target\-Grid\-Object & public & Grid\-Object & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
m\_Destination\-Tile & public & Grid\-Tile & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
m\_Debug\-Draw\-Path & public & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
m\_Next\-Pathpoint\-Index & public & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
Path & public & List{\tt <}\-Grid\-Tile\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Awake & protected virtual & void & () & On Awake we grab our components \\
Set\-New\-Destination & public virtual & void & (Grid\-Tile destination\-Grid\-Tile) & Sets a new destination the character will pathfind to \\
Update & protected virtual & void & () & On Update, we draw the path if needed, determine the next waypoint, and move to it if needed \\
Move\-Grid\-Object & protected virtual & void & () & Moves the controller towards the next point \\
Determine\-Path & protected virtual & void & (Grid\-Tile starting\-Grid\-Tile, Grid\-Tile target\-Grid\-Tile) & Determines the path to the target Grid\-Tile. Next\-Path\-Point\-Index will be -1 if a path couldn't be found \\
Determine\-Next\-Pathpoint & protected virtual & void & () & Determines the next path point \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RigidbodyFirstPersonController}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Ground\-Check & private & void & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RemoveConnectionCommand}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_window & private & Bbbt\-Window & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The window in which to remove the connection.} \\ \tabuphantomline
\_connection & private & Bbbt\-Connection & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The connection to remove.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Remove\-Connection\-Command & public & (Bbbt\-Window window, Bbbt\-Connection connection) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new Remove\-Connection\-Command instance.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CreateNodeCommand}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_window & private & Bbbt\-Window & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The window in which to add a node.} \\ \tabuphantomline
\_node & private & Bbbt\-Node & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The node to add.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Create\-Node\-Command & public & (Bbbt\-Window window, Bbbt\-Node node) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new Create\-Node\-Command instance.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoveNodeCommand}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_window & private & Bbbt\-Window & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The window in which the node should move.} \\ \tabuphantomline
\_node & private & Bbbt\-Node & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The node to move.} \\ \tabuphantomline
\_delta & private & Vector2 & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The old node position.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Move\-Node\-Command & public & (Bbbt\-Window window, Bbbt\-Node node, Vector2 delta) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Move\-Node\-Command.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CreateConnectionCommand}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_window & private & Bbbt\-Window & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The window in which to add the connection.} \\ \tabuphantomline
\_connection & private & Bbbt\-Connection & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The connection to add.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Create\-Connection\-Command & public & (Bbbt\-Window window, Bbbt\-Connection connection) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new Create\-Connection\-Command instance.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{RemoveNodeCommand}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_window & private & Bbbt\-Window & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The window in which to remove a node.} \\ \tabuphantomline
\_node & private & Bbbt\-Node & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The node to add.} \\ \tabuphantomline
\_connections & private & List{\tt <}\-Bbbt\-Connection\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The connections that need to be removed along with the node.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Remove\-Node\-Command & public & (Bbbt\-Window window, Bbbt\-Node node, List{\tt <}\-Bbbt\-Connection\-{\tt >} connections) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new Remove\-Node\-Command instance.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtCommandHistoryBrowser}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_command\-Strings & private static & Dictionary{\tt <}\-Type, string\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Maps command types to the string to be displayed in the command history browser.} \\ \tabuphantomline
\_window & private & Bbbt\-Window & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The window the browser is open in.} \\ \tabuphantomline
\_done\-Commands\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style of done command buttons.} \\ \tabuphantomline
\_undone\-Commands\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style of undone command buttons.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Command\-History\-Browser & public & (Bbbt\-Window window) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates an instance of Bbbt\-Command\-History\-Browser.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Truncate & private & string & (string value, GUIStyle style, float max\-Width) & Truncates a string to fit horizontally within a maximum width. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtHelpMenu}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_window & private & Bbbt\-Window & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The window the menu is in.} \\ \tabuphantomline
\_sections & private & List{\tt <}\-Bbbt\-Help\-Section\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The sections of the help menu.} \\ \tabuphantomline
\_header\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The help menu's button style.} \\ \tabuphantomline
\_content\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The help menu's content style.} \\ \tabuphantomline
\_border\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style used for the borders between sections.} \\ \tabuphantomline
\_y\-Offset & private & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The y offset for placing the menu's content. Determined by scrolling.} \\ \tabuphantomline
\_used\-Vertical\-Space\-Last\-Draw & private & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{How much vertical space was used last time the menu was drawn.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Help\-Menu & public & (Bbbt\-Window window) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new Bbbt\-Help\-Menu.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtHelpSection}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Header & public & string & \{ get; protected set; \} & The section's header. \\
Content & public & string & \{ get; protected set; \} & The section's content. \\
Is\-Active & public & bool & \{ get; set; \} & Whether the section's content should be displayed in the menu. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Help\-Section & public & (string header, string content) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a new instance of Bbbt\-Help\-Section.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtSidePanel}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_window & private & Bbbt\-Window & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The window the panel belongs to.} \\ \tabuphantomline
\_panel\-Rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The panel's rect.} \\ \tabuphantomline
\_navigation\-Bar\-Rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The rect for the navigation bar to the very left of the window.} \\ \tabuphantomline
\_navigation\-Bar\-Border\-Rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The rect of the navigation bar's border.} \\ \tabuphantomline
\_panel\-Border\-Rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The rect of the panel's border.} \\ \tabuphantomline
\_drag\-Area\-Rect & private & Rect & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The rect that defines the area where the mouse can drag the panel.} \\ \tabuphantomline
\_style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The panel's style.} \\ \tabuphantomline
\_selected\-Button\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style of selected buttons.} \\ \tabuphantomline
\_border\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The panel's border style.} \\ \tabuphantomline
\_is\-Dragged & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Whether the panel is currently being dragged (resized).} \\ \tabuphantomline
\_texture\-To\-Content & private & List{\tt <}\-Key\-Value\-Pair{\tt <}\-Texture2D, Bbbt\-Side\-Panel\-Content\-{\tt >}\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Maps a button in the navigation rect to content in the side panel for opening/closing the content.} \\ \tabuphantomline
\_selected\-Content & private & Bbbt\-Side\-Panel\-Content & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The currently selected content to display in the panel.} \\ \tabuphantomline
On\-Open\-Side\-Panel & public & Action & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Invoked when the side panel is opened.} \\ \tabuphantomline
On\-Close\-Side\-Panel & public & Action & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Invoked when the side panel is closed.} \\ \tabuphantomline
On\-Resize\-Side\-Panel & public & Action{\tt <}\-float\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Invoked when the side panel is resized.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Side\-Panel & public & (Bbbt\-Window window) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Constructs a side panel.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Draw & public & void & () & Draws the panel. \\
Setup\-Rects & private & void & (float width) & Sets up rects according to the width of the navigation bar. \\
Drag & private & void & (float delta) & Drags the panel. \\
Process\-Events & public & void & (Event e) & Processes events. \\
Get\-Total\-Width & public & float & (bool include\-Closed\-Panel = false) & Returns the total width of the panel and navigation bar including borders. \\
Get\-Content\-Panel\-Width & public & float & () & Returns the total width of the content panel including border. \\
Get\-Navigation\-Bar\-Width & public & float & () & Returns the total width of the navigation bar including border. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtSidePanelContent}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Draw & public abstract & void & (Rect rect) & Draws the content. \\
Process\-Events & public abstract & void & (Event e) & Processes events. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtTabCommandHistory}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Command\-Manager & public & Command\-Manager & \{ get; protected set; \} & The Command\-Manager that this command history browser operated with. \\
Done\-Commands & public & List{\tt <}\-Command\-{\tt >} & \{ get; protected set; \} & List of the names of commands that have been performed. \\
Undone\-Commands & public & List{\tt <}\-Command\-{\tt >} & \{ get; protected set; \} & List of the names of commands that have been undone. \\
Last\-Save\-Command & public & Command & \{ get; set; \} & The last performed command last time the tab was saved. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Tab\-Command\-History & public & (Command\-Manager command\-Manager) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new Bbbt\-Command\-History\-Browser.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtTreeValidationPanel}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_window & private & Bbbt\-Window & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The bb\-BT editor window.} \\ \tabuphantomline
\_nodes & private & List{\tt <}\-Bbbt\-Node\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Nodes to display warnings/errors for.} \\ \tabuphantomline
\_warnings & private & Dictionary{\tt <}\-Bbbt\-Node, List{\tt <}\-string\-{\tt >}\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Warnings to display.} \\ \tabuphantomline
\_errors & private & Dictionary{\tt <}\-Bbbt\-Node, List{\tt <}\-string\-{\tt >}\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Errors to display.} \\ \tabuphantomline
\_header\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style to use for headers.} \\ \tabuphantomline
\_warning\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style to use for warnings.} \\ \tabuphantomline
\_error\-Style & private & GUIStyle & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The style to use for errors.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Bbbt\-Tree\-Validation\-Panel & public & (Bbbt\-Window window) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Creates a new Bbbt\-Tree\-Validation\-Panel instance.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Validate & private & void & () & Validates the tree. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtSelector}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Initialize & protected override & void & (Game\-Object game\-Object) & Bbbt\-Selector doesn't use any initialisation logic. \\
On\-Terminate & protected override & void & (Game\-Object game\-Object, Bbbt\-Behaviour\-Status status) & Bbbt\-Selector doesn't use any termination logic. \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Executes the first runnable child behaviour. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtSequencer}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Initialize & protected override & void & (Game\-Object game\-Object) & Bbbt\-Sequencer does not have an On\-Initialize implementation. \\
On\-Terminate & protected override & void & (Game\-Object game\-Object, Bbbt\-Behaviour\-Status status) & Bbbt\-Sequencer does not have an On\-Terminate implementation. \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Runs through the sequencers child nodes until they have been completed or one fails. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtAllEnemiesInSight}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Loops over all potential enemies for the actor and checks if they
         are within the actors Line Of Sight \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtBehaviourTreeCallerBehaviour}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_behaviour\-Tree\-Name & private & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The name of the behaviour tree to call.} \\ \tabuphantomline
\_root & private & Bbbt\-Behaviour & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The root of the behaviour tree to call.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Behaviour\-Tree & public & Bbbt\-Behaviour\-Tree & \{ get; protected set; \} & The the behaviour tree to call. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Initialize & protected override & void & (Game\-Object game\-Object) & On\-Initialize gets called the first time the behaviour is called. \\
On\-Terminate & protected override & void & (Game\-Object game\-Object, Bbbt\-Behaviour\-Status status) & Doesn't have any termination logic. \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Ticks the root of the behaviour tree to be called. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtDebugLogBehaviour}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_message & private & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The message to print to log to the Unity console.} \\ \tabuphantomline
\_is\-Enabled & private & bool & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Whether the message is enabled. For convenient switching off without having to remove/re-add nodes.} \\ \tabuphantomline
\_log\-Type & private & Log\-Type & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The type of message to log.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
On\-Initialize & protected override & void & (Game\-Object game\-Object) & Bbbt\-Root doesn't have any initialisation logic. \\
On\-Terminate & protected override & void & (Game\-Object game\-Object, Bbbt\-Behaviour\-Status status) & Bbbt\-Root doesn't have any termination logic. \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Prints the message the debug logger is supposed to print. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtMoveToCIBehaviour}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_min\-Range & private & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The range from the CI the drone will try to move to while idling} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtMoveToClosestDepotBehaviour}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
deposit\-Range &  & float & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{How far away from a depot an actor can be and still deposit} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtTargetNearest}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Finds the enemy that is closest to the actor and assign it to the actors target variable. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BbbtCanSeeEnemyCheck}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Update\-Behaviour & protected override & Bbbt\-Behaviour\-Status & (Game\-Object game\-Object) & Checks if the actor has an enemy in its line of sight \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PublicBufferMemoryStream}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Set\-Length & public override & void & (long value) & Note: This will not make the Memory\-Stream any smaller, only larger \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BufferPool}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Buffer & public & Memory\-Stream & () & Gets a Memory\-Stream built from a buffer plucked from a thread safe pool
         The pool grows automatically.
         Closing the memory stream clears the buffer and returns it to the pool \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{HttpHelper}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Calculate\-Web\-Socket\-Key & public static & string & () & Calculates a random Web\-Socket key that can be used to initiate a Web\-Socket handshake \\
Compute\-Socket\-Accept\-String & public static & string & (string sec\-Web\-Socket\-Key) & Computes a Web\-Socket accept string from a given key \\
Read\-Http\-Header\-Async & public static async & Task{\tt <}\-string\-{\tt >} & (Stream stream, Cancellation\-Token token) & Reads an http header as per the HTTP spec \\
Is\-Web\-Socket\-Upgrade\-Request & public static & bool & (String header) & Decodes the header to detect is this is a web socket upgrade response \\
Get\-Path\-From\-Header & public static & string & (string http\-Header) & Gets the path from the HTTP header \\
Read\-Http\-Response\-Code & public static & string & (string response) & Reads the HTTP response code from the http response string \\
Write\-Http\-Header\-Async & public static async & Task & (string response, Stream stream, Cancellation\-Token token) & Writes an HTTP response string to the stream \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PingPongManager}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Ping\-Pong\-Manager & public & (Guid guid, Web\-Socket web\-Socket, Time\-Span keep\-Alive\-Interval, Cancellation\-Token cancellation\-Token) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initialises a new instance of the Ping\-Pong\-Manager to facilitate ping pong Web\-Socket messages.
         If you are manually creating an instance of this class then it is advisable to set keep\-Alive\-Interval to
         Time\-Span.Zero when you create the Web\-Socket instance (using a factory) otherwise you may be automatically
         be sending duplicate Ping messages (see keep\-Alive\-Interval below)} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Send\-Ping & public async & Task & (Array\-Segment{\tt <}\-byte\-{\tt >} payload, Cancellation\-Token cancellation) & Sends a ping frame \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PongEventArgs}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Payload & public & Array\-Segment{\tt <}\-byte\-{\tt >} & \{ get; private set; \} & The data extracted from a Pong Web\-Socket frame \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Pong\-Event\-Args & public & (Array\-Segment{\tt <}\-byte\-{\tt >} payload) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initialises a new instance of the Pong\-Event\-Args class} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WebSocketClientFactory}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Web\-Socket\-Client\-Factory & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initialises a new instance of the Web\-Socket\-Client\-Factory class without caring about internal buffers} \\ \tabuphantomline
Web\-Socket\-Client\-Factory & public & (Func{\tt <}\-Memory\-Stream\-{\tt >} buffer\-Factory) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initialises a new instance of the Web\-Socket\-Client\-Factory class with control over internal buffer creation} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Connect\-Async & public async & Task{\tt <}\-Web\-Socket\-{\tt >} & (Uri uri, Cancellation\-Token token = default(Cancellation\-Token)) & Connect with default options \\
Connect\-Async & public async & Task{\tt <}\-Web\-Socket\-{\tt >} & (Uri uri, Web\-Socket\-Client\-Options options, Cancellation\-Token token = default(Cancellation\-Token)) & Connect with options specified \\
Connect\-Async & public async & Task{\tt <}\-Web\-Socket\-{\tt >} & (Stream response\-Stream, string sec\-Web\-Socket\-Key, Web\-Socket\-Client\-Options options, Cancellation\-Token token = default(Cancellation\-Token)) & Connect with a stream that has already been opened and HTTP websocket upgrade request sent
         This function will check the handshake response from the server and proceed if successful
         Use this function if you have specific requirements to open a conenction like using special http headers and cookies
         You will have to build your own HTTP websocket upgrade request
         You may not even choose to use TCP/IP and this function will allow you to do that \\
Validate\-Server\-Certificate & static & bool & (object sender, X509Certificate certificate, X509Chain chain, Ssl\-Policy\-Errors ssl\-Policy\-Errors) & Invoked by the Remote\-Certificate\-Validation\-Delegate
         If you want to ignore certificate errors (for debugging) then return true \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WebSocketClientOptions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Keep\-Alive\-Interval & public & Time\-Span & \{ get; set; \} & How often to send ping requests to the Server
         This is done to prevent proxy servers from closing your connection
         The default is Time\-Span.Zero meaning that it is disabled.
         Web\-Socket servers usually send ping messages so it is not normally necessary for the client to send them (hence the Time\-Span.Zero default)
         You can manually control ping pong messages using the Ping\-Pong\-Manager class.
         If you do that it is advisible to set this Keep\-Alive\-Interval to zero for the Web\-Socket\-Client\-Factory \\
No\-Delay & public & bool & \{ get; set; \} & Set to true to send a message immediately with the least amount of latency (typical usage for chat)
         This will disable Nagle's algorithm which can cause high tcp latency for small packets sent infrequently
         However, if you are streaming large packets or sending large numbers of small packets frequently it is advisable to set No\-Delay to false
         This way data will be bundled into larger packets for better throughput \\
Additional\-Http\-Headers & public & Dictionary{\tt <}\-string, string\-{\tt >} & \{ get; set; \} & Add any additional http headers to this dictionary \\
Include\-Exception\-In\-Close\-Response & public & bool & \{ get; set; \} & Include the full exception (with stack trace) in the close response
         when an exception is encountered and the Web\-Socket connection is closed
         The default is false \\
Sec\-Web\-Socket\-Extensions & public & string & \{ get; set; \} & Web\-Socket Extensions as an HTTP header value \\
Sec\-Web\-Socket\-Protocol & public & string & \{ get; set; \} & A comma separated list of sub protocols in preference order (first one being the most preferred)
         The server will return the first supported sub protocol (or none if none are supported)
         Can be null \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Web\-Socket\-Client\-Options & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initialises a new instance of the Web\-Socket\-Client\-Options class} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WebSocketHttpContext}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Is\-Web\-Socket\-Request & public & bool & \{ get; private set; \} & True if this is a valid Web\-Socket request \\
Http\-Header & public & string & \{ get; private set; \} & The raw http header extracted from the stream \\
Path & public & string & \{ get; private set; \} & The Path extracted from the http header \\
Stream & public & Stream & \{ get; private set; \} & The stream AFTER the header has already been read \\
Client & public & Tcp\-Client & \{ get; private set; \} & The tcp connection we are using \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Web\-Socket\-Http\-Context & public & (bool is\-Web\-Socket\-Request, IList{\tt <}\-string\-{\tt >} web\-Socket\-Requested\-Protocols, string http\-Header, string path, Tcp\-Client client, Stream stream) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initialises a new instance of the Web\-Socket\-Http\-Context class} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WebSocketServerFactory}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Web\-Socket\-Server\-Factory & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initialises a new instance of the Web\-Socket\-Server\-Factory class without caring about internal buffers} \\ \tabuphantomline
Web\-Socket\-Server\-Factory & public & (Func{\tt <}\-Memory\-Stream\-{\tt >} buffer\-Factory) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initialises a new instance of the Web\-Socket\-Client\-Factory class with control over internal buffer creation} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Read\-Http\-Header\-From\-Stream\-Async & public async & Task{\tt <}\-Web\-Socket\-Http\-Context\-{\tt >} & (Tcp\-Client client, Stream stream, Cancellation\-Token token = default(Cancellation\-Token)) & Reads a http header information from a stream and decodes the parts relating to the Web\-Socket protocot upgrade \\
Accept\-Web\-Socket\-Async & public async & Task{\tt <}\-Web\-Socket\-{\tt >} & (Web\-Socket\-Http\-Context context, Cancellation\-Token token = default(Cancellation\-Token)) & Accept web socket with default options
         Call Read\-Http\-Header\-From\-Stream\-Async first to get Web\-Socket\-Http\-Context \\
Accept\-Web\-Socket\-Async & public async & Task{\tt <}\-Web\-Socket\-{\tt >} & (Web\-Socket\-Http\-Context context, Web\-Socket\-Server\-Options options, Cancellation\-Token token = default(Cancellation\-Token)) & Accept web socket with options specified
         Call Read\-Http\-Header\-From\-Stream\-Async first to get Web\-Socket\-Http\-Context \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WebSocketServerOptions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Keep\-Alive\-Interval & public & Time\-Span & \{ get; set; \} & How often to send ping requests to the Client
         The default is 60 seconds
         This is done to prevent proxy servers from closing your connection
         A timespan of zero will disable the automatic ping pong mechanism
         You can manually control ping pong messages using the Ping\-Pong\-Manager class.
         If you do that it is advisible to set this Keep\-Alive\-Interval to zero in the Web\-Socket\-Server\-Factory \\
Include\-Exception\-In\-Close\-Response & public & bool & \{ get; set; \} & Include the full exception (with stack trace) in the close response
         when an exception is encountered and the Web\-Socket connection is closed
         The default is false \\
Sub\-Protocol & public & string & \{ get; set; \} & Specifies the sub protocol to send back to the client in the opening handshake
         Can be null (the most common use case)
         The client can specify multiple preferred protocols in the opening handshake header
         The server should use the first supported one or set this to null if none of the requested sub protocols are supported \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Web\-Socket\-Server\-Options & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initialises a new instance of the Web\-Socket\-Server\-Options class} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ClosureContext}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Symbols & public & string[] & \{ get; private set; \} & Gets the symbols. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoonSharpHideMemberAttribute}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Member\-Name & public & string & \{ get; private set; \} & Gets the name of the member to be hidden. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Moon\-Sharp\-Hide\-Member\-Attribute & public & (string member\-Name) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoonSharpPropertyAttribute}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; private set; \} & The metamethod name (like '\_\_div', '\_\_ipairs', etc.) \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Moon\-Sharp\-Property\-Attribute & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Moon\-Sharp\-Property\-Attribute & public & (string name) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoonSharpUserDataAttribute}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Access\-Mode & public & Interop\-Access\-Mode & \{ get; set; \} & The interop access mode \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Moon\-Sharp\-User\-Data\-Attribute & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoonSharpUserDataMetamethodAttribute}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; private set; \} & The metamethod name (like '\_\_div', '\_\_ipairs', etc.) \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Moon\-Sharp\-User\-Data\-Metamethod\-Attribute & public & (string name) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MoonSharpVisibleAttribute}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Visible & public & bool & \{ get; private set; \} & Gets a value indicating whether this  is set to "visible". \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Moon\-Sharp\-Visible\-Attribute & public & (bool visible) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DispatchingUserDataDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
SPECIALNAME\_INDEXER\_GET & protected const & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The special name used by CLR for indexer getters} \\ \tabuphantomline
SPECIALNAME\_INDEXER\_SET & protected const & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The special name used by CLR for indexer setters} \\ \tabuphantomline
SPECIALNAME\_CAST\_EXPLICIT & protected const & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The special name used by CLR for explicit cast conversions} \\ \tabuphantomline
SPECIALNAME\_CAST\_IMPLICIT & protected const & string & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The special name used by CLR for implicit cast conversions} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; private set; \} & Gets the name of the descriptor (usually, the name of the type described). \\
Type & public & Type & \{ get; private set; \} & Gets the type this descriptor refers to \\
Friendly\-Name & public & string & \{ get; private set; \} & Gets a human readable friendly name of the descriptor \\
Member\-Names & public & IEnumerable{\tt <}\-string\-{\tt >} & \{ get \} & Gets the member names. \\
Members & public & IEnumerable{\tt <}\-Key\-Value\-Pair{\tt <}\-string, IMember\-Descriptor\-{\tt >}\-{\tt >} & \{ get \} & Gets the members. \\
Meta\-Member\-Names & public & IEnumerable{\tt <}\-string\-{\tt >} & \{ get \} & Gets the meta member names. \\
Meta\-Members & public & IEnumerable{\tt <}\-Key\-Value\-Pair{\tt <}\-string, IMember\-Descriptor\-{\tt >}\-{\tt >} & \{ get \} & Gets the meta members. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Dispatching\-User\-Data\-Descriptor & protected & (Type type, string friendly\-Name = null) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add\-Meta\-Member & public & void & (string name, IMember\-Descriptor desc) & Adds a member to the meta-members list. \\
Add\-Dyn\-Value & public & void & (string name, Dyn\-Value value) & Adds a Dyn\-Value as a member \\
Add\-Member & public & void & (string name, IMember\-Descriptor desc) & Adds a property to the member list \\
Find\-Member & public & IMember\-Descriptor & (string member\-Name) & Finds the member with a given name. If not found, null is returned. \\
Remove\-Member & public & void & (string member\-Name) & Removes the member with a given name. In case of overloaded functions, all overloads are removed. \\
Find\-Meta\-Member & public & IMember\-Descriptor & (string member\-Name) & Finds the meta member with a given name. If not found, null is returned. \\
Remove\-Meta\-Member & public & void & (string member\-Name) & Removes the meta member with a given name. In case of overloaded functions, all overloads are removed. \\
Index & public virtual & Dyn\-Value & (Script script, object obj, Dyn\-Value index, bool is\-Direct\-Indexing) & Performs an "index" "get" operation. This tries to resolve minor variations of member names. \\
Try\-Index\-On\-Ext\-Method & private & Dyn\-Value & (Script script, object obj, string index\-Name) & Tries to perform an indexing operation by checking newly added extension methods for the given index\-Name. \\
Has\-Member & public & bool & (string exact\-Name) & Determines whether the descriptor contains the specified member (by exact name) \\
Has\-Meta\-Member & public & bool & (string exact\-Name) & Determines whether the descriptor contains the specified member in the meta list (by exact name) \\
Try\-Index & protected virtual & Dyn\-Value & (Script script, object obj, string index\-Name) & Tries to perform an indexing operation by checking methods and properties for the given index\-Name \\
Set\-Index & public virtual & bool & (Script script, object obj, Dyn\-Value index, Dyn\-Value value, bool is\-Direct\-Indexing) & Performs an "index" "set" operation. This tries to resolve minor variations of member names. \\
Try\-Set\-Index & protected virtual & bool & (Script script, object obj, string index\-Name, Dyn\-Value value) & Tries to perform an indexing "set" operation by checking methods and properties for the given index\-Name \\
Camelify & protected static & string & (string name) & Converts the specified name from underscore\_case to camel\-Case.
		 Just a wrapper over the  method with the same name, \\
Upper\-First\-Letter & protected static & string & (string name) & Converts the specified name to one with an uppercase first letter (something to Something).
		 Just a wrapper over the  method with the same name, \\
As\-String & public virtual & string & (object obj) & Converts this userdata to string \\
Execute\-Indexer & protected virtual & Dyn\-Value & (IMember\-Descriptor mdesc, Script script, object obj, Dyn\-Value index, Dyn\-Value value) & Executes the specified indexer method. \\
Meta\-Index & public virtual & Dyn\-Value & (Script script, object obj, string metaname) & Gets a "meta" operation on this userdata. If a descriptor does not support this functionality,
		 it should return "null" (not a nil). 
		 See  for further details.
		 
		 If a method exists marked with  for the specific
		 metamethod requested, that method is returned.
		 
		 If the above fails, the following dispatching occur:
		 
		 \_\_add, \_\_sub, \_\_mul, \_\_div, \_\_mod and \_\_unm are dispatched to C\# operator overloads (if they exist)
		 \_\_eq is dispatched to System.Object.Equals.
		 \_\_lt and \_\_le are dispatched IComparable.Compare, if the type implements IComparable or IComparable\{object\}
		 \_\_len is dispatched to Length and Count properties, if those exist.
		 \_\_iterator is handled if the object implements IEnumerable or IEnumerator.
		 \_\_tonumber is dispatched to implicit or explicit conversion operators to standard numeric types.
		 \_\_tobool is dispatched to an implicit or explicit conversion operator to bool. If that fails, operator true is used.
		 
		 The script originating the request
		 The object (null if a static request is done)
		 The name of the metamember. \\
Is\-Type\-Compatible & public virtual & bool & (Type type, object obj) & Determines whether the specified object is compatible with the specified type.
		 Unless a very specific behaviour is needed, the correct implementation is a 
		 simple " return type.Is\-Instance\-Of\-Type(obj); " \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MemberDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Has\-All\-Flags & public static & bool & (this Member\-Descriptor\-Access access, Member\-Descriptor\-Access flag) & Determines whether the specified Member\-Descriptor\-Access has ALL the specified flags. \\
Can\-Read & public static & bool & (this IMember\-Descriptor desc) & Determines whether this instance can be read \\
Can\-Write & public static & bool & (this IMember\-Descriptor desc) & Determines whether this instance can be written to \\
Can\-Execute & public static & bool & (this IMember\-Descriptor desc) & Determines whether this instance can be executed (called as a function) \\
Get\-Getter\-Callback\-As\-Dyn\-Value & public static & Dyn\-Value & (this IMember\-Descriptor desc, Script script, object obj) & Gets the getter of the member as a Dyn\-Value containing a callback \\
With\-Access\-Or\-Null & public static & IMember\-Descriptor & (this IMember\-Descriptor desc, Member\-Descriptor\-Access access) & Returns the specified descriptor if it supports all the specified access modes, otherwise returns null. \\
Check\-Access & public static & void & (this IMember\-Descriptor desc, Member\-Descriptor\-Access access, object obj) & Raises an appropriate Script\-Runtime\-Exception if the specified access is not supported.
		 Checks are made for the Member\-Descriptor\-Access permissions AND for the access of instance
		 members through static userdatas. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ParameterDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
m\_Original\-Type & private & Type & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{If the type got restricted, the original type before the restriction.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get; private set; \} & Gets the name of the parameter \\
Type & public & Type & \{ get; private set; \} & Gets the type of the parameter \\
Has\-Default\-Value & public & bool & \{ get; private set; \} & Gets a value indicating whether this instance has a default value. \\
Default\-Value & public & object & \{ get; private set; \} & Gets the default value \\
Is\-Out & public & bool & \{ get; private set; \} & Gets a value indicating whether this instance is an out parameter \\
Is\-Ref & public & bool & \{ get; private set; \} & Gets a value indicating whether this instance is a "ref" parameter \\
Is\-Var\-Args & public & bool & \{ get; private set; \} & Gets a value indicating whether this instance is a variable arguments param \\
Has\-Been\-Restricted & public & bool & \{ get \} & Gets a value indicating whether this instance has been restricted. \\
Original\-Type & public & Type & \{ get \} & Gets the original type of the parameter before any restriction has been applied. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Parameter\-Descriptor & public & (string name, Type type, bool has\-Default\-Value = false, object default\-Value = null, bool is\-Out = false,
			bool is\-Ref = false, bool is\-Var\-Args = false) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Parameter\-Descriptor & public & (string name, Type type, bool has\-Default\-Value, object default\-Value, bool is\-Out,
			bool is\-Ref, bool is\-Var\-Args, Type type\-Restriction) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Parameter\-Descriptor & public & (Parameter\-Info pi) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
To\-String & public override & string & () & Returns a  that represents this instance. \\
Restrict\-Type & public & void & (Type type) & Restricts the type of this parameter to a tighter constraint.
		 Restrictions must be applied before the  containing this
		 parameter is used in any way. \\
Prepare\-For\-Wiring & public & void & (Table table) & Prepares the descriptor for hard-wiring.
		 The descriptor fills the passed table with all the needed data for hardwire generators to generate the appropriate code. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ClrToScriptConversions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Try\-Object\-To\-Trivial\-Dyn\-Value & internal static & Dyn\-Value & (Script script, object obj) & Tries to convert a CLR object to a Moon\-Sharp value, using "trivial" logic.
		 Skips on custom conversions, etc.
		 Does NOT throw on failure. \\
Try\-Object\-To\-Simple\-Dyn\-Value & internal static & Dyn\-Value & (Script script, object obj) & Tries to convert a CLR object to a Moon\-Sharp value, using "simple" logic.
		 Does NOT throw on failure. \\
Object\-To\-Dyn\-Value & internal static & Dyn\-Value & (Script script, object obj) & Tries to convert a CLR object to a Moon\-Sharp value, using more in-depth analysis \\
Enumeration\-To\-Dyn\-Value & public static & Dyn\-Value & (Script script, object obj) & Converts an IEnumerable or IEnumerator to a Dyn\-Value \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{NumericConversions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Numeric\-Types & internal static readonly & Hash\-Set{\tt <}\-Type\-{\tt >} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Hash\-Set of numeric types} \\ \tabuphantomline
Numeric\-Types\-Ordered & internal static readonly & Type[] & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Array of numeric types in order used for some conversions} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Double\-To\-Type & internal static & object & (Type type, double d) & Converts a double to another type \\
Type\-To\-Double & internal static & double & (Type type, object d) & Converts a type to double \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ScriptToClrConversions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Dyn\-Value\-To\-Object & internal static & object & (Dyn\-Value value) & Converts a Dyn\-Value to a CLR object [simple conversion] \\
Dyn\-Value\-To\-Object\-Of\-Type & internal static & object & (Dyn\-Value value, Type desired\-Type, object default\-Value, bool is\-Optional) & Converts a Dyn\-Value to a CLR object of a specific type \\
Dyn\-Value\-To\-Object\-Of\-Type\-Weight & internal static & int & (Dyn\-Value value, Type desired\-Type, bool is\-Optional) & Gets a relative weight of how much the conversion is matching the given types.
		 Implementation must follow that of Dyn\-Value\-To\-Object\-Of\-Type.. it's not very DRY in that sense.
		 However here we are in perf-sensitive path.. TODO : double-check the gain and see if a DRY impl is better. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TableConversions}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Convert\-IList\-To\-Table & internal static & Table & (Script script, System.Collections.IList list) & Converts an IList to a Lua table. \\
Convert\-IDictionary\-To\-Table & internal static & Table & (Script script, System.Collections.IDictionary dict) & Converts an IDictionary to a Lua table. \\
Can\-Convert\-Table\-To\-Type & internal static & bool & (Table table, Type t) & Determines whether the specified table can be converted to the specified type \\
Convert\-Table\-To\-Type & internal static & object & (Table table, Type t) & Converts a table to a CLR object of a given type \\
Convert\-Table\-To\-Dictionary\-Of\-Generic\-Type & internal static & object & (Type dictionary\-Type, Type key\-Type, Type value\-Type, Table table) & Converts a table to a \\
Convert\-Table\-To\-Array\-Of\-Generic\-Type & internal static & object & (Type array\-Type, Type item\-Type, Table table) & Converts a table to a T[] \\
Convert\-Table\-To\-List\-Of\-Generic\-Type & internal static & object & (Type list\-Type, Type item\-Type, Table table) & Converts a table to a \\
Table\-To\-List & internal static & List{\tt <}\-T\-{\tt >} & (Table table, Func{\tt <}\-Dyn\-Value, T\-{\tt >} converter) & Converts a table to a , known in advance \\
Table\-To\-Dictionary & internal static & Dictionary{\tt <}\-TK, TV\-{\tt >} & (Table table, Func{\tt <}\-Dyn\-Value, TK\-{\tt >} keyconverter, Func{\tt <}\-Dyn\-Value, TV\-{\tt >} valconverter) & Converts a table to a Dictionary, known in advance \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{LuaBase}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Lua\-Call & protected static & void & (Lua\-State L, lua\_Integer nargs, lua\_Integer nresults = LUA\_MULTRET) & Calls a function.
		 To call a function you must use the following protocol: first, the function to be called is pushed onto the stack; then,
		 the arguments to the function are pushed in direct order; that is, the first argument is pushed first. Finally you call
		 lua\_call; nargs is the number of arguments that you pushed onto the stack. All arguments and the function value are
		 popped from the stack when the function is called. The function results are pushed onto the stack when the function
		 returns. The number of results is adjusted to nresults, unless nresults is LUA\_MULTRET. In this case, all results from
		 the function are pushed. Lua takes care that the returned values fit into the stack space. The function results are
		 pushed onto the stack in direct order (the first result is pushed first), so that after the call the last result is on
		 the top of the stack. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{Tools}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Is\-Numeric\-Type & public static & bool & (object o) & Determines whether the specified value is of numeric type. \\
Is\-Positive & public static & bool & (object Value, bool Zero\-Is\-Positive) & Determines whether the specified value is positive. \\
To\-Unsigned & public static & object & (object Value) & Converts the specified values boxed type to its correpsonding unsigned
		 type. \\
To\-Integer & public static & object & (object Value, bool Round) & Converts the specified values boxed type to its correpsonding integer
		 type. \\
Replace\-Meta\-Chars & public static & string & (string input) & Replaces the string representations of meta chars with their corresponding
		 character values. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{AnonWrapper}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Value & public & T & \{ get; set; \} & Gets or sets the value this instance wraps. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Anon\-Wrapper & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Anon\-Wrapper & public & (T o) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DelegateProxyFactory}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Target\-Type & public & Type & \{ get \} & Gets the proxied type \\
Proxy\-Type & public & Type & \{ get \} & Gets the proxy type \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Delegate\-Proxy\-Factory & public & (Func{\tt <}\-TTarget, TProxy\-{\tt >} wrap\-Delegate) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Create\-Proxy\-Object & public & TProxy & (TTarget target) & Takes an instance of a target object and returns a proxy object wrapping it \\
Create\-Proxy\-Object & public & object & (object o) & Takes an instance of a target object and returns a proxy object wrapping it \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{AutomaticRegistrationPolicy}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Allow\-Type\-Auto\-Registration & public override & bool & (Type type) & Allows type automatic registration for the specified type.
		 NOTE: automatic type registration is NOT recommended. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DefaultRegistrationPolicy}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Handle\-Registration & public & IUser\-Data\-Descriptor & (IUser\-Data\-Descriptor new\-Descriptor, IUser\-Data\-Descriptor old\-Descriptor) & Called to handle the registration or deregistration of a type descriptor. Must return the type descriptor to be registered, or null to remove the registration. \\
Allow\-Type\-Auto\-Registration & public virtual & bool & (Type type) & Allows type automatic registration for the specified type.
		 NOTE: automatic type registration is NOT recommended. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PermanentRegistrationPolicy}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Handle\-Registration & public & IUser\-Data\-Descriptor & (IUser\-Data\-Descriptor new\-Descriptor, IUser\-Data\-Descriptor old\-Descriptor) & Called to handle the registration or deregistration of a type descriptor. Must return the type descriptor to be registered, or null to remove the registration. \\
Allow\-Type\-Auto\-Registration & public & bool & (Type type) & Allows type automatic registration for the specified type.
		 NOTE: automatic type registration is NOT recommended. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{AutoDescribingUserDataDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Name & public & string & \{ get \} & Gets the name of the descriptor (usually, the name of the type described). \\
Type & public & Type & \{ get \} & Gets the type this descriptor refers to \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Auto\-Describing\-User\-Data\-Descriptor & public & (Type type, string friendly\-Name) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Index & public & Dyn\-Value & (Script script, object obj, Dyn\-Value index, bool is\-Direct\-Indexing) & Performs an "index" "get" operation. \\
Set\-Index & public & bool & (Script script, object obj, Dyn\-Value index, Dyn\-Value value, bool is\-Direct\-Indexing) & Performs an "index" "set" operation. \\
As\-String & public & string & (object obj) & Converts this userdata to string \\
Meta\-Index & public & Dyn\-Value & (Script script, object obj, string metaname) & Gets a "meta" operation on this userdata. If a descriptor does not support this functionality,
		 it should return "null" (not a nil). 
		 These standard metamethods can be supported (the return value should be a function accepting the
		 classic parameters of the corresponding metamethod):
		 \_\_add, \_\_sub, \_\_mul, \_\_div, \_\_div, \_\_pow, \_\_unm, \_\_eq, \_\_lt, \_\_le, \_\_lt, \_\_len, \_\_concat, 
		 \_\_pairs, \_\_ipairs, \_\_iterator, \_\_call
		 These standard metamethods are supported through other calls for efficiency:
		 \_\_index, \_\_newindex, \_\_tostring \\
Is\-Type\-Compatible & public & bool & (Type type, object obj) & Determines whether the specified object is compatible with the specified type.
		 Unless a very specific behaviour is needed, the correct implementation is a 
		 simple " return type.Is\-Instance\-Of\-Type(obj); " \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{CompositeUserDataDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Descriptors & public & IList{\tt <}\-IUser\-Data\-Descriptor\-{\tt >} & \{ get \} & Gets the descriptors aggregated by this object, allowing changes to the descriptor list \\
Name & public & string & \{ get \} & Gets the name of the descriptor (usually, the name of the type described). \\
Type & public & Type & \{ get \} & Gets the type this descriptor refers to \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Composite\-User\-Data\-Descriptor & public & (List{\tt <}\-IUser\-Data\-Descriptor\-{\tt >} descriptors, Type type) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Index & public & Dyn\-Value & (Script script, object obj, Dyn\-Value index, bool is\-Name\-Index) & Performs an "index" "get" operation. \\
Set\-Index & public & bool & (Script script, object obj, Dyn\-Value index, Dyn\-Value value, bool is\-Name\-Index) & Performs an "index" "set" operation. \\
As\-String & public & string & (object obj) & Converts this userdata to string \\
Meta\-Index & public & Dyn\-Value & (Script script, object obj, string metaname) & Gets a "meta" operation on this userdata. If a descriptor does not support this functionality,
		 it should return "null" (not a nil). 
		 These standard metamethods can be supported (the return value should be a function accepting the
		 classic parameters of the corresponding metamethod):
		 \_\_add, \_\_sub, \_\_mul, \_\_div, \_\_div, \_\_pow, \_\_unm, \_\_eq, \_\_lt, \_\_le, \_\_lt, \_\_len, \_\_concat, 
		 \_\_pairs, \_\_ipairs, \_\_iterator, \_\_call
		 These standard metamethods are supported through other calls for efficiency:
		 \_\_index, \_\_newindex, \_\_tostring \\
Is\-Type\-Compatible & public & bool & (Type type, object obj) & Determines whether the specified object is compatible with the specified type.
		 Unless a very specific behaviour is needed, the correct implementation is a 
		 simple " return type.Is\-Instance\-Of\-Type(obj); " \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ProxyUserDataDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Inner\-Descriptor & public & IUser\-Data\-Descriptor & \{ get \} & Gets the descriptor which describes the proxy object \\
Name & public & string & \{ get; private set; \} & Gets the name of the descriptor (usually, the name of the type described). \\
Type & public & Type & \{ get \} & Gets the type this descriptor refers to \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Proxy & private & object & (object obj) & Proxies the specified object. \\
Index & public & Dyn\-Value & (Script script, object obj, Dyn\-Value index, bool is\-Direct\-Indexing) & Performs an "index" "get" operation. \\
Set\-Index & public & bool & (Script script, object obj, Dyn\-Value index, Dyn\-Value value, bool is\-Direct\-Indexing) & Performs an "index" "set" operation. \\
As\-String & public & string & (object obj) & Converts this userdata to string \\
Meta\-Index & public & Dyn\-Value & (Script script, object obj, string metaname) & Gets a "meta" operation on this userdata. If a descriptor does not support this functionality,
		 it should return "null" (not a nil).
		 These standard metamethods can be supported (the return value should be a function accepting the
		 classic parameters of the corresponding metamethod):
		 \_\_add, \_\_sub, \_\_mul, \_\_div, \_\_div, \_\_pow, \_\_unm, \_\_eq, \_\_lt, \_\_le, \_\_lt, \_\_len, \_\_concat,
		 \_\_pairs, \_\_ipairs, \_\_iterator, \_\_call
		 These standard metamethods are supported through other calls for efficiency:
		 \_\_index, \_\_newindex, \_\_tostring \\
Is\-Type\-Compatible & public & bool & (Type type, object obj) & Determines whether the specified object is compatible with the specified type.
		 Unless a very specific behaviour is needed, the correct implementation is a
		 simple " return type.Is\-Instance\-Of\-Type(obj); " \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{StandardEnumUserDataDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Underlying\-Type & public & Type & \{ get; private set; \} & Gets the underlying type of the enum. \\
Is\-Unsigned & public & bool & \{ get; private set; \} & Gets a value indicating whether underlying type of the enum is unsigned. \\
Is\-Flags & public & bool & \{ get; private set; \} & Gets a value indicating whether this instance describes a flags enumeration. \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Standard\-Enum\-User\-Data\-Descriptor & public & (Type enum\-Type, string friendly\-Name = null,
			string[] names = null, object[] values = null, Type underlying\-Type = null) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Fill\-Member\-List & private & void & (string[] names, object[] values) & Fills the member list. \\
Add\-Enum\-Method & private & void & (string name, Dyn\-Value dyn\-Value) & Adds an enum method to the object \\
Get\-Value\-Signed & private & long & (Dyn\-Value dv) & Gets the value of the enum as a long \\
Get\-Value\-Unsigned & private & ulong & (Dyn\-Value dv) & Gets the value of the enum as a ulong \\
Create\-Value\-Signed & private & Dyn\-Value & (long value) & Creates an enum value from a long \\
Create\-Value\-Unsigned & private & Dyn\-Value & (ulong value) & Creates an enum value from a ulong \\
Create\-Signed\-Conversion\-Functions & private & void & () & Creates conversion functions for signed enums \\
Create\-Unsigned\-Conversion\-Functions & private & void & () & Creates conversion functions for unsigned enums \\
Is\-Type\-Compatible & public override & bool & (Type type, object obj) & Determines whether the specified object is compatible with the specified type. \\
Meta\-Index & public override & Dyn\-Value & (Script script, object obj, string metaname) & Gets a "meta" operation on this userdata. 
		 In this specific case, only the concat operator is supported, only on flags enums and it implements the
		 'or' operator. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{StandardGenericsUserDataDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Access\-Mode & public & Interop\-Access\-Mode & \{ get; private set; \} & Gets the interop access mode this descriptor uses for members access \\
Name & public & string & \{ get; private set; \} &  \\
Type & public & Type & \{ get; private set; \} &  \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Standard\-Generics\-User\-Data\-Descriptor & public & (Type type, Interop\-Access\-Mode access\-Mode) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Index & public & Dyn\-Value & (Script script, object obj, Dyn\-Value index, bool is\-Direct\-Indexing) &  \\
Set\-Index & public & bool & (Script script, object obj, Dyn\-Value index, Dyn\-Value value, bool is\-Direct\-Indexing) &  \\
As\-String & public & string & (object obj) &  \\
Meta\-Index & public & Dyn\-Value & (Script script, object obj, string metaname) &  \\
Is\-Type\-Compatible & public & bool & (Type type, object obj) &  \\
Generate & public & IUser\-Data\-Descriptor & (Type type) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{StandardUserDataDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Access\-Mode & public & Interop\-Access\-Mode & \{ get; private set; \} & Gets the interop access mode this descriptor uses for members access \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Standard\-User\-Data\-Descriptor & public & (Type type, Interop\-Access\-Mode access\-Mode, string friendly\-Name = null) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Fill\-Member\-List & private & void & () & Fills the member list. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ExtensionMethodsRegistry}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Register\-Extension\-Type & public static & void & (Type type, Interop\-Access\-Mode mode = Interop\-Access\-Mode.Default) & Registers an extension Type (that is a type containing extension methods) \\
Get\-Extension\-Methods\-By\-Name & public static & IEnumerable{\tt <}\-IOverloadable\-Member\-Descriptor\-{\tt >} & (string name) & Gets all the extension methods which can match a given name \\
Get\-Extension\-Methods\-Change\-Version & public static & int & () & Gets a number which gets incremented everytime the extension methods registry changes.
		 Use this to invalidate caches based on extension methods \\
Get\-Extension\-Methods\-By\-Name\-And\-Type & public static & List{\tt <}\-IOverloadable\-Member\-Descriptor\-{\tt >} & (string name, Type extended\-Type) & Gets all the extension methods which can match a given name and extending a given Type \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{TypeDescriptorRegistry}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Default\-Access\-Mode & internal static & Interop\-Access\-Mode & \{ get set \} & Gets or sets the default access mode to be used in the whole application \\
Registered\-Types & public static & IEnumerable{\tt <}\-Key\-Value\-Pair{\tt <}\-Type, IUser\-Data\-Descriptor\-{\tt >}\-{\tt >} & \{ get \} & Gets the list of registered types. \\
Registered\-Types\-History & public static & IEnumerable{\tt <}\-Key\-Value\-Pair{\tt <}\-Type, IUser\-Data\-Descriptor\-{\tt >}\-{\tt >} & \{ get \} & Gets the list of registered types, including unregistered types. \\
Registration\-Policy & internal static & IRegistration\-Policy & \{ get; set; \} & Gets or sets the registration policy. \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Register\-Assembly & internal static & void & (Assembly asm = null, bool include\-Extension\-Types = false) & Registers all types marked with a Moon\-Sharp\-User\-Data\-Attribute that ar contained in an assembly. \\
Is\-Type\-Registered & internal static & bool & (Type type) & Determines whether the specified type is registered. Note that this should be used only to check if a descriptor
		 has been registered EXACTLY. For many types a descriptor can still be created, for example through the descriptor
		 of a base type or implemented interfaces. \\
Unregister\-Type & internal static & void & (Type t) & Unregisters a type.
		 WARNING: unregistering types at runtime is a dangerous practice and may cause unwanted errors.
		 Use this only for testing purposes or to re-register the same type in a slightly different way.
		 Additionally, it's a good practice to discard all previous loaded scripts after calling this method. \\
Register\-Proxy\-Type\_Impl & internal static & IUser\-Data\-Descriptor & (IProxy\-Factory proxy\-Factory, Interop\-Access\-Mode access\-Mode, string friendly\-Name) & Registers a proxy type. \\
Register\-Type\_Impl & internal static & IUser\-Data\-Descriptor & (Type type, Interop\-Access\-Mode access\-Mode, string friendly\-Name, IUser\-Data\-Descriptor descriptor) & Registers a type \\
Resolve\-Default\-Access\-Mode\-For\-Type & internal static & Interop\-Access\-Mode & (Interop\-Access\-Mode access\-Mode, Type type) & Resolves the default type of the access mode for the given type \\
Get\-Descriptor\-For\-Type & internal static & IUser\-Data\-Descriptor & (Type type, bool search\-Interfaces) & Gets the best possible type descriptor for a specified CLR type. \\
Is\-Type\-Blacklisted & public static & bool & (Type t) & Determines whether the specified type is blacklisted.
		 Blacklisted types CANNOT be registered using default descriptors but they can still be registered
		 with custom descriptors. Forcing registration of blacklisted types in this way can introduce
		 side effects. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{JsonTableConverter}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Table\-To\-Json & public static & string & (this Table table) & Converts a table to a json string \\
Table\-To\-Json & private static & void & (String\-Builder sb, Table table) & Tables to json. \\
Object\-To\-Json & public static & string & (object obj) & Converts a generic object to JSON \\
Json\-To\-Table & public static & Table & (string json, Script script = null) & Converts a json string to a table \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{BinaryOperatorExpression}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Create\-Sub\-Tree & private static & Expression & (Linked\-List list, Script\-Loading\-Context lcontext) & Creates a sub tree of binary expressions \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pb_ForceSceneRefresh}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Force\-Refresh & private static & void & (bool interactive) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pb_RebuildMeshes}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Strip\-And\-Pro\-Builderize & private static & void & (pb\_Object[] targets, bool interactive = true) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pb_RebuildSharedIndices}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Rebuild\-Shared\-Indices & private static & void & (pb\_Object[] targets, bool interactive = true) &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{pb_ResetEntityMaterials}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Repair\-Entity\-Materials & private static & void & () &  \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MenuManager}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Register\-Menu & public & void & (Menu\-State menu) & Adds the param menu to Menu\-Manager's list of menus \\
Remove\-Menu & public & void & (Menu\-State menu) & Removes the param menu from Menu\-Manager's list of menus \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ObsoleteSymbolsController}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add\-Symbols\-Bar & private & void & (Symbols\-Controller symbols) & Creates a symbol bar and assigns it to the passed in Symbols object. \\
Remove\-Symbols\-Bar & private & void & (Symbols\-Controller symbols) & Removes and destroys the symbol bar associated with the passed in Symbols object, if one exists. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SceneOverlayManager}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Create & public & void & (string bar\-Name, Bar\-Controller controller) & Creates a Bar\-UI and assigns it to the passed in Bar\-Controller object, then adds both to the Config. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SymbolsController}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Change\-Symbol & public & void & (Image image) & Changes symbol to the passed in image. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SymbolsOverlay}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Add\-To\-Symbol\-Config & public & void & (string symbol\-Name, Symbols\-Controller controller) & Creates a Symbols\-UI and assigns it to the passed in Symbols\-Controller object, then adds both to the Config. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{GenericPriorityQueue}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Count & public & int & \{ get \} & Returns the number of nodes in the queue.
         O(1) \\
Max\-Size & public & int & \{ get \} & Returns the maximum number of items that can be enqueued at once in this queue.  Once you hit this number (ie. once Count == Max\-Size),
         attempting to enqueue another item will cause undefined behavior.  O(1) \\
First & public & TItem & \{ get \#endif return \_nodes[1]; \} \} & Returns the head of the queue, without removing it (use Dequeue() for that).
         If the queue is empty, behavior is undefined.
         O(1) \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Generic\-Priority\-Queue & public & (int max\-Nodes) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
Generic\-Priority\-Queue & public & (int max\-Nodes, IComparer{\tt <}\-TPriority\-{\tt >} comparer) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
Generic\-Priority\-Queue & public & (int max\-Nodes, Comparison{\tt <}\-TPriority\-{\tt >} comparer) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Clear & public & void & () & Removes every node from the queue.
         O(n) (So, don't do this often!) \\
Contains & public & bool & (TItem node) & Returns (in O(1)!) whether the given node is in the queue.
         If node is or has been previously added to another queue, the result is undefined unless old\-Queue.Reset\-Node(node) has been called
         O(1) \\
Enqueue & public & void & (TItem node, TPriority priority) & Enqueue a node to the priority queue.  Lower values are placed in front. Ties are broken by first-in-first-out.
         If the queue is full, the result is undefined.
         If the node is already enqueued, the result is undefined.
         If node is or has been previously added to another queue, the result is undefined unless old\-Queue.Reset\-Node(node) has been called
         O(log n) \\
Has\-Higher\-Priority & private & bool & (TItem higher, TItem lower) & Returns true if 'higher' has higher priority than 'lower', false otherwise.
         Note that calling Has\-Higher\-Priority(node, node) (ie. both arguments the same node) will return false \\
Dequeue & public & TItem & () & Removes the head of the queue (node with minimum priority; ties are broken by order of insertion), and returns it.
         If queue is empty, result is undefined
         O(log n) \\
Resize & public & void & (int max\-Nodes) & Resize the queue so it can accept more nodes.  All currently enqueued nodes are remain.
         Attempting to decrease the queue size to a size too small to hold the existing nodes results in undefined behavior
         O(n) \\
Update\-Priority & public & void & (TItem node, TPriority priority) & This method must be called on a node every time its priority changes while it is in the queue.  
         Forgetting to call this method will result in a corrupted queue!
         Calling this method on a node not in the queue results in undefined behavior
         O(log n) \\
Remove & public & void & (TItem node) & Removes a node from the queue.  The node does not need to be the head of the queue.  
         If the node is not in the queue, the result is undefined.  If unsure, check Contains() first
         O(log n) \\
Reset\-Node & public & void & (TItem node) & By default, nodes that have been previously added to one queue cannot be added to another queue.
         If you need to do this, please call original\-Queue.Reset\-Node(node) before attempting to add it in the new queue \\
Is\-Valid\-Queue & public & bool & () & Should not be called in production code.
         Checks to make sure the queue is still in a valid state.  Used for testing/debugging the queue. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{GenericPriorityQueueNode}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Priority & public & TPriority & \{ get; protected internal set; \} & The Priority to insert this node at.  Must be set BEFORE adding a node to the queue (ideally just once, in the node's constructor).
         Should not be manually edited once the node has been enqueued - use queue.Update\-Priority() instead \\
Queue\-Index & public & int & \{ get; internal set; \} & Represents the current position in the queue \\
Insertion\-Index & public & long & \{ get; internal set; \} & Represents the order the node was inserted in \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{SimplePriorityQueue}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Count & public & int & \{ get \} \} & Returns the number of nodes in the queue.
         O(1) \\
First & public & TItem & \{ get return \_queue.First.Data; \} \} \} & Returns the head of the queue, without removing it (use Dequeue() for that).
         Throws an exception when the queue is empty.
         O(1) \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Simple\-Priority\-Queue & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
Simple\-Priority\-Queue & public & (IComparer{\tt <}\-TPriority\-{\tt >} priority\-Comparer) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
Simple\-Priority\-Queue & public & (Comparison{\tt <}\-TPriority\-{\tt >} priority\-Comparer) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
Simple\-Priority\-Queue & public & (IEquality\-Comparer{\tt <}\-TItem\-{\tt >} item\-Equality) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
Simple\-Priority\-Queue & public & (IComparer{\tt <}\-TPriority\-{\tt >} priority\-Comparer, IEquality\-Comparer{\tt <}\-TItem\-{\tt >} item\-Equality) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
Simple\-Priority\-Queue & public & (Comparison{\tt <}\-TPriority\-{\tt >} priority\-Comparer, IEquality\-Comparer{\tt <}\-TItem\-{\tt >} item\-Equality) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
Simple\-Priority\-Queue & public & () & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
Simple\-Priority\-Queue & public & (IComparer{\tt <}\-float\-{\tt >} comparer) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
Simple\-Priority\-Queue & public & (Comparison{\tt <}\-float\-{\tt >} comparer) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Instantiate a new Priority Queue} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Existing\-Node & private & Simple\-Node & (TItem item) & Given an item of type T, returns the existing Simple\-Node in the queue \\
Add\-To\-Node\-Cache & private & void & (Simple\-Node node) & Adds an item to the Node-cache to allow for many methods to be O(1) or O(log n) \\
Remove\-From\-Node\-Cache & private & void & (Simple\-Node node) & Removes an item to the Node-cache to allow for many methods to be O(1) or O(log n) (assuming no duplicates) \\
Clear & public & void & () & Removes every node from the queue.
         O(n) \\
Contains & public & bool & (TItem item) & Returns whether the given item is in the queue.
         O(1) \\
Dequeue & public & TItem & () & Removes the head of the queue (node with minimum priority; ties are broken by order of insertion), and returns it.
         If queue is empty, throws an exception
         O(log n) \\
Enqueue\-No\-Lock\-Or\-Cache & private & Simple\-Node & (TItem item, TPriority priority) & Enqueue the item with the given priority, without calling lock(\_queue) or Add\-To\-Node\-Cache(node) \\
Enqueue & public & void & (TItem item, TPriority priority) & Enqueue a node to the priority queue.  Lower values are placed in front. Ties are broken by first-in-first-out.
         This queue automatically resizes itself, so there's no concern of the queue becoming 'full'.
         Duplicates and null-values are allowed.
         O(log n) \\
Enqueue\-Without\-Duplicates & public & bool & (TItem item, TPriority priority) & Enqueue a node to the priority queue if it doesn't already exist.  Lower values are placed in front. Ties are broken by first-in-first-out.
         This queue automatically resizes itself, so there's no concern of the queue becoming 'full'.  Null values are allowed.
         Returns true if the node was successfully enqueued; false if it already exists.
         O(log n) \\
Remove & public & void & (TItem item) & Removes an item from the queue.  The item does not need to be the head of the queue.  
         If the item is not in the queue, an exception is thrown.  If unsure, check Contains() first.
         If multiple copies of the item are enqueued, only the first one is removed. 
         O(log n) \\
Update\-Priority & public & void & (TItem item, TPriority priority) & Call this method to change the priority of an item.
         Calling this method on a item not in the queue will throw an exception.
         If the item is enqueued multiple times, only the first one will be updated.
         (If your requirements are complex enough that you need to enqueue the same item multiple times and be able
         to update all of them, please wrap your items in a wrapper class so they can be distinguished).
         O(log n) \\
Get\-Priority & public & TPriority & (TItem item) & Returns the priority of the given item.
         Calling this method on a item not in the queue will throw an exception.
         If the item is enqueued multiple times, only the priority of the first will be returned.
         (If your requirements are complex enough that you need to enqueue the same item multiple times and be able
         to query all their priorities, please wrap your items in a wrapper class so they can be distinguished).
         O(1) \\
Try\-First & public & bool & (out TItem first) &  \\
Try\-Dequeue & public & bool & (out TItem first) & Removes the head of the queue (node with minimum priority; ties are broken by order of insertion), and sets it to first.
         Useful for multi-threading, where the queue may become empty between calls to Contains() and Dequeue()
         Returns true if successful; false if queue was empty
         O(log n) \\
Try\-Remove & public & bool & (TItem item) & Attempts to remove an item from the queue.  The item does not need to be the head of the queue.  
         Useful for multi-threading, where the queue may become empty between calls to Contains() and Remove()
         Returns true if the item was successfully removed, false if it wasn't in the queue.
         If multiple copies of the item are enqueued, only the first one is removed. 
         O(log n) \\
Try\-Update\-Priority & public & bool & (TItem item, TPriority priority) & Call this method to change the priority of an item.
         Useful for multi-threading, where the queue may become empty between calls to Contains() and Update\-Priority()
         If the item is enqueued multiple times, only the first one will be updated.
         (If your requirements are complex enough that you need to enqueue the same item multiple times and be able
         to update all of them, please wrap your items in a wrapper class so they can be distinguished).
         Returns true if the item priority was updated, false otherwise.
         O(log n) \\
Try\-Get\-Priority & public & bool & (TItem item, out TPriority priority) & Attempt to get the priority of the given item.
         Useful for multi-threading, where the queue may become empty between calls to Contains() and Get\-Priority()
         If the item is enqueued multiple times, only the priority of the first will be returned.
         (If your requirements are complex enough that you need to enqueue the same item multiple times and be able
         to query all their priorities, please wrap your items in a wrapper class so they can be distinguished).
         Returns true if the item was found in the queue, false otherwise
         O(1) \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{EntityTooLargeException}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Entity\-Too\-Large\-Exception & public & (string message) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Http header too large to fit in buffer} \\ \tabuphantomline
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WebSocketFrameCommon}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Toggle\-Mask & public static & void & (Array\-Segment{\tt <}\-byte\-{\tt >} mask\-Key, Array\-Segment{\tt <}\-byte\-{\tt >} payload) & Mutate payload with the mask key
         This is a reversible process
         If you apply this to masked data it will be unmasked and visa versa \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WebSocketFrameReader}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Read\-Async & public static async & Task{\tt <}\-Web\-Socket\-Frame\-{\tt >} & (Stream from\-Stream, Array\-Segment{\tt <}\-byte\-{\tt >} into\-Buffer, Cancellation\-Token cancellation\-Token) & Read a Web\-Socket frame from the stream \\
Decode\-Close\-Frame & static & Web\-Socket\-Frame & (bool is\-Fin\-Bit\-Set, Web\-Socket\-Op\-Code op\-Code, int count, Array\-Segment{\tt <}\-byte\-{\tt >} buffer) & Extracts close status and close description information from the web socket frame \\
Read\-Length & static async & Task{\tt <}\-uint\-{\tt >} & (byte byte2, Array\-Segment{\tt <}\-byte\-{\tt >} small\-Buffer, Stream from\-Stream, Cancellation\-Token cancellation\-Token) & Reads the length of the payload according to the contents of byte2 \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WebSocketFrameWriter}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
\_random & static readonly & Random & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{This is used for data masking so that web proxies don't cache the data
         Therefore, there are no cryptographic concerns} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Write & public static & void & (Web\-Socket\-Op\-Code op\-Code, Array\-Segment{\tt <}\-byte\-{\tt >} from\-Payload, Memory\-Stream to\-Stream, bool is\-Last\-Frame, bool is\-Client) & No async await stuff here because we are dealing with a memory stream \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{WebSocketImplementation}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Receive\-Async & public override async & Task{\tt <}\-Web\-Socket\-Receive\-Result\-{\tt >} & (Array\-Segment{\tt <}\-byte\-{\tt >} buffer, Cancellation\-Token cancellation\-Token) & Receive web socket result \\
Send\-Async & public override async & Task & (Array\-Segment{\tt <}\-byte\-{\tt >} buffer, Web\-Socket\-Message\-Type message\-Type, bool end\-Of\-Message, Cancellation\-Token cancellation\-Token) & Send data to the web socket \\
Send\-Ping\-Async & public async & Task & (Array\-Segment{\tt <}\-byte\-{\tt >} payload, Cancellation\-Token cancellation\-Token) & Call this automatically from server side each keep\-Alive\-Interval period
         NOTE: ping payload must be 125 bytes or less \\
Abort & public override & void & () & Aborts the Web\-Socket without sending a Close frame \\
Close\-Async & public override async & Task & (Web\-Socket\-Close\-Status close\-Status, string status\-Description, Cancellation\-Token cancellation\-Token) & Polite close (use the close handshake) \\
Close\-Output\-Async & public override async & Task & (Web\-Socket\-Close\-Status close\-Status, string status\-Description, Cancellation\-Token cancellation\-Token) & Fire and forget close \\
Dispose & public override & void & () & Dispose will send a close frame if the connection is still open \\
On\-Pong & protected virtual & void & (Pong\-Event\-Args e) & Called when a Pong frame is received \\
Build\-Close\-Payload &  & Array\-Segment{\tt <}\-byte\-{\tt >} & (Web\-Socket\-Close\-Status close\-Status, string status\-Description) & As per the spec, write the close status followed by the close reason \\
Send\-Pong\-Async & async & Task & (Array\-Segment{\tt <}\-byte\-{\tt >} payload, Cancellation\-Token cancellation\-Token) &  \\
Respond\-To\-Close\-Frame & async & Task{\tt <}\-Web\-Socket\-Receive\-Result\-{\tt >} & (Web\-Socket\-Frame frame, Array\-Segment{\tt <}\-byte\-{\tt >} buffer, Cancellation\-Token token) & Called when a Close frame is received
         Send a response close frame if applicable \\
Get\-Buffer &  & Array\-Segment{\tt <}\-byte\-{\tt >} & (Memory\-Stream stream) & Note that the way in which the stream buffer is accessed can lead to significant performance problems
         You want to avoid a call to stream.To\-Array to avoid extra memory allocation
         Memory\-Stream can be configured to have its internal buffer accessible. \\
Write\-Stream\-To\-Network & async & Task & (Memory\-Stream stream, Cancellation\-Token cancellation\-Token) & Puts data on the wire \\
Get\-Opp\-Code &  & Web\-Socket\-Op\-Code & (Web\-Socket\-Message\-Type message\-Type) & Turns a spec websocket frame opcode into a Web\-Socket\-Message\-Type \\
Close\-Output\-Auto\-Timeout\-Async & async & Task & (Web\-Socket\-Close\-Status close\-Status, string status\-Description, Exception ex) & Automatic Web\-Socket close in response to some invalid data from the remote websocket host \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ArrayMemberDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Array\-Member\-Descriptor & public & (string name, bool is\-Setter, Parameter\-Descriptor[] indexer\-Params) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Array\-Member\-Descriptor & public & (string name, bool is\-Setter) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Prepare\-For\-Wiring & public & void & (Table t) & Prepares the descriptor for hard-wiring.
		 The descriptor fills the passed table with all the needed data for hardwire generators to generate the appropriate code. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{DynValueMemberDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Is\-Static & public & bool & \{ get \} & Gets a value indicating whether the described member is static. \\
Name & public & string & \{ get; private set; \} & Gets the name of the member \\
Member\-Access & public & Member\-Descriptor\-Access & \{ get; private set; \} & Gets the types of access supported by this member \\
Value & public virtual & Dyn\-Value & \{ get \} & Gets the value wrapped by this descriptor \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Dyn\-Value\-Member\-Descriptor & protected & (string name, string serialized\-Table\-Value) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Dyn\-Value\-Member\-Descriptor & protected & (string name) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Dyn\-Value\-Member\-Descriptor & public & (string name, Dyn\-Value value) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Get\-Value & public & Dyn\-Value & (Script script, object obj) & Gets the value of this member as a  to be exposed to scripts. \\
Set\-Value & public & void & (Script script, object obj, Dyn\-Value value) & Sets the value of this member from a . \\
Prepare\-For\-Wiring & public & void & (Table t) & Prepares the descriptor for hard-wiring.
		 The descriptor fills the passed table with all the needed data for hardwire generators to generate the appropriate code. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{FunctionMemberDescriptorBase}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Is\-Static & public & bool & \{ get; private set; \} & Gets a value indicating whether the described method is static. \\
Name & public & string & \{ get; private set; \} & Gets the name of the described method \\
Sort\-Discriminant & public & string & \{ get; private set; \} & Gets a sort discriminant to give consistent overload resolution matching in case of perfectly equal scores \\
Parameters & public & Parameter\-Descriptor[] & \{ get; private set; \} & Gets the type of the arguments of the underlying CLR function \\
Extension\-Method\-Type & public & Type & \{ get; private set; \} & Gets the type which this extension method extends, null if this is not an extension method. \\
Var\-Args\-Array\-Type & public & Type & \{ get; private set; \} & Gets a value indicating the type of the Param\-Array parameter of a var-args function. If the function is not var-args,
		 null is returned. \\
Var\-Args\-Element\-Type & public & Type & \{ get; private set; \} & Gets a value indicating the type of the elements of the Param\-Array parameter of a var-args function. If the function is not var-args,
		 null is returned. \\
Member\-Access & public & Member\-Descriptor\-Access & \{ get \} & Gets the types of access supported by this member \\
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Initialize & protected & void & (string func\-Name, bool is\-Static, Parameter\-Descriptor[] parameters, bool is\-Extension\-Method) & Initializes this instance.
		 This *MUST* be called by the constructors extending this class to complete initialization. \\
Get\-Callback & public & Func{\tt <}\-Script\-Execution\-Context, Callback\-Arguments, Dyn\-Value\-{\tt >} & (Script script, object obj = null) & Gets a callback function as a delegate \\
Get\-Callback\-Function & public & Callback\-Function & (Script script, object obj = null) & Gets the callback function. \\
Get\-Callback\-As\-Dyn\-Value & public & Dyn\-Value & (Script script, object obj = null) & Gets the callback function as a Dyn\-Value. \\
Create\-Callback\-Dyn\-Value & public static & Dyn\-Value & (Script script, Method\-Info mi, object obj = null) & Creates a callback Dyn\-Value starting from a Method\-Info. \\
Build\-Argument\-List & protected virtual & object[] & (Script script, object obj, Script\-Execution\-Context context, Callback\-Arguments args,
			out List{\tt <}\-int\-{\tt >} out\-Params) & Builds the argument list. \\
Build\-Return\-Value & protected static & Dyn\-Value & (Script script, List{\tt <}\-int\-{\tt >} out\-Params, object[] pars, object retv) & Builds the return value of a call \\
Execute & public abstract & Dyn\-Value & (Script script, object obj, Script\-Execution\-Context context, Callback\-Arguments args) & The internal callback which actually executes the method \\
Get\-Value & public virtual & Dyn\-Value & (Script script, object obj) & Gets the value of this member as a  to be exposed to scripts. \\
Set\-Value & public virtual & void & (Script script, object obj, Dyn\-Value v) & Sets the value. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ObjectCallbackMemberDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Object\-Callback\-Member\-Descriptor & public & (string func\-Name) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.
		 A new member descriptor is defined, which is a function taking no parameters and returning void, doing nothing.} \\ \tabuphantomline
Object\-Callback\-Member\-Descriptor & public & (string func\-Name, Func{\tt <}\-object, Script\-Execution\-Context, Callback\-Arguments, object\-{\tt >} call\-Back) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.
		 The function described by descriptors created by this callback are defined as if they take no parameters
		 and thus don't support overload resolution well (unless they really take no parameters) but can freely be
		 used if no overload resolution is required.} \\ \tabuphantomline
Object\-Callback\-Member\-Descriptor & public & (string func\-Name, Func{\tt <}\-object, Script\-Execution\-Context, Callback\-Arguments, object\-{\tt >} call\-Back, Parameter\-Descriptor[] parameters) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.
		 Members defined with this constructor will support overload resolution.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Execute & public override & Dyn\-Value & (Script script, object obj, Script\-Execution\-Context context, Callback\-Arguments args) & The internal callback which actually executes the method \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{EventMemberDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtFields} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
MAX\_ARGS\_IN\_DELEGATE & public const & int & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{The maximum number of arguments supported in an event handler delegate} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Event\-Info & public & Event\-Info & \{ get; private set; \} & Gets the Event\-Info object of the event described by this descriptor \\
Is\-Static & public & bool & \{ get; private set; \} & Gets a value indicating whether the event described by this descriptor is static. \\
Name & public & string & \{ get \} & Gets the name of the member \\
Member\-Access & public & Member\-Descriptor\-Access & \{ get \} & Gets the types of access supported by this member \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Event\-Member\-Descriptor & public & (Event\-Info ei, Interop\-Access\-Mode access\-Mode = Interop\-Access\-Mode.Default) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Try\-Create\-If\-Visible & public static & Event\-Member\-Descriptor & (Event\-Info ei, Interop\-Access\-Mode access\-Mode) & Tries to create a new Standard\-User\-Data\-Event\-Descriptor, returning null in case the method is not 
		 visible to script code. \\
Check\-Event\-Is\-Compatible & public static & bool & (Event\-Info ei, bool throw\-Exception) & Checks if the event is compatible with a standard descriptor \\
Get\-Value & public & Dyn\-Value & (Script script, object obj) & Gets a dynvalue which is a facade supporting add/remove methods which is callable from scripts \\
Set\-Value & public & void & (Script script, object obj, Dyn\-Value v) & Sets the value. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{FieldMemberDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Field\-Info & public & Field\-Info & \{ get; private set; \} & Gets the Field\-Info got by reflection \\
Access\-Mode & public & Interop\-Access\-Mode & \{ get; private set; \} & Gets the \\
Is\-Static & public & bool & \{ get; private set; \} & Gets a value indicating whether the described property is static. \\
Name & public & string & \{ get; private set; \} & Gets the name of the property \\
Is\-Const & public & bool & \{ get; private set; \} & Gets a value indicating whether this instance is a constant \\
Is\-Readonly & public & bool & \{ get; private set; \} & Gets a value indicating whether this instance is readonly \\
Member\-Access & public & Member\-Descriptor\-Access & \{ get \} & Gets the types of access supported by this member \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Field\-Member\-Descriptor & public & (Field\-Info fi, Interop\-Access\-Mode access\-Mode) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Try\-Create\-If\-Visible & public static & Field\-Member\-Descriptor & (Field\-Info fi, Interop\-Access\-Mode access\-Mode) & Tries to create a new Standard\-User\-Data\-Field\-Descriptor, returning null in case the field is not 
		 visible to script code. \\
Get\-Value & public & Dyn\-Value & (Script script, object obj) & Gets the value of the property \\
Set\-Value & public & void & (Script script, object obj, Dyn\-Value v) & Sets the value of the property \\
Prepare\-For\-Wiring & public & void & (Table t) & Prepares the descriptor for hard-wiring.
		 The descriptor fills the passed table with all the needed data for hardwire generators to generate the appropriate code. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MethodMemberDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Method\-Info & public & Method\-Base & \{ get; private set; \} & Gets the method information (can be a Method\-Info or Constructor\-Info) \\
Access\-Mode & public & Interop\-Access\-Mode & \{ get; private set; \} & Gets the access mode used for interop \\
Is\-Constructor & public & bool & \{ get; private set; \} & Gets a value indicating whether the described method is a constructor \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Method\-Member\-Descriptor & public & (Method\-Base method\-Base, Interop\-Access\-Mode access\-Mode = Interop\-Access\-Mode.Default) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Try\-Create\-If\-Visible & public static & Method\-Member\-Descriptor & (Method\-Base method\-Base, Interop\-Access\-Mode access\-Mode, bool force\-Visibility = false) & Tries to create a new Method\-Member\-Descriptor, returning 
		 null in case the method is not
		 visible to script code. \\
Check\-Method\-Is\-Compatible & public static & bool & (Method\-Base method\-Base, bool throw\-Exception) & Checks if the method is compatible with a standard descriptor \\
Execute & public override & Dyn\-Value & (Script script, object obj, Script\-Execution\-Context context, Callback\-Arguments args) & The internal callback which actually executes the method \\
Optimize &  & void & () & Called by standard descriptors when background optimization or preoptimization needs to be performed. \\
Prepare\-For\-Wiring & public & void & (Table t) & Prepares the descriptor for hard-wiring.
		 The descriptor fills the passed table with all the needed data for hardwire generators to generate the appropriate code. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{OverloadedMethodMemberDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Ignore\-Extension\-Methods & public & bool & \{ get; set; \} & Gets or sets a value indicating whether this instance ignores extension methods. \\
Name & public & string & \{ get; private set; \} & Gets the name of the first described overload \\
Declaring\-Type & public & Type & \{ get; private set; \} & Gets the name of the first described overload \\
Overload\-Count & public & int & \{ get \} & Gets the number of overloaded methods contained in this collection \\
Is\-Static & public & bool & \{ get \} & Gets a value indicating whether there is at least one static method in the resolution list \\
Member\-Access & public & Member\-Descriptor\-Access & \{ get \} & Gets the types of access supported by this member \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Overloaded\-Method\-Member\-Descriptor & public & (string name, Type declaring\-Type) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Overloaded\-Method\-Member\-Descriptor & public & (string name, Type declaring\-Type, IOverloadable\-Member\-Descriptor descriptor) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
Overloaded\-Method\-Member\-Descriptor & public & (string name, Type declaring\-Type, IEnumerable{\tt <}\-IOverloadable\-Member\-Descriptor\-{\tt >} descriptors) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Set\-Extension\-Methods\-Snapshot & internal & void & (int version, List{\tt <}\-IOverloadable\-Member\-Descriptor\-{\tt >} ext\-Methods) & Sets the extension methods snapshot. \\
Add\-Overload & public & void & (IOverloadable\-Member\-Descriptor overload) & Adds an overload. \\
Perform\-Overloaded\-Call & private & Dyn\-Value & (Script script, object obj, Script\-Execution\-Context context, Callback\-Arguments args) & Performs the overloaded call. \\
Calc\-Score\-For\-Overload & private & int & (Script\-Execution\-Context context, Callback\-Arguments args, IOverloadable\-Member\-Descriptor method, bool is\-Ext\-Method) & Calculates the score for the overload. \\
Get\-Callback & public & Func{\tt <}\-Script\-Execution\-Context, Callback\-Arguments, Dyn\-Value\-{\tt >} & (Script script, object obj) & Gets a callback function as a delegate \\
Get\-Callback\-Function & public & Callback\-Function & (Script script, object obj = null) & Gets the callback function. \\
Get\-Value & public & Dyn\-Value & (Script script, object obj) & Gets the value of this member as a  to be exposed to scripts. \\
Set\-Value & public & void & (Script script, object obj, Dyn\-Value value) & Sets the value of this member from a . \\
Prepare\-For\-Wiring & public & void & (Table t) & Prepares the descriptor for hard-wiring.
		 The descriptor fills the passed table with all the needed data for hardwire generators to generate the appropriate code. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{PropertyMemberDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Property\-Info & public & Property\-Info & \{ get; private set; \} & Gets the Property\-Info got by reflection \\
Access\-Mode & public & Interop\-Access\-Mode & \{ get; private set; \} & Gets the \\
Is\-Static & public & bool & \{ get; private set; \} & Gets a value indicating whether the described property is static. \\
Name & public & string & \{ get; private set; \} & Gets the name of the property \\
Can\-Read & public & bool & \{ get \} & Gets a value indicating whether this instance can be read from \\
Can\-Write & public & bool & \{ get \} & Gets a value indicating whether this instance can be written to. \\
Member\-Access & public & Member\-Descriptor\-Access & \{ get \} & Gets the types of access supported by this member \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Property\-Member\-Descriptor & public & (Property\-Info pi, Interop\-Access\-Mode access\-Mode) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.
		 NOTE: This constructor gives get/set visibility based exclusively on the CLR visibility of the 
		 getter and setter methods.} \\ \tabuphantomline
Property\-Member\-Descriptor & public & (Property\-Info pi, Interop\-Access\-Mode access\-Mode, Method\-Info getter, Method\-Info setter) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the  class.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Try\-Create\-If\-Visible & public static & Property\-Member\-Descriptor & (Property\-Info pi, Interop\-Access\-Mode access\-Mode) & Tries to create a new Standard\-User\-Data\-Property\-Descriptor, returning null in case the property is not 
		 visible to script code. \\
Get\-Value & public & Dyn\-Value & (Script script, object obj) & Gets the value of the property \\
Set\-Value & public & void & (Script script, object obj, Dyn\-Value v) & Sets the value of the property \\
Optimize &  & void & () & Called by standard descriptors when background optimization or preoptimization needs to be performed. \\
Prepare\-For\-Wiring & public & void & (Table t) & Prepares the descriptor for hard-wiring.
		 The descriptor fills the passed table with all the needed data for hardwire generators to generate the appropriate code. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{ValueTypeDefaultCtorMemberDescriptor}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtProperties} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtType} & \textbf{\xdtAccessors} & \textbf{\xdtDescription} \\
Is\-Static & public & bool & \{ get \} & Gets a value indicating whether the described method is static. \\
Name & public & string & \{ get; private set; \} & Gets the name of the described method \\
Value\-Type\-Default\-Ctor & public & Type & \{ get; private set; \} & This property is equal to the value type to be constructed. \\
Parameters & public & Parameter\-Descriptor[] & \{ get; private set; \} & Gets the type of the arguments of the underlying CLR function \\
Extension\-Method\-Type & public & Type & \{ get \} & Gets the type which this extension method extends, null if this is not an extension method. \\
Var\-Args\-Array\-Type & public & Type & \{ get \} & Gets a value indicating the type of the Param\-Array parameter of a var-args function. If the function is not var-args,
		 null is returned. \\
Var\-Args\-Element\-Type & public & Type & \{ get \} & Gets a value indicating the type of the elements of the Param\-Array parameter of a var-args function. If the function is not var-args,
		 null is returned. \\
Sort\-Discriminant & public & string & \{ get \} & Gets a sort discriminant to give consistent overload resolution matching in case of perfectly equal scores \\
Member\-Access & public & Member\-Descriptor\-Access & \{ get \} & Gets the types of access supported by this member \\
\hiderowcolors \multicolumn{5}{l}{\xdtConstructors} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtParameters} & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{\textbf{\xdtDescription}} \\
Value\-Type\-Default\-Ctor\-Member\-Descriptor & public & (Type value\-Type) & \multicolumn{2}{p{\dimexpr 5\tabucolX+5\tabcolsep+\arrayrulewidth\relax}}{Initializes a new instance of the
		  class
		 representing the default empty ctor for a value type.} \\ \tabuphantomline
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
Execute & public & Dyn\-Value & (Script script, object obj, Script\-Execution\-Context context, Callback\-Arguments args) & Invokes the member from script.
		 Implementors should raise exceptions if the value cannot be executed or if access to an
		 instance member through a static userdata is attempted. \\
Get\-Value & public & Dyn\-Value & (Script script, object obj) & Gets the value of this member as a 
		  to be exposed to scripts.
		 Implementors should raise exceptions if the value cannot be read or if access to an
		 instance member through a static userdata is attempted. \\
Set\-Value & public & void & (Script script, object obj, Dyn\-Value value) & Sets the value of this member from a 
		 .
		 Implementors should raise exceptions if the value cannot be read or if access to an
		 instance member through a static userdata is attempted. \\
Prepare\-For\-Wiring & public & void & (Table t) & Prepares the descriptor for hard-wiring.
		 The descriptor fills the passed table with all the needed data for hardwire generators to generate the appropriate code. \\
\bottomrule
\end{longtabu}

\xdtbeforemembersof{MUtil}

\begin{longtabu} to \textwidth { l | X | X | X[2] | X[3] }
\hiderowcolors \multicolumn{5}{l}{\xdtMethods} \tabularnewline \midrule \showrowcolors
\textbf{\xdtMemberName} & \textbf{\xdtModifiers} & \textbf{\xdtReturnType} & \textbf{\xdtParameters} & \textbf{\xdtDescription} \\
log\-Event & public static & void & (object component, String event\-Name, bool simple = false) &  \\
\bottomrule
\end{longtabu}
% /MEMBERS
% /AUTOGENERATED
